
\section{Artefacts}

Artefacts are items which are more magical in nature\comma{} and generally cannot be synthesised directly\comma{} though they may be recreated through enchanting. Some artefacts are incredibly rare and powerful\comma{} and can be hard to track down. The list below contains only some artefacts which are commonly found in the wizarding world\comma{} and should by no means be thought of as extensive. 
\def\q{4}

 \begin{center}\begin{rndtable}{|p{\q cm} l l |}\hline \bf Name & \bf Weight & \bf Cost \\ \hline 	  
 
 %%ArtefactBegin
\singleRow{{Bludger}{Heavy}{\galleon{5}~}}
\singleRow{{Broomstick (cheap)}{Medium}{\galleon{40}~}}
\singleRow{{Broomstick (fine)}{Medium}{\galleon{500}~}}
\singleRow{{Crystal Ball}{Light}{\galleon{1}~}}
\singleRow{{Darkandles}{Light}{\sickle{4}~}}
\singleRow{{Deluminator}{Light}{\galleon{60}~}}
\singleRow{{Extending Stachel}{Light}{\galleon{100}~}}
\singleRow{{Gobstone (Set of 30)}{Light}{\sickle{5}~}}
\singleRow{{Golden Snitch}{Light}{\galleon{10}~}}
\singleRow{{Howler}{Light}{\sickle{1}~}}
\singleRow{{Invisibility Cloak}{Medium}{\galleon{240}~}}
\singleRow{{Mokeskin Pouch}{Light}{\galleon{1}~}}
\singleRow{{Obsidian Manacles}{Medium}{\galleon{150}~}}
\singleRow{{Omnioculars}{Light}{\sickle{15}~}}
\singleRow{{Pensieve}{Heavy}{\galleon{400}~}}
\singleRow{{Portkey}{(Varies)}{\galleon{16}~}}
\singleRow{{Quick\minus{}Quotes Quill}{Light}{\galleon{1}~\sickle{10}~}}
\singleRow{{Rememberall}{Light}{\galleon{1}~}}
\singleRow{{Self\minus{}Erecting Tent}{Heavy}{\galleon{24}~}}
\singleRow{{Sneakoscope}{Light}{\galleon{1}~}}
\singleRow{{Spellotape}{Light}{\sickle{4}~}}
\singleRow{{Talking Portrait}{Heavy}{\galleon{15}~}}
\singleRow{{Time\minus{}Turner}{Light}{\galleon{100000}~}}
\singleRow{{Wand}{Light}{\galleon{6}~}}
\hline
\end{rndtable}
\end{center} 

 
 \generic{Bludger}{An enchanted iron ball\comma{} weighing approximately 80kg\comma{} and yet able to fly. They possess a malicious streak\comma{} and will target any flying entity within 100m and attempt to smash into them\comma{} before moving onto their next target\comma{}}
 
 \generic{Broomstick (cheap)}{A low\minus{}range broomstick that can get off the ground\comma{} but not much more than that. Capable of carrying one passenger at speeds of up to 100mph\comma{} thought with very clumsy handling at high speeds.}
 
 \generic{Broomstick (fine)}{A high\minus{}end broomstick capable of high\minus{}speed precision flying. Capable of carrying one passenger at speeds of up to 250mph\comma{} with the handling only limited by the pilot\apos{}s rection time.}
 
 \generic{Crystal Ball}{A sphere of perfect crystal – the manufacture of these objects is a carefully curated secret. A properly trained mind can use a crystal ball to peer through the mystic veil and learn about the universe.}
 
 \generic{Darkandles}{The exact opposite of a candle\comma{} a darkandle emits darkness\comma{} rather than light. Within a 5m radius\comma{} there is total darkness\comma{} and within 5m there is only dim light\comma{} regardless of any other light sources nearby.}
 
 \generic{Deluminator}{A device designed by Dumbledore\comma{} the deluminator may be targeted at a specific light\minus{}source\comma{} at which point the light is extinguished\comma{} and absorbed by the deluminator. This light source is permanently disabled until the deluminator restores the light to it.}
 
 \generic{Extending Stachel}{A normal backpack that has been enchanted with the {\it internal extension charm}\comma{} making it several times larger on the inside than the outside. This backpack can hold up to 300L\comma{} and makes the contents 10 times lighter than normal.}
 
 \generic{Gobstone (Set of 30)}{A small set of stones used in the titular game. When knocked by another gobstone\comma{} they eject a squirt of corrosive liquid into the eyes of the target.}
 
 \generic{Golden Snitch}{A small golden\comma{} metal orb which sprouts wings when activated. The snitch then immediately attempts to evade all living beings\comma{} though sometimes it will taunt them by floating in front of their faces\comma{} before quickly vanishing.}
 
 \generic{Howler}{A magical letter that\comma{} when opened by the recipient\comma{} unfolds itself\comma{} floats and begins to scream the enclosed message\comma{} before incinerating itself. If left unopened after being delivered\comma{} it will explode violently.}
 
 \generic{Invisibility Cloak}{A cloak that renders whatever is concealed within it invisible\comma{} though external factors such as sound\comma{} or the presence of rain or snow may still give away the location. The cloak also offers no protection against spells.}
 
 \generic{Mokeskin Pouch}{A small coin pouch that can only be accessed by its owner.}
 
 \generic{Obsidian Manacles}{A magical set of handcuffs which\comma{} when firmly closed around the wrist\comma{} prevent a witch or wizard from casting any magic.}
 
 \generic{Omnioculars}{A pair of high\minus{}resolution binoculars\comma{} capable of pausing\comma{} rewinding and replaying previous events. Omnioculars are capable of 10x magnification\comma{} and a playback up to 3x slower than original of up to 1 hour of recorded footage.}
 
 \generic{Pensieve}{A large stone bowl\comma{} engraved with ancient runes and inlaid with previous stones. A pensieve can be filled with memories\comma{} in the form of a silvery glowing fluid\comma{} which can then be viewed and relived in real time.}
 
 \generic{Portkey}{A one\minus{}use device with a teleportation charm embedded in it. A portkey resembles a random piece of junk\comma{} but when activated (either by touch\comma{} or at a specific time)\comma{} teleports to a preset location.}
 
 \generic{Quick\minus{}Quotes Quill}{A quill which automatically writes down whatever is said within a 2m radius.}
 
 \generic{Rememberall}{A small glass orb filled with grey smoke\comma{} which turns bright scarlet whenever the bearer forgets something. The colour reverts to grey when the target remembers.}
 
 \generic{Self\minus{}Erecting Tent}{Outwardly a three\minus{}man tent\comma{} but due to an extension charm\comma{} its interior is large enough for around 10 adults to live comfortably. It erects and disassembles itself upon hearing a double\minus{}clap.}
 
 \generic{Sneakoscope}{A sneakoscope is a type of dark\minus{}detector that looks like a glass spinning top. It lights up\comma{} spins and whistles whenever someone in a 2m radius is doing something untrustworthy. In practice\comma{} this grants the bearer a +5 bonus to passive perception against `untrustworthy’ actors.}
 
 \generic{Spellotape}{An alternative to the {\it Stick} charm\comma{} when dealing with delicate magical objects\comma{} spellotape is an adhesive material.}
 
 \generic{Talking Portrait}{A portrait of a witch or wizard which is imbued with their personality and (to an extent) their memories\comma{} as interpreted by the artist. These paintings can wander in and out of any nearby paintings\comma{} and also visit other paintings of themselves anywhere in the world.}
 
 \generic{Time\minus{}Turner}{An incredibly powerful item\comma{} that takes the form of an hourglass on a necklace\comma{} a time turner allows one to travel backwards in time one hour for every turn of the hourglass. Attempting to travel back more than 5 hours\comma{} or otherwise interfering with the past can cause irreparable damage to the space\minus{}time continuum.}
 
 \generic{Wand}{The cornerstone of wizarding life\comma{} though magic is possible without a wand\comma{} it is much harder – nearly every witch and wizard possess one. Wands bond to their owner through a complex and unknown process\comma{} so it is vital that you only use your own wand\comma{} or one you have bonded with.}%%ArtefactEnd

\newpage
\section{Packs}

Packs are pre\minus{}arranged sets of equipment. Where a pack leaves the precise nature of an item unclear (i.e. `a book')\comma{} you may choose the exact item within the following bounds:
\begin{itemize}
	\item A book may not cost more than 50gp.
	\item A set of tools may not cost more than 30gp.
\end{itemize}

%%PackBegin

\pack{Basic Pack}{30}{A normal backpack\comma{} some normal clothes\comma{} a small dagger\comma{} a candle\comma{} and a healing potion.}

\pack{Explorer Pack}{30}{A set of adventuring clothes\comma{} a climbing set\comma{} a torch\comma{} a map case (with map)\comma{} 10 days of rations\comma{} a water flask\comma{} a bedroll and a tent.}

\pack{Fighter Pack}{30}{A weapon (your choice)\comma{} a basic set of armour\comma{} and a healing potion.}

\pack{Scholar Pack}{30}{A normal backpack\comma{} some normal clothes\comma{} 2 books\comma{} 10 sheets of paper\comma{} ink and pen\comma{} a magnifying glass and 1 set of tools.}

\pack{Student Pack}{30}{A normal backpack\comma{} 1 book\comma{} a set of potion equipment and a set of student robes.}

\pack{Thief Pack}{30}{A set of (dark) clothes\comma{} lockpicking tools\comma{} a set of ball bearings\comma{} a torch\comma{} and a set of rope.}

%%PackEnd
