\section{Potion Making}


Alchemy is the art of mixing magical and mundane ingredients together into magical potions, concoctions and other wondrous items. In order to perform alchemy, the you must have a set of Alchemy Gear (which includes the all\minus{}important cauldron).

Into the cauldron, you must then add their chosen ingredients, and then leave the potion to brew (preferably over a nice warm fire). You then perform an {\it Alchemy Check}, which is a normal d20 Intelligence check. If you are proficient in the Alchemist's tools, you also add your Expertise bonus to this check. This determines how well you mix the potion. 

There exist a large number of potions recipes in the world, a small sample of which are shown below, with more found on page \pageref{S:PotionList}. Each potion has associated with it a number of essential ingredients, a brewing time, the mixing difficulty and the number of doses that a successful mixing produces. 

If the ingredients you chose match the key ingredients of one of the potions in the list below, and if the potion was left to brew for the correct amount of time, then compare the Alchemy with the stated difficulty of the potion. If it exceeds the difficulty, then the ingredients are consumed, and a number of samples of the potion are produced, equal to the {\it Dose} statistic. 

\subsection{Failed Mixings}

If the first mixing check fails, the GM may elect to ask the alchemist in question to perform the alchemy check again. If the second check also fails, or if the GM decides to omit this optional rule, then the ingredients are consumed, and nothing happens: the fluid in the potion turns into a useless back sludge, or evaporates completely. 

If, however, the second check completes successfully, then the alchemist produces a {\it Flawed batch} of the chosen potion. A flawed batch has the same primary effect as the original potion, but has a {\it Side Effect}, which is presented at the bottom of the entry for each potion in the GM guide, but not in the Player Handbook. Some side effects are applied immediately upon mixing, and others are applied when the potion is used. 

\subsection{Modifying Potions}

The `essential ingredients' of a potion are those that one might find in a textbook. They are the safe, reproducable way to produce the stated effects. However, magic is a fickle thing, and the aspiring Potions Master should know that an extra sprinkle of Eye of Newt here, and a dash of Lemon Juice there can drastically change the effects of a potion.  

After adding the essential ingredients, each potion can then be modified by adding some optional ingredients. These optional ingredients can boost the effectiveness of the potion, in a compounding fashion \minus{} whilst two ingredients might separately increase the effectiveness by 50\%, when both mixed in together, they increase the effectiveness by 125\%.  

Each optional ingredient also has associated with it an additional DV \minus{} making the potion harder to mix. If an incorrect ingredient is added, then it increases the DV by 5, but has no additional effects, unless the GM deems it to be a particularly heinous ingredient (adding {\it Basilisk Venom} to a healing potion, for example). 

The additional ingredients are not listed in the player version of the potion list, as they are (nominally) a secret. They may learn about the additional effects of individual ingredients through research, or through in\minus{}game interactions with herbalists. A trial\minus{}and\minus{}error approach is also not (entirely) frowned upon!

\subsection{Purchasing Potions}

If a player wants to get all the tasty benefits of potion mixing, but doesn't have the skill to pull it off, then they may simply purchase the potions for the price stated in each potion description. All potions purchased on the general marked are the `base\minus{}level' version with no additional ingredients or effects. If characters wish to purchase more powerful potions, these are only available from rare artisan potioneers who make potions to order. The prices of such orders scales with the additional power of the potion. 

\subsection{Sample Recipes}

Listed below are a few sample recipes. The full list is found on page \pageref{S:PotionList}.

~

%%PotionBegin

\potion{name =Pepperup Potion, description =Bright blue gel\comma{} with a strong\comma{} spicy odour., cost =\sickle{7} , effect =Restores FP by 5 points, difficulty =10, time =1 hour, doses =3~doses, essential =Chizpurfle Fang\comma{} Ginger\comma{} Tea Leaf, optional = Dragon Liver & +100\% & 3\\ Honeywater & +25\% & 1\\ Runespoor Egg & +150\% & 5\\ Salamander Blood & +50\% & 2\\ ,othereffect  =Causes smoke to issue from the ears with a loud whistling noise.}
\potion{name =Polyjuice Potion, description =The colour\comma{} scent and taste of this potion reflect the target transformation., cost =\galleon{10} \sickle{15} , effect =Transfigure yourself into another human for 1 hour, difficulty =15, time =1 day, doses =1~dose, essential =Boomslang Skin\comma{} DNA of target\comma{} Fluxweed\comma{} Lacewing Flies, optional = Bicorn Horn & +100\% & 2\\ Knotgrass & +25\% & 1\\ Leeches & +50\% & 1\\ ,othereffect  =The transformation is randomly warped\comma{} and you end up with an ear for a mouth\comma{} and a mouth for an ear (for example).}
\potion{name =Viper\apos{}s Venom, description =A blue liquid with a slight acrid odour., cost =\sickle{9} , effect =Applies the {\it Poisoned: Mild} status effect and immediately deals 5 Poison Damage, difficulty =10, time =2 hours, doses =3~doses, essential =Asp Tail\comma{} Lobalug Venom\comma{} Nightshade, optional = Acromantula Venom & +150\% & 4\\ Basilisk Venom & +150\% & 4\\ Doxy Eggs & +50\% & 1\\ Venemous Tentacula & +75\% & 2\\ ,othereffect  =Triggers immune response so target is Resistant to poison damage for 24 hours.}
\potion{name =Wiggenweld Potion, description =Vibrant red fluid with a pleasant\comma{} herbal aroma., cost =\sickle{7} , effect =Restores HP 5 points, difficulty =10, time =1 hour, doses =3~doses, essential =Dittany\comma{} Horklump Juice\comma{} Wiggentree Bark, optional = Leeches & +75\% & 1\\ Moly & +200\% & 4\\ Murtlap Tentacles & +150\% & 3\\ Nettles & +100\% & 2\\ ,othereffect  =Injuries heal improperly\comma{} leaving the drinker Vulnerable to fire damage.}


%%PotionEnd


