\tool{Climbing Supplies}{Survival}{Pitons\comma{} rope\comma{} crampons\comma{} climbing axes and belaying devices.}{When scaling up and down vertical faces of ice and rock\comma{} you need these supplies in order to ensure that you do not plummet to your death.}
\tool{Clothesmaking Kit}{Craft}{Needle and thread\comma{} patches of material of all different kinds. Buttons\comma{} clasps and other fixtures.}{A requirement for repairing damaged clothing\comma{} or for creating your own.}
\tool{Cooking Set}{Craft}{Pots and pans\comma{} a magical heat source and an extension\minus{}charmed pouch containing all manner of herbs\comma{} spices and seasonings.}{A neat little kit useful for cooking up a delicious meal\comma{} even when out in the wild.}
\tool{Detective’s Toolkit}{Investigation}{Evidence bags\comma{} fingerprint powder (both magical and normal)\comma{} magnifying glass\comma{} and other such devices.}{Immensely useful when it comes to investigating a crime scene and surveying it for clues.}
\tool{First Aid Kit}{First Aid}{Bandages\comma{} painkillers\comma{} antiseptics wipes\comma{} as well as emergency doses of some powerful potions.}{This kit can be used to patch up small wounds. By expending this kit during a \imp{Short Rest}\comma{} you can either allow a being to heal an amout equal to a DV 7 \imp{First Aid} roll\comma{} or remove the \imp{Critical Condition} status\comma{} placing them in \imp{Critical But Stable}.}
\tool{Herbology Tools}{Nature}{Pruning shears\comma{} sample collection pots and vials\comma{} seeds\comma{} and soil fertiliser.}{All the equipment necessary to care for and plant mundane and magical plants\comma{} as well as carefully harvest samples from the more dangerous varieties.}
\tool{Masonry Tools}{Craft}{Chisel\comma{} large hammer\comma{} trowel\comma{} brushes\comma{} as well as a small amount of dry cement mixture.}{Whether you need to build a wall\comma{} or rip one down\comma{} this set of tools can help you. Also can be used for carving statues\comma{} or tunneling through solid rock – though it might take a while.}
\tool{Navigation Tools}{Survival}{A set of maps\comma{} a compass\comma{} dowsing rod\comma{} a minature sextant.}{When out in the wild\comma{} it is necessary to know exactly where you are and where you are going – without a set of Navigation tools\comma{} you are very liable to get lost.}
\tool{Painting Supplies}{Craft}{Brushes\comma{} paints (oil\comma{} watercolour\comma{} even spray\minus{}paints)\comma{} dyes\comma{} paper and a palette.}{Whether it be graffiting rude messages on the walls\comma{} or composing a beautiful landscape\comma{} you need painting supplies before you can get started.}
\tool{Potion Making Set}{Imbue}{A collapsable cauldron\comma{} a small crucible\comma{} retort\comma{} mixing and filtering implements and a number of sample vials.}{A portable set of equipment comprising the bare minimum needed to undertake a potion\minus{}mixing attempt.}
\tool{Runic Tools}{Imbue}{A number scribing chisels of various sizes\comma{} fine lensing equipment for minature work and an imbuing focus.}{A set of equipment used to inscribe even microscopic runic symbols into the surface of an object\comma{} and then channel magicl energy – thus \imp{enchanting} the object.}
\tool{Smithing Tools}{Craft}{A set of hammers\comma{} tongs\comma{} pokers and bellows\comma{} as well as a whetstone and oiled rags.}{A prerequisite for manipulating\comma{} shaping and forming raw metal into a new shape. You may need to find a proper forge to create larger objects\comma{} but even in the wilderness you can use these tools to do some preliminary repairs.}
\tool{Thieving Toolkit}{Covert}{Some lightly enchanted lockpicks\comma{} a small mirror\comma{} tweezers\comma{} some runestones and a bag of sand.}{Whilst a wizard often relies on magical means to get past locks and traps\comma{} powerful and intricate magics often require additional help. Wizard\apos{}s lockpicks are not just sticks of iron\comma{} but are often interwoven with powerful enchantments to ease to process and the set includes various arcane (runestones) and mundane (mirrors) tools which may alert you to the presence of proective countermeasures.}
\tool{Tinkering Tools}{Craft}{A collection of small tools – screwdrivers\comma{} pliers\comma{} tweezers\comma{} string and sections of wire. More muggle\minus{}oriented kits would have batteries and small electrical components such as lightbulbs.}{The DIY master\comma{} and the inventor’s\comma{} ideal toolkit. Allows you to undertake minor repair jobs\comma{} dismantle a gadget or artefact and play around with all manner of items.}
\tool{Woodworking Tools}{Craft}{Hammer and nails\comma{} chisel\comma{} plane\comma{} woodsaw and sandpaper.}{Everything you might need to construct something out of wood\comma{} or to repair or dismantle the same.}
