\input{spellDefinitions} 

\spellDoc{Nikc\apos{}s Spells}{
{ \footnotesize 
 \discTable{Memorised Spells}
{
	\spellRow{\spellEntry{Aerodynamic Rectification}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Magical Makeover}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Minor Trickery}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Prank}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Small Change Charm}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Touch of Colour}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

}}

\begin{multicols}{3}
	 \spell{
	name = Aerodynamic Rectification, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Wandtip, incant = volant, duration = 1 minute,noHigh = 1, noResist =1, noBlock = 1, effect =You imbue a 1d4 small stones or other small\comma{} nearby object with a magical aura which causes them to move more easily through the air.

When you or another being uses these as improvised throwing weapons\comma{} or as ammunition for a sling\comma{} you may add your proficiency modifier to the accuracy check\comma{} even if you are not proficient in the relevant field. On a successful hit\comma{} the object deals an additional 1d6 bludgeoning damage.
}

	 \spell{
	name = Magical Makeover, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Self, incant = crinus muto, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Alters the colour and style of the caster\apos{}s hair\comma{} apply a layer of makeup\comma{} and scrapes the dirt from under your fingernails. You may alter your appearance as if you had been attended to by a competent hair stylist and make\minus{}up artist.   

Useful for disguises\comma{} or to make yourself look suave in an instant.
}

	 \spell{
	name = Minor Trickery, school = Illusion, discipline = Bewitchment, type = Instant, level =Trivial, range =Close, incant = mico, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Create a minor magical trick\comma{} such as a flash of light\comma{} a brief shower of sparks or a puff of smoke. You could make a magical symbol float briefly in the air\comma{} or cause the hairs on the back of a target\apos{}s head to stand on end. Whilst this spell is very versatile\comma{} and the effects certainly look magical in nature\comma{} they serve no real purpose beyond looking pretty\comma{} though several enterprising wizards have used this spell on street corners whilst pretending to do muggle ``magic”.
}

	 \spell{
	name = Prank, school = Transfiguration, discipline = Conjuration, type = Instant, level =Trivial, range =Close, incant = riddikulus, duration = 2 minutes,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =You conjure something onto or near your target with the express intention of making them look as stupid as possible: Summon a funny hat onto an individual\comma{} or conjure up a note with a funny message and stick it to their back\comma{} this spell allows you to perform minor\comma{} harmless pranks in an instant.
}

	 \spell{
	name = Small Change Charm, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Wandtip, incant = psilus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =The only spell which can alter magical currency. By casting this charm on a set of Galleons\comma{} Sickles and Knuts you may transfigure them into any other combination of coins with an equal monetary value.
}

	 \spell{
	name = Touch of Colour, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Close, incant = pigmentus, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Causes the colour of an object to change to that specified by the caster. The resulting colour is not purely monochromatic\comma{} but appears as if you were viewing the object through a thick pane of coloured glass of the chosen colour.
}


\end{multicols}
}