\input{spellDefinitions} 

\spellDoc{Rakesh\apos{}s Spells}{
{ \footnotesize 
 \discTable{Memorised Spells}
{
	\spellRow{\spellEntry{Defensive Flare}{\wardSymb}}{\spellEntry{Arcane Shield}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Glowing Wand}{\concSymb}}{\spellEntry{Curse of the Bogies}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Knockback}{\instSymb}}{\spellEntry{Halt}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Minor Trickery}{\instSymb}}{\spellEntry{Levitation}{\concSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Palpitation}{\instSymb}}{\spellEntry{Locate Object}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\spellEntry{Prank}{\instSymb}}{\spellEntry{Night Vision}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Privacy Ward}{\wardSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Produce Fire}{\concSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Rainbow Sparks}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Remedy}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Sting}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

	\spellRow{\emptySpell{}}{\spellEntry{Transmutation}{\instSymb}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}{\emptySpell{}}

}}

\begin{multicols}{3}
	 \spell{
	name = Arcane Shield, school = Recuperation, discipline = Warding, type = Instant, level =Beginner, range =Self, incant = protego, noDur = 1, higher = Increase the strength of the shield by 1 point \forEvery{}.,noResist =1, noBlock = 1, effect =An ethereal shield blossoms from the end of your wand\comma{} protecting you from both magical and physical harm. 

Whenever an attack is performed against you whilst the shield is active\comma{} roll 2d4 and add this value to your Resist check or your Block value\comma{} as appropriate. If a successful Resist would limit the amount of damage taken\comma{} negate it entirely instead. 

If you fail to Resist\comma{} or the Accuracy exceeds your augmented Block value\comma{} the shield crumples and the spell is ended. The spell which broke the shield is then applied to you at half damage\comma{} with any other effects unmodified. Any other spells which hit you this round act as normal.
}

	 \spell{
	name = Curse of the Bogies, school = Maledictions, discipline = Curse, type = Instant, level =Beginner, range =Close, incant = Mucous ad nauseam, duration = 1 day,noHigh = 1, resist = Vitality, noBlock = 1, effect =A fine green mist floats from the end of your wand\comma{} into the face of the target. On a failed Resist\comma{} they contract an awful cold. The target becomes visibly ill\comma{} their nose drips snot constantly\comma{} and their throat is sore. 

Every time they open their mouth to speak\comma{} they must succeed a DV 10 Vitality Resist to avoid sneezing. Sneezing during a spell incantation causes the spell to fail.
}

	 \spell{
	name = Defensive Flare, school = Recuperation, discipline = Warding, type = Ward, level =Trivial, range =Wandtip, incant = defendo, duration = 10 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =You place a minor defensive ward onto a target\comma{} which flares into life the next time they take damage. 

If the targeted being takes damage before the end of the spell duration\comma{} the ward activates and they are considered Resistant to the attack. The ward is then removed.
}

	 \spell{
	name = Glowing Wand, school = Charms, discipline = Elemental, type = Focus, level =Trivial, range =Close, incant = lumos, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Causes the tip of your wand to glow like a torch. Casts bright light in a 2m radius\comma{} and dim light for another 5m.
}

	 \spell{
	name = Halt, school = Charms, discipline = Kinesis, type = Instant, level =Beginner, range =Close, incant = stabit, noDur = 1, noHigh = 1, resist = Speed, noBlock = 1, effect =Stop an object or being in their tracks. An inanimate object clatters to the floor and lies still. 

If used on a living being\comma{} you may choose one of the following effects\comma{} which apply only on a failed resist:
\begin{spellitemize}
\item Target moves half their movement speed this turn\comma{} before being halted 
\item Choose one accuracy check they make this turn cycle and cause it to fail {\it before} the check is made. 
\end{spellitemize}
}

	 \spell{
	name = Knockback, school = Maledictions, discipline = Hex, type = Instant, level =Trivial, range =Close, incant = flipendo, noDur = 1, higher = Each additional casting level dedicated to this spell increases the power of the energy\minus{}wave: do an additional 1d8 force damage and push the target back an extra 2 metres.,resist = Strength, negation = Blockable  and Dodgeable,effect =A wave of energy strikes into the target\comma{} causing 1d6 force damage\comma{} and if the target fails to Resist\comma{} pushing the target backwards up to 1 metre.
}

	 \spell{
	name = Levitation, school = Charms, discipline = Kinesis, type = Focus, level =Beginner, range =Sight, incant = wingardium leviosa, noDur = 1, higher = The maximum mass this spell is capable of lifting multiplies by ten for every additional spell level used to cast it.,resist = Strength, noBlock = 1, effect =Cause an object of 1kg or less to levitate whilst concentration is maintained. You may control the height of the object\comma{} but you may not move it horizontally. A being may attempt to grab hold of the levitating object\comma{} and whilst they can move it horizontally\comma{} they may only change its height by performing a Resist check\comma{} breaking the enchantment on a success.
}

	 \spell{
	name = Locate Object, school = Divination, discipline = Temporal, type = Instant, level =Beginner, range =Self, incant = locus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =After casting this spell\comma{} you must shout a description or the name of the object you are searching for. If you are within 1km of the object\comma{} you gain a snapshot of the object you are searching for\comma{} and the direction in which it is moving. 

If you are looking for a specific object\comma{} you must be familiar with it (i.e. have seen it up close at least once). Alternatively\comma{} you may describe a class of object (i.e. a necklace)\comma{} and the spell will find the nearest such object. 

This spell fails if there is no such object within range\comma{} or if the object is protected by any kind of magical ward or lock.
}

	 \spell{
	name = Minor Trickery, school = Illusion, discipline = Bewitchment, type = Instant, level =Trivial, range =Close, incant = mico, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Create a minor magical trick\comma{} such as a flash of light\comma{} a brief shower of sparks or a puff of smoke. You could make a magical symbol float briefly in the air\comma{} or cause the hairs on the back of a target\apos{}s head to stand on end. Whilst this spell is very versatile\comma{} and the effects certainly look magical in nature\comma{} they serve no real purpose beyond looking pretty\comma{} though several enterprising wizards have used this spell on street corners whilst pretending to do muggle ``magic”.
}

	 \spell{
	name = Night Vision, school = Divination, discipline = Telepathy, type = Instant, level =Beginner, range =Wandtip, incant = aspectu, duration = 2 hours,noHigh = 1, noResist =1, noBlock = 1, effect =As you touch your wand to the target\apos{}s head\comma{} their eyes flash an unearthly green. Give the target nightvision for the duration: dim light is as bright as daylight\comma{} and darkness is considered dim.
}

	 \spell{
	name = Palpitation, school = Maledictions, discipline = Curse, type = Instant, level =Trivial, range =Close, incant = vena, noDur = 1, noHigh = 1, resist = Vitality, noBlock = 1, effect =On a failed Resist\comma{} you cause the target\apos{}s heart to miss a beat. Next cycle\comma{} the target\apos{}s speed is halved.
}

	 \spell{
	name = Prank, school = Transfiguration, discipline = Conjuration, type = Instant, level =Trivial, range =Close, incant = riddikulus, duration = 2 minutes,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =You conjure something onto or near your target with the express intention of making them look as stupid as possible: Summon a funny hat onto an individual\comma{} or conjure up a note with a funny message and stick it to their back\comma{} this spell allows you to perform minor\comma{} harmless pranks in an instant.
}

	 \spell{
	name = Privacy Ward, school = Recuperation, discipline = Warding, type = Ward, level =Beginner, range =Wandtip, incant = muffliato, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Ward a region up to 5m in radius. This ward prevents sound from inside the region being heard from the outside. When inside the region\comma{} sound from both inside and outside may be heard.
}

	 \spell{
	name = Produce Fire, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Wandtip, incant = incendio, noDur = 1, higher = Casting this spell at a higher level summons a larger and hotter gout of flame.

For every additional casting\minus{}level\comma{} the gout reaches an extra 15cm from your wandtip\comma{} and does 1d10 additional heat damage. The extra heat also allows you to ignite progressively tougher materials\comma{} such as damp wood.,noResist =1, negation = Blockable  and Dodgeable,effect =A small jet of fire is emitted from the tip of your wand\comma{} akin to a large lighter. The flame reaches out about 5 cm from the tip of your wandm and can be used to ignite larger fires. 

If in melee range with a target\comma{} you can attempt to burn your target using a melee spell attack. Coming into contact with the fire does 1d10 fire damage\comma{} and applies the {\it Burned: Minor} status effect.
}

	 \spell{
	name = Rainbow Sparks, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Close, incant = verdimillious, noDur = 1, higher = Create an additional packet of sparks for each level above Beginner used to cast this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =Shoots a packet of small sparks from your wand\comma{} which rocket from the end of your wand towards a single enemy. 

You may choose the colour of the sparks from red\comma{} blue\comma{} green or yellow. The colour of the sparks reflects the damage done: fire\comma{} cold\comma{} acid and electric respectively. 

Each packet does 1d12 damage of the chosen type.
}

	 \spell{
	name = Remedy, school = Recuperation, discipline = Healing, type = Instant, level =Beginner, range =Wandtip, incant = enervate, noDur = 1, higher = This spell heals for an additional 1d8 damage for every additional spell level dedicated to it.,noResist =1, noBlock = 1, effect =Your wand emits healing rays which close small wounds as you pass your wand over them. Heal for 1d8 points of health.

If the target has a {\it Major Injury}\comma{} cannot heal them above 25\% HP.
}

	 \spell{
	name = Sting, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Sight, incant = ictus, noDur = 1, higher = \additional{1d10}{poison},noResist =1, negation = Blockable,effect =A blast of purplish energy rockets from your wand\comma{} seeking to strike the enemy in the face. Stings the target for 1d10 poison damage.
}

	 \spell{
	name = Transmutation, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Close, incant = mutatio, duration = 1 hour,higher = The maximum mass this spell is capable of transfiguring multiplies by 5 for every additional spell level used to cast it.,resist = Power, noBlock = 1, effect =Transform a 1kg non\minus{}sapient animal (or part of an animal) or object into a different animal or solid object\comma{} negated on a successful Resist. If you are targeting a being which is in combat with you\comma{} they take advantage on the Resist check. 

The transformation must (approximately) conserve mass – you cannot turn a rat into a T\minus{}Rex\comma{} for example. The final product of the transfiguration must be a non\minus{}magical in nature (i.e. you cannot enchant items through Transmutation)
}


\end{multicols}
}