\documentclass[../CoreRulebook.tex]{subfile}
\twocolumn
\chapter{Cosmology}
\label{S:Cosmology}
Though little of it is talked about in the Wizarding World, for the study of it is highly restricted, and confined almost entirely to the Department of Mysteries (and its various international variants), the universe is not as simple as it might first seem. 

Throughout most of the modern history of the Western world, it has been held that there are three planes of existence: the Mortal world, where we reside, and then two higher planes: Heaven and Hell. In contrast, modern atheism holds that there is but one plane, and some adherents of a particular interpretation of Quantum Mechanics believe that there an infinite number of copies of the Mortal plane. It seems unlikely that the true nature of these `Planes' will ever be understood by mortal minds. 

The Department of Mysteries, however, was created with the primary goal of studying these `Planes of Existence'. The Department has established that there are in indeed multiple `realms', or planes of existence. The total number of planes is actually unknown, for they are difficult to map, but the Department has so far managed to place them into 5 categories.  
{\bf 
\begin{enumerate}[itemsep = 0em]
\item The Mortal World
\item The Astral Realm
\item The Higher Planes
\item The Eldritch Domain
\item The Void
\end{enumerate}
}
It seems that there is some form of notion of `distance', although given the multidimensional nature of the realms, it is not what you or I would recongise as distance, but some realms are `further' away from the mundane reality that we exist in, and it takes significant effort to traverse this `distance'. The `closer' a Plane is, the easier it is to access. Roughly speaking, as you traverse down the above list, you get further and further away from our reality.

\subsection{The Mortal World}

The Mortal World is the universe that we see around us. It contains every star in the sky, and is seemingly infinite in extent. 

Events in this World follow well-established rules, what the Muggles call `the laws of physics', though these `laws' may be tweaked somewhat by the use of magic.

Most Sapient beings go their entire life without knowing that there is anything besides the Mortal World in existence. 

\subsection{The Astral Realm}

The Astral Realm is probably the plane that lies closest to the Mortal World, and is often imagined by those who study it as a blanket, lying over the top of the mortal realm. 

Every point in the Mortal World has a corresponding point in the Astral Realm, however, the notions of space and time that we are comfortable with do not seem to apply in the Astral Realm. Past, present and future coexist all at once, and paths through the astral realm have a habit of not ending up where you'd expect them to. 

It is from the astral realm, therefore, that seers are able to glean information about the future. It is also speculated that when a wizard apparates, they actually briefly enter into the astral realm, traverse a path that either takes no time at all, or perhaps has no length at all (or maybe both?), and then exit again, finding themselves to have instantaneously transported. 

Visually, the Astral realm looks like a translucent mimicry of the mortal realm, filled with drifting mist, thick fog and ghostlike figures. One may therefore observe what is going on in the Mortal Realm from the Astral, but not the other way around without special training. 

\subsection{The Higher Planes}

The Higher Planes is the collective name given to the realms which lie between the Astral Realm and the insanity-inducing Eldritch Domains. 

Unlike the Astral Realm, the Higher Planes are far enough away from the Mortal World that most of them do not have a 1:1 correspondance with spatial point. Some of the Planes are as large as our universe, others may encompass only a single planet, or even a single room in extreme cases. 

Most of the Planes in this category find themselves devoted to some elemental or conceptual aspect found in the real world -- be it the the Plane of Fire (Vulcan), or the Plane of Order (Machina). It is hypothesised that entities from these Planes that found their way to the Mortal Realm in the distant past were often mistaken for Gods. 

Generally speaking, the only way to travel to one of the Higher Planes is by creating a Portal, and act that requires punching a hole through the walls of reality. This is an act so potentially destructive to all life on Earth that it is classified as a Dark Art, and should only be attempted by the most skilled wizards. A list of Planes that have previously been visited is found at the end of this section. 


\subsection{The Eldritch Domains}

Little is known about the Eldritch Domains. It is thought that they are similar in structure to the Higher Planes, but are instead home to entities that have been dubbed {\it the Eldritch Horrors}. Only one Sapient -- a muggle child in the late 1890s -- has ever even glimpsed an Eldritch Domain and not been driven to complete insanity, and it is evident from his subsequent career as an author that he was not unscarred by the experience. 

The Eldritch Horrors are entities beyond human comprehension, and go by many names: the Chaos Gods, The Great Old Ones, Devourer of Stars, Harbingers of Apocalypse to name but a few. They are not inherently evil, and are in fact so utterly alien that the concept of good and evil is barely applicable to beings of such comsic power. 

\subsection{The Void}

The Void is, unlike the other realms, omnipresent. It is simultaneously the closest Realm to the Mortal World, and yet also the most distant. It is thought that the Void is the hyper-dimensional space in which all the other Planes move, the glue that holds the universe together. 

The Void possesses at least 16 spatial dimensions, and 4 temporal dimensions, which means that even objects that enter the Void simultaneously (from the point of view of another plane) will end up dispersed across the 20-dimensional manifold that represents the void. 

Utterly, completely empty, the Void is the true vacuum of the multiverse. So black that empty space seems like a thick soup, and so dark that no light may propagate. The Void truly lives up to its name. 
\par~\par
\section{Higher Planes}\label{S:Planes}

\subsection{Abyss: The Plane of Terror}

Abyss is a plane that warps itself according to the fears of those who enter it. Formed from an endless, parched wasteland under a black sun, at the centre of which lies an sinkhole so deep it seems to have no end. Embedded into the walls of the sinkhole, spiralling infinitely downwards are thousands -- millions -- of doors, each with an individuals name inscribed upon it.

Behind every door lies a room of indeterminate size, containing the thing that most terrifies the being named on the door, be it an infinite maze, a posse of evil clowns, or an ocean populated by bloodthirsty sharks. Once inside a room, it is impossible to leave until you conquer your fears. 

When entering Abyss, each individual is teleported into the room bearing their own name, and upon escaping, formless beings of shadow and darkness will attempt to force you back inside. 

{\bf Planemeld Effect:} when melded with the mortal plane, Abyss causes all entities in the region take the Terrified status.

\subsection{Aeolus: The Plane of Storms and Winds}

A plane of infinite expanse, filled with swirling air, floating clouds and drifting chunks of earth, Aelous is the Plane associated with the element of Air. 

There is no solid ground to be found in Aeolus, the civilisations found within are built upon the floating mountains that dot the skyscape, or perhaps carved out of condensed and harness cloud. These civilisations live a nomadic life as they drift through the endless sky, never fixed in one place. 

Current-charts, which map the airflow and allow you to plot a route through the sky, are the most valued currency in this domain, as are Storm-warnings, for the skies of Aeolus are often split apart by vicious storms that can last a century or more. 

Aelous is home to powerful wind-mages, who can calm the skies with a word, or whip up a brisk wind with a wave of their hand. It is these wind-mages who first constructed the Storm Avatars, and from Aeolus that Mortal wizards draw the stormclouds to construct their own facsimiles of the Avatars. 

{\bf Planemeld Effect:} when melded with the mortal plane, Aeolus causes a stormcloud fills the region giving severe obscuration, and targets inside take 2d10 electric damage per turn.

\subsection{Eden: The Plane of Nature}

A druidic paradise, Eden is a single, enormous garden that lies behind an enormous wall, which forms the boundary between this realm and the Void. Every single species of plant and animal life across the multiverse can be found living in perfect balance in Eden -- the circle of life made manifest in a single region, for all of eternity. 

No artificial structure can be built in Eden (outside of the Wall, of course), so no true civilisations are found within. The denizens of this realm -- the Gardeners -- instead tend to the wildlife, curing the sick and resolving conflicts, and are rewarded with fruit and wool, in return for their role in the Circle. 

{\bf Planemeld Effect:} when melded with the mortal plane, Eden gives the caster the ability to manipulate all plant life at will, causing them to grow as desired. 

\subsection{Elysium: The Plane of Blessings}

Appearing as a gigantic city, constructed out of gleaming silver and shining marble, populated by beings that can only be described as Angels, it is said that Elysium is the place where dreams come true. 

Indeed, one has to merely wish for something out loud, and a nearby Angel will promptly hand you the focus of your desires. Equally, the air in Elysium seems to be suffused with magic and positive energy, for every action that one attempts (even the most absurd), will succeed without question. 

Of course, there is a price for such a blessed existence: an entity known as the Scribe -- the chief angelic being -- sits atop the highest tower in Elysium, judging the actions of all the inhabitants. If they fail her test, they are expelled from the Silver City.

{\bf Planemeld Effect:} when melded with the mortal plane, Elysium grants all beings in the region check-advantage.

\subsection{Hades: The Plane of Death}

Like the astral plane, Hades appears as a mimicry of the Mortal World, albeit with a few alterations. The landscape is dotted with bomb-craters, bubonic plague pits, collapsed buildings and nuclear winter. Every single grotesque form of death is represented, somehow, in the environment, in a violent, deadly parody of the living world. 

Populated entirely by ghosts, echoes of the living, no one is quite sure what causes a soul to be left in Hades. Some lucky souls are able to escape through the cracks and back to the Mortal Realm, forming the ghosts that wizardkind are aware of, but these are only a fraction of the ghosts found in Hades. 

The living cannot spend much time in Hades, as the aura of death and decay seeps into their bones, and seeks to turn them into one of the ghouls that haunts its shattered landscape. 

The Ministry of Magic possesses a portal to Hades, it lies deep beneath the Ministry itself, at the heart of the Department of Mysteries. However, this portal is one-way, so anyone who enters it without the ability to return home will surely perish. 

{\bf Planemeld Effect:} when melded with the mortal plane, Hades forces all beings below 50\% health to pass an ATH(health) check (DV 10) or die instantly.

\subsection{Hyperborea: The Plane of Ice}

A land of endless glaciers and towering crystal-clear castles, Hyperborea is the Elemental Plane of Ice. Due to the freezing temperatures, the Hyperborean species tend to be much larger than their counterparts in other dimensions, to best preserve the heat. They also tend to be fiercly tribal -- gathering together for warmth, but deeply fearful of outsiders. 

The landscape of Hyperborea is sporadic, with vast featureless plains, interspersed with enormous mountain ranges, and fields of icebergs floating on highly-salted oceans. 

Every time a wizard in the Mortal World summons an Avatar of Ice, he first begins by summoning a single snowflake from Hyperborea. 

{\bf Planemeld Effect:} when melded with the mortal plane, Hyperborea loweres the temperature in the region to -150 degrees Celsius, doing 3d8 cold damage per turn. 

\subsection{Machina: The Plane of Order}

In Machina, everything is always in its correct place, for Machina is the Plane of Order, where chaos and randomness are abhored and reviled. Over the millenia, the denizens of Machina have constructed enormous machines that enable them to control every aspect of reality down to the microsecond. The sun always rises at the same time every day, every coin toss lands on the same side, and the same events occur every single day. 

Fearing the chaos inherent in biological systems, the denizens of Machina have also gradually replaced their organic components, until they are almost entirely mechanical in nature. The great cities that dot the moulded landsape -- tracing out perfectly tesselating grids -- are split into three sectors, depending on the modifications that the denizens have made to their bodies, and hence their preferred method of keeping order: clockwork, electronics and magic. 

It is said that the first wizard to create a Golem learned the technique from the inhabitants of Machina.

{\bf Planemeld Effect:} when melded with the mortal plane, Machina imposes order on the region, forcing all beings into their true form. Illusions shatter, transfiguration spells fail and astral effects are nullified. 

\subsection{Nirvana: The Plane of Peace}

Nirvana is an alien landscape to those who first arrive -- it is seemingly and endless white expanse, with no up or down, and no floor. Individuals move simply by willing themselves in a certain direction. The entire domain is suffused with an aura of complete contentment. All desire and anger are stripped from your body, leaving you completely at peace with your place in the universe. 

Those who spend time in Nirvana, however, claim that the whiteness is not perfectly uniform, and that they can see shapes within it. After a significant time, individuals believe that they can make out entire cities, floating in the endless expanse. Eventually, they themselves begin to merge into the whiteness, until they are one with Nirvana. Even if they leave before this happens, so much of Nirvana has infused into their bones that they are incapable of aggression or violence. 

When it was first discovered, Nirvana was proposed as a humane alternative to the wizarding prison of Azkaban, as it removed the threat of further violence completely. However, a combination of a desire for punishment and the question mark of what {\it exactly} happens when they merge with Nirvana meant that Azkaban was retained. 

{\bf Planemeld Effect:} when melded with the mortal plane, Nirvana imbues the region with peace, forbidding any being from taking combat actions in the region. 

\subsection{Pand{\ae}monium: The Plane of Chaos}

As the name suggests, Pand{\ae}monium is a realm of pure unadulterated chaos, a whirling soup of matter, energy and magic. 

A calm ocean sits metres away from a typhoon, which warps into a lake freezing in a bed of lava. Fragments of stable landscapes drift through the chaotic world, being destroyed and reformed by the whirling chaos that infuses this dimension. Even gravity is not a constant, sometimes normal, sometimes twice the usual strength, sometimes even negative. 

Pand{\ae}monium, however, will respond to an individual imposing their will on it. A simple individual may be able to impose normalcy on a region just large enough to prevent their atoms from shredding as the laws of physics morph. A particularly strong-willed individual, however, can impose order amongst the chaos -- potentially for many dozens of metres, creating a safe haven for themselves. As soon as their will is broken, however, Pand{\ae}monium will reclaim the land into its everlasting chaos. 

{\bf Planemeld Effect:} when melded with the mortal plane, Pand{\ae}monium forces all beings in the region to pass a SPR(endurance) Resist check (DV 10), or be {\it True Shapeshift}-ed into a random animal for 1 minute. 
\subsection{Scholomancia: The Plane of Knowledge}

Scholomancia is probably the smallest of the main Higher Planes, consisting as it does of a single reading room about 15 metres by 15 metres, lined with bookshelves stocked with ancient tomes. Comfortable leather furniture dots the rest of the room, which has a single inhabitant; the Librarian. 

It is rumoured that, despite its small size, the bookshelves in Scholomancia contain every book ever written (and some that weren't), and that by providing new information to the Librarian, he will lead you to the knowledge you desire. 

{\bf Planemeld Effect:} when melded with the mortal plane, Scholomancia grants all beings in the region a temporary +4 bonus to the Arcane, History and Research proficiencies. 

\subsection{Tartarus: The Plane of Torture}

The home of beings that truly enjoy causing {\it pain} on other living beings, Tartarus is perhaps the most unpleasant plane for a mortal to visit. 

Tartarus appears as a neverending maze, with corridors dripping with blood and skeletons of previous victims. The demonic residents of Tartarus move freely through the walls, hunting their prey. If they catch their them, they torture their victims for as long as possible. Advancement through their terrifying society is achieved by inventive new torture methods, particularly excrutiating torture, or for keeping a victim alive longer than expected.

If you find yourself in Tartarus, the general advice is to leave as quickly as possible. 

{\bf Planemeld Effect:} when melded with the mortal plane, Tartarus Causes all beings to suffer as if the {\it Incomprehensible Torture} spell had been cast on them with 2PP. 
\subsection{Valhalla: The Plane of Bravery}

Viking mythology tells that at the heart of Asgard, lies the great Mead Hall of Heroes; Valhalla. It is from this myth that the Plane of Bravery gets its name. Societies in Valhalla hold bravery and conquest up as the mightiest virtue, and fear to be the greatest weakness. At the heart of Valhalla, lies a stone henge -- a series of portals to other plains. As a rite of passage to be considered an adult, every individual must pass through a random portal, and bring back some plunder. The greater the plunder, the more respected in society that that individual is. 

As a result of this somewhat primitive plunder-centric economy, the civilisations of Valhalla are not technologically advanced, and mostly resemble the Middle Ages of the Mortal World, albeit studded with advanced technology and magics that have been stolen from other planes. 

Most of the great adventures in the multiverse begin their story in Valhalla. 

{\bf Planemeld Effect:} when melded with the mortal plane, Valhalla grants a temporary +5 bonus to Willpower and Endurance proficiencies. 

\subsection{Vulcan: The Plane of Fire}

Visually, Vulcan most resembles typical depictions of the Christian Hell, with enormous pools of lava, gouts of fire twenty feet high, and patrolled by demons with pools of flame for eyes. However, this domain is simply the Plane associated with Elemental Fire, not with righteous torture of the evil.

Outside of the volcano-top castles and their pools of lava, the land is covered in a fertile ash, and populated by ruby-red trees that can only distribute their seeds when the tree is consumed by fire. Diverse species of dragon, from tiny lizard-like creatures to formidable goliaths patrol the skys. The fire of this realm serves not simply to destroy, but to cleanse and refresh and as such, though Vulcan is quite alien to us mortals, it has been home to several thriving and prosperous civilisations.

At the core of every summoned Avatar of Flame, lies a single ember drawn across the multiverse from Vulcan. 

{\bf Planemeld Effect:} when melded with the mortal plane, Vulcan ignites everything in the region, doing 3d12 fire damage per turn. 
