
\makeatletter
\define@key{potion}{name}{\def\name{#1}}
\define@key{potion}{description}{\def\visible{#1}}
\define@key{potion}{cost}{\def\cost{#1}}
\define@key{potion}{effect}{\def\effect{#1}}
\define@key{potion}{difficulty}{\def\difficulty{#1}}
\define@key{potion}{time}{\def\time{#1}}
\define@key{potion}{othereffect}{\def\side{#1}}
\define@key{potion}{doses}{\def\dose{#1}}
\define@key{potion}{essential}{\def\essential{#1}}
\define@key{potion}{optional}{\def\optional{#1}}
\makeatother
\def\q{4.2}
\def\g{0.75}
\def\h{1.95}
\def\l{1.45}
\renewcommand{\potion}[1]
{
\setkeys{potion}{name=None}
	\setkeys{potion}{#1}
	\vbox{
	{\normalsize \color{rulered}\name }

	{\it \visible}
	
	
	
	\vspace{1ex}
	\begin{tabular}{>{\centering\arraybackslash}m{\g cm} >{\centering\arraybackslash}m{\h cm} >{\centering\arraybackslash}m{\g cm} >{\centering\arraybackslash}m{\l cm}}
		\bf Cost	&	\bf Mixing Time	&\bf Dose&	\bf Difficulty 
		\\
		\cost{}	&	\time{}	& \dose{}&	\difficulty{} 
	\end{tabular}

\vspace{1 ex}
{\bf Ingredients}:~~		\parbox[t]{\q cm}{ \raggedright \essential}
	
}
	{\raggedright \effect}
	
	
	{\bf Optional Ingredients:}
	
	\begin{tabular}{m{\h cm} >{\centering\arraybackslash}m{\g cm} >{\centering\arraybackslash}m{1  cm} }
		\bf Name	&	\bf Bonus	&\bf DV Cost
		\\
		\optional{}
	\end{tabular}
	
	{\bf Side Effect:} ~~ \parbox[t]{\q cm}{ \raggedright \side}
	
	\vspace{3 ex}
}

\onecolumn
\chapter{Potions \& Ingredients}	

Alchemy is the art of mixing magical and mundane ingredients together into magical potions, concoctions and other wondrous items. In order to perform alchemy, the player characters must have a set of Alchemy Gear (which includes the all\minus{}important cauldron) and be able to cast the {\it Potion Mixing Spell}. 

Into the cauldron, Players then add their chosen ingredients, they must then leave the potion to brew (preferably over a nice warm fire), before completing the process by casting the {\it Potion Mixing Spell} which, unlike any other spells, is always performed with a d20 dice. 

A number of possible potions are given both in the player handbook, and in the list below (with more information). Each potion has associated with it a number of essential ingredients, a brewing time, the mixing difficulty and the number of doses that a successful mixing produces. 

If the ingredients they have chosen match the key ingredients of one of the potions in the list below, and if the potion was left to brew for the correct amount of time, then compare this `casting check' with the stated difficulty of the potion. If it exceeds the difficulty, then the ingredients are consumed, and a number of samples of the potion are produced, equal to the {\it Dose} statistic. 

\subsection{Failed Mixings}

If the first mixing check fails, you may elect to ask the alchemist in question to perform the alchemy check again. If the second check also fails, or if you decide to omit this rule, then the ingredients are consumed, and nothing happens: the fluid in the potion turns into a useless back sludge, or evaporates completely. 

If, however, the second check completes successfully, then the alchemist produces a {\it Flawed batch} of the chosen potion. A flawed batch has the same primary effect as the original potion, but has a {\it Side Effect}, which is presented at the bottom of the entry for each potion in the GM guide, but not in the Player Handbook. Some side effects are applied immediately upon mixing, and others are applied when the potion is used. 

\subsection{Modifying Potions}

The `essential ingredients' of a potion are those that one might find in a textbook. They are the safe, reproducable way to produce the stated effects. However, magic is a fickle thing, and the aspiring Potions Master should know that an extra sprinkle of Eye of Newt here, and a dash of Lemon Juice there can drastically change the effects of a potion.  

After adding the essential ingredients, each potion can then be modified by adding some optional ingredients. These optional ingredients can boost the effectiveness of the potion mixing by an amount specified in the list below. For instance, {\it Baruffio\apos{}s Brain Elixir} increases Intelligence by 2, but can be fortified by the addition of Ginger (+100\%), Griffin Claw (+75\%) or an Owl Feather (+25\%). The addition of Ginger, therefore, would increase the power of the elixir to +4 Intelligence, whilst Griffin claw would be a +3 bonus (rounding down). 

Note that when multiple optional ingredients are added, the bonuses do not simply add, {\bf they compound each other}, meaning you must multiply them together. A mixture of the Brain Elixir with both Ginger and Griffin Claw would have a magnitude of $2 \times 100\% \times 75\% = 2 \times 2 \times 1.75 = 7$. This is higher than the +5 we would have calculated if we had simply added the bonuses to 175\%.

Each optional ingredient also has associated with it an additional DV \minus{} making the potion harder to mix. If an incorrect ingredient is added, then it increases the DV by 5, but has no additional effects, unless the GM deems it to be a particularly heinous ingredient (adding {\it Basilisk Venom} to a healing potion, for example). 

The additional ingredients are not listed in the player version of the potion list, as they are (nominally) a secret. They may learn about the additional effects of individual ingredients through research, or through in\minus{}game interactions with herbalists. A trial\minus{}and\minus{}error approach is also not (entirely) frowned upon!

\subsection{Purchasing Potions}

If a player wants to get all the tasty benefits of potion mixing, but doesn't have the skill to pull it off, then they may simply purchase the potions for the price stated in each potion description. All potions purchased on the general marked are the `base\minus{}level' version with no additional ingredients or effects. If characters wish to purchase more powerful potions, these are only available from rare artisan potioneers who make potions to order. The prices of such orders scales with the additional power of the potion. 

\newpage
\subsection{Potion List}
\scriptsize
\begin{multicols}{3}
%%PotionBegin

\potion{name =Alchemic Grenade, description =Looks like  a small grey orb\comma{} which occasionally sparks with energy., cost =15\sickle, effect =Fill with another potion and throw. The orb detonates on contact and applies the contained potion (at 50\% effectiveness) to all targets within 1 metre, difficulty =15, time =2 hours, doses =3~doses, essential =Ash\comma{} Boomberry\comma{} Dragon Fire Gland\comma{} Wartcap Powder, optional = Erumpet Horn & +200\% & 7\\ Iron & +25\% & 1\\ Nundu Venom Sac & +200\% & 7\\ Valerian & +25\% & 1\\ ,othereffect  =The powder explodes immediately on mixing\comma{} applying the effect to the potion maker.}
\potion{name =Alihotsy Draught, description =A blue liquid which emits a powerful liquorice smell, cost =10\sickle, effect =Causes uncontrollable fits of laughter\comma{} preventing the target from speaking for 2 minutes, difficulty =10, time =2 hours, doses =3~doses, essential =Alihotsy Leaves\comma{} Billywig Sting, optional = Gold & +25\% & 1\\ Runespoor Egg & +100\% & 2\\ Unicorn Hair & +100\% & 2\\ ,othereffect  =Fumes also effect the potioneer with laughter.}
\potion{name =Amortentia, description =Bright pink liquid\comma{} emitting a light purple smoke. Smells of whatever is most dear to a person., cost =6\galleon , effect =After being consumed\comma{} this potion causes the target to take the {\it Charmed} status effect on the first sapient being they see. Infatuation lasts 3 hours, difficulty =15, time =12 hours, doses =1~dose, essential =Ashwinder Eggs\comma{} Nightshade\comma{} Rose Petals, optional = Dragon Blood & +150\% & 5\\ Fire Seed & +75\% & 2\\ Manticore Skin & +200\% & 6\\ Moonstone & +50\% & 2\\ ,othereffect  =The infatuation turns violent\comma{} and the drinker flies into a rage against the target of their affections.}
\potion{name =Anti\minus{}Paralysis Potion, description =A yellow gel that smells of cat urine, cost =10\sickle, effect =Rejuvinate the drinker. Removes the {\it Paralyzed} status and restores FP by 4 points, difficulty =10, time =2 hours, doses =3~doses, essential =Aconite\comma{} Billywig Sting\comma{} Mandrake Root, optional = Eye of Newt & +25\% & 1\\ Nettles & +25\% & 1\\ Octopus Powder & +100\% & 3\\ ,othereffect  =Causes insomina for 48 hours.}
\potion{name =Antidote to Common Poisons, description =Colourless\comma{} but smells like antiseptic., cost =5\sickle, effect =Reduce the remaining time left on an ongoing potion effect by 25 \%, difficulty =10, time =1 hour, doses =3~doses, essential =Bezoar\comma{} Mandrake Root, optional = Moonstone & +25\% & 1\\ Pheonix Feather & +200\% & 4\\ Pungent Onion & +25\% & 1\\ ,othereffect  =Destroys immune system\comma{} giving a Vulnerability to Poison damage.}
\potion{name =Astral Acid, description =A light green colour\comma{} those who smell it are not usually ina fit state to describe the smell., cost =15\sickle, effect =When consumed\comma{} the target can see clearly into both the astral plane and the material plane simultaneously for 1 minute, difficulty =10, time =4 hours, doses =3~doses, essential =Billywig Sting\comma{} Fairy Wings\comma{} Vodka, optional = Hippocampus Hair & +100\% & 3\\ Niffler Fang & +75\% & 3\\ Scarab Beetles & +75\% & 3\\ Wartcap Powder & +50\% & 2\\ ,othereffect  =The target becomes transfixed by the wonder they see\comma{} and cannot move of their own volution until the potion wears off.}
\potion{name =Azimov\apos{}s Awesome Acid, description =Toxic green liquid\comma{} smells acrid., cost =10\sickle, effect =Do not drink! Destroys armour\comma{} reducing {\it Block} statistic by 2 points, difficulty =10, time =3 hours, doses =3~doses, essential =Bundium Fluid\comma{} Dragon Blood\comma{} Sphinx Saliva, optional = Basilisk Venom & +200\% & 4\\ Flobberworm Mucous & +1\% & 1\\ Lemon Juice & +25\% & 1\\ ,othereffect  =When attempting to use\comma{} has a 50\% chance of melting through the container and attacking your own armour.}
\potion{name =Baruffio\apos{}s Brain Elixir, description =A green liquid which smells of strawberries, cost =2\galleon , effect =For one hour\comma{} gain an intelligence boost of 2 points, difficulty =15, time =12 hours, doses =3~doses, essential =Centaur Hoof\comma{} Dragon Claw\comma{} Runespoor Egg, optional = Ginger & +100\% & 3\\ Griffin Claw & +75\% & 2\\ Owl Feather & +25\% & 1\\ ,othereffect  =Nerve damage causes an equal drop in the Finesse attribute.}
\potion{name =Beautification Potion, description =An iridescent liquid that seems to move of its own accord, cost =2\galleon , effect =Makes the drinker extraordinarily beautiful\comma{} giving check advantage on any being likely to be attracted to them. Lasts for 5 minutes, difficulty =15, time =12 hours, doses =3~doses, essential =Fairy Wings\comma{} Morning Dew\comma{} Rose Petals, optional = Antimony & +50\% & 2\\ Boomslang Skin & +150\% & 5\\ Daisy & +50\% & 2\\ Ginger & +75\% & 2\\ ,othereffect  =The drinker also loses the ability to speak.}
\potion{name =Befuddlement Beverage, description =A brown sludge which smells like chocolate, cost =5\sickle, effect =Applies the {\it confused} status for 2 minutes, difficulty =10, time =1 hour, doses =3~doses, essential =Doxy Venom\comma{} Hemlock Essence\comma{} Lethe River Water, optional = Lovage & +50\% & 1\\ Mercury & +75\% & 2\\ Troll Snot & +200\% & 5\\ ,othereffect  =The target instead flies into a rage}
\potion{name =Blemish Blitzer, description =A yellow paste which smells of antiseptic, cost =5\sickle, effect =When applied to the skin\comma{} instantly removes all rashes\comma{} acne\comma{} boils and other skin ailments and restores HP by 2 points, difficulty =10, time =1 hour, doses =3~doses, essential =Honeywater\comma{} Murtlap Tentacles\comma{} Tormentil Tincture, optional = Bundium Fluid & +50\% & 1\\ Copper & +50\% & 1\\ Unicorn Hair & +150\% & 4\\ ,othereffect  =Dyes the skin a permanent yellow}
\potion{name =Blood\minus{}Refilling Potion, description =To all intents and purposes\comma{} looks like blood. However\comma{} smells like roses., cost =3\galleon , effect =For 5 minutes after being drunk\comma{} causes HP to regenerate at a rate of 2 per round, difficulty =15, time =1 day, doses =3~doses, essential =Dittany\comma{} Slug Slime\comma{} Wiggentree Bark, optional = Mint & +25\% & 1\\ Moly & +200\% & 6\\ Moonstone & +50\% & 2\\ Wormwood & +100\% & 3\\ ,othereffect  =Blood\minus{}refilling causes such pain\comma{} that spells cannot be cast for the duration of the potion.}
\potion{name =Burn\minus{}healing paste, description =An orange gel with a strong alcohol smell, cost =10\sickle, effect =When applied to the skin\comma{} removes the {\it Burned: Mild} status effect and leaves the target Resistant to Fire damage for 2 minutes, difficulty =10, time =2 hours, doses =3~doses, essential =Frost Salamander Blood\comma{} Honeywater\comma{} Iron, optional = Kelpie Hair & +100\% & 3\\ Mackled Malaclaw Tail & +150\% & 5\\ Sea\minus{}Serpent Spine & +50\% & 2\\ Wormwood & +25\% & 1\\ ,othereffect  =Gel acts as an adhesive\comma{} so target sticks to everything they touch for 1 day.}
\potion{name =Calming Draught, description =A lilac soup\comma{} with a lavender aroma, cost =10\sickle, effect =Calms and soothes the target\comma{} and makes them immune to the {\it Terrified} status and {\it Rage} effect for 2 minutes, difficulty =10, time =2 hours, doses =3~doses, essential =Asphodel\comma{} Flobberworm Mucous\comma{} Lavender, optional = Glumbumble Treacle & +200\% & 5\\ Mooncalf Tears & +75\% & 2\\ Tormentil Tincture & +25\% & 1\\ Wiggentree Bark & +75\% & 2\\ ,othereffect  =The consumer becomes so calm\comma{} they fall asleep and cannot be woken for 1 hour.}
\potion{name =Conduit Concoction, description =Looks like a lightning bolt\comma{} trapped in a bottle., cost =65\galleon , effect =After being absorbed through the skin\comma{} target may nominate one damage type. Target is immune to this damage type\comma{} and recovers FP equal to the damage they would have otherwise taken from this damage type for 30 seconds, difficulty =20, time =1 week, doses =1~dose, essential =Mercury\comma{} Pheonix Feather\comma{} Thunderbird Feather, optional = Moly & +100\% & 3\\ Re\apos{}em Blood & +75\% & 2\\ Unicorn Hair & +100\% & 3\\ ,othereffect  =Target is Vulnerable to all other forms of damage except the nominated type.}
\potion{name =Curse\minus{}Countering Concoction, description =Iridescent liquid seems to shift from one colour to the next., cost =10\galleon , effect =Target is immune to spells from the {\it Curse} discipline for 2 minutes, difficulty =15, time =1 day, doses =1~dose, essential =Diricawl Feather\comma{} Moly\comma{} Unicorn Hair, optional = Mallowsweet & +25\% & 1\\ Pearl Dust & +50\% & 1\\ Sphinx Saliva & +100\% & 2\\ ,othereffect  =Target is Vulnerable to all other forms of damage.}
\potion{name =Draconic Protection Draught, description =A fiery red liquid that smells like chalk., cost =10\sickle, effect =The drinker\apos{}s skin develops scales\comma{} increasing {\it Block} statistic by 2 points, difficulty =10, time =3 hours, doses =3~doses, essential =Dragon Scale\comma{} Iron\comma{} Pogrebin Shell, optional = Bicorn Horn & +150\% & 3\\ Caterpillar & +25\% & 1\\ Copper & +50\% & 1\\ ,othereffect  =Hands become permanently claw\minus{}shaped. Gives \minus{}1 penalty to Finesse.}
\potion{name =Dragonbreath Solution, description =Looks like molten lava\comma{} and smells like sulphur., cost =3\galleon , effect =Gain the ability to summon a gout of fire from your mouth in a cone 2m long\comma{} doing 3d8 fire damage for 30 seconds, difficulty =15, time =1 day, doses =3~doses, essential =Dragon Fire Gland\comma{} Fire Seed\comma{} Peppermint\comma{} Salamander Blood, optional = Ashwinder Eggs & +75\% & 2\\ Dragon Liver & +75\% & 2\\ Fire Crab Shell & +100\% & 3\\ ,othereffect  =This ability is uncontrollable\comma{} and occurs whenever you breath out.}
\potion{name =Draught of Living Death, description =Thick\comma{} black\comma{} odourless goo., cost =3\galleon , effect =Causes a deathlike slumber from which the target cannot be woken for 5 hours, difficulty =15, time =5 hours, doses =1~dose, essential =Asphodel\comma{} Valerian\comma{} Wormwood, optional = Lavender & +25\% & 1\\ Magnesium & +50\% & 1\\ Pearl Dust & +75\% & 2\\ Sloth Brain & +200\% & 6\\ ,othereffect  =Causes hypoxia in the victim\comma{} leading to a rapid death unless treated.}
\potion{name =Drink of Despair, description =This potion has no colour to speak of\comma{} but its very sight is enough to make you scared, cost =2\galleon , effect =When consumed\comma{} the victim becomes {\it Terrified} of a random object within sight for 5 minutes, difficulty =15, time =12 hours, doses =3~doses, essential =Eye of Newt\comma{} Manticore Skin\comma{} Nettles\comma{} Nogtail Trotter, optional = Quintaped Leg & +200\% & 4\\ Venemous Tentacula & +75\% & 2\\ ,othereffect  =The terror\minus{}induced adrenaline gives a bonus to Athletics of 4.}
\potion{name =Druid\apos{}s Delight, description =Looks like an acorn. In a bottle., cost =15\sickle, effect =When placed onto soil at least one metre deep\comma{} the `acorn\apos{} burrows into the ground and causes 1 oak tree to grow overnight, difficulty =10, time =5 hours, doses =3~doses, essential =Abyssinian Shrivelfig\comma{} Caterpillar\comma{} Fire Seed\comma{} Fluxweed, optional = Daisy & +50\% & 1\\ Eye of Newt & +75\% & 2\\ Moondew & +50\% & 1\\ Wiggentree Bark & +100\% & 3\\ ,othereffect  =Tree growth occurs instantly. Target must succeed a DV 10 ATH (speed) resist check to avoid being explosively impaled for 5d8 piercing damage.}
\potion{name =Duplicating Draught, description =An eerie green\minus{}blue liquid which smells of industrial solvents., cost =28\galleon , effect =When mixed in an existing potion (other than the Duplicating Draught) produces 1 extra copy, difficulty =15, time =3 days, doses =1~dose, essential =Pearl Dust\comma{} Sea\minus{}Serpent Spine\comma{} Unicorn Blood, optional = Antimony & +75\% & 2\\ Bicorn Horn & +100\% & 3\\ Fairy Wings & +50\% & 1\\ ,othereffect  =When mixed with another potion\comma{} all copies evaporate\comma{} leaving an empty cauldron.}
\potion{name =Emanation Elimination Elixir, description =Appears as a white cloud of gas\comma{} trapped in a container, cost =15\sickle, effect =This potion is not drunk\comma{} but released into the atmosphere. It repels all gases\comma{} odours and other atmospheric effects in a radius of 5 metres, difficulty =15, time =1 hour, doses =3~doses, essential =Dragon Fire Gland\comma{} Octopus Powder\comma{} Peppermint, optional = Daisy & +50\% & 1\\ Lavender & +75\% & 2\\ Rose Petals & +50\% & 1\\ ,othereffect  =Dangerously explosive. If a spark is ignited in the radius with 5 minutes of being released\comma{} ignites the gas for 5d8 fire damage to all in the radius.}
\potion{name =Fatiguing Infusion, description =A dark blue liquid with  an odour of rotting vegetation, cost =5\sickle, effect =Drains the afflicted of 10 FP, difficulty =15, time =5 hours, doses =3~doses, essential =Antimony\comma{} Dementor Cloak\comma{} Mercury, optional = Niffler Fang & +50\% & 1\\ Pogrebin Shell & +75\% & 2\\ Venemous Tentacula & +100\% & 3\\ ,othereffect  =Restores FP\comma{} instead of draining it.}
\potion{name =Felix Felicis, description =Looks like liquid gold\comma{} and smells of warm hugs., cost =127\galleon , effect =The drinker bends the laws of probability and becomes unfathomably lucky\comma{} taking check\minus{}advantage for 10 Minutes, difficulty =20, time =2 weeks, doses =1~dose, essential =Ashwinder Eggs\comma{} Occamy Egg\comma{} Squill Bulb, optional = Erumpet Horn & +100\% & 3\\ Mercury & +50\% & 1\\ Moly & +150\% & 4\\ ,othereffect  =Dangerously addictive. If not consumed once every day\comma{} leads to catastrophic system failure and death.}
\potion{name =Final Goodnight, description =A liquid that is so totally black\comma{} it seems to suck all light in from the room, cost =65\galleon , effect =Applies the {\it Poisoned: Severe} status effect and immediately deals 50 Poison Damage, difficulty =20, time =1 week, doses =1~dose, essential =Aconite\comma{} Acromantula Venom\comma{} Hellebore\comma{} Nundu Venom Sac, optional = Basilisk Venom & +200\% & 5\\ Hemlock Essence & +50\% & 1\\ Sea\minus{}Serpent Spine & +75\% & 2\\ ,othereffect  =The fumes do half damage to the poisoner}
\potion{name =Finder\apos{} Friend, description =A glowing silver liquid that smells like treasure and opportunity., cost =19\galleon , effect =When drunk\comma{} the consumer is revealed the location of lost or forgotten items\comma{} as well as secret doors in a radius of 25 metres, difficulty =15, time =6 days, doses =3~doses, essential =Kneazle Claw\comma{} Lemon Juice\comma{} Niffler Fang, optional = Dugbog Bark & +50\% & 1\\ Ginger & +25\% & 1\\ Gold & +75\% & 2\\ ,othereffect  =For every new item they discover\comma{} they lose another.}
\potion{name =Flask of Freezing, description =A fluid which looks like the cleanest\comma{} purest water you have ever seen., cost =10\galleon , effect =When the cork is removed from the phial\comma{} the liquid expands into an arctic vortex\comma{} freezing water and dealing 5d4 cold damage in a radius of 4 Metres, difficulty =15, time =1 day, doses =1~dose, essential =Antimony\comma{} Dementor Cloak\comma{} Frost Salamander Blood, optional = Leeches & +25\% & 1\\ Morning Dew & +50\% & 1\\ Sea\minus{}Serpent Spine & +100\% & 3\\ Styx River Water & +100\% & 3\\ ,othereffect  =The flask becomes unstable\comma{} and will detonate on any jostling of the phial.}
\potion{name =Fleet Foot Fluid, description =This blue liquid swirls into a vortex of its own accord, cost =3\galleon , effect =Your movement speed is doubled for 30 seconds, difficulty =15, time =1 day, doses =3~doses, essential =Diricawl Feather\comma{} Honeywater\comma{} Nogtail Trotter, optional = Boomberry & +75\% & 2\\ Mercury & +50\% & 1\\ Owl Feather & +50\% & 1\\ ,othereffect  =Once running has started\comma{} cannot stop for 3 turns.}
\potion{name =Forgetting Fog, description =Looks like a living cloud\comma{} trapped in a jar., cost =29\galleon , effect =When inhaled\comma{} the fog causes the target to forget 2 spells\comma{} recipes etc., difficulty =20, time =3 days, doses =1~dose, essential =Doxy Venom\comma{} Lethe River Water\comma{} Lovage, optional = Acromantula Venom & +100\% & 2\\ Venemous Tentacula & +75\% & 2\\ ,othereffect  =The target causes them to forget their fears\comma{} leading to an increase in Spirit of 2 points.}
\potion{name =Garotting Gas, description =A green gas\comma{} which sits at the bottom of the container., cost =2\galleon , effect =When inhaled\comma{} the gas prevents the victim from breathing or speaking for 30 seconds, difficulty =15, time =12 hours, doses =3~doses, essential =Ash\comma{} Grindylow Claw\comma{} Kelpie Hair, optional = Antimony & +75\% & 3\\ Fluxweed & +50\% & 2\\ Quintaped Leg & +100\% & 3\\ Wartcap Powder & +75\% & 3\\ ,othereffect  =When brewed\comma{} the fumes cause this effect on the potioneer.}
\potion{name =Gift of the Gab, description =A silver liquid\comma{} which looks like mercury. No smell to speak of., cost =10\sickle, effect =Charisma bonus 2 Points, difficulty =10, time =2 hours, doses =3~doses, essential =Daisy\comma{} Honeywater\comma{} Puffskein Tongue\comma{} Silver, optional = Jobberknoll Feather & +100\% & 2\\ Mercury & +50\% & 1\\ Moondew & +25\% & 1\\ ,othereffect  =Tongue stained permanently silver.}
\potion{name =Gilly Concoction, description =Green\minus{}blown sludge. Looks and taste disgusting., cost =0\sickle, effect =Drinker develops gills and webbed hands\comma{} allowing them to survive underwater 0.5 hours, difficulty =10, time =0.5 hour, doses =1~dose, essential =Gillyweed, optional = Eye of Newt & +25\% & 1\\ Hippocampus Hair & +100\% & 3\\ Mackled Malaclaw Tail & +100\% & 3\\ Mint & +25\% & 1\\ ,othereffect  =Gills and webbed hands stay visible for 24 hours}
\potion{name =Girding Potion, description =A golden liquid with suspicious lumps in it., cost =10\galleon , effect =When drunk\comma{} increases the endurance of a target\comma{} giving them Check\minus{}Advantage in all Resist checks for 5 minutes, difficulty =15, time =1 day, doses =1~dose, essential =Doxy Eggs\comma{} Fairy Wings\comma{} Hippocampus Hair, optional = Griffin Claw & +100\% & 2\\ Unicorn Hair & +100\% & 2\\ ,othereffect  =Gain check disadvantage on all accuracy checks for the duration.}
\potion{name =Gloom\minus{}inducing Agent, description =A black\comma{} tar\minus{}like substance with an earthy aroma., cost =5\sickle, effect =Target is incapable of laughing for 5 minutes\comma{} and suffers a penalty to Spirit of 1 Points, difficulty =10, time =1 hour, doses =3~doses, essential =Glumbumble Treacle, optional = Asphodel & +50\% & 1\\ Bezoar & +100\% & 3\\ Bundium Fluid & +50\% & 1\\ ,othereffect  =Target loses the ability to speak entirely.}
\potion{name =Growing Agent, description =A green paste which seems to pulse with power, cost =5\sickle, effect =When applied to a living being\comma{} causes it to grow in size by 50 \%, difficulty =15, time =5 hours, doses =3~doses, essential =Caterpillar\comma{} Mercury\comma{} Occamy Egg, optional = Dragon Blood & +100\% & 3\\ Manticore Skin & +100\% & 3\\ Owl Feather & +25\% & 1\\ Slug Slime & +50\% & 1\\ ,othereffect  =Target also suffers from a 2 point penalty to intelligence until reduced in size.}
\potion{name =Herbicide Potion, description =A thin\comma{} pale green oil, cost =10\sickle, effect =When dropped on the ground\comma{} kills all plants in a radius of 5 metres, difficulty =10, time =2 hours, doses =3~doses, essential =Bundium Fluid\comma{} Flobberworm Mucous\comma{} Horklump Juice, optional = Basilisk Venom & +300\% & 7\\ Dragon Blood & +100\% & 2\\ Slug Slime & +50\% & 1\\ ,othereffect  =The fumes also do 2d6 HP damage to the potioneer when applied.}
\potion{name =Hero\apos{}s Brew, description =A thick golden concoction. Smell is hard to describe\comma{} but is often described as `smelling like victory\apos{}, cost =10\sickle, effect =The cowardly consumer of this potion finds themselves immune to the {\it Terrified} status effect. 10 minutes, difficulty =10, time =2 hours, doses =3~doses, essential =Griffin Claw\comma{} Troll Snot\comma{} Vodka, optional = Peppermint & +25\% & 1\\ Pheonix Feather & +100\% & 3\\ Tea Leaf & +10\% & 1\\ Unicorn Hair & +100\% & 3\\ ,othereffect  =Intelligence suffers a permanent 1 point penalty.}
\potion{name =Infusion of Strength, description =A solid yellow liquid with an incredibly sweet smell., cost =3\galleon , effect =For one hour\comma{} the drinker gets a bonus to checks that use the Strength proficiency by 2 points, difficulty =15, time =1 day, doses =3~doses, essential =Iron\comma{} Re\apos{}em Blood\comma{} Styx River Water, optional = Boomberry & +25\% & 1\\ Bubotuber Juice & +25\% & 1\\ Troll Snot & +100\% & 3\\ ,othereffect  =Permanent 2 point penalty to Finesse attribute}
\potion{name =Insulation Inocculation, description =A brown\comma{} frothy beverage which is always just the perfect temperature to warm you up., cost =15\sickle, effect =When consumed\comma{} cures a target of the {\it Frostbite: Mild} status\comma{} and prevents it from being reacquired for 10 minutes, difficulty =10, time =5 hours, doses =3~doses, essential =Coffee Beans\comma{} Fire Seed\comma{} Honeywater, optional = Fire Crab Shell & +75\% & 3\\ Ginger & +50\% & 2\\ Salamander Blood & +75\% & 3\\ Vodka & +100\% & 3\\ ,othereffect  =Your sweat becomes extra flammable: target is Vulnerable to fire damage for 1 day.}
\potion{name =Magi\minus{}Me\minus{}More, description =A red liquid that smells of almonds., cost =4\galleon , effect =For 5 minutes\comma{} Power attribute increases by 2 points, difficulty =10, time =2 days, doses =3~doses, essential =Magnesium\comma{} Re\apos{}em Blood\comma{} Runespoor Egg\comma{} Salamander Blood, optional = Dragon Liver & +100\% & 3\\ Pheonix Feather & +100\% & 3\\ Sphinx Saliva & +75\% & 2\\ ,othereffect  =The potion causes degradation of the emotional parts of your brain: permanent +1 increase to Evil attribute}
\potion{name =Malevolent Mixture, description =An angry red colour and an ominous glow accompany this potion., cost =6\galleon , effect =Causes the consumer to fly into a violent\comma{} unstoppable rage for 1 minute, difficulty =15, time =2 days, doses =3~doses, essential =Dragon Fire Gland\comma{} Hellebore\comma{} Quintaped Leg, optional = Basilisk Venom & +150\% & 5\\ Fire Seed & +75\% & 3\\ Horklump Juice & +50\% & 2\\ Nogtail Trotter & +75\% & 3\\ ,othereffect  =Their rage is specifically directed towards the brewer of the potion.}
\potion{name =Merlin\apos{}s Surprise, description =A clear\comma{} colourless and odourless liquid., cost =19\galleon , effect =The mixer whispers a word over the cauldron as this potion brews. The next time this word is uttered within 2m of the fluid\comma{} it ignites for 8d6 fire damage in a radius of 1 metre, difficulty =15, time =2 days, doses =1~dose, essential =Dragon Blood\comma{} Erumpet Horn\comma{} Jobberknoll Feather\comma{} Mercury, optional = Chizpurfle Fang & +100\% & 3\\ Fire Crab Shell & +25\% & 1\\ Fire Seed & +50\% & 2\\ Runespoor Egg & +150\% & 5\\ ,othereffect  =The potion instead responds to a randomly chosen word.}
\potion{name =Midas\apos{} Mixture, description =Smells like a strong red wine\comma{} but looks like it is made of pure gold., cost =96\galleon , effect =Target transforms everything they touch (excluding themselves) into random metals for 1 day, difficulty =20, time =2 weeks, doses =1~dose, essential =Bowtruckle Thorn\comma{} Gold\comma{} Kelpie Hair\comma{} Thunderbird Feather, optional = Boomslang Skin & +150\% & 4\\ Copper & +25\% & 1\\ Iron & +25\% & 1\\ Magnesium & +75\% & 2\\ ,othereffect  =Transfigured objects are burning hot to the touch\comma{} and do 4d4 fire damage to the afflicted.}
\potion{name =Mopsus\apos{} Tincture, description =Looks and smells like milk\comma{} but tastes of popcorn., cost =3\galleon , effect =Opens your inner eye for 5 minutes to increase Perception attribute by 2 points, difficulty =10, time =1 day, doses =3~doses, essential =Centaur Hoof\comma{} Fairy Wings\comma{} Kneazle Claw, optional = Mallowsweet & +50\% & 1\\ Moly & +100\% & 3\\ Tea Leaf & +75\% & 2\\ ,othereffect  =In opening  your inner eye\comma{} you close your actual eyes. Take the {\it Blinded} status effect for the duration.}
\potion{name =Navigator\apos{}s Necessity, description =The green colour of this solution matches the smell of fresh\minus{}cut grass it exudes., cost =15\sickle, effect =The drinker gains a perfect sense of direction and internal clock. They cannot become lost\comma{} or lose track of time for 1 day, difficulty =10, time =12 hours, doses =3~doses, essential =Iron\comma{} Owl Feather\comma{} Runespoor Egg, optional = Centaur Hoof & +75\% & 2\\ Diricawl Feather & +150\% & 4\\ Galanthus Nivalis & +100\% & 3\\ Peppermint & +25\% & 1\\ ,othereffect  =Target becomes so focussed on their location\comma{} Perception attribute takes a temporary 4 point penalty.}
\potion{name =Paralyzing Poison, description =A thick white paste, cost =0\sickle, effect =Applies the {\it Paralyzed} status effect for 15 seconds, difficulty =15, time =3 hours, doses =3~doses, essential =Lobalug Venom\comma{} Mercury\comma{} Nettles, optional = Acromantula Venom & +150\% & 5\\ Bubotuber Juice & +50\% & 2\\ Bulbadox Powder & +75\% & 2\\ Copper & +25\% & 1\\ ,othereffect  =Randomly removes one other status effect from the afflicted.}
\potion{name =Pepperup Potion, description =Bright blue gel\comma{} with a strong\comma{} spicy odour., cost =5\sickle, effect =Restores FP by 5 points, difficulty =10, time =1 hour, doses =3~doses, essential =Chizpurfle Fang\comma{} Ginger\comma{} Tea Leaf, optional = Dragon Liver & +100\% & 3\\ Honeywater & +25\% & 1\\ Runespoor Egg & +150\% & 5\\ Salamander Blood & +50\% & 2\\ ,othereffect  =Causes smoke to issue from the ears with a loud whistling noise.}
\potion{name =Philosopher\apos{}s Stone, description =A ruby\minus{}red rock\comma{} which glows with an internal light, cost =9669\galleon , effect =Turns any metal into pure gold\comma{} and produces the Elixir of Life\comma{} which provides immortality when taken at regular intervals of 1 week, difficulty =30, time =3 years, doses =1~dose, essential =Mercury\comma{} Moly\comma{} Re\apos{}em Blood\comma{} Unicorn Blood, optional = Silver & +50\% & 2\\ ,othereffect  =The `elixir\apos{} is tainted\comma{} and causes permanent\comma{} utter insanity.}
\potion{name =Polyjuice Potion, description =The colour\comma{} scent and taste of this potion reflect the target transformation., cost =10\galleon , effect =Transfigure yourself into another human for 1 hour, difficulty =15, time =1 day, doses =1~dose, essential =Boomslang Skin\comma{} DNA of target\comma{} Fluxweed\comma{} Lacewing Flies, optional = Bicorn Horn & +100\% & 2\\ Knotgrass & +25\% & 1\\ Leeches & +50\% & 1\\ ,othereffect  =The transformation is randomly warped\comma{} and you end up with an ear for a mouth\comma{} and a mouth for an ear (for example).}
\potion{name =Potion of Extreme Energy, description =A thin\comma{} brown liquid that smells of fresh coffee., cost =10\sickle, effect =When consumed\comma{} removes the need for sleep for 2 days, difficulty =10, time =2 hours, doses =3~doses, essential =Coffee Beans\comma{} Dragon Claw\comma{} Tea Leaf, optional = Lemon Juice & +50\% & 1\\ Mooncalf Tears & +75\% & 2\\ Octopus Powder & +25\% & 1\\ Runespoor Egg & +100\% & 3\\ ,othereffect  =After potion ends\comma{} take level 5 exhaustion status.}
\potion{name =Potion of Living Dreams, description =An incredibly dark violet syrup\comma{} with no smell to speak of., cost =6\galleon , effect =When consumed\comma{} causes vivid auditory and visual hallucinations for 5 minutes, difficulty =15, time =2 days, doses =3~doses, essential =Flobberworm Mucous\comma{} Hippocampus Hair\comma{} Knotgrass, optional = Billywig Sting & +75\% & 2\\ Fairy Wings & +50\% & 1\\ Kneazle Claw & +150\% & 4\\ ,othereffect  =Target is immune to all other illusions and deceptions.}
\potion{name =Potion of Safe Harbour, description =A tiny portion of a deep\comma{} royal blue liquid which tastes of boiled cabbage., cost =10\galleon , effect =When consumed\comma{} teleports to the drinker back to the location the potion was brewed\comma{} ignoring all anti\minus{}teleportation wards. Potion stops functioning after 2 days, difficulty =20, time =3 days, doses =3~doses, essential =Diricawl Feather\comma{} Horklump Juice\comma{} Thunderbird Feather, optional = Acromantula Venom & +150\% & 5\\ Dragon Scale & +150\% & 5\\ Galanthus Nivalis & +25\% & 1\\ Owl Feather & +75\% & 3\\ ,othereffect  =The teleportation occurs randomly.}
\potion{name =Potion of Sustenance, description =Looks\comma{} tastes and smells like porridge., cost =46\galleon , effect =Target does not need to eat food\comma{} or feel hunger\comma{} for 3 days, difficulty =15, time =5 days, doses =1~dose, essential =Coffee Beans\comma{} Mandrake Root\comma{} Morning Dew\comma{} Squill Bulb, optional = Dragon Blood & +100\% & 3\\ Galanthus Nivalis & +25\% & 1\\ Honeywater & +75\% & 2\\ Wiggentree Bark & +50\% & 1\\ ,othereffect  =Target must consume at least 15 litres of water per day.}
\potion{name =Sapping Solution, description =A milky white fluid with an incredibly sweet smell, cost =10\galleon , effect =Victim gets check\minus{}disadvantage on all strength\minus{}related checks for 2 minutes, difficulty =15, time =1 day, doses =1~dose, essential =Caterpillar\comma{} Doxy Eggs\comma{} Silver, optional = Mallowsweet & +50\% & 1\\ Manticore Skin & +150\% & 4\\ Mercury & +75\% & 2\\ ,othereffect  =Target gets check\minus{}advantage on all Finesse checks}
\potion{name =Savage Toxin, description =A poisonous green colour accompanies a foul rotting odour., cost =6\galleon , effect =Applies the {\it Poisoned: Severe} status effect and immediately deals 10 Poison Damage, difficulty =15, time =2 days, doses =3~doses, essential =Basilisk Venom\comma{} Hemlock Essence\comma{} Sea\minus{}Serpent Spine, optional = Acromantula Venom & +150\% & 5\\ Fire Seed & +75\% & 3\\ Nightshade & +25\% & 1\\ Nundu Venom Sac & +150\% & 5\\ ,othereffect  =Triggers immune response so target is Resistant to poison damage for 24 hours.}
\potion{name =Shrinking Agent, description =A red paste which seems to pulse with power, cost =5\sickle, effect =When applied to a living being\comma{} causes it shrink in size by 50 \%, difficulty =15, time =5 hours, doses =3~doses, essential =Abyssinian Shrivelfig\comma{} Mercury\comma{} Occamy Egg, optional = Dragon Blood & +100\% & 3\\ Grindylow Claw & +50\% & 1\\ Moke Skin & +100\% & 3\\ Niffler Fang & +25\% & 1\\ ,othereffect  =Target also suffers from a 2 point penalty to Athletics until returned to normal size}
\potion{name =Skele\minus{}grow, description =A pale yellow liquid which tastes worse than you can possibly imagine., cost =10\sickle, effect =Mends broken bones and removes the associated {\it Broken Bone} and {\it Serious Injury} (if applicable) status effects\comma{} and restores HP by 5 points, difficulty =15, time =8 hours, doses =3~doses, essential =Bundium Fluid\comma{} Fluxweed\comma{} Quintaped Leg\comma{} Scarab Beetles, optional = Dittany & +100\% & 3\\ Tormentil Tincture & +50\% & 1\\ Wiggentree Bark & +200\% & 5\\ ,othereffect  =The wrong bones grow. Hope you like having a skull instead of an arm!}
\potion{name =Sleeping Serum, description =A dark purple fluid\comma{} with sparks of gold within, cost =15\sickle, effect =Sends the consumer into a dreamless sleep for at least 1 hour if they fail a DV 10 Spirit (Endurance) check., difficulty =10, time =12 hours, doses =3~doses, essential =Flobberworm Mucous\comma{} Lavender\comma{} Valerian, optional = Mandrake Root & +50\% & 1\\ Sloth Brain & +200\% & 5\\ Wormwood & +75\% & 2\\ ,othereffect  =The target dies instantly.}
\potion{name =Solution of Nature\apos{}s Ally, description =An oily substance\comma{} the colour of a vibrant forest., cost =15\sickle, effect =When consumed\comma{} causes animal to like you. Gain check advantage on all animal\minus{}persuasion checks for 1 hours, difficulty =10, time =5 hours, doses =3~doses, essential =Dugbog Bark\comma{} Lemon Juice\comma{} Owl Feather, optional = Moly & +200\% & 5\\ Pheonix Feather & +100\% & 3\\ Rose Petals & +50\% & 1\\ Squill Bulb & +25\% & 1\\ ,othereffect  =Causes humans to hate you\comma{} taking check disadvantage on all human\minus{}related checks.}
\potion{name =Solution of Rememberance, description =This clear fluid seems to glow from within, cost =19\galleon , effect =When consumed\comma{} helps aid recollection. Target remembers 2 things they forgot, difficulty =15, time =2 days, doses =1~dose, essential =Centaur Hoof\comma{} Galanthus Nivalis\comma{} Hippocampus Hair, optional = Jobberknoll Feather & +100\% & 2\\ Kneazle Claw & +50\% & 1\\ ,othereffect  =Target remembers every awkward incident from their childhood\comma{} and permanently loses 2 Spirit out of shame.}
\potion{name =Solution of Vulnerability, description =Colour varies with the choice of active ingredient\comma{} but the smell is always the same: burned parsnips., cost =3\galleon , effect =When administered\comma{} target becomes Vulnerable to the damage type represented by the `elemental token\apos{} (i.e. a burning ember would represent fire\comma{} a rose\apos{}s thorn\comma{} piercing).  Effect lasts for 5 minutes, difficulty =15, time =1 day, doses =3~doses, essential =Bundium Fluid\comma{} Doxy Venom\comma{} Elemental Token\comma{} Grindylow Claw, optional = Basilisk Venom & +200\% & 7\\ Dragon Blood & +100\% & 4\\ Hemlock Essence & +50\% & 2\\ Leeches & +75\% & 3\\ ,othereffect  =Target becomes Resistant to all ther forms of damage.}
\potion{name =Stew of Near\minus{}Invisibility, description =An invisible liquid\comma{} can be felt but not seen., cost =10\galleon , effect =For 30 minutes\comma{} the drinker is conferred an imperfect chameleon ability\comma{} gaining a bonus to Stealth checks of 2 points, difficulty =15, time =1 day, doses =1~dose, essential =Bowtruckle Thorn\comma{} Demiguise Hair\comma{} Niffler Fang, optional = Eye of Newt & +50\% & 1\\ Pearl Dust & +50\% & 1\\ Pogrebin Shell & +100\% & 3\\ Quintaped Leg & +75\% & 2\\ ,othereffect  =Target suffers uncontrollable flatulence.}
\potion{name =Ulgard\apos{}s Unstable Catalyst, description =A fizzing\comma{} yellow\minus{}orange liquid that moves of its own accord., cost =3\galleon , effect =Add to another potion to increase the potency by 50 \%, difficulty =15, time =5 hours, doses =1~dose, essential =Ash\comma{} Bulbadox Powder\comma{} Chizpurfle Fang, optional = Dragon Liver & +100\% & 3\\ Erumpet Horn & +400\% & 10\\ Salamander Blood & +50\% & 1\\ Stinksap & +25\% & 1\\ ,othereffect  =Explodes on addition to the potion\comma{} doing 4d10 fire damage in a 5m radius.}
\potion{name =Vampric Savior, description =Smells and tastes like blood\comma{} but is a pale orange colour., cost =9\galleon , effect =Acts as a substitute for human blood for a vampire. Satiate the drinker\apos{}s need for blood for 2 days, difficulty =10, time =3 days, doses =3~doses, essential =Dragon Blood\comma{} Salamander Blood\comma{} Slug Slime, optional = Ash & +25\% & 1\\ Morning Dew & +50\% & 1\\ Re\apos{}em Blood & +100\% & 1\\ Unicorn Blood & +500\% & 7\\ ,othereffect  =Any celestial damage is 100\% lethal to the target for 2 hours after drinking this potion.}
\potion{name =Veritaserum, description =Colourless\comma{} odourless liquid. Indistinguishable from water., cost =63\galleon , effect =For 2 minutes\comma{} the drinker is forced to answer all questions fully and truthfully\comma{} if they fail a DV 10 Spirit (Willpower) check, difficulty =15, time =1 week, doses =1~dose, essential =Jobberknoll Feather\comma{} Moonstone\comma{} Wormwood, optional = Eye of Newt & +50\% & 2\\ Jarvey Fang & +150\% & 5\\ Kneazle Claw & +100\% & 3\\ Pearl Dust & +25\% & 1\\ ,othereffect  =Target babbles incoherently. What they say may be the truth\comma{} but it is not an answer to a question.}
\potion{name =Viper\apos{}s Venom, description =A blue liquid with a slight acrid odour., cost =10\sickle, effect =Applies the {\it Poisoned: Mild} status effect and immediately deals 5 Poison Damage, difficulty =10, time =2 hours, doses =3~doses, essential =Asp Tail\comma{} Lobalug Venom\comma{} Nightshade, optional = Acromantula Venom & +150\% & 4\\ Basilisk Venom & +150\% & 4\\ Doxy Eggs & +50\% & 1\\ Venemous Tentacula & +75\% & 2\\ ,othereffect  =Triggers immune response so target is Resistant to poison damage for 24 hours.}
\potion{name =Weasley\apos{}s Patented Stinking Solution, description =Looks like an empty glass jar. The smell has been described as `unholy\apos{}. The taste is worse., cost =3\galleon , effect =When released into the atmosphere\comma{} causes a cloud so vile that all beings in a 5m radius must succeed a DV 10 Spirit (Endurance) check to avoid vomiting instantly. Vomiting takes a major action, difficulty =15, time =1 day, doses =3~doses, essential =Bundium Fluid\comma{} Lacewing Flies\comma{} Octopus Powder\comma{} Pungent Onion, optional = Sloth Brain & +25\% & 1\\ Slug Slime & +25\% & 1\\ Stinksap & +50\% & 1\\ Troll Snot & +50\% & 1\\ ,othereffect  =After mixing\comma{} the stench clings to the mixer\apos{}s robes\comma{} causing anyone who touches them to also vomit.}
\potion{name =Wiggenweld Potion, description =Vibrant red fluid with a pleasant\comma{} herbal aroma., cost =5\sickle, effect =Restores HP 5 points, difficulty =10, time =1 hour, doses =3~doses, essential =Dittany\comma{} Horklump Juice\comma{} Wiggentree Bark, optional = Leeches & +75\% & 1\\ Moly & +400\% & 7\\ Murtlap Tentacles & +50\% & 1\\ Nettles & +50\% & 1\\ ,othereffect  =Injuries heal improperly\comma{} leaving the drinker Vulnerable to fire damage.}
\potion{name =Wolfsbane, description =A yellow\minus{}green solution with the odour of rotting eggs., cost =29\galleon , effect =After consuming\comma{} a werewolf cannot transform into their {\it Beast Within} form for 1 day, difficulty =18, time =3 days, doses =1~dose, essential =Aconite\comma{} Eye of Newt\comma{} Mackled Malaclaw Tail\comma{} Wormwood, optional = Kelpie Hair & +75\% & 2\\ Moonstone & +50\% & 1\\ Silver & +500\% & 13\\ ,othereffect  =An improperly mixed batch causes an instant transformation into an enraged state.}


%%PotionEnd
\end{multicols}

\section{Ingredients}

\makeatletter
\define@key{ingredient}{name}{\def\name{#1}}
\define@key{ingredient}{description}{\def\visible{#1}}
\define@key{ingredient}{cost}{\def\cost{#1}}
\define@key{ingredient}{essential}{\def\essential{#1}}
\define@key{ingredient}{optional}{\def\optional{#1}}
\define@key{ingredient}{noEssential}{\def\noessential{#1}}
\define@key{ingredient}{noOptional}{\def\nooptional{#1}}
\makeatother
\def\q{4.2}
\def\g{0.75}
\def\h{1.95}
\def\l{1.45}
\newcommand{\ingredient}[1]
{
\setkeys{ingredient}{name=None, noEssential = 0, noOptional = 0}
	\setkeys{ingredient}{#1}
		
	\vbox{
		{\normalsize \color{ForestGreen}\name{} (\cost{}) }

	{\it \visible}
	
	\begin{tabular}{l l}
	\if\noessential0
	{\bf Required in:} & \parbox[t]{\q cm}{\essential} \\
	\fi
	\if\nooptional0
	{\bf Optional in:} &\parbox[t]{\q cm}{\optional}
	\fi
	\end{tabular}
	}
}

\begin{multicols}{3}
%%IngredientBegin

\ingredient{name =Abyssinian Shrivelfig, description =A purple fruit found in the African desert. Dries up and shrinks when picked., cost =15\sickle{} , essential =Druid\apos{}s Delight and Shrinking Agent,noOptional = 1}
\ingredient{name =Aconite, description =The brilliant blue flower of a common\comma{} non\minus{}magical (but poisonous) plant., cost =5\sickle{} , essential =Anti\minus{}Paralysis Potion\comma{} Final Goodnight and Wolfsbane,noOptional = 1}
\ingredient{name =Acromantula Venom, description =Thick\comma{} black venom of the giant spiders. Very rare and potent., cost =58\galleon{} 15\sickle{} , essential =Final Goodnight,optional =Forgetting Fog\comma{} Paralyzing Poison\comma{} Potion of Safe Harbour\comma{} Savage Toxin and Viper\apos{}s Venom}
\ingredient{name =Alihotsy Leaves, description =Consuming the speckled leaves of the `hyena tree\apos{} results in uncontrollable laughter, cost =4\sickle{} , essential =Alihotsy Draught,noOptional = 1}
\ingredient{name =Antimony, description =A silver metal used as a cosmetic throughout muggle history, cost =2\galleon{} , essential =Fatiguing Infusion and Flask of Freezing,optional =Beautification Potion\comma{} Duplicating Draught and Garotting Gas}
\ingredient{name =Ash, description =Burned and blackened organic matter., cost =15\knut{} , essential =Alchemic Grenade\comma{} Garotting Gas and Ulgard\apos{}s Unstable Catalyst,optional =Vampric Savior}
\ingredient{name =Ashwinder Eggs, description =A clutch of the eggs of a fire\minus{}snake. They are red\minus{}hot\comma{} and are renowned in love potions., cost =2\galleon{} 5\sickle{} , essential =Amortentia and Felix Felicis,optional =Dragonbreath Solution}
\ingredient{name =Asp Tail, description =The tail of a poisonois European snake\comma{} used in potion making for thousands of years., cost =2\galleon{} , essential =Viper\apos{}s Venom,noOptional = 1}
\ingredient{name =Asphodel, description =A mundane member of the lily family\comma{} used in sleeping potions, cost =5\sickle{} , essential =Calming Draught and Draught of Living Death,optional =Gloom\minus{}inducing Agent}
\ingredient{name =Basilisk Venom, description =Potent purple venom from the fangs of a monstrous snake., cost =58\galleon{} 15\sickle{} , essential =Savage Toxin,optional =Azimov\apos{}s Awesome Acid\comma{} Final Goodnight\comma{} Herbicide Potion\comma{} Malevolent Mixture\comma{} Solution of Vulnerability and Viper\apos{}s Venom}
\ingredient{name =Bezoar, description =A hard\comma{} brown lump formed in the stomach of a goat., cost =5\sickle{} , essential =Antidote to Common Poisons,optional =Gloom\minus{}inducing Agent}
\ingredient{name =Bicorn Horn, description =The golden horn of a legendary beast\comma{} with many properties., cost =8\galleon{} 15\sickle{} ,  noEssential = 1optional =Draconic Protection Draught\comma{} Duplicating Draught and Polyjuice Potion}
\ingredient{name =Billywig Sting, description =The venom inside causes giddiness and levitation., cost =15\sickle{} , essential =Alihotsy Draught\comma{} Anti\minus{}Paralysis Potion and Astral Acid,optional =Potion of Living Dreams}
\ingredient{name =Boomberry, description =A small brown nut that explodes when disturbed., cost =15\sickle{} , essential =Alchemic Grenade,optional =Fleet Foot Fluid and Infusion of Strength}
\ingredient{name =Boomslang Skin, description =The brown\comma{} sloughed of skin of a nonmagical snake., cost =5\sickle{} , essential =Polyjuice Potion,optional =Beautification Potion and Midas\apos{} Mixture}
\ingredient{name =Bowtruckle Thorn, description =Living green wood harvested from the forest\minus{}dweller, cost =2\galleon{} 5\sickle{} , essential =Midas\apos{} Mixture and Stew of Near\minus{}Invisibility,noOptional = 1}
\ingredient{name =Bubotuber Juice, description =White  sap from the magic tree causes boils on contact., cost =15\sickle{} ,  noEssential = 1optional =Infusion of Strength and Paralyzing Poison}
\ingredient{name =Bulbadox Powder, description =Volatile orange powder capable of causing boils and itching, cost =4\sickle{} , essential =Ulgard\apos{}s Unstable Catalyst,optional =Paralyzing Poison}
\ingredient{name =Bundium Fluid, description =A powerfully acidic\comma{} foul smelling grey secretion., cost =4\sickle{} , essential =Azimov\apos{}s Awesome Acid\comma{} Herbicide Potion\comma{} Skele\minus{}grow\comma{} Solution of Vulnerability and Weasley\apos{}s Patented Stinking Solution,optional =Blemish Blitzer and Gloom\minus{}inducing Agent}
\ingredient{name =Caterpillar, description =Pupae form of a butterfly. A variety of species and colours., cost =15\knut{} , essential =Druid\apos{}s Delight\comma{} Growing Agent and Sapping Solution,optional =Draconic Protection Draught}
\ingredient{name =Centaur Hoof, description =Shavings from the hoof is said to contain the wisdom of the mystical people., cost =8\galleon{} 15\sickle{} , essential =Baruffio\apos{}s Brain Elixir\comma{} Mopsus\apos{} Tincture and Solution of Rememberance,optional =Navigator\apos{}s Necessity}
\ingredient{name =Chizpurfle Fang, description =The fang of the magic\minus{}absorbing insects is a powerful restorative., cost =15\sickle{} , essential =Pepperup Potion and Ulgard\apos{}s Unstable Catalyst,optional =Merlin\apos{}s Surprise}
\ingredient{name =Coffee Beans, description =Small brown berries with a high caffeine content. Used by muggles as a restorative., cost =15\knut{} , essential =Insulation Inocculation\comma{} Potion of Extreme Energy and Potion of Sustenance,noOptional = 1}
\ingredient{name =Copper, description =A chemical element with many intruiging properties., cost =5\sickle{} ,  noEssential = 1optional =Blemish Blitzer\comma{} Draconic Protection Draught\comma{} Midas\apos{} Mixture and Paralyzing Poison}
\ingredient{name =Daisy, description =A small white and yellow flower familiar to muggles., cost =15\knut{} , essential =Gift of the Gab,optional =Druid\apos{}s Delight\comma{} Beautification Potion and Emanation Elimination Elixir}
\ingredient{name =Dementor Cloak, description =A cutting from the cloak of a dementor. Oozes cold\comma{} and saps your will., cost =8\galleon{} 15\sickle{} , essential =Fatiguing Infusion and Flask of Freezing,noOptional = 1}
\ingredient{name =Demiguise Hair, description =An invisible strand of hair\comma{} with many beneficial properties., cost =8\galleon{} 15\sickle{} , essential =Stew of Near\minus{}Invisibility,noOptional = 1}
\ingredient{name =Diricawl Feather, description =A purple feather that teleports 1cm to the left every few minutes., cost =2\galleon{} 5\sickle{} , essential =Curse\minus{}Countering Concoction\comma{} Fleet Foot Fluid and Potion of Safe Harbour,optional =Navigator\apos{}s Necessity}
\ingredient{name =Dittany, description =A mundane green leaf with powerful healing properties., cost =5\sickle{} , essential =Blood\minus{}Refilling Potion and Wiggenweld Potion,optional =Skele\minus{}grow}
\ingredient{name =Doxy Eggs, description =The bright blue eggs of the trickster\minus{}fairies are mildly poisonous., cost =15\sickle{} , essential =Girding Potion and Sapping Solution,optional =Viper\apos{}s Venom}
\ingredient{name =Doxy Venom, description =This clear fluid deeply affects the brain of the victim., cost =15\sickle{} , essential =Befuddlement Beverage\comma{} Forgetting Fog and Solution of Vulnerability,noOptional = 1}
\ingredient{name =Dragon Blood, description =Dumbledore is said to have discovered 12 uses for this scarlet substance., cost =8\galleon{} 15\sickle{} , essential =Azimov\apos{}s Awesome Acid\comma{} Merlin\apos{}s Surprise and Vampric Savior,optional =Amortentia\comma{} Growing Agent\comma{} Herbicide Potion\comma{} Potion of Sustenance\comma{} Shrinking Agent and Solution of Vulnerability}
\ingredient{name =Dragon Claw, description =The powdered claw of a dragon is said to provide a potent brain\minus{}boost., cost =8\galleon{} 15\sickle{} , essential =Baruffio\apos{}s Brain Elixir and Potion of Extreme Energy,noOptional = 1}
\ingredient{name =Dragon Fire Gland, description =The red\minus{}hot glands that sit inside the mouth of a dragon\comma{} responsible for their fire\minus{}breathing., cost =8\galleon{} 15\sickle{} , essential =Alchemic Grenade\comma{} Dragonbreath Solution\comma{} Emanation Elimination Elixir and Malevolent Mixture,noOptional = 1}
\ingredient{name =Dragon Liver, description =The liver of a dragon takes on the qualities of the food that the dragon eats., cost =8\galleon{} 15\sickle{} ,  noEssential = 1optional =Dragonbreath Solution\comma{} Magi\minus{}Me\minus{}More\comma{} Pepperup Potion and Ulgard\apos{}s Unstable Catalyst}
\ingredient{name =Dragon Scale, description =A hardened scale from the hide of a dragon \minus{} the colour varies depending on the species it was harvested from., cost =8\galleon{} 15\sickle{} , essential =Draconic Protection Draught,optional =Potion of Safe Harbour}
\ingredient{name =Dugbog Bark, description =Very dense wood\minus{}like material from the back of a dugbog., cost =15\sickle{} , essential =Solution of Nature\apos{}s Ally,optional =Finder\apos{} Friend}
\ingredient{name =Erumpet Horn, description =A grey\comma{} twisted horn that has a nasty habit of exploding., cost =8\galleon{} 15\sickle{} , essential =Merlin\apos{}s Surprise,optional =Alchemic Grenade\comma{} Felix Felicis and Ulgard\apos{}s Unstable Catalyst}
\ingredient{name =Eye of Newt, description =A classic potion ingredient\comma{} these black orbs are often used to stabilise volatile potions., cost =15\knut{} , essential =Drink of Despair and Wolfsbane,optional =Druid\apos{}s Delight\comma{} Anti\minus{}Paralysis Potion\comma{} Gilly Concoction\comma{} Stew of Near\minus{}Invisibility and Veritaserum}
\ingredient{name =Fairy Wings, description =Fairies regrow their iridescent wings regularly\comma{} though fresh\minus{}plucked wings are the most potent., cost =15\sickle{} , essential =Astral Acid\comma{} Beautification Potion\comma{} Girding Potion and Mopsus\apos{} Tincture,optional =Duplicating Draught and Potion of Living Dreams}
\ingredient{name =Fire Crab Shell, description =A jewel\minus{}encrusted ruby shell that occaisionally emits a gout of flame., cost =2\galleon{} 5\sickle{} ,  noEssential = 1optional =Dragonbreath Solution\comma{} Insulation Inocculation and Merlin\apos{}s Surprise}
\ingredient{name =Fire Seed, description =A seed that burns with a hot flame whilst growing. Takes hours to cool once picked., cost =15\sickle{} , essential =Druid\apos{}s Delight\comma{} Dragonbreath Solution and Insulation Inocculation,optional =Amortentia\comma{} Malevolent Mixture\comma{} Merlin\apos{}s Surprise and Savage Toxin}
\ingredient{name =Flobberworm Mucous, description =The green\minus{}grey goo extruded by the most useless of creatures., cost =15\knut{} , essential =Calming Draught\comma{} Herbicide Potion\comma{} Potion of Living Dreams and Sleeping Serum,optional =Azimov\apos{}s Awesome Acid}
\ingredient{name =Fluxweed, description =A magical plant known for its healing and transformative properties., cost =4\sickle{} , essential =Druid\apos{}s Delight\comma{} Polyjuice Potion and Skele\minus{}grow,optional =Garotting Gas}
\ingredient{name =Frost Salamander Blood, description =The ice\minus{}cold blood of the frost salamander\comma{} a pleasant sky\minus{}blue colour., cost =2\galleon{} 5\sickle{} , essential =Burn\minus{}healing paste and Flask of Freezing,noOptional = 1}
\ingredient{name =Galanthus Nivalis, description =A mundane herb known for its memory\minus{}inducing effects., cost =2\galleon{} , essential =Solution of Rememberance,optional =Navigator\apos{}s Necessity\comma{} Potion of Safe Harbour and Potion of Sustenance}
\ingredient{name =Gillyweed, description =A magical plant with the ability to confer the consumer with gills., cost =2\galleon{} 5\sickle{} , essential =Gilly Concoction,noOptional = 1}
\ingredient{name =Ginger, description =A pleasant smelling plant and foostuff. Gives life a bit of zing., cost =15\knut{} , essential =Pepperup Potion,optional =Baruffio\apos{}s Brain Elixir\comma{} Beautification Potion\comma{} Finder\apos{} Friend and Insulation Inocculation}
\ingredient{name =Glumbumble Treacle, description =A melancholy inducing substance that looks like pink honey., cost =15\sickle{} , essential =Gloom\minus{}inducing Agent,optional =Calming Draught}
\ingredient{name =Gold, description =A rare and lustrous metal. The goal of alchemists throughout history., cost =5\galleon{} 15\sickle{} , essential =Midas\apos{} Mixture,optional =Alihotsy Draught and Finder\apos{} Friend}
\ingredient{name =Griffin Claw, description =A magic raptor\minus{}like claw. Said to confer its great intelligence to the owner., cost =2\galleon{} 5\sickle{} , essential =Hero\apos{}s Brew,optional =Baruffio\apos{}s Brain Elixir and Girding Potion}
\ingredient{name =Grindylow Claw, description =A grey talon used by the creature to suffocate its victims., cost =15\sickle{} , essential =Garotting Gas and Solution of Vulnerability,optional =Shrinking Agent}
\ingredient{name =Hellebore, description =A poisonous plant that interferes with sleep., cost =2\galleon{} , essential =Final Goodnight and Malevolent Mixture,noOptional = 1}
\ingredient{name =Hemlock Essence, description =A well known poison\comma{} known for its purple hue., cost =2\galleon{} , essential =Befuddlement Beverage and Savage Toxin,optional =Final Goodnight and Solution of Vulnerability}
\ingredient{name =Hippocampus Hair, description =This multicoloured hair is said to help the memory., cost =2\galleon{} 5\sickle{} , essential =Girding Potion\comma{} Potion of Living Dreams and Solution of Rememberance,optional =Astral Acid and Gilly Concoction}
\ingredient{name =Honeywater, description =A dilute form of honey. Useful as a potion base., cost =4\sickle{} , essential =Blemish Blitzer\comma{} Burn\minus{}healing paste\comma{} Fleet Foot Fluid\comma{} Gift of the Gab and Insulation Inocculation,optional =Pepperup Potion and Potion of Sustenance}
\ingredient{name =Horklump Juice, description =The deep red juice of the horklump is a healing agent., cost =4\sickle{} , essential =Herbicide Potion\comma{} Potion of Safe Harbour and Wiggenweld Potion,optional =Malevolent Mixture}
\ingredient{name =Iron, description =A plentiful\comma{} hard metal. Used as a base in alchemy., cost =5\sickle{} , essential =Burn\minus{}healing paste\comma{} Draconic Protection Draught\comma{} Infusion of Strength and Navigator\apos{}s Necessity,optional =Alchemic Grenade and Midas\apos{} Mixture}
\ingredient{name =Jarvey Fang, description =A curved fang containing a venom that causes involuntary babbling., cost =15\sickle{} ,  noEssential = 1optional =Veritaserum}
\ingredient{name =Jobberknoll Feather, description =This black feather forces the bearer to relive their memories in exquisite detail., cost =2\galleon{} 5\sickle{} , essential =Merlin\apos{}s Surprise and Veritaserum,optional =Gift of the Gab and Solution of Rememberance}
\ingredient{name =Kelpie Hair, description =The grey hair of the shapeshifter retains some of this magic., cost =15\sickle{} , essential =Garotting Gas and Midas\apos{} Mixture,optional =Burn\minus{}healing paste and Wolfsbane}
\ingredient{name =Kneazle Claw, description =When powdered\comma{} increases the consumer{\apos}s perception enormously., cost =2\galleon{} 5\sickle{} , essential =Finder\apos{} Friend and Mopsus\apos{} Tincture,optional =Potion of Living Dreams\comma{} Solution of Rememberance and Veritaserum}
\ingredient{name =Knotgrass, description =The result of magical experimentation on a muggle plant \minus{} the result is an unusually resilient weed which can grow almost anywhere., cost =15\knut{} , essential =Potion of Living Dreams,optional =Polyjuice Potion}
\ingredient{name =Lacewing Flies, description =A species of small green insects\comma{} known for their transparent wings., cost =15\knut{} , essential =Polyjuice Potion and Weasley\apos{}s Patented Stinking Solution,noOptional = 1}
\ingredient{name =Lavender, description =A pleasant smelling purple plant with powerful calming effects., cost =15\knut{} , essential =Calming Draught and Sleeping Serum,optional =Draught of Living Death and Emanation Elimination Elixir}
\ingredient{name =Leeches, description =Animals that feed off blood. Powerful healing properties\comma{} but gross., cost =5\sickle{} ,  noEssential = 1optional =Flask of Freezing\comma{} Polyjuice Potion\comma{} Solution of Vulnerability and Wiggenweld Potion}
\ingredient{name =Lemon Juice, description =Cloudy\comma{} acidic juice with healing properties., cost =15\knut{} , essential =Finder\apos{} Friend and Solution of Nature\apos{}s Ally,optional =Azimov\apos{}s Awesome Acid and Potion of Extreme Energy}
\ingredient{name =Lethe River Water, description =Water from a magic river. A powerful amnesiac., cost =8\galleon{} 15\sickle{} , essential =Befuddlement Beverage and Forgetting Fog,noOptional = 1}
\ingredient{name =Lobalug Venom, description =This white fluid is a mild poison\comma{} often used to amplify other ingredients., cost =15\sickle{} , essential =Paralyzing Poison and Viper\apos{}s Venom,noOptional = 1}
\ingredient{name =Lovage, description =A mundane plant with nausea inducing qualities., cost =5\sickle{} , essential =Forgetting Fog,optional =Befuddlement Beverage}
\ingredient{name =Mackled Malaclaw Tail, description =A powerful iridescent blue ingredient\comma{} useful but unstable., cost =8\galleon{} 15\sickle{} , essential =Wolfsbane,optional =Burn\minus{}healing paste and Gilly Concoction}
\ingredient{name =Magnesium, description =This lustrous metal is so reactive it must be stored in oil to prevent it reacting with air., cost =5\sickle{} , essential =Magi\minus{}Me\minus{}More,optional =Draught of Living Death and Midas\apos{} Mixture}
\ingredient{name =Mallowsweet, description =The yellow berries of this plant have many beneficial properties., cost =15\knut{} ,  noEssential = 1optional =Curse\minus{}Countering Concoction\comma{} Mopsus\apos{} Tincture and Sapping Solution}
\ingredient{name =Mandrake Root, description =Trimmings from a sentient plant that act as a powerful antidote., cost =2\galleon{} 5\sickle{} , essential =Antidote to Common Poisons\comma{} Anti\minus{}Paralysis Potion and Potion of Sustenance,optional =Sleeping Serum}
\ingredient{name =Manticore Skin, description =The manticore{\apos}s magic resistance resides within its tanned skin., cost =8\galleon{} 15\sickle{} , essential =Drink of Despair,optional =Amortentia\comma{} Growing Agent and Sapping Solution}
\ingredient{name =Mercury, description =A liquid silver metal that is constantly changing shape and form., cost =5\sickle{} , essential =Conduit Concoction\comma{} Fatiguing Infusion\comma{} Growing Agent\comma{} Merlin\apos{}s Surprise\comma{} Paralyzing Poison\comma{} Philosopher\apos{}s Stone and Shrinking Agent,optional =Befuddlement Beverage\comma{} Felix Felicis\comma{} Fleet Foot Fluid\comma{} Gift of the Gab and Sapping Solution}
\ingredient{name =Mint, description =A pleasant smelling and tasting herb. Fresh!, cost =15\knut{} ,  noEssential = 1optional =Blood\minus{}Refilling Potion and Gilly Concoction}
\ingredient{name =Moke Skin, description =A green scaled pouch that shrinks at the sign of approaching danger., cost =2\galleon{} 5\sickle{} ,  noEssential = 1optional =Shrinking Agent}
\ingredient{name =Moly, description =A golden\comma{} glowing plant that helps to heal the wounded and break curses., cost =8\galleon{} 15\sickle{} , essential =Curse\minus{}Countering Concoction and Philosopher\apos{}s Stone,optional =Blood\minus{}Refilling Potion\comma{} Conduit Concoction\comma{} Felix Felicis\comma{} Mopsus\apos{} Tincture\comma{} Solution of Nature\apos{}s Ally and Wiggenweld Potion}
\ingredient{name =Mooncalf Tears, description =Glowing fluid that seems to calm you down just by looking at it., cost =15\sickle{} ,  noEssential = 1optional =Calming Draught and Potion of Extreme Energy}
\ingredient{name =Moondew, description =Dew gathered at midnight on a new moon. Absorbs all light that hits it., cost =15\knut{} ,  noEssential = 1optional =Druid\apos{}s Delight and Gift of the Gab}
\ingredient{name =Moonstone, description =A gemstone of unknown provenance. Glows with an inner light., cost =2\galleon{} 5\sickle{} , essential =Veritaserum,optional =Amortentia\comma{} Antidote to Common Poisons\comma{} Blood\minus{}Refilling Potion and Wolfsbane}
\ingredient{name =Morning Dew, description =Blah, cost =15\knut{} , essential =Beautification Potion and Potion of Sustenance,optional =Flask of Freezing and Vampric Savior}
\ingredient{name =Murtlap Tentacles, description =The pink tentacles have a soothing effect on the skin., cost =15\sickle{} , essential =Blemish Blitzer,optional =Wiggenweld Potion}
\ingredient{name =Nettles, description =Stinging plant\comma{} but has restorative properties when brewed., cost =15\knut{} , essential =Drink of Despair and Paralyzing Poison,optional =Anti\minus{}Paralysis Potion and Wiggenweld Potion}
\ingredient{name =Niffler Fang, description =A small white fang that excudes mischief., cost =2\galleon{} 5\sickle{} , essential =Finder\apos{} Friend and Stew of Near\minus{}Invisibility,optional =Astral Acid\comma{} Fatiguing Infusion and Shrinking Agent}
\ingredient{name =Nightshade, description =A poisonous purple flower\comma{} used as a cosmetic by muggles throughout history., cost =15\sickle{} , essential =Amortentia and Viper\apos{}s Venom,optional =Savage Toxin}
\ingredient{name =Nogtail Trotter, description =The foot of the nogtail makes one as fleet as the beast itself., cost =8\galleon{} 15\sickle{} , essential =Drink of Despair and Fleet Foot Fluid,optional =Malevolent Mixture}
\ingredient{name =Nundu Venom Sac, description =A black lump of flesh responsible for producing the poisonous aura of the nundu., cost =58\galleon{} 15\sickle{} , essential =Final Goodnight,optional =Alchemic Grenade and Savage Toxin}
\ingredient{name =Occamy Egg, description =Seemingly made of solid silver\comma{} yet constantly growing in size., cost =8\galleon{} 15\sickle{} , essential =Felix Felicis\comma{} Growing Agent and Shrinking Agent,noOptional = 1}
\ingredient{name =Octopus Powder, description =A disgusting orange powder\comma{} but a powerful catalyst., cost =2\galleon{} , essential =Emanation Elimination Elixir and Weasley\apos{}s Patented Stinking Solution,optional =Anti\minus{}Paralysis Potion and Potion of Extreme Energy}
\ingredient{name =Owl Feather, description =Proximity to wizards mean that an owls feathers pick up many properties., cost =5\sickle{} , essential =Navigator\apos{}s Necessity and Solution of Nature\apos{}s Ally,optional =Baruffio\apos{}s Brain Elixir\comma{} Fleet Foot Fluid\comma{} Growing Agent and Potion of Safe Harbour}
\ingredient{name =Pearl Dust, description =A lustrous powder that gleams with positive energy., cost =2\galleon{} , essential =Duplicating Draught,optional =Curse\minus{}Countering Concoction\comma{} Draught of Living Death\comma{} Stew of Near\minus{}Invisibility and Veritaserum}
\ingredient{name =Peppermint, description =A more potent form of mint\comma{} produces gas when immersed in acid., cost =15\knut{} , essential =Dragonbreath Solution and Emanation Elimination Elixir,optional =Hero\apos{}s Brew and Navigator\apos{}s Necessity}
\ingredient{name =Pheonix Feather, description =A scarlet feather with many wonderful magical properties., cost =58\galleon{} 15\sickle{} , essential =Conduit Concoction,optional =Antidote to Common Poisons\comma{} Hero\apos{}s Brew\comma{} Magi\minus{}Me\minus{}More and Solution of Nature\apos{}s Ally}
\ingredient{name =Pogrebin Shell, description =A lump of hardened flesh that resembles stone. Exudes an ominous aura., cost =8\galleon{} 15\sickle{} , essential =Draconic Protection Draught,optional =Fatiguing Infusion and Stew of Near\minus{}Invisibility}
\ingredient{name =Puffskein Tongue, description =A long ribbon of flesh harvested from a puffskein., cost =15\sickle{} , essential =Gift of the Gab,noOptional = 1}
\ingredient{name =Pungent Onion, description =A bright green onion with a powerfully repulsive odour., cost =4\sickle{} , essential =Weasley\apos{}s Patented Stinking Solution,optional =Antidote to Common Poisons}
\ingredient{name =Quintaped Leg, description =A brown\comma{} hairy leg from a magic abomination. Filled with hatred and power., cost =8\galleon{} 15\sickle{} , essential =Malevolent Mixture and Skele\minus{}grow,optional =Drink of Despair\comma{} Garotting Gas and Stew of Near\minus{}Invisibility}
\ingredient{name =Re\apos{}em Blood, description =A vibrant yellow fluid that imbues the drinker with immense strength., cost =8\galleon{} 15\sickle{} , essential =Infusion of Strength\comma{} Magi\minus{}Me\minus{}More and Philosopher\apos{}s Stone,optional =Conduit Concoction and Vampric Savior}
\ingredient{name =Rose Petals, description =Red petals that exude lust., cost =15\knut{} , essential =Amortentia and Beautification Potion,optional =Emanation Elimination Elixir and Solution of Nature\apos{}s Ally}
\ingredient{name =Runespoor Egg, description =Deep blue eggs with an orange aura\comma{} they are said to focus the mind, cost =2\galleon{} 5\sickle{} , essential =Baruffio\apos{}s Brain Elixir\comma{} Magi\minus{}Me\minus{}More and Navigator\apos{}s Necessity,optional =Alihotsy Draught\comma{} Merlin\apos{}s Surprise\comma{} Pepperup Potion and Potion of Extreme Energy}
\ingredient{name =Salamander Blood, description =Bright red fluid that emits huge amounts of heat. A powerful catalyst., cost =2\galleon{} 5\sickle{} , essential =Dragonbreath Solution\comma{} Magi\minus{}Me\minus{}More and Vampric Savior,optional =Insulation Inocculation\comma{} Pepperup Potion and Ulgard\apos{}s Unstable Catalyst}
\ingredient{name =Scarab Beetles, description =, cost =5\sickle{} , essential =Skele\minus{}grow,optional =Astral Acid}
\ingredient{name =Sea\minus{}Serpent Spine, description =Shed from the fins of aquatic beasts\comma{} these spines are used by poisoners worldwide., cost =2\galleon{} 5\sickle{} , essential =Duplicating Draught and Savage Toxin,optional =Burn\minus{}healing paste\comma{} Final Goodnight and Flask of Freezing}
\ingredient{name =Silver, description =A rare and lustrous metal\comma{} second only to gold in its value. Feared by the undead., cost =5\galleon{} 15\sickle{} , essential =Gift of the Gab and Sapping Solution,optional =Philosopher\apos{}s Stone and Wolfsbane}
\ingredient{name =Sloth Brain, description =The diced brain of a sloth is said to contain the essence of the being., cost =2\galleon{} ,  noEssential = 1optional =Draught of Living Death\comma{} Sleeping Serum and Weasley\apos{}s Patented Stinking Solution}
\ingredient{name =Slug Slime, description =Horned slugs produce an acidic green\minus{}grey fluid that slow their targets down., cost =4\sickle{} , essential =Blood\minus{}Refilling Potion and Vampric Savior,optional =Growing Agent\comma{} Herbicide Potion and Weasley\apos{}s Patented Stinking Solution}
\ingredient{name =Sphinx Saliva, description =Used to keep the sphynx cool in the hot deserts\comma{} this fluid is also incredibly acidic., cost =2\galleon{} 5\sickle{} , essential =Azimov\apos{}s Awesome Acid,optional =Curse\minus{}Countering Concoction and Magi\minus{}Me\minus{}More}
\ingredient{name =Squill Bulb, description =The root of a non\minus{}magical plant found at high altitudes\comma{} often used to make potions palatable., cost =5\sickle{} , essential =Felix Felicis and Potion of Sustenance,optional =Solution of Nature\apos{}s Ally}
\ingredient{name =Stinksap, description =A foul smelling green sap that permeates all surfaces it touches., cost =4\sickle{} ,  noEssential = 1optional =Ulgard\apos{}s Unstable Catalyst and Weasley\apos{}s Patented Stinking Solution}
\ingredient{name =Styx River Water, description =Water from a magic river. Gives the drinker protection\comma{} but they fly into a rage., cost =8\galleon{} 15\sickle{} , essential =Infusion of Strength,optional =Flask of Freezing}
\ingredient{name =Tea Leaf, description =A muggle plant that awakens the brain\comma{} and broadens the senses. Good with milk., cost =15\knut{} , essential =Pepperup Potion and Potion of Extreme Energy,optional =Hero\apos{}s Brew and Mopsus\apos{} Tincture}
\ingredient{name =Thunderbird Feather, description =Blah, cost =8\galleon{} 15\sickle{} , essential =Conduit Concoction\comma{} Midas\apos{} Mixture and Potion of Safe Harbour,noOptional = 1}
\ingredient{name =Tormentil Tincture, description =A bright yellow fluid extracted from a plant known for its soothing properties., cost =5\sickle{} , essential =Blemish Blitzer,optional =Calming Draught and Skele\minus{}grow}
\ingredient{name =Troll Snot, description =A thick grey goo that dulls the senses\comma{} but bolsters the muscles., cost =15\sickle{} , essential =Hero\apos{}s Brew,optional =Befuddlement Beverage\comma{} Infusion of Strength and Weasley\apos{}s Patented Stinking Solution}
\ingredient{name =Unicorn Blood, description =Visibly similar to mercury\comma{} the blood of a unicorn carries a powerful curse., cost =58\galleon{} 15\sickle{} , essential =Duplicating Draught and Philosopher\apos{}s Stone,optional =Vampric Savior}
\ingredient{name =Unicorn Hair, description =A pure\minus{}white hair with many beneficial properties\comma{} if taken politely., cost =8\galleon{} 15\sickle{} , essential =Curse\minus{}Countering Concoction,optional =Alihotsy Draught\comma{} Blemish Blitzer\comma{} Conduit Concoction\comma{} Girding Potion and Hero\apos{}s Brew}
\ingredient{name =Valerian, description =A sleep\minus{}inducing plant. Poisonous in high concentrations., cost =5\sickle{} , essential =Draught of Living Death and Sleeping Serum,optional =Alchemic Grenade}
\ingredient{name =Venemous Tentacula, description =A green goo formed from the mashed plant. Highly toxic., cost =15\sickle{} ,  noEssential = 1optional =Drink of Despair\comma{} Fatiguing Infusion\comma{} Forgetting Fog and Viper\apos{}s Venom}
\ingredient{name =Vodka, description =A strong mixture of ethanol and water\comma{} usually distilled from grain or potatoes., cost =5\sickle{} , essential =Astral Acid and Hero\apos{}s Brew,optional =Insulation Inocculation}
\ingredient{name =Wartcap Powder, description =A sickly yellow powder that causes boils and rashes to break out., cost =4\sickle{} , essential =Alchemic Grenade,optional =Astral Acid and Garotting Gas}
\ingredient{name =Wiggentree Bark, description =A thick lump of bark from a magical tree. Powerful restorative properties., cost =4\sickle{} , essential =Blood\minus{}Refilling Potion and Wiggenweld Potion,optional =Druid\apos{}s Delight\comma{} Calming Draught\comma{} Potion of Sustenance and Skele\minus{}grow}
\ingredient{name =Wormwood, description =A calming\comma{} healing plant that helps you drift off to sleep., cost =5\sickle{} , essential =Draught of Living Death\comma{} Veritaserum and Wolfsbane,optional =Blood\minus{}Refilling Potion\comma{} Burn\minus{}healing paste and Sleeping Serum}


%%IngredientEnd

\end{multicols}