
\chapter{Character {Archetype}}\label{C:Archetype}\index{Archetype}\index{Class|see{Archetype}}

Whilst your character is a unique individual, an adventuring soul destined for greatness, most questers find themslves falling into one of \key{Archetypes} which helps define their abilities and goals-- are they the academic who's quest for knowledge has led to unforseen consequences, or the plucky underdog trying to quit their life of crime? 

The \imp{Archetype} (also known as the {\it class}) of your character is a way of formalising these character types. The role of your character is more than simply the job they perform, it is the prism through which they see the world. Along with their personality, it guides their very essence, how they perceieve themselves and others. The \imp{Archetype} of a character therefore has a drastic impact on the roleplaying aspect of the game.
   
As well as helping to inform what kind of person your character is, the \imp{Archetype} serves to provide them with some unique skills ({\it Features}) that they acquire and improve as they grow in power, as well as some unique special actions. 

Each \imp{Archetype} is elaborated on in more detail on their own pages. A summary is found below:
\newcommand\archEntry[2]
{
	\key{ #1} &	 \parbox[t]{5 cm}{\raggedright#2}\\
}

{
\small
\begin{center}
	\begin{rndtable}{l l l}
		\bf \imp{Archetype}		&	\bf Description
		\\
		\archEntry{Artificer}{A person trained in the delicate arts of creating and producing new items, both magical and mundane.}
		\archEntry{Auror}{A dedicated warrior-investigator, who seeks out evil and brings it to justice.} 
		\archEntry{Druid}{A person dedicated to some primal aspect of nature, earning nature-related powers and gifts.}
		\archEntry{Guru}{A person possessing great wisdom and knowledge of themselves, leveraging this for feats of self-improvement and inner strength.}
		\archEntry{Outlaw}{Someone who works outside the law, employing subterfuge and deception to achieve their aims}
		\archEntry{Responder}{A healer and specialist in reversing and preventing the cause of harm.}
		\archEntry{Scholar}{Someone dedicated to knowledge, delving deep into the inner mysteries of the universe.}
		\archEntry{Sophisticate}{Someone who moves in high society, excelling in using their social graces to achieve their aims.}
		\archEntry{Warrior}{A powerful fighter, trained in all forms of combat. They excel in kicking ass, and taking names.}
	\end{rndtable}
\end{center}
\normalsize
}

\section{\imp{Archetype} Abilities} \index{Abilities!Archetype Abilities}

Each \imp{Archetype} provides an three additional \key{Abilities}, one in each of \imp{Innate}, \imp{Practical} and \imp{Knowledge} which a character can use as normal. 

Often these abilities could be duplicated by a sufficiently high roll in another field - the \imp{Pickpocket} ability associated with the \imp{Outlaw}, for example, could be achieved through a \imp{Precision (Covert)} check. However, these skills are highly tailored and even a low dice roll represents a high degree of training in this particular skill - the same as the difference between the ugly brute-force strength required to \imp{Brawl} and the weapon skills required to \imp{Skirmish}.

A character using \imp{Pickpocket} would therefore find the same action much easier than using \imp{Covert}. 

\subsection{Assigning \imp{Archetype} Abilities} \index{Character Creation!Archetype Points}

When creating a character, you automatically gain 1 dot in each of the three \imp{Archetype} abilities, and gain another 3 dots to assign freely between them.  

\section{\imp{Archetype} Equipment \& Spells}

Each archetype also grants a list of equipment which is placed into your \imp{inventory} upon creating such a character. Where a choice is indicated (by the key word `\key{or}'), you must choose only one item from the list, unless otherwise specified. 


Included in the initial selection criteria is a selection of spells that you have memorised. This usually takes the form of a number of spells memorised from the \key{Basic Spells Table} (see below), and a choice of at least one additional spell from a smaller selection related ot the abilities of the \imp{archetype}. You may immediately transcribe these spells into the \imp{Spellbook} section of your character sheet. 

If your \imp{GM} wishes to run your characters starting from the {\it very} beginnings of their magical stories, it may be appropriate for you to start with no equipment and no spells memorised - you may roleplay purchasing your first wand, and your first lessons at Hogwarts. By the end of the first session, however, you should have acquired all of your basic skills and equipment. 


\subsubsection{Basic Spells Table} \label{T:BasicSpells}

\newcommand\impIt[2]{\key{#1}	&	{\imp{#2}} \\}
\begin{center}
\begin{rndtable}{l l}
	\key{School}	&	\key{Spells} \\
	\impIt{Alteration}{Refine, Transmute}
	\impIt{Bewtichment}{Charm, Distract, Mirage}
	\impIt{Cerebral}{Communicate, Sense}
	\impIt{Conjuration}{Bind, Manifest}
	\impIt{Curse}{Disable, Disarm}
	\impIt{Elemental}{Burn, Freeze, Gust, Illuminate, Soak}
	\impIt{Hermetics}{Heal, Restore}
	\impIt{Hex}{Force, Jinx}
	\impIt{Kinesis}{Move, Repair}
	\impIt{Temporal}{Identify}
	\impIt{Warding}{Abjure, Shield}
\end{rndtable}
\end{center}


\section{\imp{Archetype} Feats} \index{Feats!Archetype Feats}

As well as granting dice-pool \imp{Abilities} and starting equipment, an \imp{Archetype} also grants you the choice of a number of \key{Feats}, which are powerful unique skills that a character unlocks as they progress. A general list of feats accessible to all characters can be found on page \pageref{S:AllFeats}, and each \imp{Archetype} grants a number of feats unique to characters following that path.

You generally start with one \imp{Feat} chosen from your \imp{Archetype} list, though your \imp{GM} may allow you to choose a more general feat. 

\section{Advanced Start}

The default assumptions listed here for the initial \imp{skills}, \imp{feats} and \imp{spells} possessed by characters assumes that your campaign is centred around novice characters, most likely characters who are just starting at \imp{Hogwarts}. If, however, your \imp{GM} wishes to use a campaign in which characters are already matured into their powers (perhaps more akin to the \imp{Fantastic Beasts} movies), then they may decide to grant you the following additional starting bonuses:

\begin{itemize}
	\item 15 \imp{Experience} points to spend as you wish, following the normal character progression rules
	\item Two additional spells from the basic spells table, \key{or} one spell from the full spell list, \key{or} 3 enchanting runes
	\item \galleon{5} to spend on items and ingredients.
\end{itemize}

\section{Changing Archetype}

Since an \imp{Archetype} represents some fundamental aspect of a character's view of themselves and their role within the world it takes something truly monumental to alter their \imp{Archetype}. 

However, there are narrative scenarios where it makes sense for a character to switch roles as a result of events within the story - perhaps an \imp{Auror} character has been wrongly framed for a crime, and after being on the run for months they have picked up aspects of an \imp{Outlaw}'s skills. 

Such an event is rare, and should only happen if driven by a compelling narrative. When this happens, you should work with your GM to determine the nature of the change. 

Perhaps you gradually shift your abilities over a period of time - the \imp{Auror} loses his \imp{Interrogate} ability but gains the \imp{Pickpocket} ability, and after another few weeks gains knowledge of the \imp{Underworld}, until eventually they are fully an \imp{Outlaw}. Perhaps after they clear their name, they must go on a redemption arc to recover their old abilities and emerge from their life of crime.

Alternatively, the nature of the change could be dramatic and sudden - a Captain America-esque transformation turns a weedy \imp{Scholar} into a mighty \imp{Warrior} overnight, the player simply transfering the character onto a new playsheet with their new abilities and moving on from their old life. 

This is a rare and momentous undertaking, and should not be treated lightly!

\section{Archetype Inspirations}

It should go without saying that the \imp{Archetypes} presented here are based on the roles played by characters within the \imp{Harry Potter} novels and related films - with a {\it healthy} dose of modification to fit in with common RPG norms and tropes. 

It might be helpful for players' understanding of the \imp{Archetype}, and their ability to roleplay them,  to understand which characters inspired the creation of the \imp{Archetypes}:

\subsubsection{Artificer}

\imp{Artificers} are masters of creating things - perhaps the most prominent examples of \imp{Artificers} in the series are the \imp{Weasley} twins. Though their personality would seem to indicate a leaning towards \imp{Outlaws}, they are repeatedly praised for their ingenious creations, most of which are of an \imp{Alchemical} nature, though the creation of \imp{Shield Hats} and \imp{Trick Wands} shows they have a flair for \imp{Enchanting} as well. 

\imp{Severus Snape}, in his guise as the `half-blood prince' also showed an incredible ability to tweak and alter established potion recipes to new ends. He would therefore be an \imp{Alchemist-Artificer} with a high \imp{Modify} rating.

\subsubsection{Auror}

Actual \imp{Aurors} abound within the \imp{Harry Potter} novels, so it is not hard to find the inspiration for such characters. 

\imp{Harry Potter} himself ends up becoming the prototype for the \imp{Aurors} - his thirst for righteousness and justice, and his preference for less-lethal methods of combat were particular inspirations. \imp{Harry} himself is not quite as level-headed, controlled and trained as a `true' \imp{Auror} might be: \imp{Harry} probably has a very high \imp{Intuition} rating, as he seems to use his gut feelings above logic.

Because of the nature of the \imp{Harry Potter} series as it reached its conclusion, most characters' classified as Aurors tended towards being a \imp{Warrior} - to make a starker difference between these two professions, the \imp{Auror} class focusses more on the problem-solving and mystery-hunting aspects of the \imp{Auror} profession.

\subsubsection{Druid}

Druids care about, and care for, the natural order of things, the natural places in the world, and the beings which live there. Perhaps the most prominent (though perhaps not the wisest or the most skilled) druid would be \imp{Rubeus Hagrid}, who has a particular affinity for the more monstrous creatures. \imp{Newt Sacamander}, author of {\it Fantastic Beasts and Where to Find Them} is also a prominent influence. 

Of course, not everything natural is plants and beasts: the stars in the night sky and the fates they guard, as well as the primal elements of Fire, Air, Earth and Water would also fall under a Druid's domain. For this reason, \imp{Sybil Trewlany} would be a celestial druid, whilst the infamous \imp{Merlin} was recognised as a powerful elemental-druid.

\subsubsection{Guru}

It might seem that the \imp{Guru} is primarily based on the \imp{monk}-like classes found in many RPG's. In fact, the main inspiration is \imp{Luna Lovegood}. 

\imp{Luna} is known for her ditsy attitude and insane beliefs, which hides an ability to dispense great wisdom. Her unconventional beliefs also inspired the idea that \imp{Gurus} are focussed on finding new and unusual ways to do things - usually by finding new and undiscovered aspects of their own abilities. 


\subsubsection{Outlaw}

Perhaps the only true `Outlaw' within the books was \imp{Mundungus Fletcher}, a reprobate lowlife and a coward - but who certainly had great knowledge of the underworld. 

However, few would doubt that \imp{Gilderoy Lockhart} was a con artist and a crook, and so would probably end up as an \imp{Outlaw} too - though he made good use of the \imp{Alternative Profession} and \imp{Play the System} feats to appear as a well-respected \imp{Sophisticate}.

\subsubsection{Responder}

\imp{Madam Poppy Pomfrey} is perhaps the only character within the series who could be classified as a \imp{Responder}, given the relative scarcity of healers or doctors within the series. 

However, note that \imp{Responders} are far more than simple doctors and nurses waiting for the injured to arrive: they also excel in the protection of others and the negation of harm. \imp{Filius Flitwick} notably cast perhaps the most powerful protective enchantments within the series (just before the \imp{Battle of Hogwarts}), and so should probably be considered a \imp{Responder}. Equally, \imp{Molly Weasley} threw herself into battle in order to protect her children from \imp{Bellatrix Lestrange}, so she could be a \imp{Responder} with the \imp{Matyr} feat.

\subsubsection{Scholar}

Most of the teachers at \imp{Hogwarts} would obviously fall under the domain of a \imp{Scholar}, but perhaps the most famous \imp{Scholar}-character would be \imp{Hermione Granger}. 

\imp{Hermione} is well-known for her vast knowledge and near-savant level of understanding in magical fields, as well as her ability to learn new things at a rapid rate. 

\imp{Albus Dumbledore} would probably also be a \imp{Scholar} - his most famous feats include the discovery of 12 different uses for Dragons blood, and hte invention of several magical doohickeys (which could conceivably make him a \imp{Artificer} - though the distinction here is the same as between a scientist and an engineer). 


\subsubsection{Sophisticate}

Sophisticates wield their social graces to achieve their own ends, as well as wealth and power (or at least the image of it). The \imp{Malfoys} would probably be \imp{Sophisticates} - though given how rarely `I'll tell my father' worked out for \imp{Draco}, relatively poor ones. 

\imp{Rita Skeeta} weaponised her journalism career to great ends, and so would be a great \imp{Sophisticate}.  

\subsubsection{Warrior}

Many characters, by the end of the \imp{Second Wizarding War} ended up as \imp{Warriors} - people like \imp{Kingsley Shacklebolt} were forceful presences on the battlefield, and many of the \imp{Death Eaters} excelled at putting down their foes as quickly as possible. 

Characters such as \imp{Grawp} and the other giants, as well as the \imp{Centaurs} that faught \imp{Umbridge} would also be warriors - though focussed on weapons and non-magical combat. 

\input{Chapters/Part1_Characters/FeatList}
