\def\Feats
{
	\feat{}{}{0}{}
}

\def\DruidFeats
{
	\feat{A Friend to All}{Whenever an ability\comma{} spell or other effect specifies that it works on \imp{Beasts}\comma{} you may also use this ability on all \imp{non\minus{}sapient} creatures\comma{} including \imp{Monsters} and \imp{Elementals}. Such creatures will also be more inclined to treat you as an ally\comma{} with only the most savage attacking you without first being provoked.}{0}{}
	\feat{Asteria’s Eyes}{At the beginning of every dawn\comma{} you perform a small ritual underneath the fading stars to divine the future. Over the next day\comma{} you use this knowledge to grant one automatic success\comma{} or impose on automatic failure\comma{} on any roll performed by a creature you can see. You may use this ability a number of times equal to your highest \imp{Affinity} rating of \imp{Cerebral} or \imp{Divination}.}{0}{}
	\feat{Barkskin}{Gain a +2 bonus to your \imp{Base Block Bonus}. You may expend this bonus as a \imp{Resist} action\comma{} automatically nullifying up to \imp{Level Seven} harm. You lose your bonus\comma{} and this ability\comma{} until you complete a \imp{Long Rest}.}{0}{}
	\feat{Cloak of Seasons}{You are magically protected from the effects of the weather and the natural environment. You are perfectly comfortable in winter's chill\comma{} summer's blazing heat or the insect\minus{}ridden swamp regardless of your clothing (or lack thereof). At the end of each \imp{Long Rest}\comma{} you may focus this aura further to gain resistance to \imp{Fire}\comma{} \imp{Electric} or \imp{Cold} damage.}{0}{}
	\feat{Dryad’s Embrace}{When you perform any check (including \imp{spellcasting}) which targets a plant\minus{}based entity\comma{} or which seeks to learn about such an entity\comma{} you gain one additional auto\minus{}success.}{0}{}
	\feat{Exuding Aura}{You may attune yourself to your favoured aspect of nature\comma{} exuding an aura which influences the minds of others – perhaps a sweet pine smell calms them\comma{} or animal pheremones send them into a frenzy. A number of times per day equal to your \imp{Nurture} rating\comma{} you gain +2d on all \imp{Social} checks made against people within 2m of you for the next hour. You may expend a \imp{Fortitude} point to impose the \imp{Confused} or \imp{Enraged} status onto a target you can touch as a \imp{Major Action}\comma{} with a \imp{Power} equal to twice your \imp{Nuture} rating.}{0}{}
	\feat{Nymph’s Fury}{Channeling the power of primal\comma{} elemental spirits grants you additional power. When casting a spell from the \imp{Elemental} discipline\comma{} you gain one additional auto\minus{}success. Learning spells from the \imp{Elemental} discipline takes half the usual amount of time.}{0}{}
	\feat{Organic Repose}{When completing a \imp{Short Rest}\comma{} you can choose a single being to gain the benefits of a \imp{Long Rest}. You can use this ability a number of times per day equal to your \imp{Nurture} rating\comma{} but each being can only benefit from this ability once per day.}{0}{}
	\feat{Satyr Spirit}{When casting a spell or attempt to \imp{Commune} with a \imp{Beast}\comma{} or attempt to use a \imp{Knowledge} check to learn about such a creature\comma{} you gain one additional auto\minus{}success.}{0}{}
	\feat{Watchful Guardian}{A number of times per day equal to your \imp{Commune} rating\comma{} you may expand your senses to the area up to 50m around you. For 30 seconds\comma{} you may choose to see through the eyes of all the nearby \imp{Beasts}\comma{} listen through their ears\comma{} or to feel the sensation of footsteps upon the web of roots and plants – you lose your ability to see\comma{} hear\comma{} or feel through your own senses respectively. You can choose to focus on the sensations transmitted by a single plant or animal\comma{} or expand your focus to search over the entire area.}{0}{}
}

\def\SophisticateFeats
{
	\feat{A Little Bird Told Me}{Whilst in conversation with someone\comma{} provided that you have met\comma{} or have heard of them in the past\comma{} you may recall an embarrassing bit of information\comma{} or incriminating secret about them. You may choose to reveal this information\comma{} or keep it secret for later. You may use this ability a number of times per day equal to your \imp{Society} rating.}{0}{}
	\feat{Brazen}{You are so brash and bold in your approach that you can simply breeze past an error\comma{} playing it for laughs\comma{} or simply ignoring it altogether. Whenever you perform a \imp{Social} check\comma{} you may treat one \imp{Catastrophe} as a normal\comma{} benign failure. By expending a \imp{Fortitude} point\comma{} you may extend this to all \imp{Catastrophes} rolled.}{0}{}
	\feat{Charmed Life}{A number of times per day equal to your \imp{Wealth} rating\comma{} you can negate the negative consequences of a \imp{Catastrophic} failure suffered by you or your allies\comma{} or grant a +1d bonus on any check that you can see occurring.}{0}{}
	\feat{Distracting Shout}{Your forceful presence extends onto the battlefield – whilst in combat you can use a \imp{minor action} to select a target which has not yet declared their action within 10m and perform some action to get their attention. You may either force them to focus all attacks on you this turn\comma{} {\bf or} distract them\comma{} imposing a 1d penalty on any action they take.}{0}{}
	\feat{Eyes on the Prize}{Whenever you perform a \imp{Major Action} which requires a roll\comma{} you may take a 1d penalty to \imp{Take Stock} as an instantaneous action. You also gain +1d to counteract acts of sleight\minus{}of\minus{}hand and other such chicanery.}{0}{}
	\feat{Magical Conversation}{You are able to modify the incantations required for your spells such that you can slip them into conversation without anyone recognising them as such. You may cast spells on a conversation partner without the spellcasting being noticed or considered an aggressive act.}{0}{}
	\feat{Mesmerising Presence}{You may use your alluring charm to slightly hypnotise a person\comma{} gaining +1d to social checks with them and imposing the \imp{Confused} status upon your target. They remember talking to you\comma{} but they cannot recall what you talked about or why they said what they did. You may use this ability a number of times equal to your \imp{Bamboozle} rating\comma{} before requiring a \imp{Long Rest}.}{0}{}
	\feat{Natural Leader}{You're a natural born leader. While not everyone will simply surrender authority to you\comma{} they'll consent to "follow your lead." Reduce the DV of any check related to leadership or commanding others by 2.}{0}{}
	\feat{One for you\comma{} two for me}{Whenever you or your allies gain an amount of \imp{Galleons}\comma{} you gain one additional coin.}{0}{}
	\feat{Poker Face}{You are an expert at hiding your true feelings – beings cannot rely on the usual cues to read your demeanour or true motivation. Any \imp{Insight} attempts against you have a DV 2 higher than normal\comma{} and effects which would automatically detect lies or deception do not work on you.}{0}{}
	\feat{Sue For Peace}{You excel at halting violence when it breaks out. Whenever you \imp{Surrender}\comma{} it is automatically accepted. When you request a foe surrender or flee\comma{} your DV is 2 lower than normal.}{0}{}
	\feat{Unbreakable Vow}{When you willingly shake on a deal or contract with another sapient being both you and your partner are bound together by a magical oath. If either of you breaks the contract\comma{} the offending party takes the maximum amount of \imp{Harm} and falls into a \imp{Critical Condition}\comma{} alerting the other.}{0}{}
}

\def\ResponderFeats
{
	\feat{A Shoulder to Cry On}{People innately trust you more than they would most others. If you help \imp{Heal} or otherwise care for a person\comma{} they are likely to share their secrets with you – attempts to glean informaiton from your patients have a DV 3 lower than usual.}{0}{}
	\feat{Beacon of Life}{Your \imp{Hermetics} spells now channel so much positive energy that they deal \imp{harm} to unliving and evil creatures such as \imp{Demons}\comma{} \imp{Abominations}\comma{} \imp{Phantasms} and \imp{Undead}. When you deal harm using this ability\comma{} you restore health to yourself equal to half the damage dealt.}{0}{}
	\feat{Combat Medicine}{You know the basics of helping others and mainting life – even whilst under heavy time pressure. Using a \imp{First Aid Kit} no longer takes a \imp{Short Rest} for you – instead you may do so as a \imp{Minor Action}. 

In addition\comma{} using a \imp{First Aid Kit} during a \imp{Short Rest} does not expend the kit.}{0}{}
	\feat{Emergency Intervention}{When performing a \imp{Healing} check\comma{} or a \imp{Defensive} check you may choose to automatically roll the maximum number of successes. If an enemy reduces the power of this action to zero\comma{} you (or your patient\comma{} as appropriate)\comma{} fall into the \imp{Critical Condition} status. You cannot use this ability again until you take a \imp{Long Rest}.}{0}{}
	\feat{Healer}{Whenever you restore Health to a being\comma{} or remove a negative status effect\comma{} gain one additional auto\minus{}success. A number of times per day equal to your \imp{Steady Hand} rating\comma{} you may reroll any \imp{Catastrophe} dice rolled during such a check.}{0}{}
	\feat{Matyr}{Whenever an ally within 3m would take damage\comma{} you may use an instantaneous action to move towards them and transfer the damage to yourself\comma{} performing the \imp{Resist} yourself with a +1d bonus. You may use this ability a number of times per day equal to your \imp{Triage} rating.}{0}{}
	\feat{Plague Doctor}{As a \imp{Major Action}\comma{} you release a virulent pathogen around you\comma{} infecting all those within 5m of your current position (you may expend a \imp{Fortitude} point to exclude any number of allies). You may choose the effect of the pathogen (i.e. \imp{Blinded}\comma{} \imp{Confused}\comma{} \imp{Poisoned}\comma{} \imp{Enraged}\comma{} \imp{Exhausted} or \imp{Immobilised})\comma{} which has a \imp{power} equal to 3 + your \imp{Pathology} rating. Targets \imp{resist} this effect at the end of every \imp{Cycle}. You can use this ability a number of times equal to your \imp{Pathology} rating before requiring a \imp{Long Rest}.}{0}{}
	\feat{Preventative Treatment}{You gain +2d to any \imp{Defensive} actions used to reduce the effectiveness of an incoming attack. If you reduce the \imp{Power} of an attack to zero\comma{} the target(s) of the attack gain 1 point of healing.}{0}{}
	\feat{Red Cross}{By expending a \imp{Fortitude} point\comma{} you may use a \imp{Minor Action} to designate a target within \imp{Wandtip} range as a non\minus{}combatant. Any being which attempts to harm the designated target (either with a targeted attack\comma{} or an Area\minus{}of\minus{}Effect attack) must first perform a \imp{Willpower (Conviction)} check (or similar) with a DV equal to 5 + your \imp{First Aid} rating. On a failure\comma{} the attack falters and the attacker’s turn ends. This effect lasts until the target re\minus{}enters combat.}{0}{}
	\feat{Stabilising Presence}{When a target within 10m falls into the \imp{Critical Condition} status\comma{} you may instead place them into a \imp{Critical But Stable} condition as an instantaneous action. Each time you do so\comma{} perform a DV 9 \imp{Vitality (First Aid)} check: on a failure\comma{} you take a level of \imp{Exhaustion}.}{0}{}
	\feat{Warden}{Whenever you use a \imp{Major Action} to restore \imp{Health} to a being\comma{} or remove a negative  status effect\comma{} you may use an \imp{instantaneous} reaction to cast a defensive spell from the \imp{Warding} discipline. You can do this a number of times equal to your \imp{Triage} rating\comma{} before needing a \imp{Long Rest}}{0}{}
}

\def\ScholarFeats
{
	\feat{Absorb Information}{You have a near\minus{}eidetic memory\comma{} and can accurately recall any information you have seen\comma{} read\comma{} or heard about in the past 24 hours. In addition\comma{} you need to spend half the usual time in order to learn a new spell\comma{} or memorise an enchanting rune\comma{} and automatically succeed on the final memorisation roll for spells.}{0}{}
	\feat{Adapt and Adjust}{Whenever you target an ally’s spell in order to alter its effects\comma{} you gain one additional auto\minus{}success. A number of times per day equal to your \imp{Collaboration} rating\comma{} you may cast such a `modifying spell’ as a \imp{Minor Action}.}{0}{}
	\feat{Flexible Knowledge}{You may spend a day completely immersing yourself in a new set of knowledge and expertise. Convert a number of your \imp{Knowledge} dots back into experience points. You must then reassign at least this number of experience points back into your \imp{Knowledge} abilities in any new combination you wish.}{0}{}
	\feat{Learn From Failure}{When performing a check of any kind\comma{} for every consecutive previous roll (of any kind) failed by you or your allies\comma{} you gain +1d (up to a maximum of your \imp{Stubbornness} rating).}{0}{}
	\feat{Library Lover}{When you perform an intelligence\minus{}based check whilst in a library\comma{} or similar repository of knowledge\comma{} the dice associated with your \imp{Intelligence} are all counted as successes. You need only roll your \imp{Ability} dice.}{0}{}
	\feat{Magical Prodigy}{When initiating a \imp{Spellcasting} action\comma{} you may automatically reduce the DV required to cast it by 2. You may do this a number of times equal to your \imp{Intelligence} rating before you require a \imp{Long Rest}.}{0}{}
	\feat{Master of the Mind}{When an action would interrupt you casting a spell requiring continuing concentration\comma{} the DV to remain focussed is 2 lower than normal. You also gain +2 to your \imp{Base Endure Bonus}.}{0}{}
	\feat{Navigator’s Knack}{You are able to perfectly keep track of time even whilst asleep\comma{} cannot get lost except by magical means\comma{} can reproduce a map of anywhere you have been\comma{} and can always pinpoint your location anywhere on the globe given reasonable information i.e. access to the stars. In addition\comma{} if any magical effect alters your position in space\comma{} or removes you from your normal plane of existence\comma{} you are able to feel and notice this happening.}{0}{}
	\feat{Novel Technique}{Whenever you use a spell in a new or novel fashion\comma{} you gain +2d for the spellcasting effort. If you use this technique multiple times\comma{} you gain only +1d for as long as it remains `novel’ to the outside world.}{0}{}
	\feat{Subject Expertise}{Choose a spell discipline\comma{} a type of creature\comma{} or another kind of action or area of knowledge: you are considered an up\minus{}and\minus{}coming expert in this field. When performing a check of any kind to target the subject of your knowledge\comma{} use the associated skills (such as a spellcasting check) or to research more information about the subject of your expertise\comma{} you gain one additional auto\minus{}success. 

During a prolonged period of \imp{Downtime}\comma{} you may shift your choice of expertise to any other field.}{0}{}
	\feat{Well Read}{You hold in your brain a simply incredible amount of information\comma{} you may use some of this vast knowledge to gain +3d on one \imp{Knowledge} check. You can use this ability a number of times equal to your \imp{Speculation} rating before needing a long rest.}{0}{}
}

\def\ArtificerFeats
{
	\feat{Adept Alchemist}{Whenever you undertake a potion\minus{}mixing effort\comma{} you gain one additional auto\minus{}success. You may also `discover’ one common ingredient which has up to three properties of your choosing\comma{} discussing this with the GM.}{0}{}
	\feat{Apothecary}{Whenever you take a \imp{Short Rest} whilst in possession of a \imp{First Aid Kit} or an \imp{Alchemy Set}\comma{} you can brew a quick healing potion\comma{} gaining a base\minus{}level \imp{Wiggenweld Potion} (see page \pageref{P:Wiggenweld}). You cannot store more than 5 such potions using this ability.}{0}{}
	\feat{Defensive Gadgets}{At the end of every \imp{Long Rest}\comma{} you conceal a number of defensive doohickeys on your sleeve equal to your \imp{Danger} rating. You may expend one of these devices as an instantaneous action to gain the maximum number of successes on a single \imp{Resist} roll.}{0}{}
	\feat{Discerning Eyes}{At the end of every \imp{Long Rest}\comma{} roll a DV 7 check using only your \imp{Analyse} pool (min 1 success). You may expend one of these successes as an instantaneous action to learn about a target as if you had cast the \imp{Identify} spell at \levelThree{} level (though this does not count as a \imp{spellcasting} effort\comma{} and cannot be percieved by others). You may increase the level of the effect by expending additional successes.}{0}{}
	\feat{Expert Enchanter}{Whenever you undertake an enchanting effort\comma{} you gain one additional auto\minus{}success. You may also choose 5 new runes to learn instantly.}{0}{}
	\feat{Fireworks Guru}{Whenever you attempt to cause an explosion\comma{} either magical or mundane\comma{} you gain +1d to the roll. A number of times per day equal to your \imp{Modify} rating\comma{} you may also choose to double the radius of the explosion\comma{} alter its form to take on a specific shape or form\comma{} or turn it into an \imp{Implosion}.}{0}{}
	\feat{Hidden Work}{When you complete an \imp{Imbuing} or \imp{Crafting} project\comma{} you
may expend an additional hour to make your work completely hidden from inspection.
Runes are hidden and alchemical creations can appear as mundane
fluids. Only upon activation\comma{} or a spell such as \imp{Identify}\comma{} can the true
nature be divined.}{0}{}
	\feat{Idiosyncratic Inventions}{You know every oddity and quirk of your own creations: when using them\comma{} you gain one additional auto\minus{}success on any rolls required. When completing an artificing project\comma{} you may also choose to make it impossible for anyone other than you to use the item.}{0}{}
	\feat{Master Mechanist}{Whenever you undertake a tinkering or mechanical manufacturing effort\comma{} you gain one additional auto\minus{}success. You may also stray further from `realistic’ or scientific constructions and may handwave slightly more vigorously over the workings of your constructions.}{0}{}
	\feat{Quick Worker}{You take only half the normal time to perform feats of \imp{Crafting} and \imp{Imbuing} – you may perform checks every 3 hours\comma{} rather than every 6.}{0}{}
	\feat{Siege Master}{When dealing damage to or attempting to bypass a building\comma{} structure\comma{} wall\comma{} door or other such solid object\comma{} you gain two additional auto\minus{}successes.}{0}{}
	\feat{Thick Skin}{Years of accidents and lab mishaps have left you with a superhuman level of resilience. When you are afflicted by \imp{Fire}\comma{} \imp{Crushin}\comma{} \imp{Acid} or \imp{Poison} damage you may declare yourself to be \imp{Resistant} to the damage for the remainder of the turn. You may do this a number of times per day equal to your \imp{Danger} rating.}{0}{}
}

\def\WarriorFeats
{
	\feat{All Guns Blazing}{When making an attack against a small group of people\comma{} you can truly throw yourself into the attack\comma{} expending a \imp{Fortitude} point to take them all on at once. As a \imp{Major Action}\comma{} take a single attack against a number of beings (up your \imp{Rage} score) within range.}{0}{}
	\feat{Blind Rage}{When using a \imp{Rage} action to attack\comma{} you ignore all dice penalities due to injuries\comma{} and you deal an additional level of \imp{Harm}. However\comma{} you take a 1d penalty on all \imp{Resist} checks made next \imp{Combat Cycle}.}{0}{}
	\feat{Calculated Strikes}{A number of times per day equal to your \imp{Tactics} rating\comma{} you may perform one additional attack without expending a \imp{Fortitude} point. You cannot use this ability more than once on a single \imp{Combat Cycle}.}{0}{}
	\feat{Chivalrous Defence}{At any point prior to or during your action in the turn cycle\comma{} you may donate up to two dice to a creature within 2m of you that you can see. This creature may use this additional dice on any \imp{Resist} actions they take until the end of the combat cycle. You take a dice penalty on any attacks or skill checks (but not your own \imp{resists}) you make this turn equal to the number of dice donated.}{0}{}
	\feat{Command the Field}{Whenever your group performs a \imp{Reflex} roll to initiate combat\comma{} you may increase the value of one roll by an amount equal to your \imp{Tactics} rating. If the target is not \imp{surprised}\comma{} they may immediately make a full movement action before the first combat cycle begins.}{0}{}
	\feat{Duelist}{When fighting against a single foe\comma{} you gain one auto\minus{}success on all attack rolls and Resist actions. You cannot be \imp{Surprised} by a single attacker.}{0}{}
	\feat{Know Your Enemy}{Upon seeing a person\comma{} you can size them up and see what they’re capable of. You may learn their preferred {\it modus operandi} – their favoured weapons or spells\comma{} any notable weaknesses\comma{} if they prefer manipulation to fighting\comma{} and any other information the GM feels is relevant. You may use this ability a number of times per day equal to your \imp{Tactics} rating.}{0}{}
	\feat{Mighty Deeds}{Your stories of valour and heroism enrapture all those who hear them. By spending around 10 minutes telling these tales\comma{} you can distract huge numbers of people\comma{} or you can focus on an individual\comma{} rendering them \imp{Charmed} by you.}{0}{}
	\feat{Mind over Matter}{You may \imp{Endure} the damage caused by physical \imp{harm}. Whilst your \imp{Endure} rating remains above zero\comma{} dice penalties due to \imp{Harm} are one level less serious.}{0}{}
	\feat{Never Give In}{As a minor action\comma{} you take a moment to clear your head and readjust your armour. Reduce the level of \imp{Drain} in all defense statistics to 0. You must complete a \imp{Long} rest before using this ability again.}{0}{}
	\feat{Proud Leader}{Whenever you use a \imp{Minor Action} to \imp{Command} \minus{} to issue an instruction or provide guidance \minus{} if that action is a success\comma{} you regain a \imp{Fortitude} point. You may do this a number of times per day equal to your \imp{Command} rating.}{0}{}
	\feat{Student of War}{If you study\comma{} read up on and otherwise prepare for a target before engaging them in combat\comma{} the DV of all combat actions made against them is reduced by 1. A \imp{Command} \imp{MInor action} grants this bonus to all allies within 20m of you until the end of the next \imp{turn cycle}.}{0}{}
}

\def\GuruFeats
{
	\feat{Altered Consciousness}{You have attuned your mind to a different way of thinking\comma{} making it harder to infiltrate your mind. You are considered \imp{Resistant} to psychic damage\comma{} and effects to alter your mind have a DV two higher than normal.}{0}{}
	\feat{Chi Siphon}{Whenever you deal damage to a being using a \imp{Brawl} action (or a melee spell attack)\comma{} you heal yourself by 1 level of harm. You may also allocate a number of your successes to increasing this effect by 1 level each (thereby reducing the damage dealt). If the attack damage is reduced to zero by a successful \imp{Resist}\comma{} the healing effect is negated.}{0}{}
	\feat{Like the Wind}{Perform a DV 6 \imp{Fitness (Glide)} check. For every success\comma{} you can run\comma{} leap or parkour 2m across a body of water\comma{} a gaping chasm\comma{} or up a vertical surface. This uses an entire \imp{Movement} action.}{0}{}
	\feat{Meditative Purge}{You may expend a \imp{Fortitude} point as an instantaneous action to enter a meditative state\comma{} ending all ongoing status effects on your body: \imp{Poisons} are purged\comma{} \imp{Fear} is banished\comma{} and \imp{Paralysis} wears off. This does not effect status effects imposed by physical phenomena (i.e. you cannot untie ropes giving the \imp{Trapped} status)\comma{} and you must be conscious to use this ability.}{0}{}
	\feat{Metamorphmagus}{You have imbued some magic deep into your body\comma{} and are able to alter your appearance at will. A number of times per day equal to your \imp{Ego} ability you can alter your hair\comma{} the shape of your face\comma{} the colour of your eyes – and even change your height and weight to a degree. This ability is not precise enough to truly mimic a real person\comma{} and after an hour you begin to shift back to your normal form.}{0}{}
	\feat{One Of A Kind}{You’re a bit weird – but that’s OK. It lets you connect with other weirdos\comma{} outcasts\comma{} reprobates and other people lying a bit away from the average. When making a \imp{Social} check with such an entity\comma{} use your \imp{Kindness} rating in addition to whichever \imp{ability} you were already using – if using \imp{Kindness} already\comma{} double the rating for this check.}{0}{}
	\feat{Open Mind}{The way that things have always been done is not always the only (or even the best) way. A number of times per day equal to your \imp{Wisdom} rating\comma{} you may use a completely different skill\comma{} tool or ingredient for a given task. You may substitute almost any \imp{Ability} for a check\comma{} use any \imp{Tool} to complete a task\comma{} or use a random \imp{Ingredient} in a potion.}{0}{}
	\feat{Out of Body Experience}{Whilst unconscious or asleep\comma{} your spirit remains awake and aware of your surroundings even as you gain the benefits of rest. Your spectral self can move up to 10m away from your body\comma{} and can see and hear as well as you normally can. You can expend a \imp{Fortitude} point to instantly end the \imp{asleep} status and take an action.}{0}{}
	\feat{Piercing Insight}{When you gain at least one success on a \imp{Insight} check against a person\comma{} you learn enough hidden information about them that all further checks against them have a DV 1 lower than normal.}{0}{}
	\feat{Self Improvement}{Whenever you cast a spell with a range of \imp{Self}\comma{} gain one additional auto\minus{}success. In addition\comma{} a number of times per day equal to your \imp{Ego} rating\comma{} when you cast a spell with a range of \imp{Self} which would impact your combat ability\comma{} you may immediately take a melee attack on a foe in range.}{0}{}
	\feat{Silent Step}{If you know the \imp{Apparate} spell\comma{} you may cast it as a silent\comma{} wandless action using your \imp{movement}\comma{} rather than a \imp{major action}. You can do this a number of times per day equal to your \imp{Glide} ability.}{0}{}
	\feat{Wise Teacher}{As a \imp{minor action}\comma{} you take a second to talk to and inspire an ally within 2m: donating your \imp{Widsom} pool to them. They may add this pool to any check they make next turn cycle. You may use this action multiple times per cycle\comma{} but each character can only benefit from the effect once.}{0}{}
}

\def\OutlawFeats
{
	\feat{Alternative Profession}{You may choose any other \imp{Feat} from the list of another \imp{Archetype}. If the chosen \imp{Feat} keys off an ability you do not have\comma{} instead use the \imp{Savvy} ability. In addition\comma{} you may pass yourself off to others as an authentic member of your chosen \imp{Archetype}.}{0}{}
	\feat{Cover Identity}{Given enough time – perhaps a day or two – you can forge yourself a completely new identity\comma{} with the necessary paperwork and credentials to reasonably pass as whoever you desire. This may not stand up to high\minus{}level scrutiny\comma{} but most people should be easily fooled.}{0}{}
	\feat{Eyes of Greed}{You have a knack for spotting things of value. You gain +2d on any checks to look for valuable items. A number of times per day equal to your \imp{Pickpocket} rating\comma{} you may automatically determine the value of a given item that you can see.}{0}{}
	\feat{Fight Dirty}{If you use a \imp{Called Shot} to target a foe’s tender bits\comma{} pull hair\comma{} or throw sand in their eyes\comma{} etc. and the attack is successful\comma{} the target takes a dice penalty on all attacks taken next turn\comma{} equal to your \imp{Brawl} rating.}{0}{}
	\feat{Freerunning}{Your base movement speed is increased to 5\comma{} your climb speed is equal to your movement speed and your jump distance is doubled. You gain +1d on any \imp{Resist} checks against effects to slow you down or trap you.}{0}{}
	\feat{Hidden Weapon}{You can draw a previously unknown small blade from a fold in your robes\comma{} or a hidden pocket\comma{} and then use it as an instantaneous action. You can use this ability a number of times per day equal to your \imp{Covert} rating.}{0}{}
	\feat{Innocent Face}{You are always thought of as an honest and good soul. If you do something wrong which isn’t immediately attributed to you\comma{} it will most likely be blamed on something else. As long as you’re not caught red\minus{}handed killing puppies\comma{} people will try to excuse your actions and move on from your misdeeds.}{0}{}
	\feat{Naturally Shifty}{Doing unscrupulous deeds comes as naturally to you as breathing – gain one additional auto\minus{}success on any \imp{Covert} action. In addition\comma{} whilst you are outside of bright light\comma{} all \imp{Covert} actions have a DV one lower than normal.}{0}{}
	\feat{Play the System}{You know every trick and loophole in the rules and regulations. Whenever you perform a \imp{Social} check against a figure of authority\comma{} you may gain a +2d bonus. You can use this ability a number of times equal to your \imp{Savvy} rating before you need a long rest.}{0}{}
	\feat{Smuggler}{You may designate one small\minus{}ish item on your person (or a larger item within a room) as being hidden from view – it cannot be found or unwillingly removed from your person except through extreme measures. In addition\comma{} you must pay only half as much to bribe someone (\galleon{1} bribes become free).}{0}{}
	\feat{Surprise Attack}{Whenever you attack a target from a position where they cannot see you\comma{} or if they are distracted or \imp{incapacitated} in some way\comma{} the target is considered \imp{suscpetible} to the attack.}{0}{}
	\feat{Turning Tail}{A number of times per day equal to your \imp{Underworld} rating\comma{} you can learn of any hidden passages or escape routes that you may have heard about – or at least recall if any might exist nearby. You gain +2d on any rolls required to escape or otherwise flee from a foe.}{0}{}
}

\def\AurorFeats
{
	\feat{Ambush}{When you attack from hiding\comma{} spring a trap or successfully orchestrate
an ambush (either combative or social)\comma{} if the total number of successes on your first roll is less than half the number of dice rolled\comma{} you may instead use that number.}{0}{}
	\feat{Arcane Detective}{When performing an investigation\comma{} you notice if a spell has been cast nearby in the last week and may determine which spell school it belonged to. By expending a \imp{Detective’s Toolset}\comma{} you may learn exactly what spell\comma{} and how long ago it was cast.}{0}{}
	\feat{De\minus{}escalation Training}{Having been trained to capture and contain\comma{} when you take an action to contain\comma{} constrain\comma{} bind\comma{} trap or disarm a foe\comma{} rather than inflict damage\comma{} you gain +1d to the effort. When a target within range attempts to escape from their bindings\comma{} you may expend a \imp{Fortitude} point as an instantaneous action\comma{} before the check is made\comma{} to cause the attempt to fail.}{0}{}
	\feat{Deductive Senses}{Whenever a creature that you can see goes invisible\comma{} or hides\comma{} perform a DV 8 \imp{Insight (Tracking)} check as an instantaneous action. For every success\comma{} you remain aware of the target’s position (as if it were not hidden) for an additional \imp{Combat Cycle}.}{0}{}
	\feat{Fancy Footwork}{You may use an \imp{Minor action} to expend a \imp{Fortitude} point to confuse your foes with some feat of athletics and maneouvering\comma{} causing them to attack each other. Nominate two enemies within range – next turn cycle\comma{} the first of these two to take an action will attack the other\comma{} instead of their intended target.}{0}{}
	\feat{Forensic Hunter}{You gain one automatic success on any check to survey a room\comma{} check for traps or clues and otherwise investigate physical locations. You may \imp{Expend} a \imp{Detective’s Toolkit} to roll the maximum number of successes on an \imp{Investigation} check.}{0}{}
	\feat{Insightful Gaze}{You can automatically detect when someone is lying to you by telling you deliberate falsehoods. A number of times per day equal to your \imp{Interrogate} ability\comma{} you may use a \imp{Minor Action} to learn a hidden secret or a weakness of a target you can see.}{0}{}
	\feat{Lucid Reality}{A number of times per day equal to your \imp{Intuition} ability\comma{} you can use a \imp{Minor Action} to become instantly aware of the presence of any illusions and other reality or memory altering effects around you – though not their nature or precise location.}{0}{}
	\feat{Mental Conditioning}{You gain +3d against all checks to resist unnatural mental manipulation\comma{} and may expend a \imp{Fortitude} point to end an ongoing mental effect such as \imp{Charmed}.}{0}{}
	\feat{Rapid Reflexes}{You may choose to use either your \imp{Speed}\comma{} \imp{Intuition} or \imp{Alertness} abilities to contribute to your \imp{Reflex Roll}. When performing a \key{Reflex} roll\comma{} you may roll the dice twice and take the largest value.}{0}{}
	\feat{Unwavering Focus}{Once per day you may expend a \imp{Fortitude} point to reroll all \imp{Catastrophe} dice you rolled\comma{} declaring this action after the roll has been performed\comma{} but before the outcome has been narrated.}{0}{}
}

\def\AllFeats
{
	\feat{Animagus}{As an exceptionally powerful Thaumaturge\comma{} you have learned to shift your shape into that of an animal. By expending a \imp{Fortitude} point\comma{} you may instantly assume the physical attributes of your `spirit animal’. This animal is (usually) the same as your \imp{Patronus} and can only be changed if your undergo a profound change on a spiritual level. Whilst in this form\comma{} you retain your mental state\comma{} but all your physical statistics and abilities are replaced by those of the form you take. 

You may choose to revert back to your human form at any time\comma{} and you do so automatically if you are reduced to a \imp{Critical Condition} whilst in bestial form – upon transforming back you \imp{stabilise}\comma{} but do not recover any health you might have lost.}{1}{\imp{Alteration} (\fiveCape{})}
	\feat{Armour Piercing}{When a target attempts to block your attacks\comma{} their armour takes an additional level of \imp{Drain}: a \imp{full\minus{}round block} incurs one level of drain\comma{} and \imp{quickblocking} incurs two levels.}{0}{}
	\feat{Crash Course}{You study a crash course in a selection of 10 abilities you previously had no skill in\comma{} giving you a basic level of knowledge. Choose up to 10 \imp{Abilities} with a \emptyCape{} rating\comma{} and gain 1 dot in each of them.}{0}{}
	\feat{Elemental Attunement}{You feel a particular affinity for one of the elements (Fire\comma{} Water\comma{} Ice\comma{} Earth\comma{} Air\comma{} Lightning\comma{} etc.) deep within your bones. When casting a spell to manipulate\comma{} create or otherwise effect your chosen element\comma{} you gain +1d. You also gain +1d to any check to \imp{resist }damage caused by your element.}{1}{\imp{Elemental} (\threeCape{})}
	\feat{Helping Hand}{You are so proficient in helping out your allies that your `help’ action gives +3d\comma{} rather than +1.}{0}{}
	\feat{Innate Trick}{As a witch or wizard\comma{} the chaotic force of magic flows within your veins. You have learned to harness this magic in some innate way beyond the usual spellcasting. This effect is usually minor (something a Muggle could put down to an act of trickery or showmanship)\comma{} and often forms the basis of a parlour trick. 

You might be able to summon a small flame from your finger\comma{} make your eyes into burning coals or deep black voids\comma{} play a stirring soundtrack whenever they engage in a fight\comma{} know the name of every individual you meet\comma{} or some other marvellous but ultimately slightly inconsequential feat that you could imagine being the focus of conversation at a party. 

No rolls are needed to use this ability\comma{} and the GM has a veto if this tool is being used in an inappropriate fashion. {\bf This ability costs only 4 \imp{EXP}.}}{0}{}
	\feat{Instinctive Defence}{Whilst you have a \imp{wand} equipped and are able to cast spells\comma{} you gain a +2 bonus to all \imp{base defence bonuses}.}{0}{}
	\feat{Jack\minus{}of\minus{}all\minus{}Trades}{You have a surprising amount of miscellaneous skills\comma{} knowledge and abilities that you have acquired over your life\comma{} and are often able to surprise your allies with something pulled from your sleeve. 

Each day\comma{} you get 4 free dots\comma{} which you may temporarily allocate to \imp{Abilities} as and when you need them\comma{} though you may not increase any ability to more than 5 dots. You may use this enhanced ability for the next hour\comma{} before the effect wears off. You regain your dots when you complete a \imp{Long Rest}.}{0}{}
	\feat{Light Sleeper}{You need much less sleep than others\comma{} and can go from asleep to awake in a blink of an eye. You gain the benefits of a \imp{Long Rest} after only 4 hours\comma{} and the effects of \imp{Exhaustion} are always one level less severe. Any \imp{Alertness} checks called for whilst asleep have the DV reduced by 3.}{0}{}
	\feat{Loyal Companion}{You have an animal ally which is eternally loyal and devoted to you\comma{} and can carry out simple tasks: a `\imp{familiar}’. This familiar is a well trained pet and will follow simple orders\comma{} though they cannot communicate back. In addition\comma{} your bond provides you with the following bonus:


\begin{rndtable}{l l}
\key{Animal} & \key{Effect} \\
\animal{Cat}{You can expend a \imp{Fortitude} point to get one auto\minus{}success on all \imp{stealth} checks for 1 minute}
\animal{Ferret}{+1 to your \imp{Base Dodge Bonus}}
\animal{Owl}{You can see far further than a normal human\comma{} and can see clearly in dim light}
\animal{Rat}{Get +1 to your \imp{Base Endure Bonus} }
\animal{Raven}{You can mimic the voice of a person you are familiar with}
\animal{Toad}{You are \imp{Resistant} to \imp{Poison} damage}
\animal{Tortoise}{+1 to your \imp{Base Block Bonus} }
\end{rndtable}

Pets have a single health diamond\comma{} and fall into the \imp{Critical Condition} status like a normal character. If your pet dies or is permanently lost\comma{} you may bond with a new creature\comma{} changing your bonus to match.}{1}{Kinship (\twoCape)}
	\feat{Martial Arts}{You are a master of unarmed combat\comma{} making your hands into lethal weapons. Unarmed strikes now deal an additional level of damage (1 + \# Successes)\comma{} with a reduced DV of 4. In addition\comma{} before making an attack roll\comma{} you may expend a \imp{Fortitude} point to automatically roll all your \imp{Brawl} dice as successes.}{1}{Brawl (\threeCape)}
	\feat{Moving Target}{On any turn during which you move more than half your movement\comma{} your \imp{quickdodge} checks do not incur \imp{Drain} and you gain +2 to your \imp{Base Dodge Bonus}.}{0}{}
	\feat{Numbed to Pain}{When you expend a \imp{Fortitude} point to ignore the negative effects of \imp{Harm}\comma{} the effect lasts for one hour\comma{} rather than just the next round. During this time\comma{} effects which would cause immobilising pain can be ignored.}{1}{Vitality (\threeCape)}
	\feat{Parry Master}{Carrying a melee weapon grants a +2 to your base \imp{block} bonus\comma{} in addition\comma{} if you \imp{Block} an incoming melee attack to a power of \imp{zero}\comma{} you may expend a \imp{fortitude} point to \imp{disarm} your attacker.}{0}{}
	\feat{Psychic Awareness}{Your mind is especially attuned to those of others\comma{} and you can naturally sense the shift induced when a psychic power alters or interacts with minds. Whenever a psychic effect such as mind reading\comma{} memory modification\comma{} or magic which alters emotions and allegiances is used on a target within 5m of you\comma{} you are instantly aware of this – you may expend a \imp{fortitude} point to learn the target of the spell\comma{} as well as the caster and the intent of the spell.}{1}{\imp{Kindness} (\threeCape{})}
	\feat{Ritualist}{You are a strong believer that the most powerful magic is performed with large groups\comma{} in elaborate rituals\comma{} with chanting\comma{} incense and possibly a pentagram or two. Whenever you invoke a \imp{Ritual} to cast a spell\comma{} you gain one automatic success for every 3 members of the ritual (max +5d).}{1}{\imp{Occultism} (\threeCape{})}
	\feat{Second Chances}{You may re\minus{}roll any number of dice on a single check\comma{} but must keep the new result. You cannot use this ability again until you suffer a \imp{Catastrophic Failure}\comma{} or take a \imp{Long Rest}.}{0}{}
	\feat{Signature Spell}{You have a spell which is considered your `signature move’\comma{} chosen when you take this feat. When casting this spell\comma{} any rolled \imp{catastrophes} are counted as normal failures\comma{} and not deducted from the number of successes rolled. 

You may change your `signature spell’ with GM consent that your old choice no longer represents your character’s go\minus{}to move.}{0}{}
	\feat{Silent Casting}{You do not need to perform the verbal component of a spellcasting action. Efforts to silence you do not impact your spellcasting efforts\comma{} and the lack of an alerting incantation means efforts to \imp{Resist} your spells take a 1d penalty.}{0}{}
	\feat{Wandless Casting}{You are able to perform limited feats of magic without needing the crutch of a wand or ritualistic movements\comma{} so attempts to disarm your or bind you in place do not affect your spellcasting efforts. You take a 1d penalty on all wandless spellcasting efforts. All wandless actions are also silent.}{1}{Silent Casting}
}

