
\chapter{Character Progression} \label{S:Progression}\index{Character Progression|see{Progression}}\index{Progression}\index{Experience|see{Progression (Experience)}}

	
	As a character progresses through the world, they gain experience, knowledge and new skills. This allows them to develop their abilities and hence allow them to become more powerful. A \imp{Warrior} hits harder, a \imp{Scholar}'s brain is sharpened to a razor's edge, and the \imp{Artificer} learns new designs and techniques of their craft. 
	
	This character progression is enumerated through {\imp Experience Points} (\imp{Exp}). 
	
	\section{Earning Experience}\index{Progression!Experience}\index{Progression!Additional Triggers}
	
	You earn \imp{Exp} by solving problems - overcoming obstacles, defeating foes, learning new things and otherwise growing as a character. 
	
	At the end of a long day, just before you head off to sleep, you should always think back and reflect upon what you have achieved during that time: \imp{Exp} is awarded at the culmination of an adventure, in a pause in the frantic adventure, or when a character has a moment to breathe and reflect. If the \imp{GM} has timed their session well, this will often occur at the end of a session - though if a natural point is reached in the middle of a session this should not be shyed away from. 
	
	When the GM decides it is time to distribute \imp{Exp}, they will take into consideration the following:
	\begin{itemize}
		\boldItem{How many serious obstacles did they overcome?}{Did the group face a problem and neutralise it? What issues did they face? Each significant task can be awarded 1\imp{Exp}}
		\boldItem{Were these tasks new and challenging?}{Defeating a basilisk, or being chosen as prefect for the 5th time is probably less instructive than it was the 1st. If the task was especially new or novel, you may be granted an additional \imp{Exp}}
		\boldItem{Did they use their abilities to solve them?}{Each \imp{Archetype} states that they gain additional \imp{Exp} whenever they use a certain ability or approach to solve a problem.}
		\boldItem{Did they grow as a character?}{This final question is used to reward good roleplaying - overcoming internal, personal challenges, as much as those imposed by the GM. If the GM feels that a player went out of their way to inhabit and develop a character, this may be rewarded with \imp{Exp}}. 
	\end{itemize}
	
	You may negotiate with the GM and remind them of what you have accomplished and overcome since you last reflected on your achievements, but their ruling on this is final. After being awarded \imp{Exp} you may store it in the \imp{Exp Rail} on your character sheet. 
	
	
	\section{Expending Experience}\index{Aspects}\index{Abilities}\index{Affinities}\index{Abilities!Major \& Minor Abilities}\index{Feats}\index{Health}\index{Fortitude}
	
	During these moments of reflection and growth, you may also spend these experience points to increase your abilities as a character. 
	
	The available options, and the associated \imp{Exp} cost for each of these is shown below:
	
	\newcommand\expRow[2]{{\bf #1}	&	\parbox[t]{4cm}{#2}	\\}
	\begin{center}
		\begin{rndtable}{r l}
			\bf Ability	&	\bf Exp Cost
			\\
			\expRow{Increase Aspect Rating}{$=~2\times$ new attribute score}
			\expRow{Increase Affinity Rating}{$=~3\times$ new affinity score}
			\expRow{Increase Major Ability Rating}{=~New \imp{Ability} score}
			\expRow{Increase Minor Ability Rating}{=~ 1 + New \imp{Ability} score}
			\expRow{Swap Major and Minor Ability}{ =~ 1 \imp{Exp}}
			\expRow{Gain New Feat}{ =~ 7 + Current number of feats}
			\expRow{Increase Health or Fortitude}{ = 10 + 4 for each previous purchase}
		\end{rndtable}
	
	\end{center}
	
	Therefore if Simone has a rating of three in \imp{Fitness}, she would need $2\times4 = 8$ experience to increase it to a 4-rating ability. Since she has already gained 1 \imp{Feat} previously, she could also purchase a second for 8 \imp{Experience} points. However, given she has a rating of 2 in \imp{Elemental}, she would need 9 points to increase this to a 3-level rating. 


	\section{Additional Feats}
	
	In addition to feats specific to each \imp{Archetype}, below a number of feats that any character can take are presented. 
	\input{Chapters/Part1_Characters/FeatList}
	\AllFeats
