
\chapter{Family} \label{C:Species} \index{Heritage|see{Family}}\index{Family}
 
 
 Although the fate of a being is never set in stone, and is ultimately decided by free will, hard work and personal achievement, there is no denying that the heritage and familial origins of a magic wielder has a deep impact on how they initially view and interact with the world. 
 
 The \key{Family} of a character determines these initial genetic and cultural impressions, and how they impact a character.
 
 
 Since your family is rather set in stone, tt is generally impossible to switch once a character has been created, except where it makes sense within the story (i.e. a human transitioning to a Vampire after being bitten). 



\newcommand\family[4]
{
	\index{#1}
	\subsubsection{#1}
	
	#3
	
	Coming from a #2 heritage gives you the following additional bonuses and feats:

	\begin{itemize}[leftmargin = 7pt]
		#4
	\end{itemize}
}

\newcommand\famAb[3]
{
	\item \key{#1}: {\it #2}
	
	#3
}


\section{Humans}

	Humans are perhaps the most common of the magic-wielding species, their population outweighing those of the other magical species by almost a factor of 10 by the time of the 21st century. Those who cannot wield magic (`muggles') outnumber the wizards by an even larger factor. 
	
	Despite this numerical dominance, wizardkind came into their magic relatively late - unlike the other elder species, their magic is relatively weak until it is harness and focussed through the use of spells and magical wands. 

	
	\family{Muggles}{Muggle}{Muggles (also known as `no-mags' in the USA, and a variety of other names worldwide) are those humans who cannot access or control the magical forces which permeate the fabric of reality. Since the 15th century, Muggles have vastly outnumbered magical folk, by several orders of magnitude, and are found in almost every corner of the globe.
	
		Due to the \imp{International Statute of Secrecy}\index{Statute of Secrecy}, most muggles are totally unaware that magic even exists, considering it a fairy tale or a myth. A few rare muggles are aware - the parents or partners of muggleborns, as well as the incredibly rare \key{Squibs} - muggle children born to magical parents.}
		{
			\famAb{Magic Deficient}{As a muggle, you lack the ability to channel and control magical energies, or wield magical items.}{Your \imp{Affinity} scores are permanently locked at 0, you cannot cast magic, and magical items do not work for you.}
			\famAb{Physical Reliance}{Without the crutch of magic to rely on, you have been forced to become more skilled with your hands.}{Take a one-dot bonus to one of your \imp{Fitness}, \imp{Precision} or \imp{Vitality} scores, and an additional one dot in either \imp{Speed} or \imp{strength}}
			\famAb{Muggle Education}{They may not be \imp{Hogwarts}, but you have attended muggle schools and picked up some useful knowledge.}{Gain an additional 5-dots to spread between the \imp{Muggle}, \imp{Science}, \imp{Technology} and \imp{World} fields. You cannot use this to exceed a 3-dot rating.} 
			\famAb{Non-believer}{In a life devoid of magical influence, you have learned to ignore magical influences, and your brain simply shakes off things it cannot understand, which provides an unusual form of protection.}{When an obviously magical source attempts to influence your mind, take +2d to any \imp{Resist} checks.}
		}
	
	\family{Muggleborns}{Muggleborn}{Muggleborns (sometimes referred to by the derogetary term `mudbloods'\index{Mudbloods|see{Muggleborns}}) are witches or wizards who are born to totally non-magical parents. Whether their magic arises spontaneously, or because of some long-distant magical relative is unknown. Muggleborns are relatively uncommon, making up perhaps 10\% of the student body at Hogwarts. 
	
	Muggleborns are usually told about their magical power at a relatively young age, though they typically remain raised in their muggle household. Muggleborns therefore often feel that they are strung between two worlds - that of magic, and that of their original family. Because of their upbringing, muggleborns find it easiest out of all the witches and wizards to interact with th muggle world. }
	{
		\famAb{Physical Reliance}{Without the crutch of magic to rely on, you have been forced to become more skilled with your hands.}{Take a one-dot bonus to one of your \imp{Fitness}, \imp{Precision} or \imp{Vitality} scores.}
		\famAb{Coping Mechanism}{Muggleborns are frequently the subject of bullying or discrimination within the magical world, and so many develop a thick skin to deal with this, others become more empathetic towards others who suffer similarly.}{Gain an additional dot in either \imp{Bravery}, \imp{Kinship} or \imp{Kindness}}
		\famAb{Muggle Education}{Prior to learning of your magical nature, you learned a thing or two about the muggle world.}{Gain an additional 3-dots to spread between the \imp{Muggle}, \imp{Science}, \imp{Technology} and \imp{World} fields. You cannot use this to exceed a 3-dot rating.} 
		\famAb{Disguised Magic}{Growing up as a muggle, you understand how to manipulate your magic to seem more normal and acceptable to them.}{When casting a spell at or below \levelTwo{} level, you may make it seem like a normal action, or a simple muggle magic trick, thereby avoiding suspicion or violating wizarding law.} 
	} 

	\family{Halfbloods}{Halfblood}{Halfbloods are by the far the most common kind of witch or wizard - they are those who have a non-trivial amount of muggle DNA, the cutoff is typically considered having at least one muggle grandparent. The unpleasant obsession with `blood purity' which plagued the 20th century led to many Halfbloods claiming to be `purebloods', despite all evidence to the contrary. }
	{
		\famAb{Magical Household}{Magic was used to deal with most minor physical tasks in the house. Your upbringing therefore focussed more on mental than physical development.}{Gain an additional dot in either \imp{Intelligence}, \imp{Willpower} or \imp{Perception}.}
		\famAb{Split Education}{You grew up aware of both the magical and the mundane world, and so have experience with both worlds.}{Gain 3 dots to distribute between \imp{Arcane}, \imp{Nature}, \imp{Muggle}, \imp{Technology} or \imp{World}, without exceeding a 3-star rating at character creation. }
		\famAb{Working Household}{You picked up a thing or two watching your parents do their jobs}{Gain a one-dot rating in any \imp{Practical} field.}
		\famAb{Between Two Worlds}{You were raised in a household with potentially wildly different experiences in the world, as well as family who may or may not know your full abilities. As such, you are used to switching between different ways of thinking when necessary.}{At the end of a \imp{Long Rest}, you may reassign a dot from any of your \imp{Knowledge} or \imp{Practical} fields to another field of the same type. You may not use this ability to add or remove dots from fields with more than a 4-star rating.}
	}
	
	\family{Purebloods}{Pureblood}{A true-pureblood is a genuinely rare witch or wizard, able to trace their ancestry back generations through entirely magical folk. The names of a pureblood are typically well-known by those in the wizarding communities, as being essentially magical nobility -- the most famous purebloods are the so-called `Sacred 28', 28 families of renowned magical heritage including the Blacks, the Lestranges,  the Longbottoms, the Malfoys, the Potters and the Weasleys. 
	
	The high status of many purebloods in wizarding society comes an unpleasant air of elitism and entitlement, though individual purebloods are often perfectly pleasant people.
	
	As with Halfbloods, Purebloods are raised in a magical household, though unlike many halfbloods, they do so without any muggle influences whatsoever. The muggle world absolutely baffles almost all purebloods - even those who adore muggles (such as the infamous \imp{Arthur Weasley}) simply cannot wrap their heads around their way of living. 
	 
	}
	{
		\famAb{Magical Household}{Magic was used to deal with most minor physical tasks in the house. Your upbringing therefore focussed more on mental than physical development.}{Gain an additional dot in either \imp{Intelligence}, \imp{Willpower} or \imp{Perception}.}
		\famAb{Arcane Brain}{Your entire upbringing has centred around magic, to the exclusion of all else.}{You gain a two-dot rating in \imp{Arcane}, and a further point to distribute into any knowledge field except \imp{Technology} or \imp{Muggle} - in addition, you can take no dots in these fields at any other point in character creation.}
		\famAb{High Society}{Most pureblood families are well connected, and so you have grown up meeting and interacting with important people.}{Gain a one dot rating in \imp{Eloquence}.}
		\famAb{Head Start}{Being surrounded from magic from birth gives you a bit of a boost when it comes to magical education.}{You know an additional spell at character creation.}
	}




 
\section{Goblins}

Goblins are a race of exceptionally intelligent non-humans. Short in stature (rarely reaching above 4ft tall), with thick, wrinkled skin and pointed ears, their society is renowned for their crafting abilities, which often surpass even the greatest magicsmiths that humanity has to offer. 

Goblinkind has been in an almost constant state of conflict with the wizarding world - often formenting rebellion against what they see as an oppressive regime. Many in the wizarding world look down on goblinkind as ugly, untrustworthy, greedy and generally repellent - this stems in part from naked xenophobia, but also may have roots in goblin society's unusual idea of ownership: they believe that the true owner of any item is the creator, and that you may not {\it buy} an object, merely rent it. 

Despite the outright hostility faced by many Goblins, they are amongst the most prominent magical creatures in wizarding life, in part because of their role in the wizarding economy. Though they once had mighty goblin kingdoms and city-states, years of war against humanity has reduced the goblins to a number of squabbling clans scattered across the globe, as likely to fight each other as they are to right back against the wizards. 
	
	\family{Gringotts Clan}{Gringotts goblin}{The Gringotts were a clan of British goblins, specialising in the forging of items which were almost impervious to magical influence of any kind. After a particularly brutal rebellion in the 15th century, the \imp{Ministry} was able to strike a deal with one of the rebelling clans - in exchange for peace, they were to be allowed control of the wizarding bank. Their crafting abilities made them uniquely suited for the construction of magical currency.
	
	Though the \imp{Ministry} continued to meddle with - and occasionally take over - the bank, the \imp{Gringotts} became the most powerful goblin clan in the British isles. They wield immense economic and political power, though are under immense scrutiny and discrimination from the remainder of wizarding society.  
	}
	{
	\famAb{Goblin Cunning}{Growing up in a goblin society, surrounded by discrimination from wizards, forces you to become cunning and develop the ability to think on your feet.}{Gain two additional dots to distribute between \imp{Intelligence}, \imp{Deception}, or \imp{Insight}. You also know the language \imp{Gobbledegook}}
	\famAb{Crafting Knack}{Goblin society prizes the ability to forge things with your own two hands.}{Gain two additional dots to distribute between \imp{Craft} and \imp{Imbue}}
	\famAb{Goblin Magic}{Goblins do not need wands in order to cast magic spells, and have their own unique incantations for spells.}{Your spells are all considered \imp{Wandless}, but not \imp{Silent}}
	\famAb{Magenull}{The Gringotts goblins specialise in crafting efforts which nullify magical effects}{At the end of every long rest , you may select a small non-magical item that can fit in your hand. This item is completely immune to magical effects until you complete another long rest. It cannot be harmed, identified, duplicated or manipulated by magic of any kind, though secondary effects can impact it (i.e. a nearby magical explosion would cause it to move). If you do this to the same item every day for a year and day, the effect becomes permanent.}   
	}

	\family{European Goblins}{European Goblin}
	{
		Whilst the \imp{Gringotts} goblins were able to integrate themselves into society, most of the other goblin clans elected instead to withdraw almost completely to isolated, often underground, enclaves across the continent. Many amongst them still dream of returning to their better days and reclaiming some goblin crown or another, most instead turned inwards and became a society of scholars, tinkerers and artists - focussed on self-improvement, and the construction of the unique goblin identity which had been stolen from them by centuries of warfare.  
	}
	{
		\famAb{Isolated Artisans}{Within their isolated societies, most European Goblins have turned towards more esoteric pursuits.}{Gain two additional dots to distribute between \imp{Intelligence}, \imp{Willpower}, or \imp{Precision}.}
		\famAb{Goblin Education}{ You know the language \imp{Gobbledegook} and one other language. You may also distribute 2 additional dots between any \imp{Practical} or \imp{Knowledge} abilities.}
		\famAb{Goblin Magic}{Goblins do not need wands in order to cast magic spells, and have their own unique incantations for spells.}{Your spells are all considered \imp{Wandless}, but not \imp{Silent}}
		\famAb{Rebellious Streak}{Goblins have been rebelling against authority for centuries, and that fire still burns within your chest.}{Once per \imp{Long Rest}, you may target a figure of power or authority. For the next 5 minutes, all checks made in opposition to this target have a DV 1 lower than usual.}
	}

	\family{Pukwudgies}{Pukwudgie}
	{
		Grey-skinned goblins hailing from the New World, Pukwudgies are only distantly related to their European cousins, and have been free from much of the warring and discrimination associated with them. Without the constant need for political machinations to protect oneself, the pukwudgies instead revel in physical achievements - they are considered great hunters, and pride themselves in tales of fearsome beasts they have taken down (supplanting their diminutive size with potent toxins they brew themselves). 
	}
	{
		\famAb{Free Goblins}{Without the need to scheme and plot just to stay alive, pukwudgies are able to diversify their talents away from the purely mental - though they can still be fiercly intelligent.}{Gain an additional dot in \imp{Fitness}, \imp{Precision} or \imp{Intelligence}.}
		\famAb{Wild Hunters}{Pukwudgies pride themselves on their hunting abilities, and encourage their young to learn these skills from a young age.}{Gain four additional dots to distribute between \imp{Imbue}, \imp{Marksmanship}, \imp{Skirmish} and \imp{Survival}, though you cannot exceed 4 at character creation.}
		\famAb{Goblin Magic}{Goblins do not need wands in order to cast magic spells, and have their own unique incantations for spells.}{Your spells are all considered \imp{Wandless}, but not \imp{Silent}}
		\famAb{Poisoned Blades}{Pukwudgies are infamous for their use of poisoned weapons, particularly arrows, and have perfected the skill.}{Whenever you use a weapon coated with a poison, the DV to resist the poison is 2 higher than normal.} 
	}
 

\section{Hybrids}

Humans are infamously profligate, so it is of no particular surprise that many half-human people can be found out in the wizarding world. These people are normally raised by the human-half of their family - if only because those who aren't don't tend never enter wizarding society at all, remaining instead amongst their people. 

Hybrids are not generally well-liked within wizarding society - the general consensus is that if you can `pass' as human, they are happy enough to leave you alone. However, any overt displays of pride or demonstrations of non-human abilities are likely to be met with suspicion and even outright hostility. 

	\family{Half-Giants}{Half-Giant}{No-one really wants to think about the mechanics of how half-giants came to be, but half-giants are a relatively common occurance - there is usually at least one half-giant attending \imp{Hogwarts} at any one time. Seemingly human in every way besides their enormous size: teenaged half-giants are around 6-7ft tall, growing up to 8-9ft by the time they are in their mid-20s, and are incredibly solidly built. The stigma associated with the giantkin means that many try to hide their heritage by claiming to be simply `big-boned'.}
		{
			\famAb{Gigantic Size}{Your body is simply enormous, your muscles are twice the size of a normal human's - though this does have the side effect of making you a bit clumsy}{Take a 1-dots penalty to \imp{Precision}, but distribute 2 dots between \imp{Fitness} and \imp{Vitality}, and gain a bonus dot in \imp{Strength}}
			\famAb{Resilience}{Your giant blood gives you a natural abilty to shrug off magical effects.}{When \imp{Resisting} magical effects, you may use your \imp{Vitalty} pool as your base statistic for \imp{Endure}. When you gain at least 2 successes on an \imp{Endure} attempt, you suffer no \imp{Drain} }
			\famAb{Unusual Education}{You grew up knowing about the magical world, though your contact with your family led to an unconventional focus.}{Gain 3 dots to distribute amongst \imp{Arcane}, \imp{Survival}, \imp{Nature} and \imp{World}. You also know the \imp{Giant} language.}
		}

	\family{Half-Goblins}{Half-goblin}
	{
		Most half-goblins are the offspring of \imp{Gringotts} goblins, as they are the most common goblins to find in wizard society, though others can exist. Half-goblins are much shorter than average humans, though taller than the largest goblin, standing at around 5ft height at adulthood. Their appearance is mostly dominated by the human half of their genetics, though their ears are a little more pointed and their skin a little more wrinkled than one might expect for their age. 
		
		Although goblins are the subject of much discrimination, half-goblins are relatively well accepted in both societies, with many wizards not even noticing their non-human nature. For this reason, most half-goblins are raised as `normal' wizards, though their goblin influences do leave with with a certain fascination for some things. 
	}
	{
		\famAb{Keen Mind}{Your short stature doesn't lend itself to athleticism, but you find it easy to learn new information.}{Gain an additional dot in \imp{Intelligence}, \imp{Willpower} or \imp{Perception}}
		\famAb{Crafting Knack}{Even if you are not aware of your goblin ancestry, making things has always fascinated you.}{Gain two additional dots to distribute between \imp{Craft} and \imp{Imbue}}
		\famAb{Magical Education}{You learned about magic from a young age, as well as the wider world}{Gain 2 additional dots in any \imp{Knowledge} field}
		\famAb{Hidden Genetics}{Your outwardly human appearance can confound people, as their spells are tailored for a human target.}{Gain +1d to all \imp{Resist} checks against spells cast by people who do not know you are a half-goblin.}
	}

	\family{Half-Veela}{Half-Veela}{The veela themselves are near-human creatures possessing supernatural beauty, and the abilty to shift into monstrous fire-flinging harpy-like forms when angered. Their offspring with humans (almost always magic-users and rarely muggles) retain the almost-hypnotic beauty, but lack the ability to shapeshift. Most commonly found in Eastern Europe (the \imp{Veela}'s native range), enclaves of half-veela can be found across the globe.}
	{
		\famAb{Hypnotic Allue}{You possess an almost hypnotic level of beauty, allowing you to run rings around most people.}{Gain an additional dot in either \imp{Charm}, \imp{Deception}, or \imp{Insight} and a bonus dot in \imp{Eloquence}}
		\famAb{Arcane Brain}{Your entire upbringing has centred around magic, to the exclusion of all else.}{You gain a two-dot rating in \imp{Arcane}, and a further point to distribute into any knowledge field except \imp{Technology} or \imp{Muggle} - in addition, you can take no dots in these fields at any other point in character creation.}
		\famAb{Fire Affinity}{Though you cannot innately summon flames like full-veela, you have a certain level of affinity with them.}{Gain +1d on any checks to summon, manipulate, resist, or otherwise interact with fire.}    
	} 
	
	


\section{Complicating Families}

Note that, for the most part, the impact of \imp{Family} and heritage is not intrinsic to your genetics - it is a result of the house you were raised in, the experiences and values that were instilled into you as you grew up: \imp{Muggleborns} are not intrinsically less intelligent than \imp{Purebloods}, but rather the abundance of magics in a pureblood household left more time for an emphasis on booklearning and abstract thinking. 

For this reason, the actual \imp{Family} you choose may not represent your actual lineage. \imp{Harry Potter}, for example, was a \imp{half-blood} wizard with a father from a prominent \imp{pureblood} family - however, the circumstances of his childhood mean that he should probably be considered a \imp{Muggleborn}, as he was raised without magic for most of his life.  
 
 If you wish to customise your \imp{family} and heritage to better match the way in which they were raised, you may do so after discussing it with your \imp{GM}: as above, the \imp{halfblood} raised by their muggle relatives is functionally identical to a \imp{muggleborn}, or perhaps the \imp{muggleborn} daughter of a rich muggle trades in their \imp{Coping Mechanism} bonus for the \imp{High Society} bonus, as this makes sense within the narrative. 
 
 Some abilities are obviously more intrinsic to the nature of the individual: the \imp{Gigantic Size} bonus of the \imp{Half-giants} is something that no other being can gain, even if raised in a half-giant household. 
