\chapter{Adventuring Gear}

Adventuring gear is the set of (usually non\minus{}magical) items that you would need to use to survive on a day\minus{}to\minus{}day basis on an adventure.
\newcommand\generic[2]
{
	\vspace{2 ex}
	\small
	\vbox{
	{\bf #1:}~~#2
	}
	\normalsize
}


\newcommand\pack[3]
{
	\vspace{2 ex}
	\small
	\vbox{
	{\bf #1}
	
	\begin{tabular}{l p{6cm}}
		Cost: & #2 gold
	\\
		Contains: & #3
	\end{tabular}
	}
	\normalsize
}


\def\t{0.01}
\def\q{1.55}
\footnotesize
%%ItemsBegin
 \begin{center}\begin{rndtable}{|p{\q cm} l l p{\t cm} p{\q cm} l l|}\hline \tablehead \bf Name & \bf Weight & \bf Cost & ~ &\bf Name & \bf Weight & \bf Cost\\ \hline 	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Acid}	&	Light	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Ink}	&	Light	&	2gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ammunition (10 Arrows)}	&	Light	&	15gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Ink pen}	&	Light	&	2gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ammunition (10 Bolts)}	&	Light	&	15gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Jewellery (cheap)}	&	Light	&	40gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ammunition (20 Blowgun Needles)}	&	Light	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Jewellery (fine)}	&	Light	&	150gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ammunition (20 Rifle bullets)}	&	Light	&	30gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Jewellery (luxurious)}	&	Light	&	1000gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ammunition (20 Slingshot Bullets)}	&	Light	&	4gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Ladder (2m)}	&	Heavy	&	60gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Backpack (25L)}	&	Light	&	25gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Lamp}	&	Light	&	5gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Backpack (65L)}	&	Medium	&	60gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Magnifying Glass}	&	Light	&	7gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ball bearings}	&	Light	&	5gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Manacles (Iron)}	&	Medium	&	25gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Bedroll}	&	Light	&	15gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Mirror (handheld)}	&	Light	&	7gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Caltrops}	&	Medium	&	20gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Oil (flask of)}	&	Light	&	4gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Candle}	&	Light	&	1gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Paper (20 sheets A4)}	&	Light	&	2gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Case (map or scroll)}	&	Light	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Parchment (5 sheets A3)}	&	Light	&	10gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Chain (5m)}	&	Heavy	&	35gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Perfume (vial)}	&	Light	&	30gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Chalk}	&	Light	&	2gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Pole (10 ft)}	&	Light	&	10gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Chest}	&	Heavy	&	40gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Potion: Antidote}	&	Light	&	50gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Clothes (adventuring)}	&	Light	&	60gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Potion: Pepper\minus{}Up}	&	Light	&	30gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Clothes (common)}	&	Light	&	30gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Potion: Poison}	&	Light	&	100gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Clothes (fine)}	&	Light	&	80gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Potion: Wiggenweld}	&	Light	&	30gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Crowbar}	&	Medium	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Rations (1 day)}	&	Light	&	8gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Drinking Flask}	&	Light	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Rope (20m)}	&	Light	&	20gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Fishing Rod}	&	Light	&	40gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Sack}	&	Light	&	51gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Floo Powder (5 uses)}	&	Light	&	60gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Shovel}	&	Light	&	52gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Food (1 warm meal)}	&	Light	&	10gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Soap}	&	Light	&	53gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Glass Vial}	&	Light	&	8gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Tea Set}	&	Light	&	19gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Hammer}	&	Medium	&	15gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Tent (two\minus{}person)}	&	Light	&	55gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Holy Water}	&	Light	&	100gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Tinderbox}	&	Light	&	56gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Hourglass}	&	Light	&	5gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Torch}	&	Light	&	57gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Hunting Trap}	&	Light	&	50gp	&~&	 \bf \parbox[t]{\q cm}{\raggedright \footnotesize Whetstone}	&	Light	&	59gp \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Ingredient Pouch}	&	Light	&	35gp&~&~&~&~ \\ 
\hline
\end{rndtable}
\end{center} 

 
 \generic{Acid}{May be splashed on a melee opponent\comma{} or used as an improvised Ranged weapon\comma{} following the normal rules. In either case\comma{} do 3d4 acid damage.}
 
 \generic{Backpack (25L)}{The primary storage for most adventurers. A medium\minus{}sized backpack suitable for adventuring\comma{} with a volume of around 25L}
 
 \generic{Ball bearings}{As a major action\comma{} spill these on the floor covering up to 5 square metres. Any creature passing through this region must succeed on a DV10 FIN Resist check\comma{} or fall prone.}
 
 \generic{Bedroll}{Comfy enough to get a decent night\apos{}s sleep on when out on an adventure.}
 
 \generic{Caltrops}{As a major action\comma{} spill these on the floor covering up to 2 square metres. Any creature passing through this region must succeed on a DV12 FIN check\comma{} or stop moving and take 1d4 piercing damage.}
 
 \generic{Candle}{For 1 hour\comma{} shed bright light 1m radius\comma{} and dim light for a further 1m.}
 
 \generic{Case (map or scroll)}{Safely protects up to 10 large sheets of paper from the elements.}
 
 \generic{Chain (5m)}{A set of large metal links. Can be broken by a DV18 ATH (Strength) check\comma{} or by taking more than 10 physical damage.}
 
 \generic{Crowbar}{Gives advantage on Strength checks when leverage can be applied.}
 
 \generic{Drinking Flask}{Contains enough water for one person for one day}
 
 \generic{Floo Powder (5 uses)}{Can be used to navigate from one fireplace on the Floo network to another.}
 
 \generic{Holy Water}{May be splashed on a melee opponent\comma{} or used as an improvised Ranged weapon\comma{} following the normal rules. In either case\comma{} do 3d4 Celestial damage.}
 
 \generic{Hunting Trap}{Requires 2 major actions to set\comma{} and forms a ring 0.5m in radius. Any creature that steps into this ring must succeed a DV15 FIN(Speed) check\comma{} or become Trapped\comma{} and taking 1d4 piercing damage. Trap may be broken via a DV10 ATH(Strength) check\comma{} but each failed attempt does a further 1d4 piercing damage.}
 
 \generic{Ingredient Pouch}{Used to keep potion ingredients safe from the elements.}
 
 \generic{Lamp}{For 6 hours\comma{} casts a bright light in a 4m radius\comma{} and dim light for a further 3m.}
 
 \generic{Manacles (Iron)}{Can be broken via a DV15 ATH(Strength check)\comma{} but otherwise immobilises the hands of the wearer.}
 
 \generic{Oil (flask of)}{Contains enough oil to refill a lamp once.}
 
 \generic{Potion: Antidote}{Cures up to 5 points of poison damage.}
 
 \generic{Potion: Pepper\minus{}Up}{Restores 10FP}
 
 \generic{Potion: Poison}{Does 5 Poison damage per turn for 5 turns.}
 
 \generic{Potion: Wiggenweld}{Restores 10HP}
 
 \generic{Rations (1 day)}{Not particularly nourishing\comma{} but enough to fill you up and keep you alive and kicking.}
 
 \generic{Tea Set}{Contains all the ingredients to make a decent cup of tea}
 
 \generic{Tinderbox}{Contains a flint and some tinder\comma{} necessary to create a non\minus{}magical fire.}
 
 \generic{Torch}{Burns for 1 hour\comma{} casting bright light for 2m\comma{} and dim light for a further 2. May be used as an improvised weapon\comma{} where it does an additional 1d4 fire damage.}
 
 \generic{Whetstone}{Useful for sharpening a dulled weapon.}%%ItemsEnd
\normalsize


\section{Artefacts}

Artefacts are items which are more magical in nature\comma{} and generally cannot be synthesised directly\comma{} though they may be recreated through enchanting. Some artefacts are incredibly rare and powerful\comma{} and can be hard to track down. The list below contains only some artefacts which are commonly found in the wizarding world\comma{} and should by no means be thought of as extensive. 
\def\q{4}
%%ArtefactBegin
 \begin{center}\begin{rndtable}{|p{\q cm} l l |}\hline \tablehead \bf Name & \bf Weight & \bf Cost \\ \hline 	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Bludger}	&	Heavy	&	100 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Broomstick (cheap)}	&	Medium	&	1000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Broomstick (fine)}	&	Medium	&	5000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Crystal Ball}	&	Light	&	150 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Darkandles}	&	Light	&	50 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Deluminator}	&	Light	&	3000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Extending Stachel}	&	Light	&	4000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Gobstone (Set of 30)}	&	Light	&	15 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Golden Snitch}	&	Light	&	300 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Howler}	&	Light	&	15 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Invisibility Cloak}	&	Medium	&	5000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Mokeskin Pouch}	&	Light	&	250 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Obsidian Manacles}	&	Medium	&	1500 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Omnioculars}	&	Light	&	40 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Pensieve}	&	Heavy	&	2000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Portkey}	&	(Varies)	&	500 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Quick\minus{}Quotes Quill}	&	Light	&	15 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Rememberall}	&	Light	&	100 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Self\minus{}Erecting Tent}	&	Heavy	&	1000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Sneakoscope}	&	Light	&	250 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Spellotape}	&	Light	&	25 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Talking Portrait}	&	Heavy	&	750 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Time\minus{}Turner}	&	Light	&	100000 gold \\ 
	  \parbox[t]{\q cm}{\bf \raggedright \footnotesize Wand}	&	Light	&	300 gold \\ 
\hline
\end{rndtable}
\end{center} 

 
 \generic{Bludger}{An enchanted iron ball\comma{} weighing approximately 80kg\comma{} and yet able to fly. They possess a malicious streak\comma{} and will target any flying entity within 100m and attempt to smash into them\comma{} before moving onto their next target\comma{}}
 
 \generic{Broomstick (cheap)}{A low\minus{}range broomstick that can get off the ground\comma{} but not much more than that. Capable of carrying one passenger at speeds of up to 100mph\comma{} thought with very clumsy handling at high speeds.}
 
 \generic{Broomstick (fine)}{A high\minus{}end broomstick capable of high\minus{}speed precision flying. Capable of carrying one passenger at speeds of up to 250mph\comma{} with the handling only limited by the pilot\apos{}s rection time.}
 
 \generic{Crystal Ball}{A sphere of perfect crystal – the manufacture of these objects is a carefully curated secret. A properly trained mind can use these objects to peer through the mystic veil and learn about the universe.}
 
 \generic{Darkandles}{The exact opposite of a candle\comma{} a darkandle emits darkness\comma{} rather than light. Within a 5m radius\comma{} there is total darkness\comma{} and within 5m there is only dim light\comma{} regardless of any other light sources nearby.}
 
 \generic{Deluminator}{A device designed by Dumbledore\comma{} the deluminator may be targeted at a specific light\minus{}source\comma{} at which point the light is extinguished\comma{} and absorbed by the deluminator. This light source is permanently disabled until the deluminator restores the light to it.}
 
 \generic{Extending Stachel}{A normal backpack that has been enchanted with the {\it internal extension charm}\comma{} making it several times larger on the inside than the outside. This backpack can hold up to 300L\comma{} and makes the contents 10 times lighter than normal.}
 
 \generic{Gobstone (Set of 30)}{A small set of stones used in the titular game. When knocked by another gobstone\comma{} they eject a squirt of corrosive liquid into the eyes of the target.}
 
 \generic{Golden Snitch}{A small golden\comma{} metal orb which sprouts wings when activated. The snitch then immediately attempts to evade all living beings\comma{} though sometimes it will taunt them by floating in front of their faces\comma{} before quickly vanishing.}
 
 \generic{Howler}{A magical letter that\comma{} when opened by the recipient\comma{} unfolds itself\comma{} floats and begins to scream the enclosed message\comma{} before incinerating itself. If left unopened after being delivered\comma{} it will explode violently.}
 
 \generic{Invisibility Cloak}{A cloak that renders whatever is concealed within it invisible\comma{} though external factors such as sound\comma{} or the presence of rain or snow may still give away the location. The cloak also offers no protection against spells.}
 
 \generic{Mokeskin Pouch}{A small coin pouch that can only be accessed by its owner.}
 
 \generic{Obsidian Manacles}{A magical set of handcuffs which\comma{} when firmly closed around the wrist\comma{} prevent a witch or wizard from casting any magic.}
 
 \generic{Omnioculars}{A pair of high\minus{}resolution binoculars\comma{} capable of pausing\comma{} rewinding and replaying previous events. Omnioculars are capable of 10x magnification\comma{} and a playback up to 3x slower than original of up to 1 hour of recorded footage.}
 
 \generic{Pensieve}{A large stone bowl\comma{} engraved with ancient runes and inlaid with previous stones. A pensieve can be filled with memories\comma{} in the form of a silvery glowing fluid\comma{} which can then be viewed and relived in real time.}
 
 \generic{Portkey}{A one\minus{}use device with a teleportation charm embedded in it. A portkey resembles a random piece of junk\comma{} but when activated (either by touch\comma{} or at a specific time)\comma{} teleports to a preset location.}
 
 \generic{Quick\minus{}Quotes Quill}{A quill which automatically writes down whatever is said within a 2m radius.}
 
 \generic{Rememberall}{A small glass orb filled with grey smoke\comma{} which turns bright scarlet whenever the bearer forgets something. The colour reverts to grey when the target remembers.}
 
 \generic{Self\minus{}Erecting Tent}{Outwardly a three\minus{}man tent\comma{} but due to an extension charm\comma{} its interior is large enough for around 10 adults to live comfortably. It erects and disassembles itself upon hearing a double\minus{}clap.}
 
 \generic{Sneakoscope}{A sneakoscope is a type of dark\minus{}detector that looks like a glass spinning top. It lights up\comma{} spins and whistles whenever someone in a 2m radius is doing something untrustworthy. In practice\comma{} this grants the bearer a +5 bonus to passive perception against `untrustworthy’ actors.}
 
 \generic{Spellotape}{An alternative to the {\it Stick} charm\comma{} when dealing with delicate magical objects\comma{} spellotape is an adhesive material.}
 
 \generic{Talking Portrait}{A portrait of a witch or wizard which is imbued with their personality and (to an extent) their memories\comma{} as interpreted by the artist. These paintings can wander in and out of any nearby paintings\comma{} and also visit other paintings of themselves anywhere in the world.}
 
 \generic{Time\minus{}Turner}{An incredibly powerful item\comma{} that takes the form of an hourglass on a necklace\comma{} a time turner allows one to travel backwards in time one hour for every turn of the hourglass. Attempting to travel back more than 5 hours\comma{} or otherwise interfering with the past can cause irreparable damage to the space\minus{}time continuum.}
 
 \generic{Wand}{The cornerstone of wizarding life\comma{} though magic is possible without a wand\comma{} it is much harder – nearly every witch and wizard possess one. Wands bond to their owner through a complex and unknown process\comma{} so it is vital that you only use your own wand\comma{} or one you have bonded with.}%%ArtefactEnd

\newpage
\section{Packs}

Packs are pre\minus{}arranged sets of equipment. Where a pack leaves the precise nature of an item unclear (i.e. `a book')\comma{} you may choose the exact item within the following bounds:
\begin{itemize}
	\item A book may not cost more than 50gp.
	\item A set of tools may not cost more than 30gp.
\end{itemize}

%%PackBegin

\pack{Basic Pack}{30}{A normal backpack\comma{} some normal clothes\comma{} a small dagger\comma{} a candle\comma{} and a healing potion.}

\pack{Explorer Pack}{30}{A set of adventuring clothes\comma{} a climbing set\comma{} a torch\comma{} a map case (with map)\comma{} 10 days of rations\comma{} a water flask\comma{} a bedroll and a tent.}

\pack{Fighter Pack}{30}{A weapon (your choice)\comma{} a basic set of armour\comma{} and a healing potion.}

\pack{Scholar Pack}{30}{A normal backpack\comma{} some normal clothes\comma{} 2 books\comma{} 10 sheets of paper\comma{} ink and pen\comma{} a magnifying glass and 1 set of tools.}

\pack{Student Pack}{30}{A normal backpack\comma{} 1 book\comma{} a set of potion equipment and a set of student robes.}

\pack{Thief Pack}{30}{A set of (dark) clothes\comma{} lockpicking tools\comma{} a set of ball bearings\comma{} a torch\comma{} and a set of rope.}

%%PackEnd
