\onecolumn
\begin{landscape}
\small
\chapter{\vspace{-1ex}Magic Cheat Sheet}

This section contains a brief summary of the tables needed for spellcasting. This serves as a useful printout to have on hand, to avoid arduous page-flipping. 

\begin{multicols}{3}
\def\xS{1.8}
\def\wS{2}

\vbox{
\subsubsection{How to Cast}

To cast a spell, either in combat or in day-to-day life, you must declare the spell which you are about to cast. You must be holding your wand in your dominant hand, hand be able to speak the incantaiton aloud, unless you have a skill or character trait which negates these rules.	

You must then perform a check by rolling the relevant dice, and then compare this value with the Difficulty Value (DV) of the spell, and then finally deduct the appropriate FP cost. 

\subsubsection{Memory}

Spells can be cast in one of two ways: either from memory, or from the pages of a spellbook.

Spells cast from memory are considered `default', and most rules are written assuming that this is how they are being cast. 

Of course, you must first learna spell, before you can memorise it. This is what spellbooks are for. You may cast a spell from a spellbook if you have the spellbook open in front of you. Casting in this fashion takes twice as long as normal, leaves you vulnerable to attack, as well as costing more FP to cast. 

When you have book-cast a spell a certain number of times, it is considered `memorised', and you may cast it from memory in future. The formula to calculate the number of book-casts is:
$$N = 10 - \left( \text{INT modifier + Arcane Proficiency} \right)$$ 
 
}

\subsubsection{Accuracy \& Resisting}

After a spell has been cast, or an attack has been launched, you need to check that it hits its target. Living beings may instinctively either {\it Dodge} or {\it Block} an incoming attack, using whichever of their respective stats is highest:
\footnotesize
\begin{align*}
 \text{Dodge} & = 10 + \text{Finesse modifier+ bonus}
 \\
 \text{Block*} &= 10 + \text{Athletics modifier+ bonus}
\end{align*}
\small
These attributes set the DV of an {\it accuracy check} which an attacker must perform using a d20 check, plus any relevant bonuses. In combat, you may also choose to {\it Evade} or {\it Brace} as a minor action. This allows you to increase the value of Dodge or Block respectively by the value of a standard Resist check. 

You may also be asked to perform an accuracy check when casting against an object which is particularly far away or small. 

`Resisting' allows you to grit your teeth and power through the effects of a spell. Some spell effects can be overcome by a particular force of will. To do so, you roll your Resist dice (determined by the {\it Withstand} skill), and check against the DV set by the spell effect.  
\vbox{
\subsubsection{Check Type}
Every spell belongs to one of the Disciplines, which determines the character attribute to use when casting that spell. Appropriate Proficiencies may be added onto spellcasting checks as determined by character skills, or by GM's consent that it is applicable to the spell being cast.
\begin{center}
	\begin{rndtable}{c m{\xS cm} p{\wS cm}}
	\bf School	&	\bf Discipline	&	\bf Attribute
	\\
	\school{Charms}{Elemental}{\ElCheck}{Kinesis}{\KinCheck}
	\\
	\school{Divination}{Telepathy}{\TelCheck}{Temporal}{\TemCheck}
	\\
	\school{Illusion}{Bewitchment}{\BewCheck}{Psionics}{\PsiCheck}
	\\
	\school{Malediction}{Hexes}{\HexCheck}{Curses}{\CurCheck}
   \\ 
   \school{Recuperation}{Healing}{\HeaCheck}{Warding}{\WarCheck}
	\\
	\school{Transfiguration}{Alteration}{\AltCheck}{Conjuration}{\ConCheck}
	\\
	\school{Dark Arts}{Necromancy}{\NecCheck}{Occultism}{\OccCheck}
	\end{rndtable}
\end{center}


}
\vbox{
\subsubsection{Check Difficulty}

For a cast to be successful, the result of the casting check must be equal to or larger than the value given in this table:


\begin{center}
	\begin{rndtable}{c c c c c c}
		~	&{\bf Beginner}	&	{\bf Novice}	&	{\bf Adept}	&	{\bf Expert}	&	{\bf Master}
		\\
		\cellcolor{\tablecolorhead} \bf DV: &	\DVBeg	&	\DVNov	&	\DVAdp	&	\DVExp	&	\DVMas
	\end{rndtable}
\end{center}

}

\subsubsection{FP Costs}
Spells `cost' FP to cast. Failed spells cost half the amount of a successful spell and Resisting a spell costs 2FP. The FP cost of a spell is numerically equal to the difficulty of a spell, prior to any skill modifications (i.e. a skill which reduces the difficulty of a certain spell does not reduce the FP of it, and vice versa), unless the spell is being book-cast, in which case use the bracketed values.  


{\footnotesize
\def\wFP{1}
\begin{center}
	\begin{rndtable}{p{1cm} |c |   c | c |c | c}
		~	&{\bf Beginner}	&	{\bf Novice}	&	{\bf Adept}	&	{\bf Expert}	&	{\bf Master}
		\\
		\cellcolor{\tablecolorhead} \bf Memory &	\FPEntry{\DVBeg}{1}	&	\FPEntry{\DVNov}{1}	&	\FPEntry{\DVAdp}{1}	&	\FPEntry{\DVExp}{1}	&	\FPEntry{\DVMas}{1}
		\\
		\cellcolor{\tablecolorhead} \bf Book  &	\FPEntry{\DVBeg}{2}	&	\FPEntry{\DVNov}{2}	&	\FPEntry{\DVAdp}{2}	&	\FPEntry{\DVExp}{2}	&	\FPEntry{\DVMas}{2}
	\end{rndtable}
\end{center}
}
FP Regenerates at a rate of 2FP per turn cycle in which no FP was deducted. 



\end{multicols}
\end{landscape}
