\documentclass[../CoreRulebook.tex]{subfile}
\twocolumn
\chapter{Cosmology}

Though little of it is talked about in the Wizarding World, for the study of it is highly restricted, and confined almost entirely to the Department of Mysteries (and its various international variants), the universe is not as simple as it might first seem. 

Throughout most of the modern history of the Western world, it has been held that there are three planes of existence: the Mortal world, where we reside, and then two higher planes: Heaven and Hell. In contrast, modern atheism holds that there is but one plane, and some adherents of a particular interpretation of Quantum Mechanics believe that there an infinite number of copies of the Mortal plane. It seems unlikely that the true nature of these `Planes' will ever be understood by mortal minds. 

The Department of Mysteries, however, was created with the primary goal of studying these `Planes of Existence'. The Department has established that there are in indeed multiple `realms', or planes of existence. The total number of planes is actually unknown, for they are difficult to map, but the Department has so far managed to place them into 5 categories.  
{\bf 
\begin{enumerate}[itemsep = 0em]
\item The Mortal World
\item The Astral Realm
\item The Higher Planes
\item The Eldritch Domain
\item The Void
\end{enumerate}
}
It seems that there is some form of notion of `distance', although given the multidimensional nature of the realms, it is not what you or I would recongise as distance, but some realms are `further' away from the mundane reality that we exist in, and it takes significant effort to traverse this `distance'. The `closer' a Plane is, the easier it is to access. Roughly speaking, as you traverse down the above list, you get further and further away from our reality.

\subsection{The Mortal World}

The Mortal World is the universe that we see around us. It contains every star in the sky, and is seemingly infinite in extent. 

Events in this World follow well-established rules, what the Muggles call `the laws of physics', though these `laws' may be tweaked somewhat by the use of magic.

Most Sapient beings go their entire life without knowing that there is anything besides the Mortal World in existence. 

\subsection{The Astral Realm}

The Astral Realm is probably the plane that lies closest to the Mortal World, and is often imagined by those who study it as a blanket, lying over the top of the mortal realm. 

Every point in the Mortal World has a corresponding point in the Astral Realm, however, the notions of space and time that we are comfortable with do not seem to apply in the Astral Realm. Past, present and future coexist all at once, and paths through the astral realm have a habit of not ending up where you'd expect them to. 

It is from the astral realm, therefore, that seers are able to glean information about the future. It is also speculated that when a wizard apparates, they actually briefly enter into the astral realm, traverse a path that either takes no time at all, or perhaps has no length at all (or maybe both?), and then exit again, finding themselves to have instantaneously transported. 

Visually, the Astral realm looks like a translucent mimicry of the mortal realm, filled with drifting mist, thick fog and ghostlike figures. One may therefore observe what is going on in the Mortal Realm from the Astral, but not the other way around without special training. 

\subsection{The Higher Planes}

The Higher Planes is the collective name given to the realms which lie between the Astral Realm and the insanity-inducing Eldritch Domains. 

Unlike the Astral Realm, the Higher Planes are far enough away from the Mortal World that most of them do not have a 1:1 correspondance with spatial point. Some of the Planes are as large as our universe, others may encompass only a single planet, or even a single room in extreme cases. 

Most of the Planes in this category find themselves devoted to some elemental or conceptual aspect found in the real world -- be it the the Plane of Fire (Vulcan), or the Plane of Order (Machina). It is hypothesised that entities from these Planes that found their way to the Mortal Realm in the distant past were often mistaken for Gods. 

Generally speaking, the only way to travel to one of the Higher Planes is by creating a Portal, and act that requires punching a hole through the walls of reality. This is an act so potentially destructive to all life on Earth that it is classified as a Dark Art, and should only be attempted by the most skilled wizards. A list of Planes that have previously been visited is found at the end of this section. 


\subsection{The Eldritch Domains}

Little is known about the Eldritch Domains. It is thought that they are similar in structure to the Higher Planes, but are instead home to entities that have been dubbed {\it the Eldritch Horrors}. Only one Sapient -- a muggle child in the late 1890s -- has ever even glimpsed an Eldritch Domain and not been driven to complete insanity, and it is evident from his subsequent career as an author that he was not unscarred by the experience. 

The Eldritch Horrors are entities beyond human comprehension, and go by many names: the Chaos Gods, The Great Old Ones, Devourer of Stars, Harbingers of Apocalypse to name but a few. They are not inherently evil, and are in fact so utterly alien that the concept of good and evil is barely applicable to beings of such comsic power. 

\subsection{The Void}

The Void is, unlike the other realms, omnipresent. It is simultaneously the closest Realm to the Mortal World, and yet also the most distant. It is thought that the Void is the hyper-dimensional space in which all the other Planes move, the glue that holds the universe together. 

The Void possesses at least 16 spatial dimensions, and 4 temporal dimensions, which means that even objects that enter the Void simultaneously (from the point of view of another plane) will end up dispersed across the 20-dimensional manifold that represents the void. 

Utterly, completely empty, the Void is the true vacuum of the multiverse. So black that empty space seems like a thick soup, and so dark that no light may propagate. The Void truly lives up to its name. 
\par~\par
\section{Higher Planes}

\subsection{Abyss: The Plane of Terror}

Abyss is a plane that warps itself according to the fears of those who enter it, formed from an endless, parched wasteland under a black sun, at the centre of which lies an sinkhole so deep it seems to have no end. Embedded into the walls of the sinkhole, spiralling infinitely downwards are thousands -- millions -- of doors, each with an individuals name inscribed upon it.

Behind each door lies a room of indeterminate size. Each room contains the thing that most terrifies the being named on the door, be it an infinite maze, a posse of evil clowns, or an ocean populated by bloodthirsty sharks. Once inside a room, it is impossible to leave until you conquer your fears. 

When entering Abyss, each individual is teleported into the room bearing their own name, and upon escaping, formless beings of shadow and darkness will attempt to force you back inside. 

\subsection{Aeolus: The Plane of Storms and Winds}

A plane of infinite expanse, filled with swirling air, floating clouds and drifting chunks of earth, Aelous is the Plane associated with the element of Air. 

There is no solid ground to be found in Aeolus, the civilisations found within are built upon the floating mountains that dot the skyscape, or perhaps carved out of condensed and harness cloud. These civilisations live a nomadic life as they drift through the endless sky, never fixed in one place. 

Current-charts, which map the airflow and allow you to plot a route through the sky, are the most valued currency in this domain, as are Storm-warnings, for the skies of Aeolus are often split apart by vicious storms that can last a century or more. 

Aelous is home to powerful wind-mages, who can calm the skies with a word, or whip up a brisk wind with a wave of their hand. It is these wind-mages who first constructed the Storm Avatars, and from Aeolus that Mortal wizards draw the stormclouds to construct their own facsimiles of the Avatars. 

\subsection{Eden: The Plane of Nature}

A druidic paradise, Eden is a single, enormous garden that lies behind an enormous wall, which forms the boundary between this realm and the Void. Every single species of plant and animal life across the multiverse can be found living in perfect balance in Eden -- the circle of life made manifest in a single region, for all of eternity. 

No artificial structure can be built in Eden (outside of the Wall, of course), so no true civilisations are found within. The denizens of this realm -- the Gardeners -- instead tend to the wildlife, curing the sick and resolving conflicts, and are rewarded with fruit and wool, in return for their role in the Circle. 



\subsection{Elysium: The Plane of Blessings}

Appearing as a gigantic city, constructed out of gleaming silver and shining marble, populated by beings that can only be described as Angels, it is said that Elysium is the place where dreams come true. 

Indeed, one has to merely wish for something out loud, and a nearby Angel will promptly hand you the focus of your desires. Equally, the air in Elysium seems to be suffused with magic and positive energy, for every action that one attempts (even the most absurd), will succeed without question. 

Of course, there is a price for such a blessed existence: an entity known as the Scribe -- the chief angelic being -- sits atop the highest tower in Elysium, judging the actions of all the inhabitants. If they fail her test, they are expelled from the Silver City.

\subsection{Hades: The Plane of Death}

Like the astral plane, Hades appears as a mimicry of the Mortal World, albeit with a few alterations. The landscape is dotted with bomb-craters, bubonic plague pits, collapsed buildings and nuclear winter. Every single grotesque form of death is represented, somehow, in the environment, in a violent, deadly parody of the living world. 

Populated entirely by ghosts, echoes of the living, no one is quite sure what causes a soul to be left in Hades. Some lucky souls are able to escape through the cracks and back to the Mortal Realm, forming the ghosts that wizardkind are aware of, but these are only a fraction of the ghosts found in Hades. 

The living cannot spend much time in Hades, as the aura of death and decay seeps into their bones, and seeks to turn them into one of the ghouls that haunts its shattered landscape. 

The Ministry of Magic possesses a portal to Hades, it lies deep beneath the Ministry itself, at the heart of the Department of Mysteries. However, this portal is one-way, so anyone who enters it without the ability to return home will surely perish. 

\subsection{Hyperborea: The Plane of Ice}



\subsection{Machina: The Plane of Order}

\subsection{Nirvana: The Plane of Peace}

\subsection{Pand{\ae}monium: The Plane of Chaos}

\subsection{Scholomancia: The Plane of Knowledge}

\subsection{Tartarus: The Plane of Torture}

\subsection{Valhalla: The Plane of Bravery}



\subsection{Vulcan: The Plane of Fire}

Visually, Vulcan most resembles typical depictions of the Christian Hell, with enormous pools of lava, gouts of fire twenty feet high, and patrolled by demons with pools of flame for eyes. However, this domain is simply the Plane associated with Elemental Fire, not with righteous torture of the evil.

Outside of the volcano-top castles and their pools of lava, the land is covered in a fertile ash, and populated by ruby-red trees that can only distribute their seeds when the tree is consumed by fire. Diverse species of dragon, from tiny lizard-like creatures to formidable goliaths patrol the skys. The fire of this realm serves not simply to destroy, but to cleanse and refresh and as such, though Vulcan is quite alien to us mortals, it has been home to several thriving and prosperous civilisations.

At the core of every summoned Avatar of Flame, lies a single ember drawn across the multiverse from Vulcan. 