\documentclass[CoreRulebook.tex]{subfile}

\chapter{Health, Fortitude \& Statuses}

Each character has two more attributes, which determine their physical and mental wellbeing respectively: Health and Fortitude. Magic is can be taxing both mentally and physically, and so it is vital that each character keeps track of how they are doing. Statuses are longer-term effects that may impact your attributes either postiviely or negatively, and are often the result of spells or potions used on your character.

\section{Health}

Health is the physical status of your character: attacking a character lowers their health, and when the health points (HP) of a character reach zero, that character is killed. A character{\apos}s maximum health is calculated from:
$$\text{max HP} = 2 \times \text{ATH (health)} + \text{relevant bonuses}$$
When your HP limit is raised (say, by the vita maxima spell), your current HP is raised by the same amount. In contrast, when your HP ceiling is lowered, you only lose HP if the ceiling is lowered below your current health levels. It is never possible to have more than your maximum HP. 

\textbf{If your character is reduced to 0HP, then they acquire the Critical Condition status: they are completely immobilised, and will lose 1HP per turn. When you reach -10HP, you are dead, and nothing can bring you back. }

Characters regenerate health slowly as minor wounds heal, at a rate of 1HP per hour whilst not in combat (unless there is a status effect blocking the healing effect), increasing to 3HP per hour when asleep. This counter is reset every time your character takes additional damage. Status effects such as Serious Wound may impact the maximum HP which can be reached by natural healing, without external intervention. 

\section{Fortitude}

Fortitude is a character{\apos}s ability to concentrate, which is necessary to cast spells and some other non-magic feats. Performing magic takes effort, and a character{\apos}s fortitude points (FP) will be slowly eroded by engaging in such mental effort.  A character{\apos}s maximum mental fortitude is calculated from:
$$\text{max FP} =  \text{SPR (willpower)} +\text{INT (arcane) }+  \text{relevant bonuses}$$
The same rules about raising/lowering the max level apply to Fortitude, as well as Health. Fortitude is used to cast spells, all spells have an associated fortitude cost written next to them -- as well as resist magic, and other actions which require intense concentration. You must subtract the relevant amount from your FP when performing such an action (plus or minus the appropriate amount for bonuses, power-boosted spells etc.)

When your FP reaches zero, your mind is exhausted, and so you will no longer be able to engage in such complex actions. Unlike HP, FP regenerates during combat; at a rate of 2FP per combat cycle where you do not cast a spell. Outside of combat, the regeneration rate is 8FP per hours, increasing to 20 per hour whilst asleep. 

Note that the maximum values of your HP and FP are dynamic values: when your ATH, SPR or INT values change, so do they. This is an important consideration when deciding which attributes to increase when levelling up. 



\section{Statuses}
Statuses are temporary effects applied to a character, usually due to a spell or a magic item, though sometimes mundane objects can confer statuses such as burns. Often these effects come with a built-in time constraint, after which time, the status is removed. It is possible to have more than one status effect at any given time. 

Some statuses come in 3 different levels: mild, moderate and severe; the effects for each are labelled using the notation mild/ moderate / severe: the three levels of burns are indicated to do 1/2/3 damage per turn, meaning that a mild burn does 1 damage per turn, whilst a severe burn does 3. 

A list of statuses is found on the next page.

\def\w{2}
\def\x{6}
\def\y{6}
\def\z{3}
\onecolumn
\footnotesize
%% This table is automatically generated from the table in a .xlsx file, compiled into text by a matlab script
%%StatusBegin
\begin{center} \begin{longtable}{|m{\w cm}|m{\x cm}|m{\y cm}|m{\z cm}|}\hline \normalsize \bf Status & \normalsize \bf Description & \normalsize \bf Effect & \normalsize \bf Duration \\ \hline \hline \bf \begin{flushleft} Asleep\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Visiting the land of nod.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Can take no actions, but health and fortitude regenerate at a rate of 1d6 HP for every hour over 3 hours that they are asleep.
Character is unaware of what is going on around them.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Until waking\end{flushleft}}  \\ \hline \bf \begin{flushleft} Blinded\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Your eyes are temporarily overloaded by a bright light.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks that would normally require vision fail.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}1 hour\end{flushleft}}  \\ \hline \bf \begin{flushleft} Broken Bone\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have suffered an injury that has broken your bone.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Cannot use the limb in question until it is healed. This is a major injury (see below).\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Until healed\end{flushleft}}  \\ \hline \bf \begin{flushleft} Broken Wand\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Your wand is broken, and cannot perform properly.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All spell checks get a -5 penalty, and spell failures are particularly severe.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Until wand is repaired\end{flushleft}}  \\ \hline \bf \begin{flushleft} Burned\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Heat has damaged your body, but the effects are ongoing.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Does 1 / 2 / 3 damage per turn (depending on the severity), unless cold water is applied. 
Even after water is applied, you are 50\% more vulnerable to fire damage.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}10 turns.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Calm Mind\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Your mind is calm and clear, you are undistracted.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks receive a +1 bonus.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Lasts for 1 hour, or until hurt.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Check Advantage\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have the upper hand\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}For each affected check type, you roll the dice twice ÿ and take the highest of the two values\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}As specified\end{flushleft}}  \\ \hline \bf \begin{flushleft} Check Disadvantage\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}A negative effect is stopping you performing at your best\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}For each affected check type, you roll the dice twice ÿ and take the lowest of the two values\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}As specified\end{flushleft}}  \\ \hline \bf \begin{flushleft} Confused\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}A fog descends upon your brain, and you are unable to think clearly,\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}After committing to an action, perform a 1d6 check. 5-6, the action is successful. 3-4, the action misses/doesn`t work. 1-2, the action backfires randomly to you or your allies.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}3 turns\end{flushleft}}  \\ \hline \bf \begin{flushleft} Critical Condition\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You are close to death, bleeding out.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}You are totally unable to act. 1HP lost per turn. When reaching -10HP, you are dead.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}\end{flushleft}}  \\ \hline \bf \begin{flushleft} Deaf\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Your ears have been damaged, hopefully only temporarily!\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All hearing-based checks fail\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}3 turns, or otherwise specified\end{flushleft}}  \\ \hline \bf \begin{flushleft} Diseased\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have contracted a disease.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Specifics of the effects vary according to the disease. Knowledge checks are needed to learn more.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Never\end{flushleft}}  \\ \hline \bf \begin{flushleft} Exhaustion\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have not slept in a long time, your mind and body are weary.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Every turn, perform a SPR (endurance) check (difficulty 15), if it fails, fortitude costs of actions are doubled, and regeneration of health and fortitude halt.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Until resting.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Frostbite\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}The cold has damaged your body, and it cannot function properly, but the biggest toll is on your sluggish thoughts.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Halts fortitude regeneration, and drains 1 / 2 / 3 fortitude per turn, unless warmth is applied.

Even after warmth is applied, you are 50\% more vulnerable to cold damage.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}10 turns.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Hypoxia\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Oxygen is not reaching your vital organs, you struggle to concentrate, but your brain is slowly shutting down.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks get a -5 penalty. If not cured within 2 minutes, death follows.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}2 minutes\end{flushleft}}  \\ \hline \bf \begin{flushleft} Invisible\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Light passes straight through you; you are hidden from sight.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}In adverse conditions (i.e. rain and snow), can still be visually detected. Does not stop noise.  Otherwise, visual perception checks to find you fail.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Various (depends on cause.)\end{flushleft}}  \\ \hline \bf \begin{flushleft} Lucky\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}The result of a Felix Felicius potion, you become extra-ordinarily lucky.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks used by the player get a +5 bonus, and all checks against the player suffer a -3 hit.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}1 hour\end{flushleft}}  \\ \hline \bf \begin{flushleft} Major Injury\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have suffered a major injury.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Cannot heal above 50\% HP until the major injury is fixed.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}Until healed\end{flushleft}}  \\ \hline \bf \begin{flushleft} Poisoned\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}A nefarious chemical, a toxin, has been introduced into your system.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Does 2 / 3 / 5 damage per turn (unless otherwise directed).\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}10 turns.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Silenced\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You find yourself unable to make any sounds.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}Cannot speak, or cast verbal magic.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}2 turns (unless otherwise directed).\end{flushleft}}  \\ \hline \bf \begin{flushleft} Stunned\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}You have been knocked unconscious\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}As if you were asleep, but without the regeneration.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}3 turns\end{flushleft}}  \\ \hline \bf \begin{flushleft} Terrified\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Your knees knock, your hands shake, and your mind turns inwards: you{\apos}re scared.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks get a -3 penalty. Cannot get closer to the cause of the fear.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}5 turns, or until the cause is removed.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Trapped\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Ropes, snares or magic are holding you back, preventing you from moving.\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}You are fixed in one place, and cannot move. Some traps may also immobilise the arms, in which case you may not perform actions which require your arms.\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}3 turns, or until the trap is released.\end{flushleft}}  \\ \hline \bf \begin{flushleft} Unlucky\end{flushleft}  &  \parbox[t]{\x cm}{\begin{flushleft}Things are just not going your wayÿ\end{flushleft}}  &   \parbox[t]{\y cm}{\begin{flushleft}All checks get a -2 penalty\end{flushleft}}  &   \parbox[t]{\z cm}{\begin{flushleft}1 week\end{flushleft}}  \\ \hline \end{longtable} \end{center}%%StatusEnd
\normalsize
\twocolumn

\section{Damage \& Damage Types}

When you are attacked, or do something stupid, you must pay the price. This is called `taking damage'. There are different ways for you to take damage, and these have different effects associated with them. 

Many effects specify what kind of damage they do (for instance, a sword does 1d8 slashing damage). This helps the players and the GM work out how the damage is done, and also how it is affected by any weaknesses and resistances possessed by the target. 

{\bf Acid} 

A spray of acid burns through 1cm physical armour to reduce the HP of the being within. 

{\bf Bludgeoning}

The blunt-force of a hammer, or the force of falling on the ground is very difficult to protect against, reducing the HP by a large amount, and risking breaking a bone. 

{\bf Cold}

Cold damage seeps at your willpower, subtracting from FP rather than HP, until FP is zero, at which point it starts leaching HP.  Roll a 1d4, if 1 rolled, acquire Frostbite status. 


{\bf Concussive}

A shockwave from an explosion, passes through physical armour to reduce HP. In addition, target rolls a 1d4, if a 1 is rolled acquire the Deaf status for 3 turns. 

{\bf Electric}

A bolt of lightning can arc from one target to the next, damaging the HP of all it touches. Electric damage can pass through objects and beings which are in contact. 

{\bf Fatigue}

Fatigue damage drains FP from the afflicted. 

{\bf Fire}

Fire damage burns the flesh to reduce the HP. Roll 1d6, 1-2 gives a mild burn, 2-4 gets a moderate burn, 5-6, no effect. 

{\bf Force}

A pure magical energy that directly damages HP. 


{\bf Holy}

A searing white light damages the undead, and banishes the unliving. Has no effect on living beings.  

{\bf Necrotic}

The evil energies of the undead withers your soul as it damages your body -- reducing HP and FP by equal amounts. 

{\bf Piercing}

Daggers, spears and teeth can puncture even the thickest armour to damage HP. Piercing attacks experience only 50\% the usual armour rating. 

{\bf Poison}

Venemous stings and poisoned weapons damage HP. Roll 1d6, 1-2, mild poisoned status for 3 turns, 3-6, no effect.  

{\bf Psychic}

Damage that originates not from the body, but from the mind. Bypasses all protections to damage HP, and 50\% again to FP. 

{\bf Slashing}

Swinging blades and flashing claws damage the HP of unprotected targets. 