\documentclass[CoreRulebook.tex]{subfile}

\chapter{Character Progression \& Skills}

\section{Character Progression}
Each character has a `level' associated with them, which denotes how far your character has progressed, and how powerful they are.  Levelling your character is key to progressing: it unlocks new skills, boosts your attributes, and gives access to new spells. A higher-level magic user is a stronger magic user. A stronger magic user is less likely to get eaten by a passing beast, which is generally considered a good thing. 

\subsection{Experience}

Increasing the level of your character (`levelling up') is achieved by accumulating experience. To progress from level 1 to level 2, you must accumulate 100 experience points (EP). When your character reaches 100EP, they ascend to level 2, and the counter is reset. To go from level 2 to level 3 you need to acquire another 200 EP, and so on and so forth. The EP needed to go from level $x$ to $x+1$ is calculated from:

$$ EP_{x \to x + 1} = 100 x $$

Experience is gained by completing actions and defeating enemies. Experience is awarded for completing difficult actions such as casting a spell, mixing a potion, defeating an enemy in combat, or convincing someone to give you something. The GM will instruct you to roll a dice, and you will gain that much experience from completing the action.

The dice you roll (and hence the amount of experience you gain) from such an action depends on your proficiency in that skill. For instance, a first year student gains far more knowledge and experience from casting wingardium leviosa than a seasoned auror does. Hence, as you progress, you will learn less experience from trivial actions. 

As a rough guide, performing an action (such as casting a spell) which is of the same proficiency level as you are will get a 2d20 roll, using one level below your proficiency is a 2d12, and so on:

\begin{center}
	\begin{rndtable}{|c c|}
	\hline \bf Relative Proficiency & \bf Experience Roll
	\\ 
	Same level 		& 	2d20
	\\ 
	1 level below 	&	2d12
	\\ 
	2 levels below	& 	2d8
	\\ 
	3 levels below	&	2d6
	\\ 
	4 levels below 	& 	2d4
	\\ 	\hline
\end{rndtable}
\end{center}

For example, a character with the Adept Battlemage (combat magic) skill would roll a 2d20 for successfully casting the Impediment Jinx (an adept level combat spell), whilst if they were an Master Thaumaturge (transfiguration), they would only get to roll a 2d8 for casting an Adept transfiguration spell, as this is 2 levels below Master. 

Experience is only awarded when an action is truly succesful (i.e. a spell has to hit its target, as well as be succesfully cast). 

\subsection{Levelling Up}
When your experience reaches the requisite amount, you immediately trigger the levelling up process. When you level up, you make the following changes to your character:

\begin{itemize}[itemsep=0em]
	\item Increase character level by 1, and reset EXP counter to zero (you may carry any excess EXP over)
	\item Increase Archetype level by one {\bf OR} choose a new archetype (see multiclassing rules on page \pageref{S:Multiclassing}). Add any new Features you gain at this point.
	\item You may choose one of the following:
	\begin{itemize}[itemsep=0em]
		\item Increase an attribute by 2, or two attributes by 1
		\item Choose a new Skill, if you meet the minimum prerequisites
	\end{itemize}
	\item Calculate new HP and FP ceilings
	\item Reset HP and FP to maximum
	\item Reset spell-learned counter
\end{itemize}

\subsection{Other Changes}

The GM may also decide that, during the normal course of play, you have done something that warrants a permanent bonus or penalty -- be it something you have learned from extensive practice, or a gift from some higher being -- the GM will grant you a bonus to your Attributes or Proficiencies. This will probably most commonly be used to penalise players for immoral actions -- by increasing their EVL level.

\newpage
\section{Skills}

Skills are learned abilities that your character picks up along the way. They can be learned either by levelling up or given as gifts by external devices. Some skills are only temporary and will wear off after a while. Skills are key to learning new and more powerful magic, as well as ulocking useful abilities. Most skills come in 5 levels: Beginner, Novice, Adept, Expert and Master, which must be learned in that order. 

The 8 most important skills are the magic-school skills: skills which are each associated with one of the 7 schools of magic (and Resist checks). They are,

\begin{center}
\begin{rndtable}{|c c|}
\hline \bf  Magic School  &  \bf Associated Skill
\\ 
Hexes \& Curses  	& 	Battlemage
\\
Transfiguration		& 	Thaumaturgus
\\
Charms				&	Sorcerer
\\
Recuperation	& 	Defender
\\
Illusion				&	Magician
\\
Divination			& 	Clairvoyant
\\
Dark Arts			& 	Necromancy
\\
Resist Checks		& Withstand
\\ \hline
\end{rndtable}
\end{center}

Learning more powerful spells in each school of magic requires more and more levels in the relevant skill. To cast Expert level Hexes and Curses, you need to be an Expert Battlemage, and so on. 

Other skills gives you access to more powerful abilities as well. 

\subsection{Prerequisites}

Some skills list a minimum ability score, or other threshold that your character must posses before they take that skill. If you do not meet the threshold, you cannot take the skill, unless you are provided it by external means, such as a Class Feature. 

In addition, for multi-level skills, when you take a skill you cannot take another level in that skill until you level up twice. If a character takes a skill at level $x$, then the prerequisite of the next level is that a character is level $x+2$. This includes skills that are given by Class Features -- if you are given a level in a skill by a Class Feature at level 8, you must wait until level 10 to level up again.

\subsection{Automatic Skill Aquiring} \label{S:Auto}

Some skills are acquired automatically through levelling up, without you having to choose. Sometimes, these skills may be givn to your by the GM for narrative reasons, or in order to further a stagnating game. 

The 8 Magic skills can indeed be levelled up by player choice in the usual fashion in order to get access to those spells slower. However, you may also gain these skills simply by reaching the appropriate level:

\begin{center}
\begin{rndtable}{|c|c|}
\hline \bf  Skill Level  &  \bf Acquiring Level
\\ 
Beginner 	&    1
\\
Novice		&    5
\\
Adept		&     10
\\
Expert         &     15   
\\ \hline
\end{rndtable}
\end{center}

When an auto-levelling is incurred, if you already have that spellcasting level thanks to taking the apropriate Skill manually, you instead get a +1 increase to your arcane wisdom for each Skill you took. This only applies to manually-chosen skills, it does not apply to increases due to the Spellcasting Improvement archetype feature. 


\onecolumn
\section{Skill List}
\def\w{2.6}
\def\x{1}
\def\y{11.5}
\def\z{2}
\footnotesize

%%SkillBegin\begin{center} \tablealternate \begin{longtable}{|m{\w cm}  m{\y cm} m{\x cm} m{\z cm}|}\hline \tablehead \normalsize \bf Name  & \normalsize \bf Effect & \bf \normalsize Levels & \normalsize \bf Prerequisite \\ \hline \hline \bf \begin{flushleft} Ambidextrous\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}No penalty for using items in your non-dominant hand.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it FIN $> 10$\end{center}}  \\  \bf \begin{flushleft} Animagus\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Transform into an non-magical animal at will. This animal must be chosen at the moment you acquire this skill, and cannot be changed afterwards. Transforming costs 5FP and constitutes a major action.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Expert Thaumaturgy\end{center}}  \\  \bf \begin{flushleft} Apparate\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Perform a SPR (willpower) check.
Apparition difficulty is 18 / 17 / 15 / 15 / 12 / 12.
If successful, character teleports to a region that they are intimately familiar with (Beginner), have visited before (Adept), or have heard of (Master).\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Adept Sorcerer\end{center}}  \\  \bf \begin{flushleft} Archer\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Use a 1d4/ 1d6 / 1d8  /1d10  /1d12 / 1d20 dice to determine your long range accuracy checks.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Battlemage\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast Hexes \& Curses
You are able to use Hexes \& Curses which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Brawler\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Can perform non-magical melee attacks. Each level unlocks a different type of combat: 
\\ 1: Unarmed combat 
\\ 2: Small melee weapons (daggers, knives) 
\\ 3: One handed melee weapons (swords, spears, axes) 
\\ 4:  Two-handed melee weapons (warhammer, battleaxes, broadsword) 
\\ 5: Complex weapons\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Flying Lessons\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}At Beginner level, you become proficient in using broomsticks, and may use them to fly. Flight related checks gain a + 1 / 2 / 3 / 4 / 5 boost.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Catastrophic Critical\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Upon a critical hit opportunity, roll a 1d 4 / 6 / 8 / 10 / 20. Multiply the damage by the outcome of this dice roll. This overrides the usual critical procedure.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Clairvoyant\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast diviniation spells

You are able to use Divination spells which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Cleave\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}If a melee attack kills an opponent, you may perform a second attack using the same weapon on one adjacent opponent, dividing the damage done by 2 for every subsequent kill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Strength $>2$\end{center}}  \\  \bf \begin{flushleft} Defence Against the Dark Arts\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Take check-advantage when performing a resist check against any Dark-Arts spells cast by a wizard with an EVL less than your character level\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Defender\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast Recuperationspells
You are able to use Recuperation magic which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Eagle-Eyed\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Increases the effective range of your vision by 50\%\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Elegant Avoidance\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Can use either ATH(Speed) or FIN(precision) attribute to perform evasion checks.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Emergency Care\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You may take a major action to perform a {\it stabilization} action. Perform an EMP(healing) check (DV 15), if successful, remove the {\it Critical Condition} status and apply the {\it Critical but Stable} condition\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Familiar\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You may have one of the following to accompany you: 
\\ Beginner:   Newt, Toad 
\\ Novice:       Cat, Rat, Snake
 \\ Adept:        Owl, Poltergeist 
 \\ Expert:       Hippogriff, Phoenix 
\\Master:      (negotiate with your GM!)\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Flora \& Fauna > 2\end{center}}  \\  \bf \begin{flushleft} Fast Caster\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May cast an additional spell per major action. If the first spell fails, however, this negates the effect, and you may not complete the second spell. 
Does not apply to counterspells.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Adept Battlemage\end{center}}  \\  \bf \begin{flushleft} Focussed Caster\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}When interrupted (i.e. by taking damage) during a concentration spell, you may perform a d20 SPR(endurance) check (DV 14) to stay focussed.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Golden Touch\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Sell items for 50\% more than stated price.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it CHR $>10$\end{center}}  \\  \bf \begin{flushleft} Knife Handler\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Bladed weapons do + 1 / 2 / 3 / 4 / 5 damage, and they last twice as long before becoming dull.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it LVL 2\end{center}}  \\  \bf \begin{flushleft} Linguist\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}For each level of this skill, you can pick a new language to learn. Each language must be declared when levelling up. To learn Parseltongue, you require EVL to be greater than 4.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Magician\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast Illusion spells
You are able to use Illusion spells which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Meditation\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Fortitude regeneration gets a + 2 / 3 / 4 / 5 / 6 boost per turn where magic is not used.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Adept Defender\end{center}}  \\  \bf \begin{flushleft} Metamorphmagus\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Perform a CHR check. GM sets the difficulty dependent on the extent to which you must change your appearance, and the surrounding circumstances.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Expert Thaumaturgy\end{center}}  \\  \bf \begin{flushleft} Mimicry\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You can mimic the voice of another sapient, or the call of an animal, provided you have heard them for at least 1 minute previously.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it CHR > 13\end{center}}  \\  \bf \begin{flushleft} Momentum Dodge\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}If you begin the phase behind cover, you may emerge from cover, take an action, and still be considered to be in an evasion phase, taking a 4 / 3 / 2 / 1 / 0 point penalty to the evasion check. \\ You may not move the next turn.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it ATH > 10\end{center}}  \\  \bf \begin{flushleft} Muggle Lover\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}All muggle-related checks get check-advantage.
In addition, muggles are less likely to be suspicious of you.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Musician\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Replace your wand with your music: perform all illusion \& protective magic with your instrument of choice, using a CHR (performance) check. Spells take 2 turns to cast in this fashion. 
Using Silent Casting negates this effect.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Performance > 0\end{center}}  \\  \bf \begin{flushleft} Necromancer\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d/6/8/10/12/20 die to cast Dark Arts spells.
You can use Dark Arts spells which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} On the Ball\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Get 10 / 15 / 20 / 25 / 30 seconds to make a decision about a counterspell, rather than the usual 5\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Overcome Resistance\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Choose a damage type: fire, cold, electric, necrotic and holy. You may ignore any resistance below 100\% to this type. Every time you take this skill again, choose a different damage type.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Beginner Battlemage\end{center}}  \\  \bf \begin{flushleft} Parry\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Acts in place of a counterspell in close range physical combat. The attacker and defender both perform an ATH (strength) check (with weapon modifiers). If the defender succeeds, the attack fails.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Novice Brawler\end{center}}  \\  \bf \begin{flushleft} Proficiency Boost\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Choose one proficiency associated with an attribute with a score > 10. Increase that proficiency by 1.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}7\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Various\end{center}}  \\  \bf \begin{flushleft} Raw Power\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Once per day, may use perform a POW check to cast a spell, rather than the specified check, at the cost of doubling the FP cost of the cast.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Shadow Walker\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Every movement is considered as an Evasion Action, choosing to take an Evasive action grants check-advantage to evvasion check.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Stealth $>3$\end{center}}  \\  \bf \begin{flushleft} Signature Spell\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You may have 1/2/3 spells that are your `signatureÿ. These spells must be one level below your current level in their respective fields, but you get a +3 casting check on these spells.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}3\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Novice in at least one school\end{center}}  \\  \bf \begin{flushleft} Silent Magic\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Spells that normally require an incantation can be used silently.
Silent magic checks suffer   -4 / - 2 / 0 penalty to all checks.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}3\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Sleight of Hand\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}If a muggle catches you doing magic, perform a CHR (dexterity) check (difficulty 16) using sleight of hand to convince them that your magic is just trickery.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it FIN > 14\end{center}}  \\  \bf \begin{flushleft} Sorcerer\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast Charms \\
You are able to use Charms which match your skill in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Spellmaker\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Once per week, you may design your own spell (with GMs consent) by taking 1 hour. The GM will decide the appropriate type, level, DV and FP costs.The spell must be in a school you a Master in, and you must successfully cast it within three attempts for the spellmaking to be successful. 

If successful, the spellmaker memorises the spell. They may also transcribe the spell onto paper (1 major action) so others can book-cast it.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Master in at least one school\end{center}}  \\  \bf \begin{flushleft} Surge\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You may take one extra major action in your turn. This skill cannot be used again until you rest for 4+ hours.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Terrifying\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}All enemies perform a SPR (endurance) Resist check, whilst you perform a POW/EVL (intimidate) check (whichever is larger). If the check fails, target acquires {\it Terrified} status.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it POW $>14$ or EVL $>6$\end{center}}  \\  \bf \begin{flushleft} Thaumaturgus\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May use a 1d6/8/10/12/20 die to cast Transfiguration spells \\
You are able to use Transfiguration spells which match your level in this skill.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Auto-gained at LVL 1\end{center}}  \\  \bf \begin{flushleft} Undead Benefactor\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Healing spells work on the undead.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Novice Defender\end{center}}  \\  \bf \begin{flushleft} Wandless Magic\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}May cast a spell without using a wand. All wandless magic is also silent. Wandless magic casting checks take a 50\% penalty, unless used by a non-human species.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Adept Silent Magic\end{center}}  \\  \bf \begin{flushleft} Warder\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Protective spells and wards get a +2 / 3 / 4 / 5 / 6 bonus to their effectiveness.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Weak Spot\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Attacks when an opponentÿs armour is still intact get a +4 bonus.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Precision $>2$\end{center}}  \\  \bf \begin{flushleft} Withstand\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Resist checks may use a 1d6/8/10/12/20 dice.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Species: Behind the Scenes\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Stealth Proficiency gets +3 bonus. Your small stature means that all attacks on you are considered `precision' shots.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it House-Elf Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Corrupted Blood\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You are susceptible to Holy Damage. Wounds caused by silver or blessed weapons do double damage.

Prolongued (greater than 1 second) with silver does 5d8 holy damage (for vampires, this also extends to garlic, holy water and crucifixes).\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Vampire and Werewolf Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Enormous Size\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Strength, Health and Endurance proficiencies get +2 bonus. Stealth, Precision, Dexterity and Deception proficiencies get -1 penalty. You are considered proficient with all Strength-based weapons.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Half-Giant Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Fury\apos{}s Visage\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}In human form, Persuasion proficiency gets +3 bonus. 

Once per day, you may shed human form and take on the visage of the {\it Fury} for up to 1 hour, or until dismissed as a minor action. Replace all memorised spells with {\it Fury\apos{}s Fire}, gain a bonus to Resist checks equal to one third your character level and take the following stat modifiers:
ATH: +3, SPR: +2, POW: +4, CHR: -5, EVL:+ 4\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Half-Veela Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Night\apos{}s Child\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Gain a permanent nightvision bonus, but become susceptible to the sun. For every minute you spend exposed to sunlight, suffer a 1-point penalty to ATH, SPR and POW (min 0).\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Vampire Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Vampric Feeding\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}When within 1m of a target, you may use a major action to feed on them, dealing 2d4 necrotic damage (+1d4 for every two character levels above 2nd) to a target, and restore yourself the same amount of HP.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Vampire Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Wolfblood\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Gain a +3 bonus to Endurance proficiency, and +2 to Speed and Perception.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Werewolf Species Ability\end{center}}  \\  \bf \begin{flushleft} Species: Wolfmoon\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}When the full Moon rises, you take the form of a mindless beast (controlled by the GM) for 12 hours, unless the Wolfsbane potion is taken.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Werewolf Species Ability\end{center}}  \\  \bf \begin{flushleft} Spellbinder\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Gain a +1/2/3/4/5 point bonus on enchanting checks.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it Adept Thaumaturge\end{center}}  \\  \bf \begin{flushleft} Tool-User\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}Choose a new tool to become proficient in.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}5\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \bf \begin{flushleft} Merciful\end{flushleft}  &   \parbox[t]{\y cm}{\begin{flushleft}You may attempt to turn a lethal blow into a knockout strike. When performing an attack that would otherwise kill the target, perform a DV 6 FIN (Precision) check. If it passes, the target is knocked unconscious, rather than killed.\end{flushleft}}  &   \parbox[t]{\x cm}{\begin{center}1\end{center}}  &   \parbox[t]{\z cm}{\begin{center} \it \end{center}}  \\  \hline\end{longtable} \end{center}%%SkillEnd

\twocolumn
\normalsize

