\begin{multicols}{4} \raggedbottom\subsubsection{Charms}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Banshee Wail

\item Create Fire (*) 

\item Create Trap (*) 

\item Create Water (*) 

\item Fresh Air

\item Halt

\item Illuminate Wand

\item Levitation (*) 

\item Mark Surface

\item Preserve Object


\end{itemize}
} \vfill\subsubsection{Dark Arts}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Blight (*) 

\item Eldritch Knowledge

\item Shadow Blast (*) 

\item Shroud of Darkness

\item Vicious Slash (*) 


\end{itemize}
} \vfill\subsubsection{Divination}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Astral Assistance (*) 

\item Hunter\apos{}s Mark

\item Identify

\item Locate (*) 

\item Receive Omen

\item Sense Traps

\item Speak in Tongues

\item Telepathic Bond


\end{itemize}
} \vfill\subsubsection{Hexes}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Acidic Burst (*) 

\item Cause Confusion

\item Green Sparks (*) 

\item Knockback

\item Sting (*) 

\item Trip


\end{itemize}
} \vfill\subsubsection{Illusion}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Blur (*) 

\item Chaotic Whispers (*) 

\item Charm Entity

\item Glamour (*) 

\item Imbue Bravery

\item Night Vision

\item Throw Voice


\end{itemize}
} \vfill\subsubsection{Recuperation}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Aid Charm (*) 

\item Caterwauling Ward

\item Magical Shield (*) 

\item Minor Healing

\item Privacy Ward

\item Reinforce Shield (*) 

\item Stoneskin

\item Sunburst (*) 


\end{itemize}
} \vfill\subsubsection{Transfiguration}
\vbox{
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Alter Hair

\item Basic Transmutation (*) 

\item Change Colour

\item Conjure Flowers

\item Launch Spike (*) 

\item Potion Mixing Spell

\item Silver Shield (*) 

\item Steelclaw


\end{itemize}
} \vfill~\vfill~\end{multicols}\clearpage\begin{multicols}{3}\spell{name = Acidic Burst, incant = ambustum, school = Hex, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 4, duration = 2 minutes,higher = An Adept level caster may add 1d6 damage for every 3 character levels over 5th level.,effect =Fills a cube of size 4m with an acidic cloud that does 5 acid damage per turn. In a confined space\comma{} the cloud lasts indefinitely.}
\spell{name = Aid Charm, incant = subsidium, school = Recuperant, type = Instant, level =Beginner, fp = 2, attribute =EMP, proficiency = , noProf = 1, dv = 3, duration = 1 hour,higher = At 4th\comma{} 8th\comma{} 12th and 16th levels\comma{} the HP ceiling is raised by 5\comma{} 8\comma{} 10\comma{} and 15 respectively.,effect =Raise the HP ceiling of a target by 3. If target has HP$>0$\comma{} also increase HP by this amount.}
\spell{name = Alter Hair, incant = crinus muto, school = Transfiguration, type = Instant, level =Beginner, fp = 2, attribute =CHR, proficiency = Deception, dv = 4, duration = 2 hours,higher = ,noHigh = 1, effect =Alters the colour and style of the casters hair. Useful for disguises.}
\spell{name = Astral Assistance, incant = auxilio, school = Divination, type = Ritual (2 turns), level =Beginner, fp = 5, attribute =EMP, proficiency = Arcane, dv = 5, duration = 0,noDur = 1, higher = An expert\minus{}level caster may roll 2d4 when performing this spell.,effect =By laying your hand upon a sapient being\comma{} you may channel magical energy into them. On the next check the target performs\comma{} roll 1d4\comma{} and add it to the check (+1 per PP\comma{} max 3). If the check fails\comma{} both the target and the caster take 1d6 psychic damage.}
\spell{name = Banshee Wail, incant = magnus surgerus, school = Charm, type = Instant, level =Beginner, fp = 3, attribute =SPR, proficiency = Performance, dv = 5, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =All targets in hearing range take 2 points of psychic damage (+3 per PP)\comma{} and awaken if they are sleeping.}
\spell{name = Basic Transmutation, incant = formum mutatio, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, duration = 1 hour,higher = A character above 6th level may add 1 free PP for every 3 character levels above 3rd.,effect =Transform a 200g non\minus{}sapient animal or object into a different animal or solid object. 
Each power point doubles the mass of objects that can be transformed.  Objects must be simple in nature.}
\spell{name = Blight, incant = thanatos, school = Abomination, type = Instant, level =Beginner, fp = 4, attribute =EVL, proficiency = , noProf = 1, dv = 5, duration = 0,noDur = 1, higher = An adept level caster may add an extra d4 of damage for every 4 character levels above 2nd.,effect =A cylinder of necrotic energy extends outwards from you in a radius of 10m (doubled with every PP\comma{} max 1km). All simple plants within range die instantly\comma{} and all other living beings take 1d4 necrotic damage (+1 per PP)}
\spell{name = Blur, incant = celeritate, school = Illusion, type = Instant, level =Beginner, fp = 4, attribute =CHR, proficiency = , noProf = 1, dv = 3, duration = 3 turns,higher = When cast by an adept\minus{}level caster\comma{} the first attack directed at the target also automatically misses.,effect =The target seems to become blurry around the edges\comma{} it is difficult to tell exactly where they are\comma{} and where they aren{\apos}t.
Gain check advantage on evasion checks for 3 turns.}
\spell{name = Caterwauling Ward, incant = caterwaul, school = Recuperant, type = Ward, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 3, duration = 2 weeks,higher = ,noHigh = 1, effect =Casts a ward on the area which emits a high\minus{}pitched scream when an unknown being crosses the threshold. 
Radius is (10 + $2\times$PP) metres. Ward decays after 2 weeks.}
\spell{name = Cause Confusion, incant = confundo, school = Hex, type = Instant, level =Beginner, fp = 5, attribute =CHR, proficiency = Deception, dv = 3, duration = 3 turns,higher = ,noHigh = 1, effect =Target performs a Resist Magic check against casting check\comma{} if it fails\comma{} then target acquires the Confused status.  If it succeeds\comma{} do 5 fatigue damage.}
\spell{name = Change Colour, incant = pigmentus, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 4, duration = 2 days,higher = ,noHigh = 1, effect =Causes the colour of an object to change.}
\spell{name = Chaotic Whispers, incant = rastarum, school = Illusion, type = Concentration, level =Beginner, fp = 4, attribute =SPR, proficiency = Deception, dv = 4, duration = 2 minutes,higher = At 7th\comma{} 15th and 18th level\comma{} use a d6\comma{} d10 and d12 respectively for the damage check.,effect =Target hears a voice in their ear whispering maddening words\comma{} that slowly drive them insane. Target takes (1 + PP)d4  psychic damage per turn\comma{} unless they pass a SPR(endurance) Resist check against the casting check\comma{} at which point the spell is broken.}
\spell{name = Charm Entity, incant = sismeus amici, school = Illusion, type = Instant, level =Beginner, fp = 5, attribute =CHR, proficiency = Persuasion, dv = 4, duration = 1 hour,higher = ,noHigh = 1, effect =Causes the target to like you\comma{} persuasion checks get a (2+PP) bonus\comma{} max 5.}
\spell{name = Conjure Flowers, incant = orchideous, school = Transfiguration, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiency = , noProf = 1, dv = 5, duration = 3 days,higher = ,noHigh = 1, effect =Conjures flowers from thin air.}
\spell{name = Create Fire, incant = incendio, school = Charm, type = Concentration, level =Beginner, fp = 3, attribute =SPR, proficiency = , noProf = 1, dv = 3, duration = 0,noDur = 1, higher = An Adept\minus{}level caster may summon a larger gout of flame\comma{} which does an extra 1d6 fire damage for every 4 character levels above 2nd.,effect =A small jet of fire is emitted from the tip of your wand. 
Coming into contact with fire does 1d6 fire damage\comma{} and applies a minor Burned status effect.}
\spell{name = Create Trap, incant = dolus, school = Charm, type = Ritual (2 turns), level =Beginner, fp = 4, attribute =FIN, proficiency = Stealth, dv = 5, duration = 0,noDur = 1, higher = A character above 10th level may add free PP to the effect\minus{}spell equal to one\minus{}third their character level.,effect =Combine a magical ward with one of your existing spells. After casting the trap spell\comma{} cast the effect\minus{}spell to imbue the trap with that effect. 
If successful\comma{} creates a hidden magical trap of radius 50cm on any solid surface\comma{} with the effect of the original spell when triggered by an entity touching the trap. If you wish to keep a trap hidden from the GM\comma{} write down the location\comma{} spell and associated check values on a piece of paper\comma{} to be revealed when the trap is triggered.}
\spell{name = Create Water, incant = aguamente, school = Charm, type = Concentration, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = An adept\minus{}level caster may summon a torrent of water\comma{} which does 1d4 bludgeoning damage for every 3 character levels above 3rd.,effect =A jet of water is emitted from the tip of your wand\comma{} useful for extinguishing fires\comma{} or cleaning surfaces\comma{} however conjured water cannot be drunk.}
\spell{name = Eldritch Knowledge, incant = vetitum scenticus, school = Abomination, type = Ritual (3 turns), level =Beginner, fp = 6, attribute =EVL, proficiency = Arcane, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Gain access to eldritch knowledge. The Demons of the Deep will answer one of your questions\comma{} but the answers might drive you mad.
The question must be said out loud for all to hear\comma{} but the answer may be written down and passed to your privately.}
\spell{name = Fresh Air, incant = klinneract, school = Charm, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =A gust of air refreshes the air in a 2m radius (+1 per POW) around the caster\comma{} removing any gaseous effects and smelling faintly of lavender.}
\spell{name = Glamour, incant = lux stultium, school = Illusion, type = Instant, level =Beginner, fp = 3, attribute =INT, proficiency = Deception, dv = 3, duration = 1 hour,higher = When cast by a character greater than 8th level\comma{} the DV of the check is equal to the caster level.,effect =Create a superficial glamour around a person or object\comma{} a simple trick of the light. The glamour disintegrates upon physical or magical contact\comma{} and can be seen to be fake if an observer passes an INT(perception) Resist check\comma{} DV=5.}
\spell{name = Green Sparks, incant = verdimillious, school = Hex, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = Every 3 character levels above 2nd level\comma{} add another spark.,effect =Emits 3 green sparks from your wand\comma{} which can be made to strike at the enemy. 
Each spark does 1 force damage \cvdv.}
\spell{name = Halt, incant = stabit, school = Charm, type = Instant, level =Beginner, fp = 2, attribute =SPR, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Stop 1 inanimate object in its tracks\comma{} if mid\minus{}air\comma{} it drops to the ground. If the target is particularly small or fast (i.e. an arrow in mid\minus{}flight) the caster must pass a FIN(precision) check (DV 12) in order to hit the target.}
\spell{name = Hunter\apos{}s Mark, incant = venari, school = Divination, type = Instant, level =Beginner, fp = 3, attribute =INT, proficiency = , noProf = 1, dv = 4, duration = 3 days,higher = ,noHigh = 1, effect =If casting check exceeds passive resist value\comma{} caster is aware of the location of the target for the next 3 days\comma{} or until the mark is removed by magical means.}
\spell{name = Identify, incant = dicemi, school = Divination, type = Instant, level =Beginner, fp = 6, attribute =INT, proficiency = Research, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Learn the properties of the target: be it learning about the nature of the target\comma{} or the ingredients of a potion.
The more power points dedicated to the spell\comma{} the more information that is revealed.}
\spell{name = Illuminate Wand, incant = lumos, school = Charm, type = Concentration, level =Beginner, fp = 1, attribute =INT, proficiency = , noProf = 1, dv = 2, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Causes the tip of your wand to glow\comma{} like a torch. Casts bright light for 2m radius\comma{} and dim light for 10m. Spell last indefinitely\comma{} until concentration is broken\comma{} and does not require extra FP per turn.}
\spell{name = Imbue Bravery, incant = fortudus, school = Illusion, type = Instant, level =Beginner, fp = 2, attribute =SPR, proficiency = Persuasion, dv = 3, duration = 1 hour,higher = ,noHigh = 1, effect =Imbue your target with fortitude and vigour. They gain check\minus{}advantage on all Fear\minus{}Resist checks for 1 hour.}
\spell{name = Knockback, incant = flipendo, school = Hex, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =A wave of energy strikes into the target\comma{} causing (1+(PP)d4) force damage\comma{} and pushing the target backwards up to (1+PP) metres.}
\spell{name = Launch Spike, incant = voco dens, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = An expert\minus{}level caster may do 1d12 piercing damage per spike,effect =Conjure (1+PP) enormous spikes to transfigure itself from the surrounding walls/floor\comma{} impaling the target. Each spike does 1d6 piercing damage.}
\spell{name = Levitation, incant = wingardium leviosa, school = Charm, type = Concentration, level =Beginner, fp = 5, attribute =FIN, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = A character above 6th level may add 1 free PP for every 3 character levels above 3rd.,effect =Cause an object of 500g or less to levitate\comma{} controlling the vertical distance at will. 
Each power point dedicated doubles the mass of the object that can be lifted.}
\spell{name = Locate, incant = locus, school = Divination, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiency = Research, dv = 4, duration = 0,noDur = 1, higher = An master\minus{}level clairvoyant may perform a SPR(willpower) check to overcome magical shields blocking this spell\apos{}s effect.,effect =Learn the location of non\minus{}magical objects or an unshielded living being.}
\spell{name = Magical Shield, incant = protego, school = Recuperant, type = Concentration, level =Beginner, fp = 5, attribute =POW, proficiency = , noProf = 1, dv = 5, duration = 0,noDur = 1, higher = When cast by a character greater than 10th level\comma{} the AC provided is equal to the character level + $2 \times PP$.,effect =Erects an ethereal shield in front of you that absorbs incoming magical attacks.
Shielding charm provides a magical AC by 10+PP against all incoming spells\comma{} but does not protect against physical damage\comma{} or the aftereffects of magic (i.e. a nearby explosion). This AC is eroded by all damage\minus{}causing effects.}
\spell{name = Mark Surface, incant = stylum, school = Charm, type = Concentration, level =Beginner, fp = 2, attribute =FIN, proficiency = Dxterity, dv = 2, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Use your wand as anything from a thin marker to a thick paintbrush\comma{} the {\it paint} is a magical adhesive that sticks to any surface\comma{} and may be of any colour you choose.}
\spell{name = Minor Healing, incant = enervate, school = Recuperant, type = Concentration, level =Beginner, fp = 3, attribute =EMP, proficiency = Healing, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Heal for 2 points per turn. 
If the target has a serious wound\comma{} i.e. a broken bone\comma{} cannot heal beyond 50\% health. Only works on living creatures.}
\spell{name = Night Vision, incant = aspectu, school = Illusion, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiency = Perception, dv = 3, duration = 2 hours,higher = ,noHigh = 1, effect =Give the target nightvision for one hour: dim light is as bright as daylight\comma{} and darkness is consdiered dim.}
\spell{name = Potion Mixing Spell, incant = , noIncant = 1, school = Transfiguration, type = Ritual(5 turns), level =Beginner, fp = 2, attribute =INT, proficiency = Arcane, dv = 0, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Used to mix a potion. See page \pageref{S:Enchanting} for details.}
\spell{name = Preserve Object, incant = preseritas, school = Charm, type = Instant, level =Beginner, fp = 2, attribute =FIN, proficiency = dexterity, dv = 3, duration = 10 days,higher = ,noHigh = 1, effect =The target is unaffected by the flow of time for the duration of the spell\comma{} and does not rot or otherwise decay.}
\spell{name = Privacy Ward, incant = muffliato, school = Recuperant, type = Ward, level =Beginner, fp = 6, attribute =SPR, proficiency = , noProf = 1, dv = 4, duration = 1 hour,higher = ,noHigh = 1, effect =A buzzing sound fills the ears of anyone trying to listen in on your conversations whilst you are in the warded area. Lasts for one hour\comma{} and has a radius of 2m.}
\spell{name = Receive Omen, incant = , noIncant = 1, school = Divination, type = Ritual (3 turns), level =Beginner, fp = 2, attribute =INT, proficiency = , noProf = 1, dv = 3, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Use your tea leaves to receive an omen about the future. Ask a question about the outcome of an event. The tea leaves will tell you if the outcome is positive\comma{} negative\comma{} or neutral. Takes 4 minutes to cast.}
\spell{name = Reinforce Shield, incant = praesidium, school = Recuperant, type = Concentration, level =Beginner, fp = 2, attribute =INT, proficiency = Arcane, dv = 4, duration = 0,noDur = 1, higher = When cast by an expert\minus{}level caster\comma{} you may restore a shield to 150\% of its original strength.,effect =Restore the strength of a target shield or magical ward by (2+PP) points per turn that this spell is maintained. Cannot restore the strength to more than the original level.}
\spell{name = Sense Traps, incant = antidolus, school = Divination, type = Instant, level =Beginner, fp = 4, attribute =INT, proficiency = Understand Other, dv = 5, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Attempt to discover any traps in your immediate vicinity. If successful\comma{} you may learn the location of the trap\comma{} and the trigger (but not the effect). Success conditions are set by the GM.}
\spell{name = Shadow Blast, incant = malusangui, school = Abomination, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 2, duration = 0,noDur = 1, higher = An novice\minus{}level caster does 2 extra points for each point that the CV exceeds the DV\comma{} and an Expert\minus{}level caster does 4 extra.,effect =Hurl shadows at you enemy\comma{} dealing 1 necrotic damage for every casting point over the difficulty level.}
\spell{name = Shroud of Darkness, incant = tenebrosa, school = Abomination, type = Instant, level =Beginner, fp = 4, attribute =EVL, proficiency = , noProf = 1, dv = 4, duration = 2 minutes,higher = ,noHigh = 1, effect =Extinguish all light within a (10 + 2$\times$PP) metre radius\comma{} and all attempts to create new light fail\comma{} unless caster\apos{} passive POW check exceds the casting check.}
\spell{name = Silver Shield, incant = argentipus, school = Transfiguration, type = Instant, level =Beginner, fp = 6, attribute =INT, proficiency = , noProf = 1, dv = 5, duration = 1 hour,higher = When cast by a character above 10th level\comma{} the shield no longer degrades with each strike\comma{} and instead acts as a normal shield with an AC equal to 15 + 2$\times$PP.,effect =Conjures a floating silver shield from thin air\comma{} to defend you. Shield absorbs both physical and magical attacks for up to (15+2$\times$PP) damage points\comma{} before breaking. The caster has limited control over the shield whilst it is active\comma{} using a major action to move it up to 3m in any direction.}
\spell{name = Speak in Tongues, incant = lingua maxima, school = Divination, type = Ritual (5 minutes), level =Beginner, fp = 8, attribute =EMP, proficiency = Understand Other, dv = 4, duration = 4 minutes,higher = ,noHigh = 1, effect =By meditating for 5 minutes\comma{} you may understand and speak the language of a willing target individual. Target must be a sapient being\comma{} or otherwise able to speak at least one language.}
\spell{name = Steelclaw, incant = ferscabere, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, duration = 1 day,higher = ,noHigh = 1, effect =Transfigures an animal{\apos}s claws into large steel talons\comma{} increasing their physical damage by (5 + 2$\times$PP)}
\spell{name = Sting, incant = ictus, school = Hex, type = Instant, level =Beginner, fp = 5, attribute =SPR, proficiency = , noProf = 1, dv = 2, duration = 0,noDur = 1, higher = An expert level caster may add 2 damage \cvdv\comma{} rather than the usual 1.,effect =Stings the target for 2 poison damage\comma{} plus one \cvdv.}
\spell{name = Stoneskin, incant = lapis pellium, school = Recuperant, type = Instant, level =Beginner, fp = 4, attribute =SPR, proficiency = Endurance, dv = 4, duration = 5 minutes,higher = ,noHigh = 1, effect =Increase the target{\apos} AC by 10+PP. Does not stack.}
\spell{name = Sunburst, incant = sol maxima, school = Recuperant, type = Instant, level =Beginner, fp = 4, attribute =SPR, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = When cast by a character greater than 6th level\comma{} do 1d6 extra damage for every 3 levels above 3rd.,effect =A burst of bright light does 1d6 holy damage to all targets in a sphere 5m radius.}
\spell{name = Telepathic Bond, incant = conanimus, school = Divination, type = Ritual (2 turns), level =Beginner, fp = 5, attribute =EMP, proficiency = Understand Other, dv = 5, duration = 2 days,higher = ,noHigh = 1, effect =Form a mental connection between your mind and the mind of a willing target. You may then use this connection to communicate silently. Target must be within touching distance when the spell is cast\comma{} but the bond has no distance limit after that.}
\spell{name = Throw Voice, incant = ventrilofors, school = Illusion, type = Concentration, level =Beginner, fp = 4, attribute =INT, proficiency = Deception, dv = 2, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =Cast your voice such that it appears to be coming from somewhere up to 5+$\times PP$ metres away.}
\spell{name = Trip, incant = lubricor, school = Hex, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = ,noHigh = 1, effect =If the target is moving this turn cycle and fails an ATH Resist check\comma{} they go sprawling onto the ground taking 1d4 bludgeoning damage\comma{} and take the `Prone Position’ status.}
\spell{name = Vicious Slash, incant = sectumsempra, school = Abomination, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, duration = 0,noDur = 1, higher = At 8th level\comma{} do 2d6 damage. At 14th\comma{} use 4d6\comma{} and at 20th level\comma{} use 10d6.,effect =Gouges at the target\comma{} leaving deep\comma{} cursed wounds\comma{} for 1d6 points of slashing damage.}
\end{multicols}