\begin{multicols}{4} \raggedbottom\subsubsection{Charms}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Banshee Wail

\item Create Fire

\item Create Trap

\item Create Water

\item Fresh Air

\item Halt

\item Illuminate Wand

\item Levitation

\item Mark Surface

\item Preserve Object


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Cut Object

\item Fix Object

\item Haste

\item Lightning Bolt

\item Lock

\item Mage Hands

\item Silence

\item Smokescreen

\item Stick

\item Summon Object

\item Unlock


\end{itemize}
\subsubsection{Dark Arts}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Blight

\item Eldritch Knowledge

\item Shadow Blast

\item Shroud of Darkness

\item Vicious Slash


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Contagion

\item Dark Healing

\item Incomprehensible Torture

\item Instill Terror

\item Necrosis

\item Plague of Insects

\item Summon Void


\end{itemize}
\vfill\null
\columnbreak\subsubsection{Divination}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Astral Assistance

\item Hunter\apos{}s Mark

\item Identify

\item Locate

\item Receive Omen

\item Sense Traps

\item Speak in Tongues

\item Telepathic Bond


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item All\minus{}seeing Eye

\item Astral Caltrops

\item Crystal Gazing

\item Detect Magic

\item Detect Thoughts

\item Eavesdrop

\item Obfuscation


\end{itemize}
\subsubsection{Hexes \& Curses}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Acidic Burst

\item Cause Confusion

\item Green Sparks

\item Knockback

\item Sting

\item Trip


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Arctic Chill

\item Cascading Missiles

\item Disarm

\item Hoist Enemy

\item Mental Burden

\item Perpetual Hunger

\item Prevent Movement

\item Strangle

\item Stunning Blast

\item Summon Bat Bogeys


\end{itemize}
\vfill\null
\columnbreak\subsubsection{Illusion}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Blur

\item Chaotic Whispers

\item Charm Entity

\item Glamour

\item Imbue Bravery

\item Night Vision

\item Throw Voice


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Blinding Light

\item Calming Aura

\item Conceal Inscription

\item Enchant Animal

\item Piper{\apos}s Illusion

\item Sleep

\item Violent Phantasms


\end{itemize}
\subsubsection{Recuperation}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Aid Charm

\item Caterwauling Ward

\item Magical Shield

\item Minor Healing

\item Privacy Ward

\item Reinforce Shield

\item Stoneskin

\item Sunburst


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Anti\minus{}Muggle Ward

\item Checkup

\item Countercurse

\item Heal Being

\item Lesser Ward

\item Release Trapped Being

\item Runic Shield

\item Stabilise Patient


\end{itemize}
\vfill\null
\columnbreak\subsubsection{Transfiguration}
\textbf{Level 1 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Alter Hair

\item Basic Transmutation

\item Change Colour

\item Conjure Flowers

\item Launch Spike

\item Potion Mixing Spell

\item Silver Shield

\item Steelclaw


\end{itemize}
\textbf{Level 2 Spells}
\begin{itemize}[itemsep=0em]
\renewcommand\labelitemi{-}
\item Conjure Bubble

\item Fabricate Object

\item Harden Object

\item Make Trecherous

\item Pumpkin Head

\item Summon Snake

\item Summon Weak Avatar

\item Thick Air


\end{itemize}
\end{multicols}\clearpage\begin{multicols}{3}\spell{name = Acidic Burst, incant = ambustum, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 4, effect =Fills a 5m target area with an acidic cloud that does (1+ CV – DV) acid damage per turn. Cloud lasts for 10 cycles\comma{} unless in a confined space\comma{} where it lasts until removed by other means.}
\spell{name = Aid Charm, incant = subsidium, school = Recuperation, type = Instant, level =Beginner, fp = 2, attribute =EMP, proficiency = , noProf = 1, dv = 4, effect =Target has HP ceiling raised by 5 points for 1 hour}
\spell{name = All\minus{}seeing Eye, incant = orbis, school = Divination, type = Instant, level =Novice, fp = 4, attribute =INT, proficiency = Perception, dv = 6, effect =You may create an invisible\comma{} magic eye in front of you\comma{} that hovers. You mentally see everything that the eye sees\comma{} and may use a major action to instruct the eye to move up to 10m in any direction (including vertical). Eye cannot pass through solid walls\comma{} but may squeeze through gaps as small as 4cm in diameter.}
\spell{name = Alter Hair, incant = crinus muto, school = Transfiguration, type = Instant, level =Beginner, fp = 2, attribute =CHR, proficiency = Deception, dv = 4, effect =Alters the colour and style of the casters hair. Useful for disguises. Degrades after 5 hours.}
\spell{name = Anti\minus{}Muggle Ward, incant = repello mugletum, school = Recuperation, type = Ward, level =Novice, fp = 6, attribute =INT, proficiency = , noProf = 1, dv = 7, effect =Forms a warded area that muggles can neither see\comma{} nor enter. 
The warded area is a circle 5m in radius + 5m for every power point dedicated to the spell.}
\spell{name = Arctic Chill, incant = gelidus, school = Hexes \& Curses, type = Concentration, level =Novice, fp = 7, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =An area of (2 + PP) metres around the target is decreased in temperature by 50 degrees celsius. Those caught in the region take (1+PP)d4 of cold damage\comma{} and apply the mild Frostbite status effect.}
\spell{name = Astral Assistance, incant = auxilio, school = Divination, type = Ritual (2 turns), level =Beginner, fp = 5, attribute =EMP, proficiency = Arcane, dv = 5, effect =By laying your hand upon a sapient being\comma{} you may channel magical energy into them. On the next check the target performs\comma{} roll 1d4\comma{} and add it to the check (+1 per PP\comma{} max 3). If the check fails\comma{} both the target and the caster take 1d6 psychic damage.}
\spell{name = Astral Caltrops, incant = Caltrops, school = Divination, type = Instant, level =Novice, fp = 5, attribute =SPR, proficiency = , noProf = 1, dv = 7, effect =The target acts as if the terrain posseses caltrops for 10 turns. Caltrops do psychic damage}
\spell{name = Banshee Wail, incant = magnus surgerus, school = Charms, type = Instant, level =Beginner, fp = 3, attribute =SPR, proficiency = Performance, dv = 5, effect =All targets in hearing range take 2 points of psychic damage (+3 per PP)\comma{} and awaken if they are sleeping.}
\spell{name = Basic Transmutation, incant = formum mutatio, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, effect =Transform a 200g non\minus{}sapient animal or object into a different animal or solid object. 
Each power point doubles the mass of objects that can be transformed.  Lasts for 1 hour. Objects must be simple in nature.}
\spell{name = Blight, incant = thanatos, school = Dark Arts, type = Instant, level =Beginner, fp = 4, attribute =EVL, proficiency = , noProf = 1, dv = 5, effect =A wave of necrotic energy extends outwards from you in a radius of 10m (doubled with every PP\comma{} max 1km). All plants within range die instantly\comma{} and all other living beings take 1d4 necrotic damage (+1 per PP)}
\spell{name = Blinding Light, incant = caecus, school = Illusion, type = Instant, level =Novice, fp = 5, attribute =POW, proficiency = , noProf = 1, dv = 5, effect =Direct a brilliant beam of light at the target. If target fails an INT(Perception) Resist check against the casting check\comma{} they are blinded for 4 turns.}
\spell{name = Blur, incant = celeritate, school = Illusion, type = Instant, level =Beginner, fp = 4, attribute =CHR, proficiency = , noProf = 1, dv = 3, effect =The target seems to become blurry around the edges\comma{} it is difficult to tell exactly where they are\comma{} and where they aren{\apos}t.
Gain check advantage on evasion checks for 3 turns.}
\spell{name = Calming Aura, incant = paxus, school = Illusion, type = Instant, level =Novice, fp = 8, attribute =CHR, proficiency = Willpower, dv = 6, effect =Calms the target down. Remove terrified status from target.}
\spell{name = Cascading Missiles, incant = unda delor, school = Hexes \& Curses, type = Instant, level =Novice, fp = 5, attribute =FIN, proficiency = , noProf = 1, dv = 7, effect =Fires multiple bursts of energy that do 3+1d4 force damage to up to (3+PP) targets. 
Each power point added adds +1 damage\comma{} and +1 target.}
\spell{name = Caterwauling Ward, incant = caterwaul, school = Recuperation, type = Ward, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 3, effect =Casts a ward on the area which emits a high\minus{}pitched scream when an unknown being crosses the threshold. 
Radius is (10 + $2\times$PP) metres. Ward decays after 2 weeks.}
\spell{name = Cause Confusion, incant = confundo, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 5, attribute =CHR, proficiency = Deception, dv = 3, effect =Do 2 Fatigue damage.
Target performs a Resist Magic check against casting check\comma{} if it fails\comma{} then target acquires the Confused status.  If it succeeds\comma{} do 5 fatigue damage.}
\spell{name = Change Colour, incant = pigmentus, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 4, effect =Causes the colour of an object to change. Lasts for 2 days.}
\spell{name = Chaotic Whispers, incant = rastarum, school = Illusion, type = Concentration, level =Beginner, fp = 4, attribute =SPR, proficiency = Deception, dv = 4, effect =Target hears a voice in their ear whispering maddening words\comma{} that slowly drive them insane. Target takes (1 + PP)d4  psychic damage per turn\comma{} until they pass a SPR(endurance) Resist check with DV = casting check.}
\spell{name = Charm Entity, incant = sismeus amici, school = Illusion, type = Instant, level =Beginner, fp = 5, attribute =CHR, proficiency = Persuasion, dv = 4, effect =Causes the target to like you\comma{} persuasion checks get a (2+PP) bonus\comma{} max 5.}
\spell{name = Checkup, incant = dispungo, school = Recuperation, type = Instant, level =Novice, fp = 6, attribute =EMP, proficiency = Understand Other, dv = 6, effect =Enquire as to the health status of the target\comma{} find out their remaining HP\comma{} as well as any status effects they currently posses.}
\spell{name = Conceal Inscription, incant = occulto, school = Illusion, type = Instant, level =Novice, fp = 6, attribute =INT, proficiency = Deception, dv = 4, effect =Makes a message\comma{} drawing or marking on a surface invisible to the naked eye.}
\spell{name = Conjure Bubble, incant = ebublio, school = Transfiguration, type = Instant, level =Novice, fp = 6, attribute =FIN, proficiency = , noProf = 1, dv = 6, effect =Conjures a large\comma{} hard\minus{}to\minus{}pop airtight bubble (strength 8) which the caster can use to encase enemies\comma{} or to protect themselves.}
\spell{name = Conjure Flowers, incant = orchideous, school = Transfiguration, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiency = , noProf = 1, dv = 5, effect =Conjures flowers from thin air. Lasts for 3 days.}
\spell{name = Contagion, incant = vastantes, school = Dark Arts, type = Instant, level =Novice, fp = 6, attribute =EVL, proficiency = , noProf = 1, dv = 6, effect =If target fails a Resist (health) check against the casting check\comma{} contracts a disease. All positive modifiers and proficiency bonuses are set to zero until cured. Disease is contagious and each time they touch an afflicted individual\comma{} being must Resist\comma{} or contract the disease also.}
\spell{name = Countercurse, incant = finite maledictum, school = Recuperation, type = Instant, level =Novice, fp = 5, attribute =INT, proficiency = Arcane, dv = 6, effect =Remove the effects of an active curse or hex. The caster of the curse performs the casting check again: If the casting check of the counterpsell (+1 for each power point dedicated) is larger than this second check\comma{} the curse is removed.}
\spell{name = Create Fire, incant = incendio, school = Charms, type = Concentration, level =Beginner, fp = 3, attribute =SPR, proficiency = , noProf = 1, dv = 3, effect =A small jet of fire is emitted from the tip of your wand. 
Coming into contact with fire does 1d6 fire damage\comma{} and applies a minor Burned status effect.
(Larger jets of fire have a difficulty of 9\comma{}  do 4d6  fire damage and apply a Moderate burn)}
\spell{name = Create Trap, incant = dolus, school = Charms, type = Ritual (2 turns), level =Beginner, fp = 4, attribute =FIN, proficiency = Stealth, dv = 5, effect =Combine a magical ward with one of your existing spells. Cast the other spell first\comma{} then perform the trapping check.
If successful\comma{} creates a hidden magical trap of radius 50cm on any solid surface\comma{} with the effect of the original spell when triggered by an entity touching the trap. The effects of the trap are less than the original spell\comma{} but more power points make the trap more powerful. 
If you wish to keep a trap hidden from the GM\comma{} write down the location\comma{} spell and associated check values on a piece of paper\comma{} to be revealed when the trap is triggered.}
\spell{name = Create Water, incant = aguamente, school = Charms, type = Concentration, level =Beginner, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 4, effect =A jet of water is emitted from the tip of your wand\comma{} useful for extinguishing fires\comma{} or cleaning surfaces. 
(Larger jets of water have a difficulty of 16. Conjured water cannot be drunk)}
\spell{name = Crystal Gazing, incant = Gazing, school = Divination, type = Ritual (4 turns), level =Novice, fp = 3, attribute =EMP, proficiency = , noProf = 1, dv = 7, effect =Gaze into your crystal ball\comma{} and ask a question of the cosmos. You will receive a yes or a no answer to any question you ask.}
\spell{name = Cut Object, incant = diffindo, school = Charms, type = Instant, level =Novice, fp = 6, attribute =FIN, proficiency = Precision, dv = 5, effect =Cut two objects apart. 
If used on a living being\comma{} causes a deep cut\comma{} for 1d6 + 3 slashing damage.}
\spell{name = Dark Healing, incant = tenebrosa sudarium, school = Dark Arts, type = Instant, level =Novice, fp = 6, attribute =POW, proficiency = , noProf = 1, dv = 5, effect =Heal for one HP for each casting point over the difficulty. Remove half of this HP from an ally.}
\spell{name = Detect Magic, incant = revelio, school = Divination, type = Instant, level =Novice, fp = 5, attribute =EMP, proficiency = , noProf = 1, dv = 5, effect =Reveals to the caster any active spells in the in 15m range. Will deactivate charms whose sole purpose is to remain hidden.}
\spell{name = Detect Thoughts, incant = psychopractum, school = Divination, type = Concentration, level =Novice, fp = 15, attribute =EMP, proficiency = Understand Other, dv = 7, effect =You may observe the mind of a target individual. Unlike legilimency\comma{} thought\minus{}detection is not an exact science\comma{} and you will only get a vague shape of their thoughts. If casting check is below the target{\apos}s passive perception\comma{} they become aware of the process.}
\spell{name = Disarm, incant = expelliarmus, school = Hexes \& Curses, type = Instant, level =Novice, fp = 6, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =Target performs a Resist Magic check\comma{} if casting check exceeds Resist check\comma{} then the object in the target{\apos}s hand is hurled in a random direction.}
\spell{name = Eavesdrop, incant = dumauris, school = Divination, type = Concentration, level =Novice, fp = 5, attrurns.}
\spell{name = Blight, incant = thanatos, school = Dark Arts, type = Cast, level =Beginner, fp = 4, attribute =EVL, proficiency = , dv = 5, effect =A wave of necrotic energy extends outwards from you in a radius of 10m (doubled with every PP\comma{} max 1km). All plants within range die instantly\comma{} and all other living beings take 1d4 necrotic damage (+1 per PP)}
\spell{name = Blingind Light, incant = caecus, school = Illusion, type = Effect Only, level =Novice, fp = 5, attribute =POW, proficiency = , dv = 5, effect =Direct a brilliant beam of light at the target. If target fails an INT(Perception) Resist check\comma{} they are blinded for 4 turns.}
\spell{name = Blood Barrier, incant = confusangui, school = Dark Arts, type = Ritual (8 turns), level =Expert, fp = 5, attribute =EVL, proficiency = , dv = 8, effect =Use blood to draw warding runes onto an object or person. Erects a swirling red magical barrier with AC 10\comma{} plus 5 for every casting point over the difficulty. Barrier blocks all physical and magical damage and is immune to acid erosion\comma{} but is eroded by holy damage. 
Each individual{\apos}s blood can only be used once for blood magic.}
\spell{name = Blur, incant = celeritate, school = Illusion, type = Effect Only, level =Beginner, fp = 4, attribute =CHR, proficiency = , dv = 3, effect =The target seems to become blurry around the edges\comma{} it is difficult to tell exactly where they are\comma{} and where they aren{\apos}t.
Gain check advantage on evasion checks for 3 turns.}
\spell{name = Boost Health, incant = levo, school = Recuperation, type = Cast, level =Expert, fp = 11, attribute =EMP, proficiency = Healing, dv = 9, effect =Give the target a temporary +150\caster\comma{} removing any gaseous effects and smelling faintly of lavender.}
\spell{name = Glamour, incant = lux stultium, school = Illusion, type = Instant, level =Beginner, fp = 3, attribute =INT, proficiency = Deception, dv = 3, effect =Create a superficial glamour around a person\comma{} a simple trick of the light. The glamour disintegrates upon physical or magical contact.}
\spell{name = Green Sparks, incant = verdimillious, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, effect =Emits (5+PP) green sparks from your wand\comma{} which can be made to strike at the enemy. 
Each spark does (1 + CV – DV) force damage.}
\spell{name = Halt, incant = stabit, school = Charms, type = Instant, level =Beginner, fp = 2, attribute =SPR, proficiency = , noProf = 1, dv = 4, effect =Stop 1 inanimate object (+1 for every power point dedicated) in its tracks\comma{} if mid\minus{}air\comma{} it drops to the ground.}
\spell{name = Harden Object, incant = duro, school = Transfiguration, type = Instant, level =Novice, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 7, effect =Freezes a non\minus{}living object into its current form. Object gains an effective AC of 25. Lasts for 2 days.}
\spell{name = Haste, incant = silvam currere, school = Charms, type = Instant, level =Novice, fp = 5, attribute =INT, proficiency = , noProf = 1, dv = 5, effect =The target has their Speed proficiency increased by 1 point (+1 per PP) for 5 minutes. At the end of the effect\comma{} target must take 1 turn to rest.}
\spell{name = Heal Being, incant = episkey, school = Recuperation, type = Instant, level =Novice, fp = 5, attribute =EMP, proficiency = Healing, dv = 5, effect =Heal minor status effects like burns\comma{} bruises\comma{} broken noses and so on. If no status effect present\comma{} heal for 2HP + two for each CV over DV}
\spell{name = Hoist Enemy, incant = levicorpus, school = Hexes \& Curses, type = Instant, level =Novice, fp = 8, attribute =FIN, proficiency = , noProf = 1, dv = 8, effect =Target is hoisted into the air. Whilst airborne\comma{} all checks by the target suffer a \minus{}2 penalty. 
Caster can then throw target up to 2 metres in any direction\comma{} with the target taking 1d6 damage.}
\spell{name = Hunter\apos{}s Mark, incant = venari, school = Divination, type = Instant, level =Beginner, fp = 3, attribute =INT, proficiency = , noProf = 1, dv = 4, effect =If casting check exceeds passive resist value\comma{} caster is aware of the location of the target for the next 3 days\comma{} or until the mark is removed by magical means.}
\spell{name = Identify, incant = dicemi, school = Divination, type = Instant, level =Beginner, fp = 6, attribute =INT, proficiency = Research, dv = 3, effect =Learn the properties of the target: be it learning about the nature of the target\comma{} or the ingredients of a potion.
The more power points dedicated to the spell\comma{} the more information that is revealed.}
\spell{name = Illuminate Wand, incant = lumos, school = Charms, type = Concentration, level =Beginner, fp = 1, attribute =INT, proficiency = , noProf = 1, dv = 2, effect =Causes the tip of your wand to glow\comma{} like a torch. Casts bright light for 2m radius\comma{} and dim light for 10m. Spell last indefinitely\comma{} until the counterspell (knox) is used. No other spells can be used whilst lumos is active.}
\spell{name = Imbue Bravery, incant = fortudus, school = Illusion, type = Instant, level =Beginner, fp = 2, attribute =SPR, proficiency = Persuasion, dv = 3, effect =Imbue your target with fortitude and vigour. They gain check\minus{}advantage on all Fear\minus{}Resist checks for 1 hour.}
\spell{name = Incomprehensible Torture, incant = Crucio, school = Dark Arts, type = Concentration, level =Novice, fp = 8, attribute =EVL, proficiency = Chaos, dv = 6, effect =Causes immense pain to the target\comma{} paralysing them whilst the spell is cast. 
Does (PP)d4 psychic damage per turn.}
\spell{name = Instill Terror, incant = timeant, school = Dark Arts, type = Instant, level =Novice, fp = 5, attribute =CHR, proficiency = Intimidation, dv = 6, effect =Target performs a SPR (endurance) Resist check\comma{} if the check is less than the casting check\comma{} the target acquires the {\it Terrified} status.}
\spell{name = Knockback, incant = flipendo, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 3, effect =Causes 2 points of force damage\comma{} and knocks the target back 1 metre. Each power point adds one metre to the knockback distance and 1 damage point. May need to consider impact (see `falling’)}
\spell{name = Launch Spike, incant = voco dens, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, effect =Conjure 1 enormous spike (+ 1 for each power point) to transfigure itself from the surrounding walls/floor\comma{} impaling the target. Each spike does 1d6 piercing damage.}
\spell{name = Lesser Ward, incant = tueor, school = Recuperation, type = Ward, level =Novice, fp = 5, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =Erects a ward in a cylinder around an individual. Ward is 20cm larger in radius than the individual is wide\comma{} and 20cm taller. This ward protects you from up to 15 damage of all types\comma{} before it fails. Ward may move with the target\comma{} and can be cast on self. 
Ward disintegrates after 1 day.}
\spell{name = Levitation, incant = wingardium leviosa, school = Charms, type = Concentration, level =Beginner, fp = 5, attribute =FIN, proficiency = , noProf = 1, dv = 4, effect =Cause an object of 500g or less to levitate\comma{} controlling the vertical distance at will. 
Each power point dedicated doubles the mass of the object that can be lifted.}
\spell{name = Lightning Bolt, incant = baubilious, school = Charms, type = Instant, level =Novice, fp = 8, attribute =POW, proficiency = , noProf = 1, dv = 5, effect =Releases a bolt of lightning from the end of your wand. 
Lightning can initiate fires\comma{} blind your foes\comma{} or can be used directly in combat\comma{} where it deals 1 damage for every check point over the difficulty\comma{} + 3 for every power point dedicated.}
\spell{name = Locate, incant = locus, school = Divination, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiencout of a vial\comma{} but cannot use them to attack.}
\spell{name = Magical Shield, incant = protego, school = Recuperation, type = Concentration, level =Beginner, fp = 5, attribute =POW, proficiency = , dv = 5, effect =Erects an ethereal shield in front of you that absorbs incoming magical attacks.
Shielding charm increases AC by 15+PP against all incoming spells\comma{} but does not protect against physical damage\comma{} or the aftereffects of magic (i.e. a nearby explosion)}
\spell{name = Make Trecherous, incant = transgresso, school = Transfiguration, type = Cast, level =Novice, fp = 8, attribute =INT, proficiency = , dv = 6, effect =Transform the ground in a 5m radius around target into a deep bog\comma{} a bed of sharpened blades\comma{} or into a sticky mess\comma{} with the associated terrain costs.}
\spell{name = Mark Surface, incant = stylum, school = Charms, type = Concentration, level =Beginner, fp = 2, attribute =FIN, proficiency = Dxterity, dv = 2, effect =Use your wand as anything from a thin marker to a thick paintbrush\comma{} the {\it paint} is a magical adhesive that sticks to any surface\comma{} and may be of any colour you choose.}
\spell{name = Mental Burden, incant = onus, school = Hexes \& Curses, type = Cast, level =Novice, fp = 5, attribute =SPR, proficiency = Willpower, dv = 8, effect =If the target fails a resist magic check\comma{} all spells cost 2FP more than their stated value for 6 turns.}
\spell{name = Minor Healing, incant = enervate, school = Recuperation, type = Concentration, level =Beginner, fp = 3, attribute =EMP, proficiency = Healing, dv = 3, effect =Heal for 2 points per turn. 
If the target has a serious wound\comma{} i.e. a broken bone\comma{} cannot heal beyond 50\te =FIN, proficiency = Dxterity, dv = 2, effect =Use your wand as anything from a thin marker to a thick paintbrush\comma{} the {\it paint} is a magical adhesive that sticks to any surface\comma{} and may be of any colour you choose.}
\spell{name = Mental Burden, incant = onus, school = Hexes \& Curses, type = Instant, level =Novice, fp = 5, attribute =SPR, proficiency = Willpower, dv = 8, effect =If the target fails a resist magic check\comma{} all spells cost 2FP more than their stated value for 6 turns.}
\spell{name = Minor Healing, incant = enervate, school = Recuperation, type = Concentration, level =Beginner, fp = 3, attribute =EMP, proficiency = Healing, dv = 3, effect =Heal for 2 points per turn. 
If the target has a serious wound\comma{} i.e. a broken bone\comma{} cannot heal beyond 50\% health. Only works on living creatures.}
\spell{name = Necrosis, incant = carnes mortis, school = Dark Arts, type = Instant, level =Novice, fp = 6, attribute =POW, proficiency = Chaos, dv = 7, effect =Do 1d4 necrotic damage and 1d4 poison damage for every point over the casting check.}
\spell{name = Night Vision, incant = aspectu, school = Illusion, type = Instant, level =Beginner, fp = 3, attribute =EMP, proficiency = Perception, dv = 3, effect =Give the target nightvision for one hour: dim light is as bright as daylight\comma{} and darkness is consdiered dim.}
\spell{name = Obfuscation, incant = obscuras, school = Divination, type = Ritual (1 hour), level =Novice, fp = 7, attribute =POW, proficiency = Willpower, dv = 6, effect =Those attempting to use divination to spy on you must pass a SPR (perception) Resist check  (difficulty 10 + PP) for the spell to work.
Lasts for one week.}
\spell{name = Perpetual Hunger, incant = inedia, school = Hexes \& Curses, type = Instant, level =Novice, fp = 6, attribute =SPR, proficiency = , noProf = 1, dv = 7, effect =The afflicted feels perpetual\comma{} soul\minus{}sapping hunger. Every turn where food is not consumed\comma{} suffer 2 necrotic damage. Lasts for 10 turns.}
\spell{name = Piper{\apos}s Illusion, incant = , noIncant = 1, school = Illusion, type = Ritual (2 turns), level =Novice, fp = 6, attribute =CHR, proficiency = Performance, dv = 5, effect =If one has an instrument\comma{} this spell hypnotises all those who hear it and fail SPR (willpower) Resist check. When the spelncy = \comma{} dv = 5\comma{} effect =Erects an ethereal shield in front of you that absorbs incoming magical attacks.
Shielding charm increases AC by 15+PP against all incoming spells\comma{} but does not protect against physical damage\comma{} or the aftereffects of magic (i.e. a nearby explosion)}
\spell{name = Make Trecherous\comma{} incant = transgresso\comma{} school = Transfiguration\comma{} type = Cast\comma{} level =Novice\comma{} fp = 8\comma{} attribute =INT\comma{} proficiency = \comma{} dv = 6\comma{} effect =Transform the ground in a 5m radius around target into a deep bog\comma{} a bed of sharpened blades\comma{} or into a sticky mess\comma{} with the associated terrain costs.}
\spell{name = Mark Surface\comma{} incant = stylum\comma{} school = Charms\comma{} type = Concentration\comma{} level =Beginner\comma{} fp = 2\comma{} attribute =FIN\comma{} proficiency = Dxterity\comma{} dv = 2\comma{} effect =Use your wand as anything from a thin marker to a thick paintbrush\comma{} the {\it paint} is a magical adhesive that sticks to any surface\comma{} and may be of any colour you choose.}
\spell{name = Mental Burden\comma{} incant = onus\comma{} school = Hexes \\& Curses\comma{} type = Cast\comma{} level =Novice\comma{} fp = 5\comma{} attribute =SPR\comma{} proficiency = Willpower\comma{} dv = 8\comma{} effect =If the target fails a resist magic check\comma{} all spells cost 2FP more than their stated value for 6 turns.}
\spell{name = Minor Healing\comma{} incant = enervate\comma{} school = Recuperation\comma{} type = Concentration\comma{} level =Beginner\comma{} fp = 3\comma{} attribute =EMP\comma{} proficiency = Healing\comma{} dv = 3\comma{} effect =Heal for 2 points per turn. 
If the target has a serious wound\comma{} i.e. a broken bone\comma{} cannot heal beyond 50\ead, incant = melofors, school = Transfiguration, type = Instant, level =Novice, fp = 7, attribute =SPR, proficiency = , noProf = 1, dv = 6, effect =Target performs a Resist Magic check\comma{} if the casting check exceeds the Resist check\comma{} the enemy{\apos}s head is encased in a pumpkin. Apply the Blinded effect until it is removed.}
\spell{name = Receive Omen, incant = , noIncant = 1, school = Divination, type = Ritual (3 turns), level =Beginner, fp = 2, attribute =INT, proficiency = , noProf = 1, dv = 3, effect =Use your tea leaves to receive an omen about the future. Ask a question about the outcome of an event. The tea leaves will tell you if the outcome is positive\comma{} negative\comma{} or neutral. Takes 4 minutes to cast.}
\spell{name = Reinforce Shield, incant = praesidium, school = Recuperation, type = Concentration, level =Beginner, fp = 2, attribute =INT, proficiency = Arcane, dv = 4, effect =Restore the strength of a target shield or magical ward by (2+PP) points per turn that this spell is maintained.}
\spell{name = Release Trapped Being, incant = relashio, school = Recuperation, type = Instant, level =Novice, fp = 6, attribute =SPR, proficiency = Willpower, dv = 5, effect =Force objects and beings to release the target from their grip if they fail an ATH(strength) Resist check.}
\spell{name = Runic Shield, incant = scutum, school = Recuperation, type = Instant, level =Novice, fp = 5, attribute =INT, proficiency = Arcane, dv = 6, effect =Choose a Damage Type. Target is 10\% resistant to that damage type (+10\% for each PP) for 1 hour.}
\spell{name = Sense Traps, incant = antidolus, school = Divination, type = Instant, level =Beginner, fp = 4, attribute =INT, proficiency = Understand Other, dv = 5, effect =Attempt to discover any traps in your immediate vicinity. If successful\comma{} you may learn the location of the trap\comma{} and the trigger (but not the effect). Success conditions are set by the GM.}
\spell{name = Shadow Blast, incant = malusangui, school = Dark Arts, type = Instant, level =Beginner, fp = 3, attribute =POW, proficiency = , noProf = 1, dv = 2, effect =Hurl shadows at you enemy\comma{} dealing 1 necrotic damage for every casting point over the difficulty level.}
\spell{name = Shroud of Darkness, incant = tenebrosa, school = Dark Arts, type = Instant, level =Beginner, fp = 4, attribute =EVL, proficiency = , noProf = 1, dv = 4, effect =Extinguish all light within a 10m radius (+2 for every PP to the spell)}
\spell{name = Silence, incant = silencio, school = Charms, type = Instant, level =Novice, fp = 6, attribute =CHR, proficiency = Persuasion, dv = 5, effect =Target performs a resist magic check. If the check fails\comma{} they cannot speak for 2 turns +1 for each power point dedicated.}
\spell{name = Silver Shield, incant = argentipus, school = Transfiguration, type = Instant, level =Beginner, fp = 6, attribute =INT, proficiency = , noProf = 1, dv = 5, effect =Conjures a silver shield from thin air\comma{} to defend you. Shield absorbs both physical and magical attacks for up to 15 damage points\comma{} before breaking.}
\spell{name = Sleep, incant = somnus, school = Illusion, type = Instant, level =Novice, fp = 5, attribute =CHR, proficiency = , noProf = 1, dv = 6, effect =If target fails a SPR(Endurance) resist magic check\comma{} they enter into a deep slumber for (5 + 2 $\times$ PP) turns}
\spell{name = Smokescreen, incant = fumus insterio, school = Charms, type = Instant, level =Novice, fp = 5, attribute =FIN, proficiency = Deception, dv = 3, effect =Thick white smoke issues from the end of your wand\comma{} giving a Severe obscuration for all targets in a 10m radius.}
\spell{name = Speak in Tongues, incant = lingua maxima, school = Divination, type = Instant, level =Beginner, fp = 8, attribute =EMP, proficiency = Understand Other, dv = 4, effect =By meditating for 5 minutes\comma{} you may understand and speak the language of a willing target individual. Effect lasts until concentration is broken.}
\spell{name = Stabilise Patient, incant = firmum, school = Recuperation, type = Instant, level =Novice, fp = 4, attribute =EMP, proficiency = Healing, dv = 7, effect =Stabilises the patient and removes the \textit{Critical Condition} status.}
\spell{name = Steelclaw, incant = ferscabere, school = Transfiguration, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, effect =Transfigures an animal{\apos}s claws into large steel talons\comma{} increasing their physical damage by +5 . Each power point dedicated gives these talons + 2 damage.  Lasts for 1 day.}
\spell{name = Stick, incant = obharesco, school = Charms, type = Instant, level =Novice, fp = 4, attribute =INT, proficiency = , noProf = 1, dv = 6, effect =Stick two objects together.}
\spell{name = Sting, incant = ictus, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 5, attribute =SPR, proficiency = , noProf = 1, dv = 2, effect =Stings the target for (2 + CV – DV) poison damage.}
\spell{name = Stoneskin, incant = lapis pellium, school = Recuperation, type = Instant, level =Beginner, fp = 4, attribute =SPR, proficiency = Endurance, dv = 4, effect =Increase the target{\apos} AC by 10 for 5 minutes (25 combat rounds). Does not stack.}
\spell{name = Strangle, incant = offoco, school = Hexes \& Curses, type = Instant, level =Novice, fp = 4, attribute =SPR, proficiency = , noProf = 1, dv = 7, effect =Target must resist magic every turn until they succeed\comma{} during this time they are deprived of oxygen\comma{} and eventually succumb to hypoxia under the usual rules. A successful resist check breaks the spell.}
\spell{name = Stunning Blast, incant = stupefy, school = Hexes \& Curses, type = Instant, level =Novice, fp = 8, attribute =POW, proficiency = Willpower, dv = 6, effect =Target performs a Resist Magic check\comma{} if casting check exceeds Resist check\comma{} then target is Stunned for 5 turns.}
\spell{name = Summon Bat Bogeys, incant = vespernasum, school = Hexes \& Curses, type = Instant, level =Novice, fp = 7, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =Causes the mucus in the target{\apos}s nose to gain sentience\comma{} take the form of a (1+PP) small bats\comma{} and attack the target. 
Each bat\minus{}bogey does 1d4 +2 points of acid damage per turn for 3 turns (unless removed).}
\spell{name = Summon Object, incant = accio, school = Charms, type = Concentration, level =Novice, fp = 6, attribute =SPR, proficiency = , noProf = 1, dv = 6, effect =Summon non\minus{}shielded objects within a 500m radius. They will fly to your current position as long as concentration is maintained.}
\spell{name = Summon Snake, incant = serpensortia, school = Transfiguration, type = Instant, level =Novice, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =Summons a venomous snake out of the tip of the caster{\apos}s wand. The snake has 8HP and does 1d6 poison damage upon biting. Every extra power point gives the snake +1 HP and +1 attack.  Lasts for 10 minutes.}
\spell{name = Summon Void, incant = inanis, school = Dark Arts, type = Concentration, level =Novice, fp = 8, attribute =EVL, proficiency = Chaos, dv = 7, effect =Summon a true Void\comma{} a gap in the fabric of reality that attracts all objects within a 5m radius. Everything in radius must perform an ATH(Strength) Resist against the casting check to grab onto something.}
\spell{name = Summon Weak Avatar, incant = elementos, school = Transfiguration, type = Ritual (5 minutes), level =Novice, fp = 7, attribute =INT, proficiency = Arcane, dv = 8, effect =Summon a Weak Avatar of your choice (Storm\comma{} Ice or Fire) to be under your command for 10 turns\comma{} after which it dissolves.}
\spell{name = Sunburst, incant = sol maxima, school = Recuperation, type = Instant, level =Beginner, fp = 4, attribute =SPR, proficiency = , noProf = 1, dv = 4, effect =A burst of bright light does 1d6 holy damage to all targets in a 5m radius.}
\spell{name = Telepathic Bond, incant = conanimus, school = Divination, type = Ritual (2 turns), level =Beginner, fp = 5, attribute =EMP, proficiency = Understand Other, dv = 5, effect =Form a mental connection between your mind and the mind of a willing target. You may then use this connection to communicate silently. 
Target must be within touching distance when the spell is cast\comma{} but the bond has no distance limit after that.
Lasts for 2 days.}
\spell{name = Thick Air, incant = temporio, school = Transfiguration, type = Concentration, level =Novice, fp = 7, attribute =POW, proficiency = , noProf = 1, dv = 6, effect =Transforms the air around the target into a thick soup\comma{} slowing their movement by 20\% (each power point makes the target move slower). Lasts for 1 minute.}
\spell{name = Throw Voice, incant = ventrilofors, school = Illusion, type = Concentration, level =Beginner, fp = 4, attribute =INT, proficiency = Deception, dv = 2, effect =Cast your voice such that it appears to be coming from somewhere up to 5+$\times PP$ metres away.}
\spell{name = Trip, incant = lubricor, school = Hexes \& Curses, type = Instant, level =Beginner, fp = 4, attribute =FIN, proficiency = , noProf = 1, dv = 4, effect =If the target is moving this turn cycle and fails an ATH Resist check\comma{} they go sprawling onto the ground taking 1d4 bludgeoning damage\comma{} and take the `Prone Position’ status.}
\spell{name = Unlock, incant = alohomora, school = Charms, type = Instant, level =Novice, fp = 3, attribute =FIN, proficiency = Dexterity, dv = 5, effect =Unlock objects. Mundane locks will fall open for you\comma{} whilst to open magically locked objects\comma{} the unlocking must exceed the locking casting check.}
\spell{name = Vicious Slash, incant = sectumsempra, school = Dark Arts, type = Instant, level =Beginner, fp = 4, attribute =POW, proficiency = , noProf = 1, dv = 4, effect =Gouges at the target\comma{} leaving deep\comma{} cursed wounds\comma{} for 1d6 points of slashing damage\comma{} plus two for every PP.}
\spell{name = Violent Phantasms, incant = umbra impetia, school = Illusion, type = Instant, level =Novice, fp = 7, attribute =SPR, proficiency = , noProf = 1, dv = 6, effect =Multiple phantasms attack the target\comma{} doing (1+PP)d4 psychic damage for every turn that the phantasms are active. 
Once the original spell hits the targets\comma{} phantasms exist only within the target{\apos}s mind\comma{} and may pass through all shields and defences. 
Phantasms are active for (3+PP) turns}
\end{multicols}