\documentclass[../CoreRulebook.tex]{subfile}

\chapter{Casting Spells}

Spells are how Wizards and Witches get by in the world, it is what makes them special. 

Spells are broken down into 7 categories: Hexes \& Curses, Transfiguration, Charms, Recuperation, Illusion, Divination, and Dark Arts. Different types of spells require different abilities to cast: illusion spells often require the charisma and deception to overpower the target{\apos}s willpower, whilst hexes and curses often rely on sheer magical power for their effectiveness.

All spells are cast by performing the relevant checks -- rolling a dice, and then adding on the associated skill modifiers and bonuses for that check type -- and then deducting the associated fortitude cost. Each spell has its own check type, which is specified in the spell list below. The dice that you get to use to perform the casting check depends on the level of the skill that you have in the associated school of magic (i.e. the 7 skills associated with each of the 7 schools of magic). 

If you possess enough FP to make the cast, and the casting check is greater than or equal to the difficulty of the spell (also listed in the spell tables), then the spell is successfully cast. 

The dice that you get are enumerated below:

\begin{center}
	\begin{rndtable}{|c c c|}

	\bf Level & \bf  Name & \bf Die
	\\ 
	1 & Beginner & 1d6
	\\
	2 & Novice & 1d8
	\\
	3 & Adept & 1d10 (with 0 = 10)
	\\
	4 & Expert & 1d12
	\\
	5 & Master & 1d20
	\\ \hline
	\end{rndtable}
\end{center}

As you get more and more powerful in each of the 7 schools of magic, you therefore unlock larger and larger dice, which grants you access to more powerful spells, and also makes casting spells of a lower level easier and easier (as there is less chance of failure). 

There are two kinds of spell: an effect-only spell, which either succeeds or does not; and a power-dependent spell, where the outcome of the spell can vary depending on the success of the casting. 

Effect-Only spells are the most basic kind of spell, for example, the Fire-Starting charm (\textit{incendio}), either starts a fire, or it does not, and the Compass Spell (\textit{point me}) either tells you which way North is, or it does not. These spells are therefore in the first class: effect-only. Contrast this with the Torturing Curse (\textit{crucio}). This can not only succeed or fail, but can cause varying amounts of pain. It is therefore a power-dependent spell, as the success of the spell can vary.

Effect-only (E-Class) spells are cast by performing the check type specified in the tables below.

Power-dependent (P-class) spells have the same casting mechanism except you may choose to donate PWR points towards the spell before the check is initialised, up to the total PWR of your character. Each additional PWR point dedicated towards the spell increases the effectiveness of the spell, doing more damage, or adding more side effects. However, powerful spells are more difficult to cast: for each power point you add on, you increase the difficulty value and the fortitude cost of the spell by 1.

Hence, a spell which does 1d8 of damage to target, with a difficulty of 10 and costing 5 Fortitude can be boosted with 5 PWR points to do 1d8 + 5 damage, but the boosted spell has a difficulty of 15, and a Fortitude cost of 10. 
Hence, there is a higher chance of failure, but the rewards for success are much higher! The maximum number of PWR points you can assign a spell is limited by your PWR attribute itself (you can{\apos}t assign more PWR than you have).

The GM may decide that a particular usage of an E-Class spell warrants an extra effort, despite a nominal effect-only status, i.e. setting light to an entire building, rather than starting a campfire would still use incendio, but clearly is a far more powerful use of the firelighting charm! The GM has the authority to override the difficulty and checks required for a spell if the situation calls for it. 

The Fortitude cost for a spell is deducted only after it is successfully cast. If the casting fails, then only half of the fortitude cost is deducted (rounded up), plus whatever negative effects the failed cast might have. 

Oh, one final rule. If your character is saying the incantation, so must you. Bonus points for good acting.


\chapter{Learning New Spells}

Spells are learned by studying, either from books, or from a teacher.
 
To learn a spell, you must purchase a spell book from a vendor (or find a Professor who already knows the spell), and dedicate an entire day to learning that spell. When that day is up, you get three attempts to cast the spell using the usual casting check. 

If at least one of these casting checks succeeds, you have successfully learned the spell, and you may add it to your arsenal. If all three checks fail, you go have to go back to the start, and begin the learning process again, losing another day in the process. 

Each spellbook contains three spells that you can learn, before you must purchase another, and you are originally limited to learning only 3 spells per level. When you level up, this counter resets, and you may learn another 3 spells.

A professor who already knows the spell you want to learn is an adequate replacement for a spellbook, and may teach an unlimited number of students an unlimited number of spells, but only if they already know the spell. A professor must learn a spell in the usual fashion (unless they can find another professor to teach them!)

\chapter{Resisting Magic}

Some spells, even after they have successfully been cast, can be resisted by the target, if they have a strong enough willpower to overpower the caster; spells such as {\it confundus}, and {\it stupefy}, as well as most illusion spells. 

Resist Magic is (unless told otherwise) a SPR (endurance) check using the Resist Magic dice granted to you by your level in the {\it Contervail} skill. If the spell is a power dependent spell, the Resist Magic check gets a -1 penalty for each PWR point dedicated to the spell. 

This Resist check is then compared with the casting check. If the Resist check is greater than the casting check, then the spell has no effect. If, however, the Resist Magic check is lower, then the spell effect is applied. 

Successfully Resisting a spell costs 2 FP. If you have fewer than 2 FP, then you cannot Resist.

You can perform multiple Resists over the course of a Turn Cycle, if multiple combatants attack you with spells that require one, the only qlimit is when your FP runs out. However, each subsequent resist gets harder and harder: you suffer a 1 point penalty to your check for each Resist you have already performed this cycle. This counter resets after you have completed your turn. 

\onecolumn
\chapter{Spell List}

The following is a list of all the available spells, the checks required to cast them,  the cost of doing so, and the effects each spell has. Some spells are specified as having a duration in either minutes or turns depending on if they are generally considered combat spells or not. If you decide to use a spell outside of its normal parameters, these are considered interchangeable -- a spell that lasts one hour lasts for 60 turns of combat, and vice versa. 
\def\t{2.9}
\def\u{1.7}
\def\v{1.7}
\def\w{1.2}
\def\x{1.5}
%\def\y{1.2}
\def\z{7.3}

\footnotesize
%%SpellBegin\subsection*{Hexes \& Curses} \addcontentsline{toc}{section}{Spell School: Hexes \& Curses } Combat-based magic, used to incapacitate or even inflict pain upon your enemies.\\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Acidic Burst\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Fills a 5m target area with an acidic cloud that does 1 acid damage per turn + 1 for each point over the casting check. Cloud lasts for 10 cycles, unless in a confined space, where it lasts until removed by other means.\end{flushleft}} \\  \bf \begin{center}Confundus Charm \\ {\it confundo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (Deception)\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Do 2 Fatigue damage.
Target performs a Resist Magic check, if it fails, then target acquires the Confused status.\end{flushleft}} \\  \bf \begin{center}Green Sparks \\ {\it  verdimillious}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Emits 5 green sparks from your wand, which can be made to strike at the enemy. 
Each spark does one force damage per 1 check point over the difficulty value. Each power point added gives another spark.\end{flushleft}} \\  \bf \begin{center}KnockBack Jinx \\ {\it  flipendo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes 2 points of force damage, and knocks the target back 1 metre. Each power point adds one metre to the knockback distance and 1 damage point. May need to consider impace (see `fallingÿ)\end{flushleft}} \\  \bf \begin{center}Stinging Hex \\ {\it  ictus }\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Stings the target for 1 poison damage + 1 for each check point over the difficulty value.\end{flushleft}} \\  \bf \begin{center}Trip jinx \\ {\it lubricor}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the target is moving this turn cycle, they go sprawling onto the ground taking 1d4 of damage. They cannot perform a spell until they get up, which takes a turn cycle. They may, however, crawl.\end{flushleft}} \\  \bf \begin{center}Arctic Chill Hex \\ {\it gelidus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}An area of 2 metres (+1 for every power point dedicated) around the target is plunged into absolute cold. Those caught in the region take 2d4 of cold damage, and apply the mild Frostbite status effect.\end{flushleft}} \\  \bf \begin{center}Bat Bogey Hex \\ {\it  vespernasum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes the mucus in the target{\apos}s nose to gain sentience, take the form of a small bat, and attack the target. 
Each bat-bogey does 1d4 +2 points of piercing damage per turn for 3 turns (unless removed). Each power point adds one bat.\end{flushleft}} \\  \bf \begin{center}Body-Bind Curse  \\ {\it petrificus totalus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (willpower)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a resist magic check against the casting check, if it fails, target acquires the Trapped status effect.\end{flushleft}} \\  \bf \begin{center}Cascading Jinx  \\ {\it unda delor}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Fires multiple bursts of energy that do 3+1d4 force damage to up to 3 targets. 
Each power point added adds +1 damage, and +1 target.\end{flushleft}} \\  \bf \begin{center}Curse of Mental Burden \\ {\it onus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR  \\ (willpower)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the target fails a resist magic check, all spells cost 2FP more than their stated value for 6 turns.\end{flushleft}} \\  \bf \begin{center}Curse of Perpetual Hunger \\ {\it inedia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The afflicted feels perpetual, soul-sapping hunger. Every turn where food is not consumed, suffer 2 necrotic damage. Lasts for 10 turns.\end{flushleft}} \\  \bf \begin{center}Disarming Spell  \\ {\it Expelliarmus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a Resist Magic check, if casting check exceeds Resist check, then the object in the target{\apos}s hand is hurled in a random direction.\end{flushleft}} \\  \bf \begin{center}Lifting Hex \\ {\it Levicorpus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target is hoisted into the air. Whilst airborne, all checks by the target suffer a -2 penalty. 
Caster can then throw target up to 2 metres in any direction, with the target taking 1d6 damage.\end{flushleft}} \\  \bf \begin{center}Strangle \\ {\it offoco}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target must resist magic every turn until they succeed, during this time they are deprived of oxygen, and eventually succumb to hypoxia under the usual rules. A successful resist check breaks the spell.\end{flushleft}} \\  \bf \begin{center}Stunning Hex  \\ {\it  stupefy}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW \\ (willpower)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a Resist Magic check, if casting check exceeds Resist check, then target is Stunned for 3 turns.\end{flushleft}} \\  \bf \begin{center}Acid Arrow Hex  \\ {\it  saeclifors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjures a stream of corrosive, poisonous acid from the tip of your wand. Dissolves objects, clothes and skin alike. 
Does 4 + 1d6 acid damage\end{flushleft}} \\  \bf \begin{center}Blasting Curse  \\ {\it  confringo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Launches a fireball at the target, doing 3+1d8 fire damage + 1 for every power point dedicated to the spell, over a 2m radius. 
Targets suffer a moderate burn.\end{flushleft}} \\  \bf \begin{center}Flagrante Curse  \\ {\it flagrante}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes a target object to heat up to unimaginable temperatures, doing 5 fire damage every time the target object is touched, and applies a severe Burn status effect.
Lasts for 3 turns.\end{flushleft}} \\  \bf \begin{center}Hex of the Recurring Light \\ {\it catena}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A beam of blinding light shoots from your wand, striking one target before moving onto the next. Targets take 1d8 of fire damage (doubled if they are UnLife or Undead) and are Blinded if they fail a resist magic check. Each target has the chance to avoid/counterspell this spell, the next target only recieves the beam If the previous one was hit. 3 targets may be hit, +1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Impediment Jinx  \\ {\it impedimentia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a Resist Magic check, if the check fails, the target is Paralyzed for one turn. The target (and the player controlling that character) cannot communicate with anyone until the curse is removed.\end{flushleft}} \\  \bf \begin{center}Object Swarm Hex  \\ {\it  Oppugno}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes nearby objects to hurl themselves at the target, doing 1d10 + 2 of bludgeoning damage.\end{flushleft}} \\  \bf \begin{center}Scrambling Curse \\ {\it traferus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The target has their abilities scrambled for the duration of the curse. The GM randomly reassigns the character attributes (so FIN would take on the ATH value for the duration of the curse). Lasts for 5 turns, +1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Dragon{\apos}s Breath Curse \\ {\it draco flammor}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}13\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A torrent of flame erupts from the tip of your wand for up to 10 metres in front of the caster, incinerating everything in its path. Water cannot quench this fire, and it causes 1d10 worth of dimage damage, and applies a Severe Burn to whatever it comes into contact with.\end{flushleft}} \\  \bf \begin{center}Expulsion Curse  \\ {\it  expulso}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Launches a magical bolt at the target which, if it makes contact, causes the object to violently tear itself apart. 
Does 1d10 + 6 force damage, plus 1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Meteor Strike \\ {\it bothynus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon flaming rocks from the heavens, doing 1d8 bludgeoning damage and 1d6 fire damage to all enemies in a 10m radius + 2m for every power point dedicated.\end{flushleft}} \\  \bf \begin{center}Patronus Charm  \\ {\it  Expecto Patronus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (Willpower)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon your greatest, happiest memories into physical form: your patronus. The patronus will prevent any Un-Life creatures from approaching you for three turns + 1 for every power point dedicated to the spell. \\ Alternatively, the patronus may be directed to directly attack the undead, in which case it does 2d6 worth of holy damage, + 4 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Shield Breaker Hex  \\ {\it  misericorde}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}16\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Finds the weak point in the armour, and exploits it: if the casting check exceeds the shield capabilities of the weakest defensive spell of the target, all shields (both physical and magical) are removed, and cannot be re-established for two turns.\end{flushleft}} \\  \bf \begin{center}Shockwave Curse \\ {\it inpusla}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}11\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A shockwave emanates from the caster in every direction, for a radius of 10m, doing one damage for every point over the casting check and hurling all unprotected away from the caster to the edge of the affected region. Does 1d8 concussive damage.\end{flushleft}} \\  \bf \begin{center}Voodoo Curse \\ {\it speculo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}15\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the target fails a resist magic check, the lifeforce of the target is inexorably tied to another object (or living being). What happens to one, happens to the other.\end{flushleft}} \\  \bf \begin{center}Bestow Curse \\ {\it maledicto}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}19\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Casts a permanent curse on the target. You may choose the effects of this curse, though the GM has a veto. Be inventive!\end{flushleft}} \\  \bf \begin{center}Bone Crushing Curse  \\ {\it  obcillo ossium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}14\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:19\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A great force smashes into the opponent, breaking their bones. 
Does 1d12 + 7 bludgeoning damage, plus 1 for every power point dedicated to the spell. Applies the Broken Bone status effect.\end{flushleft}} \\  \bf \begin{center}Disintegration Curse  \\ {\it reducto}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect-Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}16\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the spell makes contact with matter, causes it to instantly disintegrate. Living beings take 3d8 worth of force damage.\end{flushleft}} \\  \bf \begin{center}Tempest Jinx \\ {\it  fulgurum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}18\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:18\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summons a stormcloud which hovers above the battlefield, emitting lightning bolts which strike all your enemies within a 25 metre radius once per turn, dealing 1d6 +2 points of unavoidable electric damage for 10 turns.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Transfiguration} \addcontentsline{toc}{section}{Spell School: Transfiguration } Alter the very fabric of reality with these spells, changing one thing, into another and even conjuring things from thin air.  \\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Colour-Changing Charm \\ {\it pigmentus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes the colour of an object to change. Lasts for 2 days.\end{flushleft}} \\  \bf \begin{center}Flower Conjuring Spell  \\ {\it Orchideous}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjures flowers from thin air. Lasts for 3 days.\end{flushleft}} \\  \bf \begin{center}Hair Altering Spell  \\ {\it Crinus Muto}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (deception)\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Alters the colour and style of the casters hair. Useful for disguises. Degrades after 5 hours.\end{flushleft}} \\  \bf \begin{center}Launch Spike \\ {\it voco dens}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjure 1 enormous spike (+ 1 for each power point) to transfigure itself from the surrounding walls/floor, impaling the target. Each spike does 1d6 piercing damage.\end{flushleft}} \\  \bf \begin{center}Potion Mixing Spell\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} 1d20 INT \\ (Arcane)\\~\\ Target:0\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Used to mix a potion. See page \pageref{S:Enchanting} for details.\end{flushleft}} \\  \bf \begin{center}Silver Shield Spell \\ {\it argentipus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjures a silver shield from thin air, to defend you. Shield absorbs both physical and magical attacks for up to 15 damage points, before breaking.\end{flushleft}} \\  \bf \begin{center}Steelclaw charm \\ {\it ferscabere}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transfigures an animal{\apos}s claws into large steel talons, increasing their physical damage by +5 . Each power point dedicated gives these talons + 2 damage.  Lasts for 1 day.\end{flushleft}} \\  \bf \begin{center}Switching Spell  \\ {\it formum mutatio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transform a 200g non-sapient animal or object into a different animal or solid object. 
Each power point doubles the mass of objects that can be transformed.  Lasts for 1 hour.\end{flushleft}} \\  \bf \begin{center}Boggart Banish Charm  \\ {\it Riddikulus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Forces a Boggart into a form that the caster finds funny.\end{flushleft}} \\  \bf \begin{center}Fabrication Spell \\ {\it facere}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (dexterity)\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Construct an object from raw materials, assembling it at a molecular level. May manipulate 500g of raw material in this fashion, doubling the mass with every power point dedicated. Consruction is permanent, and cannot be undone.\end{flushleft}} \\  \bf \begin{center}Hardening Charm \\ {\it  duro}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Turns non-living targets into stone.
Lasts 1 day.\end{flushleft}} \\  \bf \begin{center}Pumpkin Head Jinx  \\ {\it Melofors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a Resist Magic check, if the casting check exceeds the Resist check, the enemy{\apos}s head is encased in a pumpkin. Apply the Blinded effect until it is removed.\end{flushleft}} \\  \bf \begin{center}Snake Summons Spell \\ {\it  Serpensortia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summons a venomous snake out of the tip of the caster{\apos}s wand. The snake has 8HP and does 1d6 poison damage upon biting. Every extra power point gives the snake +1 HP and +1 attack.  Lasts for 10 minutes.\end{flushleft}} \\  \bf \begin{center}Summon Weak Avatar \\ {\it elementos }\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT  \\ (arcane)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon a Weak Avatar of your choice (Storm, Ice or Fire) to be under your command for 10 turns, after which it dissolves.\end{flushleft}} \\  \bf \begin{center}Thick-Air Charm \\ {\it  temporio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transforms the air around the target into a thick soup, slowing their movement by 20\% (each power point makes the target move slower). Lasts for 1 minute.\end{flushleft}} \\  \bf \begin{center}Bird-Flocking Charm  \\ {\it Avis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summons a flock of 6 small birds (+1 for each power point) to do your bidding. Each bird has 1HP and can do 1d4 of piercing damage. Lasts for 10 minutes.\end{flushleft}} \\  \bf \begin{center}Conjure object\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ {dexterity}\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjure a 200g inanimate, non-magical object from thin air. Each power point dedicated doubles the mass/complexity of the object that can be conjured\end{flushleft}} \\  \bf \begin{center}Enchantment Ritual\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}20\end{center}} &    \parbox[t]{\x cm}{\begin{center} 1d20 FIN \\ (arcane)\\~\\ Target:0\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The enchantment ritual used to imbue items with magical effects. See page \pageref{S:Enchanting} for details.\end{flushleft}} \\  \bf \begin{center}Golem Creation Spell \\ {\it lapis libiri}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW \\ (arcane)\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Breathe life into a block of inanimate matter, turning it into a hulking Golem. Basic spell produces a Weak Stone Golem. 1 power point gives a weak iron golem, 2 gives a weak crystal golem, 3 a capable stone golem and so on. Require a large amount of the golem material to cast.\end{flushleft}} \\  \bf \begin{center}Make Trecherous \\ {\it transgresso}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transform the ground in a 5m radius into a deep bog, a bed of sharpened blades, or into a sticky mess, with the associated terrain costs.\end{flushleft}} \\  \bf \begin{center}Material Switching Hex \\ {\it  protenius}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Change the material that the target is made up of. The change is monolithic: you change the entirety of the target into a single material (i.e. no subdivisions).\end{flushleft}} \\  \bf \begin{center}Size Altering Charm  \\ {\it  engorgio/ reducio }\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Multiply or divide the size of an entity by 2 (+1 for each power point). 
Multiple size alterations can be unstable. Effect lasts for 5 turns.\end{flushleft}} \\  \bf \begin{center}Trapping Spell  \\ {\it  Incarcerous}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect-Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjures thick ropes from thin air, to wrap around the target, immobilising them. Lasts for 5 minuts.\end{flushleft}} \\  \bf \begin{center}Vanishing Spell  \\ {\it  Evanesco}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center}Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Cause a 200g animal or object to vanish, without a trace. 
Each power point doubles the mass of objects that can be vanished.\end{flushleft}} \\  \bf \begin{center}Animagus Reveal Spell  \\ {\it homorphus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (willpower)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Forces an animagus back into their human form if they fail a Resist check.\end{flushleft}} \\  \bf \begin{center}Bubble Charm  \\ {\it Ebublio }\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Conjures a large, hard-to-pop airtight bubble (strength 8) which the caster can use to encase enemies, or to protect themselves.\end{flushleft}} \\  \bf \begin{center}Copying Charm  \\ {\it Gemino}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}13\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Creates a copy of an object in your possession, which is identical to the first, until it disintegrates 12 hours later.\end{flushleft}} \\  \bf \begin{center}Draconifors Spell   \\ {\it Draconifors }\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transform 1d6 small objects into miniature dragons to fight by your side. Dragons have 8HP and do 1d6 fire damage
Each power point dedicated to the spell gives dragons +1 HP and attack.\end{flushleft}} \\  \bf \begin{center}Permanence Spell \\ {\it perpetuus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}15\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}When cast on any transfigured or conjured object, fixes that transfiguration and removes the time constraint. This spell can be broken, at which point the time constraints are reinstated.\end{flushleft}} \\  \bf \begin{center}Summon Capable Avatar \\ {\it elementos temporio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}11\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT  \\ (arcane)\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon a Capable Avatar of your choice (Storm, Ice or Fire) to be under your command for 20 turns, after which it dissolves.\end{flushleft}} \\  \bf \begin{center}Un-Transform Spell  \\ {\it Reparifarge}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect-Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transfiguration countercharm: undoes the effect of any transfiguration spell (but can not banish summoned objects). 
Spell is successful if casting check exceeds the check that cast the original spell.\end{flushleft}} \\  \bf \begin{center}Guardian Charm\\ {\it piertotum locmotum }\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR  \\ (willpower)\\~\\ Target:22\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Transform nearby statues, trees and other inanimate objects into powerful guardians to fight by your side. Guardians are considered as Capable Stone Golems unless otherwise indicated.\end{flushleft}} \\  \bf \begin{center}Smoke Daggers  \\ {\it fumus defendus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}15\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:19\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes 5 daggers to coalesce out of smoke, and fly towards the target. 
Each dagger that hits the target does 1 point of physical damage for every check point over the difficulty. 
Each power point dedicated to the attack adds 3 more daggers.\end{flushleft}} \\  \bf \begin{center}Summon Master Avatar \\ {\it caro elementum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}14\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (arcane)\\~\\ Target:22\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon an Strong Avatar of your choice (Storm, Ice or Fire) to be under your command for 30 turns, after which it dissolves.\end{flushleft}} \\  \bf \begin{center}True Shapeshift \\ {\it muto}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}16\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}You assume the form of any object you wish, provided it has approximately the same size as you. You are indistinguishable from this object until you choose to break the spell.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Charms} \addcontentsline{toc}{section}{Spell School: Charms } Manipulate objects with magic: cause things to levitate, fix things that are broken and control the elements.\\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Fire starting spell  \\ {\it incendio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A small jet of fire is emitted from the tip of your wand. 
Coming into contact with fire does 1d6 fire damage, and applies a minor Burned status effect.
(Larger jets of fire have a difficulty of 14,  do + 3  fire damage and apply a Moderate burn)\end{flushleft}} \\  \bf \begin{center}Fresh Air Charm \\{\it klinneract}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:3\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A gust of air refreshes the air in a 2m radius (+1 per POW) around the caster, removing any gaseous effects and smelling faintly of lavender.\end{flushleft}} \\  \bf \begin{center}Halt spell \\{\it stabit}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Stop 1 inanimate object (+1 for every power point dedicated) in its tracks, if mid-air, it drops to the ground.\end{flushleft}} \\  \bf \begin{center}Illumination Spell   \\ {\it lumos}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}1\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes the tip of your wand to glow, like a torch. Casts bright light for 2m radius, and dim light for 10m. Spell last indefinitely, until the counterspell (knox) is used. No other spells can be used whilst lumos is active.\end{flushleft}} \\  \bf \begin{center}Levitation Spell   \\ {\it wingardium leviosa}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Cause an object of 500g or less to levitate, controlling the vertical distance at will. 
Each power point dedicated doubles the mass of the object that can be lifted.\end{flushleft}} \\  \bf \begin{center}Marker Charm \\ {\it stylum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (dexterity)\\~\\ Target:2\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Use your wand as anything from a thin marker to a thick paintbrush, the {\it paint} is a magical adhesive that sticks to any surface, and may be of any colour you choose.\end{flushleft}} \\  \bf \begin{center}Water Spout Charm   \\ {\it aguamente}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A jet of water is emitted from the tip of your wand, useful for extinguishing fires, or cleaning surfaces. 
(Larger jets of water have a difficulty of 16. Conjured water cannot be drunk)\end{flushleft}} \\  \bf \begin{center}Cutting Charm   \\ {\it diffindo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Cut two objects apart. 
If used on a living being, causes a deep cut, for 1d6 + 3 slashing damage.\end{flushleft}} \\  \bf \begin{center}Fixing Charm   \\ {\it reparo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Fix the target. Can only fix an object if you know what it is supposed to be when repaired.\end{flushleft}} \\  \bf \begin{center}Locking Charm   \\ {\it colloportus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Magically lock an object.\end{flushleft}} \\  \bf \begin{center}Silencing Charm   \\ {\it silencio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (persuasion)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a resist magic check. If the check fails, they cannot speak for 2 turns +1 for each power point dedicated.\end{flushleft}} \\  \bf \begin{center}Sticking Charm   \\ {\it obharesco}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Stick two objects together.\end{flushleft}} \\  \bf \begin{center}Summoning Charm    \\ {\it accio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon non-shielded objects within a 500m radius. They will fly to your current position.\end{flushleft}} \\  \bf \begin{center}Unlocking Charm    \\ {\it alohomora}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Unlock objects. Mundane locks will fall open for you, whilst to open magically locked objects, the unlocking must exceed the locking casting check.\end{flushleft}} \\  \bf \begin{center}Elemental Blade Charm \\ {\it gladio subtantia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The elements are bent to your will, and a blade of nature-incarnate solidifies around your wand. You now wield a sword made out of pure fire, water, air, ice, lightning or earth, held together by your strength of will. In addition to the physical cutting effect, this blade also imparts an elemental effect, i.e. a blade of fire causes burns etc. This spell lasts as long as you maintain concentration, and no other spells can be cast whilst it is active.\end{flushleft}} \\  \bf \begin{center}Featherweight Charm   \\ {\it pluma gravitas}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (arcane)\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Make the target object as light as a feather, it does not encumber you.
(Note that heavy weapons such as axes may lose their effectiveness when made featherweight)\end{flushleft}} \\  \bf \begin{center}Fire Manipulating Spell   \\ {\it ignipare}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Take control of an existing fire, and manipulate it to your will, creating walls of fire, or sending it flying towards your enemies.  
Range of the spell is 1m + 1 for every power point dedicated. More power points also let you perform more extravagant feats. \\ Manipulated fire does 1d8 worth of damage, and applies a moderate burn status.\end{flushleft}} \\  \bf \begin{center}Freezing Charm   \\ {\it glacius}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Freeze the target. When used the combat, trap the target in place and do 1d6 worth of damage by encasing them in a block of ice. The target is trapped until they are thawed out, at which point the Frostbite status is applied.\end{flushleft}} \\  \bf \begin{center}General Counterspell   \\ {\it finite incantatem}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}End any active spell. If the spell was cast by anyone other than yourself, the counterspell check must exceed the original casting check (does not work on enemy shields or curses).\end{flushleft}} \\  \bf \begin{center}Spell Replay Charm   \\ {\it priori incantatem}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (arcane)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Reveal the last spell that a wand cast.\end{flushleft}} \\  \bf \begin{center}Water manipulation spell   \\ {\it aguapare}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Manipulate bodies of water, creating whirlpools, waves or maelstroms.
Range of the spell is 1m +1 for every power point dedicated. More power points also let you perform more extravagant feats. \\ Being trapped in turbulent water does 1d4 worth of damage whilst the target is trapped. This spell may be maintained indefinitely once cast, but no other spells may be cast until this spell is halted. Requires a source of water to manipulate.\end{flushleft}} \\  \bf \begin{center}Cushioning Charm  \\ {\it sofus }\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Painlessly break the fall of the target from any height up to 100m + 100 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Earth manipulation spell   \\ {\it defodio }\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW \\ (strength)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Control the very ground itself. Form sinkholes, dig holes, or even cause minor earthquakes.
Range is 3m + 1 for every power point dedicated to the spell. More power points also let you perform more extravagant feats. \\ Violent earth manipulation causes 3 + 2d8 of damage.\end{flushleft}} \\  \bf \begin{center}Extension Charm   \\ {\it tarditia hoovium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Makes the target container 2 times (+1 for each power point) larger on the inside than it is on the outside.  
Lasts for 5 turns.\end{flushleft}} \\  \bf \begin{center}Freedom charm \\ {\it liber}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Remove all impediments to movement if the casting check exceeds the trapping check\end{flushleft}} \\  \bf \begin{center}Lightning Charm   \\ {\it baubilious}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Releases a bolt of lightning from the end of your wand. 
Lightning can initiate fires, blind your foes, or can be used directly in combat, where it deals 1 damage for every check point over the difficulty, + 3 for every power point dedicated.\end{flushleft}} \\  \bf \begin{center}Air Manipulation Spell   \\ {\it vente}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Control the air around you. Can be used to manipulate the weather, blow enemies off their feet, deflect objects, and there are even rumours of people using it to fly!
Range is 3m + 1 for every power point dedicated to the spell.  More power points also let you perform more extravagant feats.\end{flushleft}} \\  \bf \begin{center}Hour Reversal Charm   \\ {\it tempus fugit}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}20\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:25\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Control time itself, stepping backwards through the hours to relive them again. 
Reverse time by 1 hour + 1 for each power point dedicated to the spell, but beware, even when successfully cast, this is a very unstable spell.\end{flushleft}} \\  \bf \begin{center}Mass Kinesis Charm   \\ {\it ballatutti}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}13\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:21\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Control huge numbers of objects as they levitate and move around: write a thousand books with a thousand quills, or conduct a swordfight with 15 blades at once. 
The more power points dedicated to the spell, more and heavier objects can be controlled.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Recuperation} \addcontentsline{toc}{section}{Spell School: Recuperation } Set up wards and protective barriers, and heal those who are injured. Recuperative magic is used to stop further harm coming to individuals under your protection. \\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Aid Charm\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target has HP ceiling raised by 5 points for 1 hour\end{flushleft}} \\  \bf \begin{center}Caterwauling Charm  \\ {\it  caterwaul}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Casts a ward on the area which emits a high-pitched scream when an unknown being crosses the threshold. 
Radius is 10m + 2 for every power point dedicated to the spell. Ward decays after 2 weeks.\end{flushleft}} \\  \bf \begin{center}Minor Healing Spell  \\ {\it enervate}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Heal small wounds: restore 3 HP to the target, or wake them if they are unconscious.
If the target has a serious wound, i.e. a broken bone, cannot heal beyond 50\% health. Only works on living creatures.\end{flushleft}} \\  \bf \begin{center}Privacy Ward  \\ {\it  muffliato}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A buzzing sound fills the ears of anyone trying to listen in on your conversations whilst you are in the warded area. Lasts for one hour, and has a radius of 2m.\end{flushleft}} \\  \bf \begin{center}Reinforcement Charm \\ {\it praesidium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Restore the strength of a target shield or magical ward by 2 points per turn that this spell is maintained, +1 for every power point that is dedicated. This spell only needs to be cast once, but the FP cost is deducted every turn.\end{flushleft}} \\  \bf \begin{center}Shielding Charm  \\ {\it protego}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Erects an ethereal shield in front of you that absorbs incoming magical attacks. When cast as a single action, the spell can be maintained for multiple turns , but no other spell can be cast whilst the shield is maintained. When cast as a counterspell, lasts only for that single action. 
If the incoming spell has a casting check that exceeds the shield casting check (+2 for every power point dedicated), the shield is shattered. The shielding charm protects only against magic, not against physical damage.\end{flushleft}} \\  \bf \begin{center}Stoneskin \\ {\it Lapis Pellium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (precision)\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Increase the target{\apos} AC by 10 for 5 minutes (25 combat rounds). Does not stack.\end{flushleft}} \\  \bf \begin{center}Sunburst \\ {\it sol maxima}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A burst of bright light does 1d6 holy damage to all targets in a 5m radius.\end{flushleft}} \\  \bf \begin{center}Trap Spell  \\ {\it  dolus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN \\ (stealth)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Combine a magical ward with one of your existing spells. Cast the other spell first, then perform the trapping check.
If successful, creates a hidden magical trap, with the effect of the original spell when triggered. The effects of the trap are less than the original spell, but more power points make the trap more powerful. 
If you wish to keep a trap hidden from the GM, write down the location, spell and associated check values on a piece of paper, to be revealed when the trap is triggered.\end{flushleft}} \\  \bf \begin{center}Checkup Charm \\ {\it dispungo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\(understand other)\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Enquire as to the health status of the target, find out their remaining HP, as well as any status effects they currently posses.\end{flushleft}} \\  \bf \begin{center}Counter curse  \\ {\it  finite maledictum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (Arcane)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Remove the effects of an active curse or hex. The caster of the curse performs the casting check again: If the casting check of the counterpsell (+1 for each power point dedicated) is larger than this second check, the curse is removed.\end{flushleft}} \\  \bf \begin{center}Healing Spell   \\ {\it  episkey}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Heal minor status effects like burns, bruises, broken noses and so on. If no status effect present, heal for 1HP for each casting point over the difficulty value.\end{flushleft}} \\  \bf \begin{center}Immunity Charm \\ {\it immunis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Make the target immune to one damage type for 3 turns. Can only be cast once every 5 turns.\end{flushleft}} \\  \bf \begin{center}Lesser Ward   \\ {\it  tueor}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Erects a semi-permanent barrier around an individual. This ward protects you from up to 10 damage of all types, before it fails. Ward moves with the target, and can be cast on self. 
Ward disintegrates after 1 day.\end{flushleft}} \\  \bf \begin{center}Muggle Repelling Ward  \\ {\it  repello muggletum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Forms a warded area that muggles can neither see, nor enter. 
The warded area is a circle 5m in radius + 5m for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Releasing Spell  \\ {\it  relashio})\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (willpower)\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Force objects and beings to release the target from their grip.\end{flushleft}} \\  \bf \begin{center}Runic Ward\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (arcane)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Choose a Damage Type. Target is 10\% resistant to that damage type (+10\% for each PP) for 1 hour.\end{flushleft}} \\  \bf \begin{center}Stabilising Spell  \\ {\it  firmum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Stabilises the patient and removes the \textit{Critical Condition} status.\end{flushleft}} \\  \bf \begin{center}Anti-Apparition Ward \\ {\it nonvidetus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Prevents apparition inside the designated area. Maximum area is 20m in radius. Ward decays after one week.\end{flushleft}} \\  \bf \begin{center}Blessing \\ {\it benedicte}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Give the target Advantage in all checks for 10 turns.\end{flushleft}} \\  \bf \begin{center}Bone Mending Charm  \\ {\it  ossium emendo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Mends bones and other serious physical ailments. Heals for 5 HP + 1 for every power point dedicated to the spell.  
Removes the \textit{Major Injury} status effect.\end{flushleft}} \\  \bf \begin{center}Ironwall Ward \\ {\it ferromurrum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}16\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Forms a shield around the warded area that absorbs 30 points of damage + 5 for every power point dedicated to the spell. 
The Ironwall is opaque and soundproof, and is two-way. Nothing can entire or leave across the threshold of the ward.\end{flushleft}} \\  \bf \begin{center}Mirror Shield Charm  \\ {\it  repente}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A more powerful version of the shielding charm (see protego for full description), but rather than spells being absorbed by the shield, they are reflected back at the caster. Mirror shield also defends against physical attacks.\end{flushleft}} \\  \bf \begin{center}Spare the Wounded \\ {\it clementia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Protects the target from being attacked any further if their health falls below 5HP.\end{flushleft}} \\  \bf \begin{center}Threshold Ward \\ {\it  desino}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Prevents objects from passing over the edge of the ward. Usually cast on doorways and entrances. The ward is immune to all physical damage, but can only survive 8 points of spell damage.\end{flushleft}} \\  \bf \begin{center}Wall of a Million Blades \\ {\it heus nocivious}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (arcane)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Create a wall up to 10 m long and 3m tall. This wall is composed of swirling magical blades that do 3d8 slashing damage to any creature that touches it. Wall has a strength of 10, and lasts 5 cycles.\end{flushleft}} \\  \bf \begin{center}Ailment Charm \\ {\it  sana}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Heals the target of status effects such as burns, frostbite, poisons and some minor diseases. 
Restores 4 HP.\end{flushleft}} \\  \bf \begin{center}Anti-Magic Ward  \\ {\it  prohibere incantatum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}No magic can be cast inside the warded area, although magic cast outside may travel over the boundary. 
Range is 10m + 2 for every power point dedicated. Decays after 4 days.\end{flushleft}} \\  \bf \begin{center}Beartrap Ward \\ {\it ursa dentes}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW \\ (stealth)\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A ward that creates an invisible trap of 2m in radius. When a being crosses over the threshold, the ward slams shut, doing 1d8+3 worth of piercing damage and applying the Trapped status effect.\end{flushleft}} \\  \bf \begin{center}Health Boost Charm  \\ {\it  levo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}11\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Give the caster a temporary +50\% boost to their maximum HP, and adds current HP to match. Lasts for 3 turns, + 1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Holy Ward  \\ {\it pervertutem luminis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Create a region where the Unlife cannot pass. Unlife attempting to cross the barrier are ignited for 1d12 worth of holy damage, and a Major Burn. 
Shield fails when 30 damage has been done + 2 for every power point dedicated to the spell. Radius of ward is 10m.\end{flushleft}} \\  \bf \begin{center}Inversion Zone \\ {\it contrarum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} FIN\\~\\ Target:14\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}This spell creates a permanent warded area inside which all magic performs exactly the opposite to its intended purpose. Healing spells cause harm, hexes heal and shields amplify the spells passing through them.\end{flushleft}} \\  \bf \begin{center}Major Ward \\ {\it  tueormaxima}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Individual Ward (see Lesser Ward) that protects against 25 damage.\end{flushleft}} \\  \bf \begin{center}Fidelius Ward \\ {\it  onsigno scientia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}20\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:22\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Seals away all knowledge of the target inside the mind of the {\it Keeper}. The target can then only be seen, detected, and even known of by the caster, and the keeper, and those that they tell. The ultimate protective ward, since no-one even knows that the target exists. 
The caster cannot also be the Keeper, and if the target is a place (i.e. a house), then the Keeper cannot reside in the region. 
Spell takes 1 day to cast, during which time no other spells can be cast.\end{flushleft}} \\  \bf \begin{center}Magical Stability Ward \\ {\it victoria maximus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}18\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Creates a region where magic is safer and more successful: all spell checks in the warded area get + 2 bonus, and get Advantage. 
Ward interferes with all other warding magic.\end{flushleft}} \\  \bf \begin{center}Total Health Ritual \\ {\it  vita maxima}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}20\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (healing)\\~\\ Target:19\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Restores a character to full health, and removes all negative status effects. Cannot be cast on the self. Takes 2 turns to cast.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Illusion} \addcontentsline{toc}{section}{Spell School: Illusion } Impose your will on other people, and alter the way they perceive the world.\\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Blur \\ {\it celeritate}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The target seems to become blurry around the edges, it is difficult to tell exactly where they are, and where they aren{\apos}t.
Dodging checks do not prevent you from moving next turn.\end{flushleft}} \\  \bf \begin{center}Charming Charm  \\ {\it sismeus amici}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (persuasion)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes the target to like you, persuasion checks get a +2 bonus, and +1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Glamour Charm  \\ {\it  lux stultium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (deception)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Create a superficial glamour around a person, a simple trick of the light. The glamour disintegrates upon physical or magical contact.\end{flushleft}} \\  \bf \begin{center}Night vision \\ {\it aspectu}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (perception)\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Give the target nightvision: dim light is as bright as daylight, and darkness is consdiered dim.\end{flushleft}} \\  \bf \begin{center}Throw Voice Charm  \\ {\it  ventrilofors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (deception)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Cast your voice such that it appears to be coming from somewhere up to 5 metres away (+5 for every power point dedicated to the spell).\end{flushleft}} \\  \bf \begin{center}Blind \\ {\it caecus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If target fails a resist check, they are blinded for 4 turns.\end{flushleft}} \\  \bf \begin{center}Calming Charm  \\ {\it  paxus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (willpower)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Calms the target down. Target performs a Resist magic check with a +4 bonus (-1 for each power point dedicated to the spell), if the check fails, they will stop attacking.\end{flushleft}} \\  \bf \begin{center}Concealment Charm \\ {\it  occulto}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (deception)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Used to conceal messages, makes them invisible to the naked eye.\end{flushleft}} \\  \bf \begin{center}Nature{\apos}s Friend Charm  \\ {\it  nonparum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (Flora \& Fauna)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Commune with an animal: it will join you as an ally for 4 turns.\end{flushleft}} \\  \bf \begin{center}Phantasm Charm  \\ {\it  umbra impetia}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Multiple phantasms attack the target, doing 2 psychic damage for every turn that the phantasms are active. 
Once the original spell hits the targets, phantasms exist only within the target{\apos}s mind, and may pass through all shields and defences. 
Phantasms are active for 2 turns + 1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Piper{\apos}s Illusion Chant\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (performance)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If one has an instrument, this spell hypnotises all those who hear it and fail a 1d10 SPR test (difficulty 18). 
This spell is not blocked by non-specialist wards or shields. Takes 2 turns to cast.\end{flushleft}} \\  \bf \begin{center}Sleeping Charm \\ {\it somnus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If target fails a resist magic check, they enter into a deep slumber for 5 turns +1 for every power point dedicated to the spell\end{flushleft}} \\  \bf \begin{center}Chameleon Charm  \\ {\it  dissimulo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (Stealth)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes the target to take on the exact colour and texture of the background, making them hard to spot when stationary. 
Concealment checks get a + 4 bonus when stationary, and + 1 when moving.\end{flushleft}} \\  \bf \begin{center}Occlumency  \\ {\it occlumens}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (Endurance)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Set up barriers around your mind to defend yourself. 
Legilimency will not work on you, and all other mind-altering spells take a 2 point casting penalty\end{flushleft}} \\  \bf \begin{center}Shatter Illusions   \\ {\it  conlidus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR \\ (Endurance)\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Remove all illusion spells from the target.\end{flushleft}} \\  \bf \begin{center}Entrancing Enchantment   \\ {\it  meamicus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the target fails a resist magic check (-1 penalty for each power point dedicated to the spell), they become hopelessly besotted with the caster for 2 turns.\end{flushleft}} \\  \bf \begin{center}Fury  \\ {\it  irafors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (willpower)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a Resist Magic check, if they fail, target flies into a mindless rage and begins attacking all those around them. 
Lasts for 1 turn + 1 for every casting point above the difficulty level.\end{flushleft}} \\  \bf \begin{center}Legilimency  \\ {\it  legilimens}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a resist magic check (with 1 penalty per power point dedicated to the spell), if it fails, the caster gets to peer inside their mind, and know their deepest secrets,  or even alter memories.\end{flushleft}} \\  \bf \begin{center}Memory Modification Charm   \\ {\it  obliviate}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}You may modify the memories of a target, even causing them to forget skills and spells that they currently know.\end{flushleft}} \\  \bf \begin{center}True Illusion \\ {\it stultuvisus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}15\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (deception)\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Create a perfect illusion of an environment (up to 20m in radius) or people (up to 3), which can be interacted with by the target. Illusions can only have the knowledge that the caster has.
Illusion lasts for 10 turns.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Divination} \addcontentsline{toc}{section}{Spell School: Divination } Peer through the mystic veil and perceive things beyond human comprehension: past, present and future.\\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Identification Charm  \\ {\it  dicemi}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT \\ (research)\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Learn the properties of the target: be it learning about the nature of the target, or the ingredients of a potion.
The more power points dedicated to the spell, the more information that is revealed.\end{flushleft}} \\  \bf \begin{center}Locator Spell  \\ {\it  locus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (research)\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Learn the location of non-magical objects or an unshielded living being.\end{flushleft}} \\  \bf \begin{center}Tea Leaves\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}2\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Use your tea leaves to receive an omen about the future.\end{flushleft}} \\  \bf \begin{center}Telepathic Bond  \\ {\it conanimus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Form a mental connection between your mind and the mind of a willing target. You may then use this connection to communicate silently. 
Target must be within touching distance when the spell is cast, but the bond has no distance limit after that.
Lasts for 2 days.\end{flushleft}} \\  \bf \begin{center}Astral Caltrops\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The target acts as if the terrain posseses caltrops for 10 turns. Caltrops do psychic damage\end{flushleft}} \\  \bf \begin{center}Crystal Gazing\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Gaze into your crystal ball, and ask a question of the cosmos. You will receive a yes or a no answer to any question you ask.\end{flushleft}} \\  \bf \begin{center}Destination Spell  \\ {\it  iterante}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Reveals the next destination that destiny has in store for you, get a hint from the GM about the outcome of an action.\end{flushleft}} \\  \bf \begin{center}Detect Magic Spell \\ {\it  revelio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Reveals to the caster any active spells in the in 15m range. Will deactivate charms whose sole purpose is to remain hidden.\end{flushleft}} \\  \bf \begin{center}Eavesdropping Charm  \\ {\it  dumauris}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Can listen in on conversations up to 10m away (+2 m for every power point dedicated to the spell).\end{flushleft}} \\  \bf \begin{center}Obfuscation Spell  \\ {\it  obscuras}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW (willpower)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Those attempting to use divination to spy on you must pass a 1d6 SPR check (difficulty 4 + 1 for every power point dedicated to this spell) for the spell to work.
Lasts for one week.\end{flushleft}} \\  \bf \begin{center}Contingency Charm \\ {\it fortasse}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} INT\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}You forsee a need for defence in the future, but you can{\apos}t quite see when. The contingency charm allows you to store a spell in an alternative dimension, to be called forth instantly when you need it. After casting the contingency charm, you may then cast the spell that you wish to store. When activated, you may then use this spell as if you had declared a counterspell, in addition to your regular movements. You may have a maximum of three contingencies at any one time.\end{flushleft}} \\  \bf \begin{center}Glimpse Charm  \\ {\it  posterus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Get a fleeting glimpse into the future: Automatically dodge the next attack, in addition to your regular action, OR, your next attack always hits its target.\end{flushleft}} \\  \bf \begin{center}Hone Reflexes\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}By predicting the flow of time, you can give the target the ability to make moves without thinking: give the target 1d4 extra major actions next turn. Each target can only get this boost once per day.\end{flushleft}} \\  \bf \begin{center}Planemeld  \\ {\it  promoveo}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Merge your physical form with a higher plane of existence, temporarily transcending this reality and making a pact with the benevolent beings that reside there. Your senses become more acute, your mind is refreshed, but you may not cause harm for a period of time. 
HP and Fortitude restored by 3 points, casting checks get a +2 bonus for 2 turns, but no combat magic may be used for 4 turns. +1 to all numerical values for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Sense Humans Charm  \\ {\it  hominem revelio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Reveals the presence of humanoid life nearby. 
Radius of spell is 4m, plus one metre for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Astral Projection  \\ {\it  ambilofors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}9\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Leave your physical form behind, and explore an area as your astral self. 
Your astral self is undetectable to most, and has 3 HP + 1 for every power point dedicated to the spell. 
If your astral self is killed, your physical body{\apos}s HP is reduced to zero, and your enter into the Critical Condition status.\end{flushleft}} \\  \bf \begin{center}Commune with the Dead \\ {\it  amisit amicum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If one of your friends has passed away during your journey, you may summon their spirit, and learn one piece of information from them, or temporarily borrow one of their skills and/or spells for 1 turn + 1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}Tag charm \\ {\it signum}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}7\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP \\ (understand other)\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Place a mystical marker on the target which enables your allies to strike more accurately at them. Stealth checks fail, and evasion checks get a -5 penalty for 2 turns + 1 for every power point dedicated.\end{flushleft}} \\  \bf \begin{center}Mists of Time  \\ {\it  momento aeternitatis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}15\end{center}} &    \parbox[t]{\x cm}{\begin{center} EMP\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Enter into a trance, whereby you can observe the past or the future, to uncover what was, or what will be. 
You may observe 1 day into the future, or 1 year into the past, +1 for every power point dedicated to the spell.\end{flushleft}} \\  \bf \begin{center}True Sight \\ {\it  vidergo sumus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}12\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}For 1 hour, you see things as they truly are. You see hidden traps, secret doors, and astral projections. You can see through illusion spells, and attempts to deceive you are in vain.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}\subsection*{Dark Arts} \addcontentsline{toc}{section}{Spell School: Dark Arts } Evil spells, used by evil people. Expect a heavy burden on your soul if you rely on the dark arts to accomplish your goals.\\ \footnotesize \begin{center} \tablealternate \begin{longtable}{|m{\t cm} m{\u cm} m{\v cm} m{\w cm} m{\x cm} m{\z cm}|}\hline \tablehead {\normalsize \bf Name } & {\normalsize \bf Class} & {\normalsize \bf Mastery}& {\normalsize \bf FP}  & {\normalsize \bf Check} & \bf {\normalsize Effect}  \\ \hline \hline \bf \begin{center}Blight \\ {\it thanatos}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}A wave of necrotic energy extends outwards from you in a radius of 10m (doubled with every PP, max 1km). All plants within range die instantly, and all other living beings take 1d4 necrotic damage (+1 per PP)\end{flushleft}} \\  \bf \begin{center}Eldritch Knowledge Spell  \\ {\it  vetitum scenticus}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Gain access to eldritch knowledge. The Demons of the Deep will answer one of your questions, but the answers might drive you mad.
The question must be said out loud for all to hear, but the answer may be written down and passed to your privately.\end{flushleft}} \\  \bf \begin{center}Shadow Blast \\ {\it  malusangui}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}3\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:4\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Hurl shadows at you enemy, dealing 1 necrotic damage for every casting point over the difficulty level.\end{flushleft}} \\  \bf \begin{center}Shroud of Darkness \\ {\it tenebrosa}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:6\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Extinguish all light within a 10m radius (+2 for every PP to the spell)\end{flushleft}} \\  \bf \begin{center}Slashing Curse \\ {\it  sectumsempra}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Beginner\end{center}}  &   \parbox[t]{\w cm}{\begin{center}4\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:5\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Gouges at the target, leaving deep, cursed wounds, for 1d6 points of slashing damage, plus two for every PP to the spell.\end{flushleft}} \\  \bf \begin{center}Dark Healing \\ {\it tenebrosa sudarium}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If in shadow, heal for one HP for each casting point over the difficulty. Remove half of this HP from an ally.\end{flushleft}} \\  \bf \begin{center}Terror Curse  \\ {\it  fear me}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (intimidation)\\~\\ Target:7\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Target performs a 1d10 SPR (endurance) check, if the check is less than the casting check, the target acquires the {\it Terrified} status.\end{flushleft}} \\  \bf \begin{center}Torturing Curse  \\ {\it Crucio}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL \\ (Chaos)\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Causes immense pain to the target, paralysing them whilst the spell is cast. 
Once successfully cast, this spell can be continuously maintained until the caster stops, but caster cannot perform other actions whilst the spell is maintained.  
Does 1 point of psychic damage per PP.\end{flushleft}} \\  \bf \begin{center}Void Spell \\ {\it  inanis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Novice\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL \\ (Chaos)\\~\\ Target:8\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summon a true Void, a gap in the fabric of reality that sucks in everything nearby. 
Lasts for 1 turn, plus 1 extra turn per PP.\end{flushleft}} \\  \bf \begin{center}FiendFyre  \\ {\it  pyrkagius}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:10\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Summons a cursed fire that consumes everything that it touches.
Does 1d8 fire damage to all it touches, and will actively seek out targets. 
Attempts to extinguish the fiendfyre must defeat a 1d12 SPR check against the casting check\end{flushleft}} \\  \bf \begin{center}Killing Curse  \\ {\it  Avada Kedavra}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:14\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the spell makes contact with the target, kills them instantly. There is no countercurse.\end{flushleft}} \\  \bf \begin{center}Living Shadow Curse  \\ {\it  vivent umbrafors}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}8\end{center}} &    \parbox[t]{\x cm}{\begin{center} SPR\\~\\ Target:11\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Bring the very shadows to life: a being of pure darkness will stalk your enemies, attacking them whenever they stray near the shadows, doing 1d10 worth of necrotic damage. 
Last 3 turns + 1 for every PP.\end{flushleft}} \\  \bf \begin{center}Necrotic curse \\ {\it carnes mortis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Adept\end{center}}  &   \parbox[t]{\w cm}{\begin{center}6\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW \\ (chaos)\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Do 1 necrotic damage and 1 poison damage for every point over the casting check.\end{flushleft}} \\  \bf \begin{center}Blood Barrier  \\ {\it confusangui}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}5\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:9\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Use blood to draw warding runes onto an object or person. Erects a magical with 4 strength, plus 1 for every casting point over the difficulty.
Each individual{\apos}s blood can only be used once for blood magic.\end{flushleft}} \\  \bf \begin{center}Controlling Hex  \\ {\it Imperius}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}11\end{center}} &    \parbox[t]{\x cm}{\begin{center} CHR \\ (persuasion)\\~\\ Target:13\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}If the target fails a resist magic check, the target is placed under the complete control of the caster for 1 turn + 1 turn for every PP.\end{flushleft}} \\  \bf \begin{center}Zombie Curse  \\ {\it  inferi exorior}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Expert\end{center}}  &   \parbox[t]{\w cm}{\begin{center}10\end{center}} &    \parbox[t]{\x cm}{\begin{center} POW\\~\\ Target:12\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Breathes unlife into dead bodies, and turns them into ghastly puppets, performing your every whim: the inferi.\end{flushleft}} \\  \bf \begin{center}Chaos Magic  \\ {\it chaomal portis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Power Dependent\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}20\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL \\ (chaos)\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Open a portal to the depths of hell, where the Demons of the Deep reside. 
For every turn that the portal remains open, it casts random Dark Magic at all targets outside a 2m radius of the caster. These spells increase in power as the portal remains open. 
The portal stays open for 2 turns, plus one turn per PP.\end{flushleft}} \\  \bf \begin{center}Horcrux Creation Ritual  \\ {\it  pervinco mortis}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}25\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}The caster places a portion of their soul into another object. Write down the horcrux on a piece of paper and keep it hidden. 

Whilst a horcrux exists, the character cannot be killed, however creating a Horcrux reduces all casting checks by 2 for each horcrux that is created.  
Can only be cast if the caster has murdered an innocent in cold blood.\end{flushleft}} \\  \bf \begin{center}Soul Snare  \\ {\it  necro decipula}\end{center} &  \parbox[t]{\u cm}{\begin{center}Effect Only\end{center}}  &   \parbox[t]{\v cm}{\begin{center} Master\end{center}}  &   \parbox[t]{\w cm}{\begin{center}14\end{center}} &    \parbox[t]{\x cm}{\begin{center} EVL\\~\\ Target:20\end{center}}&      \parbox[t]{\z cm}{\begin{flushleft}Capture the soul of a recently killed enemy. 
This soul may be used to instantly cast any other spell without a casting check or fortitude cost, or alternatively; absorbed to heal the character to full health and fortitude. 
Only one soul may be trapped at any given, and no power points may be dedicated to the instant-casting.\end{flushleft}} \\  \hline\end{longtable} \end{center} \normalsize \vspace{4ex}%%SpellEnd
