\chapter{Tools}

\newcommand\tool[2]
{
	\vspace{2 ex}
	\small
	\vbox{
	{\bf #1}
	
	#2
	}
	\normalsize
}

A tool helps you to do something you couldn't otherwise do with your bare hands \minus{}\minus{} or even with your wand \minus{}\minus{} such as craft or repair an item\comma{} forge a document\comma{} or pick a lock. Anyone can use a tool\comma{} but only someone who is proficient in it will be able to use a tool to its full potential. Proficiency in a tool is granted through Racial or Archetype abilities\comma{} or by taking the Tool\minus{}User Skill. 

A common list of tools is presented below:


%%ToolsBegin
  \begin{center}\begin{rndtable}{|l l l|}\hline \tablehead \normalsize \bf Name & \normalsize \bf Weight & \normalsize \bf Cost \\ \hline 	\bf Alchemy Gear	&	Medium	&	\sickle{11}~\knut{25}
 \\ 
	\bf Broomstick	&	Medium	&	Various
 \\ 
	\bf Climbers Kit	&	Medium	&	\sickle{8}~\knut{15}
 \\ 
	\bf Cooking Utensils	&	Medium	&	\sickle{3}~\knut{10}
 \\ 
	\bf Disguise Kit	&	Light	&	\sickle{3}~\knut{10}
 \\ 
	\bf First Aid Kit	&	Light	&	\sickle{13}~\knut{15}
 \\ 
	\bf Forgery Tools	&	Light	&	\sickle{2}~\knut{20}
 \\ 
	\bf Gaming Set	&	Medium	&	\sickle{3}~\knut{10}
 \\ 
	\bf Herbology Tools	&	Medium	&	\sickle{4}~
 \\ 
	\bf Jeweller\apos{}s Tools	&	Light	&	\sickle{11}~\knut{25}
 \\ 
	\bf Lockpicking Tools	&	Light	&	\sickle{6}~\knut{25}
 \\ 
	\bf Musical Instrument	&	Various	&	\galleon{2}~
 \\ 
	\bf Navigator\apos{}s Tools	&	Light	&	\sickle{3}~\knut{10}
 \\ 
	\bf Repair Kit	&	Medium	&	\sickle{5}~
 \\ 
	\bf Runic Tools	&	Light	&	\galleon{1}~\knut{20}
 \\ 
	\bf Smithing Tools	&	Heavy	&	\sickle{7}~\knut{15}
 \\ 
\hline
\end{rndtable}
\end{center} 

 
 \tool{Alchemy Gear}{A must\minus{}have for the budding alchemist\comma{} potion equipment typically consists of a collapsable cauldron\comma{} an alembic\comma{} a distillation setup\comma{} and a titration column. Proficiency in this set of equipment allows you to add your Expertise bonus to potion making attempts.}
 
 \tool{Broomstick}{The primary mode of travel for the wizarding world. Most everyone can use a broomstick to get from A to B if they need to. However\comma{} to perform any kind of advanced flying – to cast spells\comma{} perform evasive maneouvres and so on – requires one to be proficient in the use of a broomstick.}
 
 \tool{Climbers Kit}{Required for scaling up vertical faces\comma{} or abseiling down them. You move at one\minus{}quarter your walking speed\comma{} unless you have proficiency in this tool\comma{} in which case you move at half\minus{}speed.}
 
 \tool{Cooking Utensils}{Useful for producing life\minus{}sustaining nutrition out in the wilderness. Proficiency in this toolset means meals cooked restore one level of exhaustion when eaten.}
 
 \tool{Disguise Kit}{A pouch of minor cosmetics\comma{} dyes and small props allows you to alter your appearance through non\minus{}magical means. Proficiency allows you to add your Expertise bonus to subsequent Deception and Stealth checks made by the disguised individual.}
 
 \tool{First Aid Kit}{A first aid kit allows you to perform medical procedures\comma{} when in a pinch. Used without proficiency and passing a DV15 Intelligence check allows you to Stabilise a dying individual. With proficiency\comma{} can heal 1d4 damage.}
 
 \tool{Forgery Tools}{This kit of parchments\comma{} papers\comma{} inks and wax seals enables you to attempt to produce convincing fakes and forgeries\comma{} though they can be seen through with a DV10 Intelligence check. Proficiency allows you to add your Expertise bonus to the DV required to spot that the forgery is a fake.}
 
 \tool{Gaming Set}{A set of a mundane or magical game\comma{} such as Wizard chess. Proficiency in this toolset allows you to add your Expertise bonus to all checks whilst playing that game. Each subsequent game requires a new proficiency.}
 
 \tool{Herbology Tools}{Tools required to grow your own plants – pruning shears\comma{} plant nutrients and so on \minus{} as well as to harvest plants you find in the wild. Proficiency in these tools lets you harvest double the usual number of samples from a plant.}
 
 \tool{Jeweller\apos{}s Tools}{A set of tools used to determine the authenticity and nature of mundane and enchanted objects\comma{} a Jeweller\apos{}s set bears a visual similarity to the muggle tools from which they get their name – an eyeglass and some simple alchemical equipment. Proficiency allows you to add your Expertise bonus to all checks used to investigate the nature of an item.}
 
 \tool{Lockpicking Tools}{Whilst a wizard often relies on magical means to get past locks and traps\comma{} powerful and intricate magics often require additional help. Wizard\apos{}s lockpicks are not just sticks of iron\comma{} but are often interwoven with powerful enchantments to ease to process and the set includes various arcane and mundane tools for use in such situations. Proficiency with them enables you to add your Expertise bonus to lockpicking checks.}
 
 \tool{Musical Instrument}{Merely possessing a musical instrument allows you to make crude noises\comma{} but you require proficiency to truly play an instrument\comma{} and you may add your Expertise bonus to all checks relating to the instrument. Each subsequent instrument requires a new proficiency.}
 
 \tool{Navigator\apos{}s Tools}{A requirement for long\minus{}distance navigation. Allows you to chart a course for a on\minus{}foot travel\comma{} broomstick flight\comma{} ship\apos{}s course for journeys greater than 5 hour. Proficiency in these tools allows you to add 1 hour for every point of your Expertise bonus.}
 
 \tool{Repair Kit}{A set of tools for performing minor repairs to armour and clothing. Proficiency allows you to halve the time required to repair a set to full strength\comma{} and allows you to repair {\\it Destroyed} armour.}
 
 \tool{Runic Tools}{Runic tools allow you to engrave intricate runes on a surface with exquisite accuracy\comma{} a requirement for the creation of the fine magical matrices used in Enchanting. Proficiency in these tools allows you to add your Expertise bonus to Enchanting checks.}
 
 \tool{Smithing Tools}{Required to forge new items out of raw material. Proficiency grants you the ability to add your Expertise bonus to smithing related checks\comma{} and doubles the value of items you can produce in your downtime.}%%ToolsEnd


