\input{EncounterDefinitions}

\begin{document}
\encounter{Peeve’s “Light”\minus{}Hearted Fun}
{A simple encounter for low\minus{}level characters based out of Hogwarts. Peeves the Poltergeist is known for his trickery and his pranks – which sometimes veer off into the downright dangerous. 

For this encounter\comma{} Peeves has somehow managed to get hold of a number of \imp{Solon}s\comma{} crystalline\comma{} elemental entities capable of manipulating light.}{\encounterBeast{name = Solon, species = Light Elemental, mind = Non\minus{}Sapient, category = Elemental, rating = III, abilities = \ability{Floating}{The \name{} naturally floats in the air using its \imp{Flight} ability.}, article = A, movement = \speeds{\speedrating{Flying}{8}}, fit =2, prs =3, vit =3, cha =2, dec =0, ins =1, int =1, wil =3, pcp =2, hasDamage = 1, damage =\key{Immune} to \textit{Incandescent}\comma{} \key{Resistant} to \textit{Fire} and \key{Susceptible} to \textit{Bludgeoning}, nUnharmed=1, nBruised=1, nHurt=1, nInjured=1, nWounded=0, nMangled=0, block=4, dodge=1, defy=2, fortitude=1, imageStack=0, hasSkills = 1, skills = \skill{Spellcasting}{3}
\skill{Flight}{2}
, hasAttacks = 1, attacks = \ability{Crystal Shards}{Whenever the \name{} takes physical damage\comma{} they may choose to take an additional level of harm to deflect fragments of their body into a creatue within 2m\comma{} dealing level 5 \imp{Stabbing} damage.}

\ability{Elemental Magic}{The solon may use its \imp{Spellcasting} ability to cast spells. It knows the \imp{Illuminate}\comma{} \imp{Sense} and \imp{Move} spells.}, hasLanguages = 1, languages = \speaks{Empyrean}, hasImage = 1, image = solon, 
participants = { {a}, {Solon 2}, {Solon 3}}, 
description = \name{}s are lesser elementals hailing from the Radiant Gardens\comma{} the Elemental plane of light. They are crystalline creatures\comma{} and glow with an inner radiance which shifts and refracts through their bodies as they move.}\encounterBeast{name = Poltergeist, species = Apparitions, mind = Ineffable, category = Phantasm, rating = II, abilities = \ability{Phaseshift}{A \name{} may use an action to shift between corporeal and incorporeal form and vice versa. Whilst in incorporeal form the \name{} is immune to all harm\comma{} can fly and can pass through solid objects.}, article = A, movement = \speeds{\speedrating{Flying}{12}}, fit =2, prs =5, vit =1, cha =2, dec =3, ins =3, int =2, wil =4, pcp =3, hasDamage = 1, damage =\key{Resistant} to \textit{All damage}, nUnharmed=1, nBruised=1, nHurt=1, nInjured=0, nWounded=0, nMangled=1, block=1, dodge=4, defy=3, fortitude=2, imageStack=0, hasSkills = 1, skills = \skill{Covert}{4}
\skill{Flight}{3}
\skill{Marksmanship}{3}
\skill{Spellcasting}{2}
, hasAttacks = 1, attacks = \ranged{Throw Objects}{10}{7}{\minus{}2}{Bashing damage}{1 + Successes}

\ability{Arcane Trickster}{A \name{} may use their \imp{Spellcasting} ability to cast the \imp{Move\comma{} Degrade\comma{} Mirage} and \imp{Bypass} spells.}, hasLanguages = 1, languages = \speaks{Human languages}, hasImage = 1, image = peeves, 
participants = { {Peeves}}, 
description = A poltergeist is an amortal\comma{} indestructable spirit of chaos and mischief. They appear as a short\comma{} childlike figure dressed in a motley jester\apos{}s garb\comma{} with glowing orange eyes\comma{} which twinkle with mischief. 

Brought into existence by a critical mass of humans\comma{} trickery and mischief\comma{} poltergeists haunt the specific place which they are tied to. 

Unusually out of apparitions and other spiritual creatures\comma{} poltergeists are able to take on physical form and cast primitive forms of magic \minus{} which they use to wreak chaos and play pranks on unsuspecting humans.}}

\end{document}