\input{EncounterDefinitions}

\begin{document}
\encounter{Radiant Gardens Encounter}
{Light Elementals Attack!}{\encounterBeast{name = Chalkydri, species = Light Elemental, mind = Non\minus{}sapient, category = Elemental, rating = V, abilities = \ability{Winged Herald}{The \name{} may use its \imp{Flight} skill to take to the skies\comma{} gaining a flying speed of 30m per round}

\ability{Spectral Mesmer}{Any creature which comes within 20m and can see the \name{} must gain at least one success on a DV 8 check (recommended \imp{Willpower (Conviction)} to tear their eyes away from the hypnotising lights emanating from the \name{}\comma{} on a failure\comma{} they must spend their entire turn doing nothing but staring at the \name{}.}

\ability{Light Siphon}{At the end of every round\comma{} if the \name{} can see a source of light\comma{} they regenerate health equal to a DV 4 \imp{Regeneration} check}, article = A, movement = \speeds{\speedrating{Walking}{5}\speedrating{Flying}{20}}, fit =4, prs =2, vit =4, cha =3, dec =0, ins =2, int =3, wil =4, pcp =3, hasDamage = 1, damage =\key{Immune} to \textit{Incandescent\comma{} Fire}, nUnharmed=3, nBruised=3, nHurt=3, nInjured=2, nWounded=1, nMangled=0, block=3, dodge=6, defy=4, fortitude=5, imageStack=1, hasSkills = 1, skills = \skill{Spellcasting}{7}
\skill{Flight}{5}
\skill{Regeneration}{4}
\skill{Speed}{2}
, hasAttacks = 1, attacks = \melee{Reptilian Jaws}{10}{0}{Stabbing}{3 + Successes}

\melee{Jagged Tail}{10}{2}{Bashing}{5 + Successes (Reach 5m)}

\area{Downdraft}{circle 10m radius below current flying position)}{8}{0}{Prone}{1 + Successes}

\ability{Bringer of Dawn}{The \name{} may use its \imp{Spellcasting} ability to cast the \imp{Illuminate} spell.}, hasLanguages = 1, languages = \speaks{Empyrean}, hasImage = 1, image = chalkydri, 
participants = { {Chalkydri 1}}, 
description = Also known as the `Heralds of Dawn’\comma{} these copper\minus{}skinned\comma{} winged serpent\minus{}like creatures were often mistaken for a species of \imp{Dragon} throughout history\comma{} and it is only recently that their true origins have been determined. 

Possessing the face and tail of a crocodile\comma{} but the body of a lion and rows upon rows of rainbow\minus{}coloured wings (up to 14 pairs on the oldest known specimen)\comma{} these creatures typically reside within the coronosphere of a sun\comma{} or near some other cosmically powerful source of light\comma{} descending planetside only for a few hours per year\comma{} and even then\comma{} they appear only during the first few moments of dawn. 

When the sunlight hits their copper\minus{}bronze skin\comma{} it splits off into a mesmerising rainbow display\comma{} and causes their entire body to hum with a resonance like a chorus of angels. Legend holds that it is this song which brings the dawn\comma{} rather than the other way around.

Though they do not seem particularly intelligent\comma{} and are currently classified as `beasts’ by the \imp{Ministry}\comma{} this does not mean that they are savage – in fact\comma{} the \name{} are often kind and gentle creatures\comma{} the few times that they have been recorded as coming into direct conflict with humans it was eventually discovered that the humans were threatening some other life form with extinction\comma{} drawing the ire of the \name{}.}\encounterBeast{name = Solon, species = Light Elemental, mind = Non\minus{}Sapient, category = Elemental, rating = III, abilities = \ability{Floating}{The \name{} naturally floats in the air using its \imp{Flight} ability.}, article = A, movement = \speeds{\speedrating{Flying}{8}}, fit =2, prs =3, vit =3, cha =2, dec =0, ins =1, int =1, wil =3, pcp =2, hasDamage = 1, damage =\key{Immune} to \textit{Incandescent}\comma{} \key{Resistant} to \textit{Fire} and \key{Susceptible} to \textit{Bludgeoning}, nUnharmed=1, nBruised=1, nHurt=1, nInjured=1, nWounded=0, nMangled=0, block=4, dodge=1, defy=2, fortitude=1, imageStack=0, hasSkills = 1, skills = \skill{Spellcasting}{3}
\skill{Flight}{2}
, hasAttacks = 1, attacks = \ability{Crystal Shards}{Whenever the \name{} takes physical damage\comma{} they may choose to take an additional level of harm to deflect fragments of their body into a creatue within 2m\comma{} dealing level 5 \imp{Stabbing} damage.}

\ability{Elemental Magic}{The solon may use its \imp{Spellcasting} ability to cast spells. It knows the \imp{Illuminate}\comma{} \imp{Sense} and \imp{Move} spells.}, hasLanguages = 1, languages = \speaks{Empyrean}, hasImage = 1, image = solon, 
participants = { {Solon 1}, {Solon 2}}, 
description = \name{}s are lesser elementals hailing from the Radiant Gardens\comma{} the Elemental plane of light. They are crystalline creatures\comma{} and glow with an inner radiance which shifts and refracts through their bodies as they move.}\encounterBeast{name = Phlogiston, species = Light Elemental, mind = Ineffable, category = Elemental, rating = IV, abilities = \ability{Phaseshift}{The \name{} may use its \imp{Shapechanging} ability to morph into gaseous form\comma{} where it may use its flight speed\comma{} but loses the ability to use \imp{Evaporating Blast}. It may use this ability again to morph back into liquid form.}, article = A, movement = \speeds{\speedrating{Walking}{2}\speedrating{Flying}{40}}, fit =1, prs =5, vit =3, cha =4, dec =0, ins =3, int =5, wil =3, pcp =2, hasDamage = 1, damage =\key{Immune} to \textit{Incandescent} and \key{Resistant} to \textit{All physical damage}, nUnharmed=6, nBruised=0, nHurt=0, nInjured=0, nWounded=1, nMangled=0, block=0, dodge=4, defy=3, fortitude=4, imageStack=1, hasSkills = 1, skills = \skill{Flight}{10}
\skill{Shapechanging}{5}
\skill{Spellcasting}{5}
, hasAttacks = 1, attacks = \ranged{Evaporating Blast}{100}{6}{\minus{}1}{Incandescent}{1 + Successes}

\ability{Elemental Magic}{The \name{} may use its \imp{Spellcasting} ability to cast spells. It knows the \imp{Illuminate}\comma{} \imp{Fire} and \imp{Move} spells.}, hasLanguages = 1, languages = \speaks{Empyrean}, hasImage = 1, image = phlogiston, 
participants = { {Phlogiston 1}}, 
description = A highly unusual magical creature\comma{} originating from the Plane of Light\comma{} but subsequently spreading to all corners of reality\comma{} A phlogiston is a creature of liquid light\comma{} a sentient\comma{} glowing pool of power and warmth. 

Though normally calm and blissful creatures\comma{} when angered or afraid\comma{} the phlogiston can shift into a gaseous form\comma{} or evaporate parts of its form entirely into powerful blasts of light.}}

\end{document}