\documentclass[oneside, 9pt,english]{extbook}

\usepackage{../../HPpack}


\title{\key{Cerise's Memory}}

\date{September - December, 2020}

\begin{document}

	\maketitle
	
	\section{First Days at Hogwarts}
	\key{Cerise Umbridge} first arrived at \imp{Hogwarts} in September 2019, along with her trusty half-kneazle sidekick \key{Norman}. Continuing the family tradition, she was promptly sorted into \imp{Slytherin} house. Secretly, however, she would much rather have been in \imp{Hufflepuff}, but the ramifications from her family had she asked the \imp{Sorting Hat} to reconsider would be too bad to even imagine. 
	
	Despite her snooty facade and distrust of others, \imp{Cerise}'s desire to make friends soon led her to falling in with an unusual crowd: her classes placed her alongside  the scholarly \key{Helena}, the troublesome \key{Nikc} and the enormous (both physically, and in heart) \key{Luke}. Together they bested the challenge of the \imp{Hogwarts Hunt}: defeating the crafty imp \imp{Solovei} and locating the mighty \imp{Gloves of Muromets}, which were promptly claimed by \imp{Luke}.
	
	\section{The Thing Beneath The Tree}
	Over the next few weeks, this group of intrepid youngsters continued to learn and grow - acquiring a handful of new spells and abilities. To the surprise of everyone, they even managed to best the impromptu dueling instructor, \key{Derek Hofstadtler}, a \imp{Ministry Auror} who had been sent to investigate some unusual reports in the grounds of \imp{Hogwarts}. 
	
	A couple of days later, on the 10th of \imp{December}, they again encountered \imp{Derek} looking beaten and roughed up, discussing a form of `corruption'. Buoyed with confidence after defeating him, the group decided to go see what the problem was for themselves. 
	
	After sneaking past the sickly \imp{Whomping Willow}, which was surrounded by acres of dying, yellowing grass, the group descended into some earthen caverns beneath the tree's roots. Following a tunnel, they spiralled down and around for hundreds of metres - as the tunnel slowly morphed from excavated earth to carved stone, and finally into a large, artificial, stone shaft, which continued ever-downwards.
	
	Finally, the group reached the end of the line: a vast, inky black expanse stretched out before them in the form of an incomprehensibly large cavern. Upon stepping over the threshold, their magical illumination was extinguished, and from deep within the chamber, a mechanical whirring, thrumbing, throbbing noise began to grow louder. A series of pale blue lights began to dance and flicker in the far distance: with more and more of them bursting into life, approaching the group.
	
	Finally, a source of light emerged - illuminating a gigantic, humanoid face appearing out of the darkness, inches from their faces. Evidently artificial, the face was carved from stone and metal, cogs and rotating gears could
be seen behind its terrifying viasge. Sparks of electricity danced across its surfaces, though a near-impercetible high-pitched whine was the only sound they heard. 

They saw no body, for the being was shrouded in darkness - if it was of human proportions, it would have been 20 - maybe 30 - feet tall. 

	As the mechanical sounds increased in intensity, the group did the only thing they could: they ran. 
	
	\section{An Empty Castle}
	As they turned tail and fled down the corridor, a blinding white flash seemed to emanate from every surface,
temporarily blinding everyone. As they turned to look back down the corridor, they discovered that the
opening to the cavern had been replaced by a perfect copper wall, which resisted all further investigation.
No other sign of their terrifying experience remained.

Still quaking in their boots, the group fled mindless and paying no heed to their surroundings, until they
reached the safety of \imp{Hogwarts Library}, where they tried to learn all they could about constructs and hidden
chambers. After an hour of fruitless search, something began to bug the students - or rather, the lack of something.

Casting their minds back, the group realised they hadn’t seen a single
person since they entered the cavern. The four immediately leaped back into action, and scoured the castle,
looking for signs of life - but none came. Even \imp{Norman} was nowhere to be found, though the presence of the comforting
link between master and familiar assured her that Norman was still alive.
The talking portraits were the only semi-sentient beings to be found, and informed the investigating group
that several hours ago (approximately when the group was below ground), an almighty hubbub came, and
the entire student body, as well as the staff, filed out of the main hall, and out through the main exit of the
school.

The trail of rubbish and debris led the group all the way to \imp{Hogsmeade} station, where the \key{Hogwarts Express}
stood, engines fired up - but empty. Closer inspection appeared to indicate that the trail of debris stopped
a few dozen metres before the train station.

As the group explored the train, Luke couldn’t help do the one thing he’d always wanted to do - and entered
the main cabin, and tugged on the whistle. As the train ‘choo choo’d happily, a sudden magical pressure seemed to press at all four students’ eyes, and
the world faded into darkness and confusion.

\section{Wizards Under Attack}

The group awoke to find themselves inside the \imp{Hogwarts Express}, which was parked in an underground railway station. Surrounding them were dozens of \imp{Aurors}, with wands pointing in their faces. The \imp{Minister for Magic} himself, \key{Galen Rex} was there, demanding to know what had happened. 

Over the course of the next few days, the group were questions (even interrogated) multiple times about what they knew. Although they proffered the whole and complete truth, nothing they said seemed to help. Eventually, the group learned that there had been a number of attacks across the \imp{Wizarding World} on the 10th December - the day they had descended beneath the tree. The nature of these attacks remained unclear, but a number of automaton-like metal creatures had attacked \imp{Ministries} across the globe - with casualties in the thousands, even tens of thousands. \imp{London} itself had seemed to escape - a large explosion outside the main entrance was attriubted to a failed attack. 

In the event of such an attack, the \imp{Hogwarts Express} was supposed to be used to instantly evacuate the school - but the only people to appear were our fearsome foursome. The rest of the school were nowhere to be found. 

\imp{Minister Rex} asked the group to do him a favour: the absence of \imp{Hogwarts} threatened the stability of the fragile alliances which held the non-human world and the human world together. In particular, he noted, the Giant Clans, centaurs and mer-people north of the \key{Dee Line} signed their treaties of peace and unity with \imp{Hogwarts} itself - not the \imp{Ministry}, who they view as an illegitimate government. As the only representatives of \imp{Hogwarts} available, it fell to them to become ambassadors, and hopefully prevent the fracturing of wizarding society.

After being granted a \key{Ministry Badge} for official business, and an allowance of \imp{Galleons}, the group went to prepare themselves for their new mission.

Whilst perusing the goods in \key{Diagon Alley}, a mysterious individual was spotted legging it through the crowds carrying a crate- when the group tried to intervene, chasing him into a back alley, the individual immediately went for the kill, almost spearing \imp{Helena} through the heart and almost burning \imp{Nikc} alive.
 
 After a dangerous combat, \imp{Cerise} was eventually able to entomb their attacker in ice. \imp{Luke} nailed their now-chilly foe into a crate of oranges he found in this dingy alley - reasoning at least he'd have a snack when he thawed.
 
 The crate, now left on the ground, turned out to have a nasty surprise within it: a gigantic spider leaped from the box and tried to finish off the weakened \imp{Nikc}. \imp{Helena} eventually managed to spear the critter on a conjured spike. 
 
 A note found on their icy captive led them to \key{The Coffin House}, a creepy shop in \key{Nockturn Alley}, which appeared to have been raided recently by the \imp{Ministry}. Their \imp{Badge} allowed them access, and they discovered what the authorities had missed: a trapdoor leading into the inky depths. 
 
 The group rallied together, and dropped through the hatch, to face what came next. 
  
	\section{The Fog Descends}

	As \imp{Cerise} tries to recall these events, they feel somewhat clouded, as if the scenes were covered in a thick fog. The closer the event is to the group dropping through the hatch, the murkier the memory becomes - flashes of memory reveal slightly altered versions of events - their captive killed, rather than captured - \imp{Luke} under attack from the spider, not \imp{Nikc}. The very rules governing reality seem to bend and flex in her memory, as if the world had undergone some paradigm shift. 
	
	Locations, faces and names get more and more muddled in \imp{Cerise}s head, especially in the hour or so before they dropped through the hatch - until the fog descends completely.
\end{document}
