\documentclass[oneside, 9pt,english]{extbook}

\usepackage{../../HPpack}


\title{\key{Memories of the Past}}

\date{September - March, 2020}

\begin{document}
	\maketitle
	
	\subsection{First Days}
	
	The first few memories of our new characters are somewhat banal (as if some of them had not existed for the first part of the story) - at least, by \imp{Hogwarts} standards. The excitement of coming to the near-mythical \imp{Hogwarts} is a certainly a special and unique feeling - and not something to downplay.  

	They arrived in \imp{Hogwarts} in September of 2019, and after being sorted into their respective \imp{Houses}, they went about exploring what wizarding life had to offer.
	
	They learned some of their first new spells - and began to undertake the personal journeys which would shape the kind of person they would grow up to be. They almost certainly competed in the puzzling \imp{Hogwarts Hunt} event held in October - though they ultimately missed out on a crucial clue due to a poorly placed ``Keep Out" sign, which many allege was placed there by the ultimate winners, an act which many considered cheating. 
	
	Some of them also ended up getting extremely ill a few days later, when it was discovered that someone had swapped the labels around in the \imp{Potions} storeroom, leading to a lesson about the healing properties of the \key{Wiggenweld} potion to become a horrifying lesson in the toxic properties of the \imp{Venemous Tentacula}.
	
	\subsection{The Attacks}
	
	On the 10th of December, however, something drastic happened: the \imp{Wizarding World} was attacked.
	
	The nature of these attacks remained unclear, but a number of automaton-like metal creatures had attacked \imp{Ministries} across the globe - with casualties in the hundreds, even thousands. \imp{London} itself had seemed to escape - a large explosion outside the main entrance was attributed to a failed attack, but no casualties were reported. 
	
	Even as the first whispers of something amiss circulated the school, the teachers hurried the students out of the front gate - all the way to \imp{Hogsmeade Station}, where the \key{Hogwarts Express} was waiting. 
	
	As the school piled aboard - panic beginning to set in - the train departed. Not in the normal way, however, as it seems that the entire train had been turned into a \key{Portkey}. As the world turned to darkness, and seemed to press in on them all from every angle, they re-apparated into an underground train station. 
	
	The teaching staff, alongside some \imp{Ministry Aurors} led the students down into some secured accommodation, where they remained until the all-clear was given. Given the proximity to the normal end of term and the Christmas hollidays, the decision was taken to send students home early. 
	


	\subsection{Returning to School}

		Despite Christmas being a somewhat sombre affair - given the immense loss of life - when students returned to \imp{Hogwarts} in January, things quickly returned to normal. 
		
		Of course, the primary topic of conversation remained: {\it who was responsible for the attacks?} Most people were convinced that a Goblin sepratist movement was behind the attacks - the machines were clearly highly magical, artificial devices of the kind that only \imp{Goblins} could construct. Some disputed this however - after all, what could they possibly have gained?
		
		In mid-January, the \imp{Ministry} revealed that a strike-team had successfully located the culprits of the attack, and swiftly dealt with them. An unfortunate accident, however, had triggered a failsafe device within the criminals' lair, and brought an entire mountain down on top of the group - killing everyone involved. The Daily Prophet was able to reveal that the perpetrators were indeed primarily goblins, though a number of giants and centaurs, and even a handful of wizards, had been co-opted into their nefarious scheme, and ultimately met their end underneath that mountain.
	
	\subsection{Coming Together}
	
	By the end of \imp{February}, things had indeed returned to normal. Schoolwork continued, and assignments stacked up. 
	
	Though they had no doubt seen each other, and interacted in their first 6 months at \imp{Hogwarts}, our group was first brought together as a unit through the machinations of \key{Professor Janet Su}, the \imp{Charms} teacher. She had prepared a special assignment - worth 50\% of their final grade for this year. Working in small groups, they had to produce something that would showcase ingenuity, magical talent and a greatness of spirit: besides these words, her only other advice was "\key{impress me}".
	
	These four individuals, therefore, find themselves thrust together on the intrepid quest to impress a middle aged school employee. 
\end{document}
