\documentclass[oneside, 9pt,english]{extbook}

\usepackage{../../HPpack}


\title{\key{True History}}

\date{5000 BC - February, 2020}

\begin{document}
	\maketitle
	
	\section{The Demon Wars}
	
	Though humans are loathe to admit it, they were not the first sapient creatures to arise on Earth - or even the first humanoids. Indeed: the \imp{Centaurs}, \imp{Goblins}, \imp{Giants} and \imp{Merpeople} had been walking the Earth for millenia before humans decided to stop flinging faeces at each other, and begin working together.
	
	Before the rise of human civilisation, however, the sapient races faced a true existential threat: great and powerful \key{Demons} stalked the surface of the earth, attempting to enslave all that they could, and destroy those that they could not. Great demonic kingdoms rose and fell, engulfed in endless wars and battles as they vied for dominance. 
	
	The skies literally burned as the \imp{demons} worked their slaves to death in their mines and factories. Primitive humans, goblins, centaurs and giants slaved away together, whilst beneath the waves the water demons tormented the \imp{merpeople}. Whilst there were pockets of free people, resistances and rebellions, the \imp{demons} were able to hold control over the entire planet - those who lived outside of the demon's control were forced into a nomadic existence, hunting and gathering in a world on the brink of death.
	
	Some say that it was the work of a dying centaur king - others say it was an accident in some gruesome demonic experiment - but however it came to pass, it was during this period that the first humans were imbued with the spark of magic: the first witches and wizards were born. 
	
	
	With their newfound power, these witches and wizards were finally able to fight back effectively, wielding great primal magical forces. Through hundreds of years of warfare, working together, the sapient races were able to drive the demons back. In a climactic battle fought upon the corpses of millions upon millions of warriors, the greatest living mages banded together and were able to \key{banish} the \imp{demon kings} out of this \imp{Realm}, stranding them to wander the cosmos. 
	
	From this point, the demons were routed, and the sapient races joined forces to hunt them down, killing those that could die, and banishing those that could not. The only demonic forces left were pitiful shadows of their masters, too weak to cause harm, and too much hassle to exterminate completely. 
	
	The Sapient races congratulated themselves on their victory, and went their separate ways. The humans abandoned their nomadic ways, and began laying down the first cities, followed soon after by the goblins, though the Giants and the Centaurs preferred their nomadic lives, and set off to find forests and hills to live upon. 
	
	
	\section{The Giant Exodus}
	
	Of course, peace could never last long. Around 3000BC, a new trouble arose. 
	
	The giants, at this time, were already a fractured group, comprised of a number of clans: the mountain-dwelling \imp{Ganthans}, the forest-loving \imp{Basajaun}, the tech-focussed \imp{Cyclopes} and the icy \imp{Jotuns}. However, there was a fifth group - the \imp{Humbaba}. 
	
	Shunned by the rest of the \imp{Giants} because they had collaborated with the \imp{demons}, the \imp{Humbaba} had retreated beneath ground. There, in the bones of the earth, they had studied necromancy and discovered digusting fonts of necromantic energy which fed twisted abominations too evil to stand the light of day. For decades they hid amongst the maddening fumes, become ever more crazed and fuelled with anger and hatred. 
	
	Eventually, the king \key{Shamash-Bel} hatched a scheme to destroy the other giants, who they saw as having betrayed them. 
	
	Bursting from beneath the Earth, the \imp{Humbaba} took the other giants by surprise, and almost forced them into extinction - only the \imp{Ganthans} were safe in their mountainous forts. The other sapient races saw the plight of their former allies and once again joined forces to force the \imp{Humbaba} back underground. \imp{Shamash-Bel} was never defeated in battle - though he was never heard from again. 
	
	The damage was seemingly done, however, all the other clans - beside the \imp{Ganthans} -- were driven to near-extinction. To this day, their numbers remain extremely limited. The distinction between the \imp{Giants} were eventually lost to history - and the \imp{Ganthans} become known to wizardkind as `True Giants', whilst their once noble brothers and sisters were delegated to \imp{Giantkin} - mere footnotes in history, oddities and variations on the \imp{Giantish}-theme. 
	
	The \imp{Giantkin} retreated from the affairs of the sapient races, the \imp{Jotuns} to the far north and south, \imp{Basjaun} into the wild forests. There they hid and licked their wounds, as the \imp{Ganthans} built a society for themselves without them.
	
	\section{\imp{Y Twll Yn Byd}}
	
	Thousands of years later, around 300AD, a young wizard, \key{Myrddin}, was born to muggle parents in a small village in Wales. When his powers were discovered, he was sent to live amongst the \imp{Druids}, where he cultivated an immense affinity for the primal elements. 
	
	Renowned as one of the most powerful wizards of his age, \imp{Myrddin} was one of the first mages in Britain to use a magic wand (though his was, in fact, an oaken staff with a core of `pure lightning'). Such was his reputation as a mighty wizard that he was sent to represented the druids at the court of Knights and Kings, whom he served loyally for decades. 
	
	\imp{Myrddin} continued to improve his gifts, surpassing all other mages of his age. As his power grew, so did his hunger for more knowledge. From his laboratory sprang almost 500 of the spells used by modern wizards, as well as countless enchanted objects, potions and magical discoveries of every kind. 
	
	It was, however, never enough. 
	
	\imp{Myrddin} eventually became convinced that the very nature of reality was constraining him, and he saught to find a way to spread his wings beyond the palty concerns of life and death, time and space. 
	
	Within his laboratory, \imp{Myrddin} began to experiment with the nature of the cosmos. Ignorant of the past, and the horrors that saught to return to Earth, he pushed to far, and too fast. On April 28th 428 AD, a tiny rip in the fabric of space - a gap into the \imp{Voidic Continuum} - was produced in his lab. 
	
	From this tear came bounding forth the forces of hell. Demons thought long banished attempted to push back into the world, seeping through the cracks that \imp{Myrrdin} had torn across dimensions, seeking to reclaim their lost home, and destroy everything that the sapient races had built in the intervening millenia. 
	
	
	For decades - centuries - the wizards fought a secret war, fighting back every demonic incursion without letting the everyday folk see the chaos and destruction that loomed upon them. And yet, they could never again reach the \imp{Twll}, and so the rift remained open, and the demons just kep coming. \imp{Myrddin} himself led every charge, determined that his mistake would not doom humanity, and he became known as a mighty general, a warrior unmatched. 
	
	As the casualties mounted, the demons stepped up their attacks, toppling empires and murdering queens across the world. Gathering together the mightiest witches and wizards he could find, \imp{Myrrdin} led them into battle, cutting a swathe through the demonic hoards. This mighty group - the \key{First Wizengamot} - reached the \imp{Twll}, and closed it, ending the war. 
	
	The cost was great: of the 5,000 mages who walked into battle, only \imp{Myrrdin} emerged. He refused to speak of what had happened within his lab, and personally led the greatest \imp{Obliviation} campaign in history, wiping the minds of almost every living human of the events that had transpired. 
	
	\section{The Convergence}
	
	For the next 600 year, \imp{Myrddin} continued to work as a scholar and a philanthropist - his reputation as the greatest mage who had ever lived only continued to grow. 
	
	He was even offered to become the head of \imp{Slytherin House} when Hogwarts was founded in the 900s. Though he turned down the offer, he recommended \imp{Salazar Slytherin} for the role, and allowed them to use one of his old \imp{Wizards Towers} as the location for the new school, and was often known to provide impromptu seminars to the first few generations of students. 
	
	In the year 1054, however, a new star appeared in the sky - outshining all others. 
	
	\imp{Myrddin} - now going by the name \key{Merlin} - saw this as an ill omen, for he knew a secret that no-one else alive knew: the \imp{Twll Yn Byd} remained open. All those centuries ago, he had not been able to shut it, and had instead slaughtered his own people, using dark necromantic arts to channel their deaths into the most powerful act of magic witnessed since the banishing of the demons. Merlin had personally killed over 5000 of his own warriors - friends and family alike - bleeding them of their magical power. This new sign indicated that a \imp{Convergence} was to begin, and could potentially re-open the Twll, undoing everything he had sacrificed. 
		
	That very day, \imp{Merlin} vanished, and was never seen again.
	
	The location of his laboratory, and the \imp{Twll yn Byd} remain lost to his day. 
	
	
	
	\section{The Witch Hunts}
	
	\section{The Modern Day}
\end{document}
