
\newcommand\status[2]
{
\subsubsection{\it #1}

#2

}

\chapter{Statuses List}\label{S:StatusList}

%%StatusBegin\status{Asleep}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item An asleep being can take no actions\comma{} and is unaware of their surroundings.\item Passive Perception takes \minus{}5 penalty\item HP regenerates at 1d10 per hour\item After 8 hours all HP is regenerated\comma{} unless there is a serious injury.\item Can be awoken by loud noises\comma{} or on a successful (passive) perception check.\end{itemize}}

\status{Blinded}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A blinded being fails all checks that require sight.\item All accuracy checks by the afflicted are considered `blindfighting\apos{}\item All attacks on the being get check\minus{}advantage.\end{itemize}}

\status{Broken Bone}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item This is a {\it Serious Injury} (see below)\item The broken limb cannot be used\item Any time the broken bone is touched\comma{} requires a DV15 Spirit (Endurance) check to prevent howling in pain.\item If left to naturally heal\comma{} there is a 50\% chance it will set incorrectly\comma{} giving permanent check disadvantage until this is rectified.\end{itemize}}

\status{Burned: Mild}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A mild burn leaves one weak against future changes in temperature\item Fire and Cold damage are 50\% as effective.\end{itemize}}

\status{Burned: Severe}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A deep tissue burn is a {\it Serious Injury}\item A severely burned individual loses all feeling (except pure agony) in the entire afflicted limb\comma{} and cannot move it without causing excruciating pain.\item Take 2 HP damage per minute.\end{itemize}}

\status{Calm Mind}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item All checks receive a +1 bonus.\item This effect is terminated early if the target takes psychic damage\end{itemize}}

\status{Charmed}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A charmed being cannot attack or otherwise target their charmer with negative effects.\item Charmer has check\minus{}advantage on all checks relating to the target.\end{itemize}}

\status{Confused}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A confused target cannot speak coherently and cannot move.\item Confused entities are considered {\it Distracted}\item Take check\minus{}disadvantage on all rolls.\item Can attempt to snap out of confusion once per turn by repeforming the original Resist check.\end{itemize}}

\status{Critical (But Stable)}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item Take this status after being cured of the {\it Critical Condition} status\comma{} but still below 0HP.\item Character falls unconscious (see below)\comma{} and can take no action.\end{itemize}}

\status{Critical Condition}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A character takes this status after falling to 0HP\item Character falls unconscious (see below)\comma{} and can take no action.\item Lose 1 HP per combat cycle.\item At \minus{}10 HP\comma{} the being dies.\end{itemize}}

\status{Deaf}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A deafened being cannot hear\comma{} and so fails on all ability checks relating to sound.\item Perception attribute takes a 4 point penalty\item Can only communicate through vague gestures or written word\comma{} unless both parties know sign language.\end{itemize}}

\status{Distracted}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item The next attack on you is considered a {\it Critical Strike}.\item When taking damage\comma{} you must succeed a DV10 Spirit (Willpower) check\comma{} or halt all actions this turn.\end{itemize}}

\status{Encumbered}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item Being is overloaded by too many heavy objects\item All movement speeds reduced to 25\% of their normal value\comma{} and Dodge stat reduced to half its normal value.\item Gain one exhaustion level for every kilometre moved whilst encumbered.\end{itemize}}

\status{Enraged}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item Become mindlessly furious\comma{} and perceive all beings as hostile to you.\item All actions must be spent performing attacks on the nearest living (or unliving) being to you\comma{} or moving into a position where you can attack them.\item The GM reserves the right to take control of your character for the duration of the effect\end{itemize}}

\status{Exhaustion}{Exhaustion is a measure of how tired a being is\comma{} and comes in multiple degrees of severity. A being gains levels in Exhaustion through magical means\comma{} or through failing to look after themselves\comma{} as per page \pageref{S:Survival}. They may lose levels through healing\comma{} or by finding a place to rest and recover. 

\begin{tabular}{l l}
\bf Level  &  \bf Effect
\\
0: Fine    & No effect
\\
1: Distracted   & Disadvantage on Finesse and Perception checks
\\
2: Tired:  & Disadvantage on all ability and accuracy checks
\\
3:  Lethargic:  & Speed halved
\\
4: Drained:  & HP and FP maximum halved
\\
5: Catatonic:  & Speed set to 0
\\
6: Dead   & Character Death
\end{tabular}

These effects are compounding\comma{} so a Lethargic character has disadvantage on checks\comma{} as well as having their speed halved.}

\status{Frostbite: Mild}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A creature with mild frostbite finds that their natural regeneration abilities are halted.\item Finesse attribute takes a 4 point penalty\comma{} as your fingers get clumsy and lose feeling.\end{itemize}}

\status{Frostbite: Severe}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A severe case of frostbite is a {\it Serious Injury}\item Lose FP at a rate of 2 per minute. When FP is zero\comma{} lose HP at the same rate.\end{itemize}}

\status{Hypoxia}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A being becomes hypoxic if oxygen cannot reach the brain.\item Intelligence attribute takes a 4 point penalty.\item FP is set to zero.\item If not cured within 2 minutes\comma{} the being dies.\end{itemize}}

\status{Incapacitated}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item An incapacitated being can take no actions.\item All Athletics and Finesse resist checks fail.\end{itemize}}

\status{Invisible}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item An invisible creature cannot be detected through sight. For the purposes of Stealth\comma{} the creature is considered {\it Severely Obscured}.\item In adverse conditions (i.e. rain and snow)\comma{} can still be visually detected. Does not stop noise.\item Attacks on the creature must be considered {\it Blindfighting}\end{itemize}}

\status{Paralyzed}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A paralyzed creature is totally incapacitated\comma{} but is aware of their surroundings.\item For the purposes of accuracy\comma{} they are considered inanimate objects.\end{itemize}}

\status{Poisoned: Mild}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A mild poison causes you to vomit if you overexert yourself: beings cannot take full\minus{}turn movements without passing a DV15 Vitality check.\item Athletics attribute takes a 4 point penalty.\item Accuracy checks take check disadvantage\end{itemize}}

\status{Poisoned: Severe}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A badly poisoned being is suffering from a {\it Serious injury}\comma{} and will surely perish soon.\item Being experiences visual and auditory hallucinations\item Lose HP at a rate of 3 HP per minute.\item Athletics attribute takes an 8 point penalty (min 0).\item Accuracy checks take check disadvantage\end{itemize}}

\status{Prone Position}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A prone creature can only move via crawling\comma{} at half speed.\item Take disadvantage on all accuracy checks\item All close\minus{}range attacks on the prone creature are considered Critical Strikes.\item Condition can be ended by taking a major action to stand up.\end{itemize}}

\status{Serious Injury}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A serious injury is one which cannot be expected to heal naturally\comma{} without major medical intervention.\item All HP regeneration is capped at 50\% the maximum health\comma{} until the injury is healed.\end{itemize}}

\status{Silenced}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A silenced being cannot speak.\item Can only communicate through vague gestures or written word\comma{} unless both parties know sign language.\item Spellcasting is forbidden\comma{} unless they have he {\it Silent Casting} ability.\end{itemize}}

\status{Terrified}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item A terrified creature has check\minus{}disadvantage whilst they can see the source of their fear.\item Cannot willingly move closer to the source of their fear.\end{itemize}}

\status{Trapped}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item You are fixed in one place\comma{} and cannot move.\item Your speed is set to zero.\item Must use the {\it Block} instinct. Dodge value is set to zero.\end{itemize}}

\status{Unconscious}{\begin{itemize} \renewcommand\labelitemi{\minus{}}\item An unconscious creature is totally incapacitated\comma{} and can take no actions. They are totally unaware of their surroundings.\item For the purposes of accuracy\comma{} they are considered inanimate objects.\item The creature drops whatever they were holding and takes the prone position.\item All resist checks fail.\item All attacks on the being are considered Critical Strikes.\end{itemize}}

%%StatusEnd