\status{Asleep}{Whether by choice\comma{} or by magical influence\comma{} a being is generally completely helpless whilst asleep\comma{} and unable to take any form of action. 

If imposed by an external source on an unwilling target\comma{} the victim remains asleep for approximately 5 minutes for every \imp{power} used to subdue them.}{\item No actions or movement can be taken\item After 7 hours\comma{} a \imp{Long Rest} has been completed.\item Status is terminated upon taking \imp{harm}\comma{} or if a suitable stimulus is present.}

\status{Blinded}{Physical trauma to the eyeballs\comma{} as well as overloading them with a bright light leads to the optic centres shutting down. 

Status typically lasts for one round per \imp{Power} used\comma{} though in exceptional circumstances\comma{} may be permanent.}{\item All \imp{Attack} checks by the afflicted are considered \imp{Fighting Blind}\item \imp{Resist} checks are performed at a 2d penalty\item Most checks which rely on vision (i.e. \imp{perception} and \imp{insight} etc.) will automatically fail.}

\status{Burned}{Prolonged contact with a heat source can leave one with severe tissue damage\comma{} and leaves the victim particularly susceptible to changes in temperature.}{\item Target is considered \imp{Susceptible} to \imp{Fire} and \imp{Cold} damage.}

\status{Charmed}{Almost always imposed by magical or hypnotic means\comma{} the \imp{charmed} status means that the target percieves their charmer as their dearest\comma{} friend\comma{} and an ally to be protected at all costs.}{\item A charmed being cannot attack or otherwise target their charmer with negative effects.\item Charmer gains +3d on all \imp{social} checks made against the charmed being}

\status{Confused}{A confused target cannot speak coherently and cannot move.}{\item Confused entities are considered {\it Distracted}\item Take check\minus{}disadvantage on all rolls.\item Can attempt to snap out of confusion once per turn by repeforming the original Resist check.}

\status{Critical (But Stable)}{Take this status after being cured of the {\it Critical Condition} status\comma{} but still below 0HP.}{\item Character falls unconscious (see below)\comma{} and can take no action.}

\status{Critical Condition}{A character takes this status after falling to 0HP}{\item Character falls unconscious (see below)\comma{} and can take no action.\item Lose 1 HP per combat cycle.\item At \minus{}10 HP\comma{} the being dies.}

\status{Deaf}{A deafened being cannot hear\comma{} and so fails on all ability checks relating to sound.}{\item Perception attribute takes a 4 point penalty\item Can only communicate through vague gestures or written word\comma{} unless both parties know sign language.}

\status{Distracted}{The next attack on you is considered a {\it Critical Strike}.}{\item When taking damage\comma{} you must succeed a DV10 Spirit (Willpower) check\comma{} or halt all actions this turn.}

\status{Encumbered}{Being is overloaded by too many heavy objects}{\item All movement speeds reduced to 25\% of their normal value\comma{} and Dodge stat reduced to half its normal value.\item Gain one exhaustion level for every kilometre moved whilst encumbered.}

\status{Enraged}{Become mindlessly furious\comma{} and perceive all beings as hostile to you.}{\item All actions must be spent performing attacks on the nearest living (or unliving) being to you\comma{} or moving into a position where you can attack them.\item The GM reserves the right to take control of your character for the duration of the effect}

\status{Exhaustion}{Exhaustion is a measure of how tired a being is\comma{} and comes in multiple degrees of severity. A being gains levels in Exhaustion through magical means\comma{} or through failing to look after themselves\comma{} as per page \pageref{S:Survival}. They may lose levels through healing\comma{} or by finding a place to rest and recover. 

\begin{tabular}{l l}
\bf Level  &  \bf Effect
\\
0: Fine    & No effect
\\
1: Distracted   & Disadvantage on Finesse and Perception checks
\\
2: Tired:  & Disadvantage on all ability and accuracy checks
\\
3:  Lethargic:  & Speed halved
\\
4: Drained:  & HP and FP maximum halved
\\
5: Catatonic:  & Speed set to 0
\\
6: Dead   & Character Death
\end{tabular}

These effects are compounding\comma{} so a Lethargic character has disadvantage on checks\comma{} as well as having their speed halved.}{}

\status{Frostbite: Mild}{A creature with mild frostbite finds that their natural regeneration abilities are halted.}{\item Finesse attribute takes a 4 point penalty\comma{} as your fingers get clumsy and lose feeling.}

\status{Frostbite: Severe}{A severe case of frostbite is a {\it Serious Injury}}{\item Lose FP at a rate of 2 per minute. When FP is zero\comma{} lose HP at the same rate.}

\status{Hypoxia}{A being becomes hypoxic if oxygen cannot reach the brain.}{\item Intelligence attribute takes a 4 point penalty.\item FP is set to zero.\item If not cured within 2 minutes\comma{} the being dies.}

\status{Incapacitated}{An incapacitated being can take no actions.}{\item All Athletics and Finesse resist checks fail.}

\status{Invisible}{An invisible creature cannot be detected through sight. For the purposes of Stealth\comma{} the creature is considered {\it Severely Obscured}.}{\item In adverse conditions (i.e. rain and snow)\comma{} can still be visually detected. Does not stop noise.\item Attacks on the creature must be considered {\it Blindfighting}}

\status{Paralyzed}{A paralyzed creature is totally incapacitated\comma{} but is aware of their surroundings.}{\item For the purposes of accuracy\comma{} they are considered inanimate objects.}

\status{Poisoned: Mild}{A mild poison causes you to vomit if you overexert yourself: beings cannot take full\minus{}turn movements without passing a DV15 Vitality check.}{\item Athletics attribute takes a 4 point penalty.\item Accuracy checks take check disadvantage}

\status{Poisoned: Severe}{A badly poisoned being is suffering from a {\it Serious injury}\comma{} and will surely perish soon.}{\item Being experiences visual and auditory hallucinations\item Lose HP at a rate of 3 HP per minute.\item Athletics attribute takes an 8 point penalty (min 0).\item Accuracy checks take check disadvantage}

\status{Prone Position}{A prone creature can only move via crawling\comma{} at half speed.}{\item Take disadvantage on all accuracy checks\item All close\minus{}range attacks on the prone creature are considered Critical Strikes.\item Condition can be ended by taking a major action to stand up.}

\status{Serious Injury}{A serious injury is one which cannot be expected to heal naturally\comma{} without major medical intervention.}{\item All HP regeneration is capped at 50\% the maximum health\comma{} until the injury is healed.}

\status{Silenced}{A silenced being cannot speak.}{\item Can only communicate through vague gestures or written word\comma{} unless both parties know sign language.\item Spellcasting is forbidden\comma{} unless they have he {\it Silent Casting} ability.}

\status{Terrified}{A terrified creature has check\minus{}disadvantage whilst they can see the source of their fear.}{\item Cannot willingly move closer to the source of their fear.}

\status{Trapped}{You are fixed in one place\comma{} and cannot move.}{\item Your speed is set to zero.\item Must use the {\it Block} instinct. Dodge value is set to zero.}

\status{Unconscious}{An unconscious creature is totally incapacitated\comma{} and can take no actions. They are totally unaware of their surroundings.}{\item For the purposes of accuracy\comma{} they are considered inanimate objects.\item The creature drops whatever they were holding and takes the prone position.\item All resist checks fail.\item All attacks on the being are considered Critical Strikes.}

