\documentclass[oneside]{book}
\usepackage{fontspec}
\usepackage{array}
\usepackage{subfiles}

\usepackage{tikz}
\usepackage{longtable}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{tcolorbox}
\usepackage[left = 1in, right = 1 in, top = 0.7in, bottom = 0.26in]{geometry}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{array}
\def\apos{'}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}

\newfontfamily{\HP}{[ParryHotter.TTF]}
\renewcommand{\arraystretch}{0.15}
\setlength{\tabcolsep}{4pt}
\titleformat{\chapter} {\vspace{-10ex}\normalfont\bfseries\HP\Huge}{}{0pt}{}[\vspace{-2ex}]

\titleformat{\section}{\vspace{-3ex}\normalfont\Large\it\centering}{}{0em}{\titlerule[0.3pt] \\}[{\titlerule[0.3pt]}]

\titleformat{\subsection}{\vspace{-2ex}\normalfont\bf \Large}{}{0em}{}[{}]
\begin{document}
\title{{\HP The Story So Far}}

\maketitle

\section{Chapter One: The Introduction}


In our first outing, our four characters arrived at Hogwarts School of Witchcraft \& Wizardry, were sorted into their houses, and found themselves in a group together, whereupon they made introductions. We therefore met:
\begin{itemize}
	\item Helena (Ravenclaw), played by Laura
	\item Nikc (Gryffindor), played by Adam
	\item Cerise (Slytherin), played by Chloe
	\item Luke (Hufflepuff, the Half-Giant), played by Liam
\end{itemize}
After a quick DADA lesson, in which Luke (unsuccessfully) attempted to hulk-smash a small goblinoid, our protagonists were summoned to a special meeting. 

\section{Chapter Two: Preparing For the Hunt}

In this meeting, the four students, along with the rest of the first years were informed of a new educational challenge the school are trialling: the Hogwarts Hunt. Professor Bogoliubov, the Russian DADA teacher explained the rules:

The first to track down a pair of magical gloves gets to keep them! With the teachers standing in front of a birdcage perched on a large rock formation, they were informed that the gloves would be released on Thursday morning, and that upon being released, there would be 6 tasks around the castle, which would give them clues as to the location of the gloves.

Between then and now, they have the entire castle's resources to use to prepare themselves for this challenge. 

Our heroes decided to spend their first afternoon learning some new spells, and then headed back to the DADA classroom, and discovered that the birdcage contained a Diricawl (a teleporting dodo), and decided to head down to Hagrid's hut, to learn about the diricawl and other magical creatures. 

Unfortunately, Hagrid didn't have much to say, though Cerise managed to sneak a peek at some maps on Hagrid's walls, which seemed to depict a number of locations across Eastern Europe and beyond. 

The group continued to work hard, learning more and more useful knowledge -- including checking every copy of Care of Magical creatures books out of the library. They also decided to lock everyone else out of a session in the divination classroom, using the age old tactic of `putting up a sign'. 

Later, whilst scouting the potions classroom for useful information and ingredients Nikc took the opportunity to swap a bunch of labels around on the meticulously catalogued ingredients, before the group snuck into the old Potions Master's office, and discovered it to be abandoned.

Despite the harmless intent, Nikc's shenanigans soon had some rather dire consequences for the other students who turned up to learn some potions. Attempts to brew a simple antidote to common poisons resulted in a virulent poison being created, and those unfortunate enough to test their creations (approximately 20 students) found themselves in the hospital wing for the next few days, in rather exquisite agony. 

\section{Chapter Three: The Hogwarts Hunt}


Having cut the level of competition quite significantly, the group woke up the next morning feeling confident in their ability to win the task, and take the gloves for themselves. 

After an executive decision from Luke, the group decided to start at the top of the castle, and work their way down, taking on a dastardly riddle in the divination class room and utilising their healing and warding spells to save helpless soul from attack in the Recuperation classroom - gaining new clues each time they succeeded. 

Perhaps their greatest challenge was presented by the DADA department who provided them with...an empty room, lined with levers and with a door at one end. Nikc couldn't help himself, and pulled one lever after another, repeatedly summoning new creatures for the group to fight - until Cerise and Helena simply walked up to the door and realised it was never locked.

Even outside of the tasks, the group faced difficulty as they discovered a bunch of beasts were roaming free. Luckily, the maps that Cerise had spotted had allowed them to learn informaiton about these relatively obscure beasts, which mostly hailed from Russia and the Ural mountains. After dealing with these additiona challenges, task after task was completed, until the group had a full set of clues:

\begin{itemize}
	\item SOLOVEI IS IN THE FOREST
	\item GLOVES ARE WITH `Z'
	\item ALL `X's ARE `Y'
	\item BOGLIUBOV IS `Y'
	\item HAGRID IS IN CHARGE OF `X's
	\item `Z' IS AN `X' `Y'
\end{itemize}

They deduced that the Gloves were with a being named `Solovei', which resided in the Forbidden Forest. Utilising their hoard of stolen books, they read up on Solovei and learned that this diminutive pixie has a fearsome reputation. Prepared for battle, the group headed out into the forest. 

After a tense and nerve-wracking walk through the forest, stalked by a being they couldn't quite see, the group successfully managed to engage Solovei in combat, and defeated him in a magical duel. Cerise took the magical brown gloves he had on his person, and slipped them on in triumph. 

Only then, did the group begin to understand their error, as the gloves tightened and tightened around Cerise's wrists, until they could no longer be removed. As she panicked at this intrusion, Cerise also discovered that whenever she attempted an action, the gloves opposed her, jerking from one side to the next erratically, causing her to fail at even simple tasks. 

The group had been decieved, ironically, by the truth. When solving the riddle in their first challenge, they had failed to notice the riddle-behind-the-riddle, and had gained a clue which, though perfectly true (Solovei was indeed in the forest), was not helpful to their cause. 

With Cerise impaired by her curs\'ed gloves, the group trudged back to the castle despondent, and recovered the `true' clue from the divination classroom: `Z' IS IN PLAIN SIGHT. Still none the wiser, the group trudged back to the DADA classroom, and flipped through their books on Russian creatures, hoping for inspiration. 

Just as Nikc read aloud the chapter on {\it Pogrebins}, a species of demon which look like giant boulders whilst asleep, Cerise and Helena experienced a moment of revelation - they knew exactly where a rock demon would hide in plain sight: the gigantic boulder that the Diricawl had been stood upon at the beginning of the task, and which was now only a mere few metres from them now.  

After gingerly approaching the rock, they successfully managed to awake the grouchy Pogrebin, and convinced it to return to sleep without a fight. As the Pogrebin awoke, the group spotted (and recovered) the package he had been guarding: the Gloves!

As Cerise touched the {\it real} gloves, her cursed pair crumbled away into dust - leaving them with their prize. 

Bogoliubov emerged from a side room, and congratulated them on their victory, even if they had fallen for her sneaky little trick in the forest. She welcomed them to keep the gloves, which Luke - enamoured with the stories of the warrior-wizard who had previously owned them - eagerly took her up on, slipping them effortlessly onto his giant hands. 

The group took a moment to appreciate their achievement, and to bask in the glory of a job well done....ish. 

\section{Chapter Four: Under the Tree}

Life continued as normal at Hogwarts for the next few months - lessons came and went, and they expanded their knowledge of the magical world, though practical application of magic was somewhat thin on the ground. Well, until the day that the Fearsome Four, and their class, were led down to a small antechamber off the main hall, and introduced to the concept of {\it wizard's duels}. 

The four of them took to this new skill like a duck to water, and worked together in unison so well that, despite their limited use of magic, they easily overpowered the student demonstrators present. Even when Derek Hofstadtler, a visiting auror offered to show them how a {\it real} warrior fights, he made the critical error of underestimating the group and they managed to surprise him until he was - somehow - defeated. 

This victory was enough to fill the group with a sense of invulnerability so great that, when they later saw Derek looking dishevelled and beaten, discussing `the problem', they decided to go take a look for themselves. 

It didn't take long for the group to dicern that the problem (and potentially the source of Derek's bet-up appearance) was the Whomping Willow, the living tree found near the edge of the grounds. It seemed as though a deek sickness had set into the earth around the tree: the grass had turned yellow and sickly, and the Willow seemed sluggish, and perhaps even in pain. 

Taking advantage of the sluggish movements of the tree, the four students slipped in to the trunk, and discovered a burrow of some kind, deep in the root system. After deliberating, they lowered themselves into the dark. 

Illuminating their wands, they found themselves in a large den, and could hear a snuffling noise coming from a tunnel off to one side - presumably the denizen of this space. Of more concern was the large tunnel leading off in the opposite direction, which the group immediately began to explore. Down and down, round and round - the tunnel descended and spiralled for what felt like miles. Attempts to orient themselves failed, and they had no idea where they were, or truly how far the four of them had travelled. 

As the tunnel marched on, its composition changed. What was previously tunneled earth and tree roots become gradually more regimented - the corners began to square off, the earthen floor and walls became uniform and packed as the tunnel became wide enough to drive two cars down, side by side. Eventually the packed earth morphed into a stone corridor. At the end of the corridor, a great expanse yawned - pitch black and impenetrable. 

As the group peered across the threshold into this great cavern - a man-made hall, perhaps? -- their magical illumination was immediately extinguished, leaving them in the dark. From deep within the chamber, a mechanical whirring, thumbing, throbbing sound began to grow louder, and a series of pale blue lights began to dance, impercetible and faint, in the far distance. 

Eventually, a natural source of light - some fire - was established, and the group recoiled in terror. 

Out of the flickering torchlight, a truly gigantic semi-humanoid face appeared, peering towards them out of the darkness. Evidently artificial, the face was carved from stone and metal, cogs and rotating gears could be seen behind its terrifying viasge. If this face were attached to a body, it was so enormous that it was hidden by the encompassing darkness - which would imply that the being was 20, maybe 30 feet tall. It's emotionless face peered ever closed, looming out of the darkness at the four 1st year students. 

They did the only thing they could: they ran. 

As they turned tail and fled down the corridor, a blinding white {\it flash} seemed to emanate from every surface, temporarily blinding everyone. As they turned to look back down the corridor, they discovered that the opening to the cavern had been replaced by a perfect copper wall, which resisted all further investigation. No other sign of their terrifying experience remained. 

Still quaking in their boots, the group fled mindless and paying no heed to their surroundings, until they reached the safety of Hogwarts Library, where they tried to learn all they could about constructs and hidden chambers. 

After an hour of fruitless search, something began to bug the students - or rather, the {\it lack} of something. The silence which pervaded the castle. Casting their minds back, the group realised they hadn't seen a single person since they entered the cavern. The four immediately leaped back into action, and scoured the castle, looking for signs of life - but none came. 

Even Norman - Cerise's feline familiar - was nowhere to be found, though the presence of the comforting link between master and familiar assured her that Norman was still alive. 

The talking portraits were the only semi-sentient beings to be found, and informed the investigating group that several hours ago (approximately when the group was below ground), an almighty hubbub came, and the entire student body, as well as the staff, filed out of the main hall, and out through the main exit of the school. 

The trail of rubbish and debris led the group all the way to Hogsmeade station, where the Hogwarts Express stood, engines fired up - but empty. Closer inspection appeared to indicate that the trail of debris stopped a few dozen metres {\it before} the train station. 

As the group explored the train, Luke couldn't help do the one thing he'd always wanted to do - and entered the main cabin, and tugged on the whistle. 

As the train `choo choo'd happily, a sudden magical pressure seemed to press at all four students' eyes, and the world faded into darkness and confusion. 

\section{Chapter Five: London Under Fire}

As the confusion abated, and the cobwebs slowly 

\end{document}
