\documentclass[a5paper,twocolumn, 10pt]{article}
\usepackage{../HPpack}

\usepackage{titling}
\newgeometry{left = 0.5cm, right = 0.5cm, top = 0.3cm,bottom = 0.1cm}
\title{A}
\author{ }
\date{\vspace{-2.5 cm}}
\def\s{0.3}
\def\w{2.1}





\newcommand\spellBook[3]
{
\cleartorightpage
\title{\vspace{-5 ex} {\Large  \bf #1} \\ \small A book containing #2 spells}
\maketitle
#3

}

\begin{document}
%%SpellbookBegin

 \spellBook{a}{Trivial \& Beginner-level Elemental}{
\spell{
	name = Compel Flames, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Close, incant = ignisempus, noDur = 1, higher = When cast at a higher level\comma{} the maximum area of fire that you can affect doubles \forEvery{}\comma{} and the damage caused by the flame increases by 1d6. You may also perform more extravagant feats of fire manipulation\comma{} at the whim of your GM. Be inventive!,noResist =1, negation = Blockable  and Dodgeable,effect =Upon targeting an area of flame up to 1 metre squared that you can see within range\comma{} you can manipulate the fire in a number of ways:

\begin{spellitemize}
\item You can move the fire up to 3 metres in any direction\comma{} either by igniting new fuel\comma{} or as a magically floating floating ball of fire. 
\item You can diminish the ignited area by half (but can never extinguish it)\comma{} or multiply it by two (note that if it exceeds your maximum controllable area you do not control that bit of the blaze)
\item You can change the colour of the flame
\item You can cause the flame to take on simple shapes and animate them at your direction. 
\item You can render yourself immune to this bit of fire (applies only to non\minus{}magical fire\comma{} or fire you created yourself)
\item Lash out at a target within melee range of the fire\comma{} dealing 1d6 fire damage\comma{} using an Elemental Accuracy check. 
\end{spellitemize}

You may use any of these effects as long as concentration is maintained. When focus is broken\comma{} the fire resumes its normal course.
}
\spell{
	name = Contact Shock, school = Charms, discipline = Elemental, type = Instant, level =Trivial, range =Wandtip, incant = electrum, noDur = 1, higher = \additional{1d6}{Electric},noResist =1, noBlock = 1, effect =Charge the tip of your wand with electrical energy. This energy is discharged when your wand\minus{}tip next touches a surface. Does 2 electrical damage on contact\comma{} and also fries any electrical equipment it comes into contact with.
}
\spell{
	name = Direct Fluids, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Close, incant = aguasempus, noDur = 1, higher = When cast at a higher level\comma{} the maximum volume of water that you can effect doubles \forEvery{}. You may also perform more extravagant feats of water manipulation\comma{} at the whim of your GM. Be inventive!,resist = Strength, noBlock = 1, effect =Upon targeting a volume of water (or similar fluids with a water\minus{}like consistency) up to one metre cube that you can see within range\comma{} you can manipulate it in a number of ways:

\begin{spellitemize}
\item You can move the water\comma{} or otherwise alter the flow by up to 3 metres
\item You can cause the water to form simple shapes\comma{} and animate them at your direction. 
\item You can clear the water\comma{} or cause it to become opaque and cloudy. This lasts for up to one hour after you break concentration.
\item Drown: if your animated water is within melee range of a being\comma{} you may use a major action to wrap it around their face\comma{} depriving them of air on a failed Resist. Target can re\minus{}perform this check at the end of every turn. 
\item Still the water\comma{} or generate waves and ripples across the surface
\end{spellitemize}
}
\spell{
	name = Earthrumble, school = Charms, discipline = Elemental, type = Instant, level =Beginner, range =Close, incant = crith, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =A mild tremor shakes the ground. All beings in a 10m radius must succeed a Resist check\comma{} or become {\it Distracted} in the next turn cycle.
}
\spell{
	name = Glowing Wand, school = Charms, discipline = Elemental, type = Focus, level =Trivial, range =Close, incant = lumos, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Causes the tip of your wand to glow\comma{} like a torch. Casts bright light in a 2m radius\comma{} and dim light for another 10m. This spell last indefinitely\comma{} until Focus is broken\comma{} and does not require drain FP after the initial effect is activated.
}
\spell{
	name = Howling Winds, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Close, incant = vente, noDur = 1, higher = When cast at a higher level\comma{} you can perform more extravagant feats of wind manipulation. The penalty to ranged accuracy checks increases by 1 \forEvery{}.

As an adept\minus{}level spell\comma{} each turn you may choose one being being within the region affected by your gust\comma{} and cause them to take disadvantage on any accuracy checks they make this turn.,noResist =1, noBlock = 1, effect =Energise the winds\comma{} and manipulate the air within a radius of 5m around you. This breeze is strong  enough to subtly alter the path of projectiles passing through the region (all ranged weapon attacks take a 1 point penalty to accuracy)\comma{} or to cause a commotion by slamming doors and howling through open windows.
}
\spell{
	name = Pebbledash, school = Charms, discipline = Elemental, type = Instant, level =Beginner, range =Close, incant = mologan, noDur = 1, higher = This spell gains an additional 1d4 bludgeoning damage for every additional spell level dedicated to it.,noResist =1, negation = Blockable  and Dodgeable,effect =Imbue the earth with purpose: a nearby patch of loose earth and pebbles launches itself at a target in range\comma{} dealing 2d4 bludgeoning damage.
}
\spell{
	name = Produce Fire, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Wandtip, incant = incendio, noDur = 1, higher = Casting this spell at a higher level summons a larger and hotter gout of flame.

For every additional casting\minus{}level\comma{} the gout reaches an extra 15cm from your wandtip\comma{} and does 1d6 additional heat damage. The extra heat also allows you to ignite tougher materials\comma{} such as damp wood.,noResist =1, negation = Blockable  and Dodgeable,effect =A small jet of fire is emitted from the tip of your wand\comma{} akin to a large lighter. 
Coming into contact with fire does 1d6 fire damage\comma{} and applies the {\it Burned: Minor} status effect.
}
\spell{
	name = Produce Water, school = Charms, discipline = Elemental, type = Focus, level =Beginner, range =Wandtip, incant = aguamente, noDur = 1, higher = Casting this spell at a higher level summons a more powerful torrent of water. 

For each additional casting level\comma{} the jet of water doubles in intensity \minus{} reaching an extra 30cm and doing 1d8 bludgeoning damage.,noResist =1, negation = Blockable  and Dodgeable,effect =A jet of water is emitted from the tip of your wand\comma{} in a fountain approximately 30cm in length\comma{} useful for extinguishing fires small\comma{} or cleaning surfaces.

Note\comma{} however\comma{} that Gamp\apos{}s Laws of Elemental Transfiguration states that all conjured water evaporates upon drinking: it cannot be used for sustenance.
}
\spell{
	name = Refreshing Breeze, school = Charms, discipline = Elemental, type = Instant, level =Trivial, range =Close, incant = klinneract, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =A gust of air refreshes the air in a sphere of radius 3 metres around the caster\comma{} removing any gaseous effects and smelling faintly of lavender.
}
}
 \spellBook{b}{Trivial \& Beginner-level Kinesis}{
\spell{
	name = Discarnate Digits, school = Charms, discipline = Kinesis, type = Instant, level =Beginner, range =Close, incant = titillatio, duration = 5 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =The caster produces an ethereal pair of hands that lasts for the duration of the spell\comma{} or until they move more than 10m away from the caster. You can use a minor action to control the hands. You can use the hand to manipulate an object\comma{} open an unlocked door or container\comma{} stow or retrieve an item from an open container\comma{} or pour the contents out of a vial\comma{} but cannot use them to attack or carry items heavier than {\it Light}. Hands may be moved at a speed of 10m per turn\comma{} in addition to their action.
}
\spell{
	name = Fusion, school = Charms, discipline = Kinesis, type = Instant, level =Beginner, range =Sight, incant = obharesco, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Stick two objects together\comma{} as if you had fused them together at a molecular level. To break them apart requires either slicing the objects apart\comma{} or pulling them hard enough to break one (or both) of the objects.
}
\spell{
	name = Halt, school = Charms, discipline = Kinesis, type = Instant, level =Beginner, range =Close, incant = stabit, noDur = 1, noHigh = 1, resist = Speed, noBlock = 1, effect =Stop an object or being in their tracks. An inanimate object clatters to the floor and lies still. 

If used on a living being\comma{} you may choose one of the following effects\comma{} which apply only on a failed resist:
\begin{spellitemize}
\item Target moves half their movement speed this turn\comma{} before being halted 
\item Choose one accuracy check they make this turn cycle and cause it to fail {\it before} the check is made. 
\end{spellitemize}
}
\spell{
	name = Housemage\apos{}s Delight, school = Charms, discipline = Kinesis, type = Instant, level =Trivial, range =Close, incant = savatch, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Emit a cone of energy from your wand 2m in length. 

Any being within this cone finds their clothes have been cleaned and dried\comma{} leaving them comfortably warm and smelling faintly of lavender. Dirty surfaces\comma{} or those defaced with writing and graffiti are wiped clean and left sparkling and immaculate.
}
\spell{
	name = Levitation, school = Charms, discipline = Kinesis, type = Focus, level =Beginner, range =Sight, incant = wingardium leviosa, noDur = 1, higher = The maximum mass this spell is capable of lifting multiplies by ten for every additional spell level used to cast it.,resist = Strength, noBlock = 1, effect =Cause an object of 1kg or less to levitate whilst concentration is maintained. You may control the height of the object\comma{} but you may not move it horizontally. A being may attempt to grab hold of the levitating object\comma{} and whilst they can move it horizontally\comma{} they may only change its height by performing a Resist check\comma{} breaking the enchantment on a success.
}
\spell{
	name = Magical Marker, school = Charms, discipline = Kinesis, type = Focus, level =Trivial, range =Wandtip, incant = stylum, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Use your wand as anything from a thin marker to a thick paintbrush. The tip of the {\it brush} can be up to 0.5m away from the tip of your wand\comma{} but follows the motion of your wand exactly. The {\it paint} is a magical adhesive that sticks to any surface\comma{} and may be of any colour you choose.
}
\spell{
	name = Spectral Knife, school = Charms, discipline = Kinesis, type = Instant, level =Beginner, range =Close, incant = diffindo, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =Cut into any solid object\comma{} as if you had wielded a sharp\comma{} adamantium knife with a blade of up to 10cm in length.
If used on a living being\comma{} it is as if you wielded an exceptionally sharp knife\comma{} dealing 2d4 slashing damage.
}
}
 \spellBook{c}{Trivial \& Beginner-level Telepathy}{
\spell{
	name = Aid Ally, school = Divination, discipline = Telepathy, type = Instant, level =Beginner, range =Wandtip, incant = auxilio, noDur = 1, higher = Gain an additional 1d4 bonus for every {\bf two} additional casting levels dedicated to this spell.,noResist =1, noBlock = 1, effect =By laying your hand upon a sapient being\comma{} you may channel magical energy into them. On the next check the target performs\comma{} roll 1d4\comma{} and add it to the check.
}
\spell{
	name = Comprehend Languages, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Beginner, range =Self, noIncant = 1, duration = 10 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =By performing a complex ritual involving many strips of paper and arcane runes\comma{} you gain the ability to comprehend any verbal\comma{} written or somatic language\comma{} by siphoning off the telepathic residue left behind by the orignal communicator. 

This ability only works if the communication was performed by someone who understood what they were writing. If writing was merely copied down from another source\comma{} or were the speech merely learned by rote\comma{} there is no telepathic residue for you to interpret\comma{} and so the spell fails.
}
\spell{
	name = Detect Magic, school = Divination, discipline = Telepathy, type = Instant, level =Beginner, range =Close, incant = revelio, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Reveals to the caster any active spells or magical effects within a radius of 5 metres. You see an aura around any object or creature currently imbued with magical effects\comma{} with different colours corresponding to different disciplines of magic. 

Will deactivate charms whose sole purpose is to remain hidden. 

This spell can detect magical barriers\comma{} but cannot see beyond them.
}
\spell{
	name = Eavesdrop, school = Divination, discipline = Telepathy, type = Focus, level =Trivial, range =Close, incant = dumauris, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You fortify your own hearing to such an extent that you can listen in on conversations up to 20 meters away with perfect clarity.
}
\spell{
	name = Engender Anxiety, school = Divination, discipline = Telepathy, type = Instant, level =Beginner, range =Close, incant = falciparum, noDur = 1, higher = This spell does 1d10 damage when cast as a Novice spell\comma{} and subsequently increases by 1d10 \forEvery{},resist = Logic, noBlock = 1, effect =You allow yourself to be caught rifling through the target\apos{}s most embaressing and anxiety\minus{}inducing memories\comma{} and perhaps say something aloud to indicate your awareness. 

The mental stress causes the target to take 1d6 psychic damage (halved on a successful resist).
}
\spell{
	name = Eyes of the Beast, school = Divination, discipline = Telepathy, type = Focus, level =Beginner, range =Sight, incant = oculi bestia, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =You may enter into the mind of a beast\comma{} if it fails to Resist (a friendly beast does not resist this spell). For the duration of the spell you may see\comma{} hear and otherwise sense exactly what the animal does.
}
\spell{
	name = Night Vision, school = Divination, discipline = Telepathy, type = Instant, level =Beginner, range =Wandtip, incant = aspectu, duration = 2 hours,noHigh = 1, noResist =1, noBlock = 1, effect =As you touch your wand to the target\apos{}s head\comma{} their eyes flash an unearthly green. Give the target nightvision for the duration: dim light is as bright as daylight\comma{} and darkness is considered dim.
}
}
 \spellBook{d}{Trivial \& Beginner-level Temporal}{
\spell{
	name = Distressing Omen, school = Divination, discipline = Temporal, type = Instant, level =Beginner, range =Close, incant = mitus, noDur = 1, higher = \additional{1d8}{psychic},resist = Logic, noBlock = 1, effect =Speak aloud an omen\comma{} layering into your voice the power of the future\comma{} to warp the mind of your opponent. Target must succeed on a Resist check or take 1d8 psychic damage.
}
\spell{
	name = Identify Object, school = Divination, discipline = Temporal, type = Ritual (5 minutes), level =Beginner, range =Wandtip, incant = dicemi, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =By touching your wand\minus{}tip to an object and entering into a deep trance\comma{} you may learn about the object. 

You learn any magical effects the object may have been enchanted or cursed with and the uses and limitations of those effects. You also learn the purpose of the object (if unknown)\comma{} and the provenance of it. 

If the object possesses a notable history\comma{} you may also learn fragments of that past.
}
\spell{
	name = Locate Object, school = Divination, discipline = Temporal, type = Instant, level =Beginner, range =Self, incant = locus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =After casting this spell\comma{} you must shout a description or the name of the object you are searching for. If you are within 1km of the object\comma{} you gain a snapshot of the object you are searching for\comma{} and the direction in which it is moving. 

If you are looking for a specific object\comma{} you must be familiar with it (i.e. have seen it up close at least once). Alternatively\comma{} you may describe a class of object (i.e. a necklace)\comma{} and the spell will find the nearest such object. 

This spell fails if there is no such object within range\comma{} or if the object is protected by any kind of magical ward or lock.
}
\spell{
	name = Receive Omen, school = Divination, discipline = Temporal, type = Ritual (2 minutes), level =Trivial, range =Self, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Use your tea leaves to receive an omen about the future. Ask a question about the outcome of an event. The tea leaves will tell you if the outcome is positive\comma{} negative\comma{} or neutral.
}
}
 \spellBook{e}{Trivial \& Beginner-level Bewitchment}{
\spell{
	name = Aura of Kindness, school = Illusion, discipline = Bewitchment, type = Instant, level =Beginner, range =Close, incant = amicus, duration = 1 hour,higher = Gain an additional +1 bonus \forEvery{},noResist =1, noBlock = 1, effect =This spell creates an aura of kindness and warmth around you. If the target is not overtly hostile\comma{} this causes then to like you: charisma checks by the caster on the individual get a +1 bonus for the duration of the spell.
}
\spell{
	name = Blur, school = Illusion, discipline = Bewitchment, type = Instant, level =Beginner, range =Wandtip, incant = celeritate, duration = 3 turns,higher = Gain an additional +1 bonus \forEvery{},noResist =1, noBlock = 1, effect =The target of this spell (which may be the catser) seems to become blurry around the edges\comma{} it is difficult to tell exactly where they are\comma{} and where they aren{\apos}t.
Gain a +2 bonus to Dodge for the duration.
}
\spell{
	name = Glamour, school = Illusion, discipline = Bewitchment, type = Instant, level =Beginner, range =Close, incant = lux stultium, duration = 1 hour,noHigh = 1, resist = Attention, noBlock = 1, effect =Create a superficial glamour around a person or object\comma{} a simple magical hologram which sits on top of the true surface. This hologram takes any form the caster can imagine\comma{} but can only perform minor movements – an illusion over the face of a target may open its mouth as the target does\comma{} but nothing more complex than this. 

The glamour disintegrates upon physical or magical contact\comma{} and can be seen to be fake if observer succeeds on a Resist check.
}
\spell{
	name = Hypnotic Lights, school = Illusion, discipline = Bewitchment, type = Instant, level =Beginner, range =Sight, incant = fascum, duration = 1 minute,noHigh = 1, resist = Intelligence, noBlock = 1, effect =Multicoloured\comma{} iridescent orbs dance in the sky\comma{} fascinating up to 1d4 creatures that see them\comma{} if they fail a DV 8 Resist check. These creatures cannot remove their gaze from the orbs\comma{} and will stop all other actions for the duration of the hypnotism. Every time the hypnotised beings take damage\comma{} they may attempt to Resist.
}
\spell{
	name = Illusory Form, school = Illusion, discipline = Bewitchment, type = Focus, level =Beginner, range =Close, incant = lux, noDur = 1, higher = The size of the illusory region (i.e. the side\minus{}length of the bounding cube) doubles \forEvery{}.,resist = Attention, negation = Blockable,effect =Create an illusion\comma{} a construction of light\comma{} in a region of space within range. The image occupies a space no larger than a cube with sides 1m in length\comma{} and the form can be anything that the caster can clearly envisage. 

This illusion cannot make a sound and is non\minus{}corporeal\comma{} but does not disintegrate on contact like a {\it Glamour}. Whilst the caster maintains focus\comma{} the illusion (and the space it ocucpies) may be manipulated and altered to mimic the illusion walking and moving\comma{} for example. If concentration is broken\comma{} the illusion instantly dissolves into nothingness. 

An observer may determine that the illusion is not real by performing a Resist check as a major action\comma{} or by attempting to physically interact with it.
}
\spell{
	name = Lure, school = Illusion, discipline = Bewitchment, type = Instant, level =Trivial, range =Close, incant = ollius, noDur = 1, noHigh = 1, resist = Logic, noBlock = 1, effect =Choose a target that you can see within range\comma{} and create a dangling lure in front of their face\comma{} or some other illusion to draw their attention towards you. On a failed resist\comma{} the target will\comma{} if possible\comma{} use its actions this turn to attack you instead of another target. If the target would be unable to make an attack against you this turn\comma{} the spell fails.
}
\spell{
	name = Minor Trickery, school = Illusion, discipline = Bewitchment, type = Instant, level =Trivial, range =Close, incant = mico, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Create a minor magical trick\comma{} such as a flash of light\comma{} a brief shower of sparks or a puff of smoke. You could make a magical symbol float briefly in the air\comma{} or cause the hairs on the back of a target\apos{}s head to stand on end. Whilst this spell is very versatile\comma{} and the effects certainly look magical in nature\comma{} they serve no real purpose beyond looking pretty\comma{} though several enterprising wizards have used this spell on street corners whilst pretending to do muggle ``magic”.
}
\spell{
	name = Throw Voice, school = Illusion, discipline = Bewitchment, type = Focus, level =Trivial, range =Close, incant = ventrilofors, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Cast your voice such that\comma{} when you speak\comma{} your voice appears to emanate from somewhere up to 15 metres away from your actual position.
}
}
 \spellBook{f}{Trivial \& Beginner-level Psionics}{
\spell{
	name = Chaotic Whispers, school = Illusion, discipline = Psionics, type = Focus, level =Beginner, range =Sight, incant = rastarum, noDur = 1, higher = The whispers gain in power when this spell is cast at a higher level: doing 1d8 additional damage for each additional casting level.,resist = Logic, noBlock = 1, effect =The target hears a voice in their ear whispering maddening words that slowly drive them insane. Target may take a minor action to perform a Resist check at the start of their turn\comma{} when one succeeds\comma{} the spell is broken. 

Whispers do 1d8 psychic damage per turn that the spell is active.
}
\spell{
	name = False Friendship, school = Illusion, discipline = Psionics, type = Instant, level =Beginner, range =close, incant = amicus maxmius, duration = 1 hour,noHigh = 1, resist = Willpower, noBlock = 1, effect =If the target fails to resist\comma{} you place the idea inside their mind that you are their ally. Gain advantage on all charisma checks directed at the target for the duration  the spell\comma{} if they are not already overtly hostile. At the end of the spell\comma{} or if they succeed in Resisting\comma{} the target becomes aware that you have enchanted and deceived them\comma{} and will become hostile or otherwise seek vengeance.
}
\spell{
	name = Manipulate Emotions, school = Illusion, discipline = Psionics, type = Instant, level =Trivial, range =Close, incant = motus conus, duration = 2 minutes,noHigh = 1, resist = Willpower, noBlock = 1, effect =If the target fails to resist\comma{} you may manipulate their emotions such that they feel an intense emotion of your choosing. You can make them feel incredibly happy\comma{} or incredibly sad\comma{} scared\comma{} or brave. The target is unaware that you have manipulated them in this fashion until the spell effect ends or the successfully Resist.
}
\spell{
	name = Piercing Wail, school = Illusion, discipline = Psionics, type = Instant, level =Beginner, range =Close, incant = magnus surgerus, noDur = 1, higher = The wail gains an additional 1d4 psychic damage for every additional spell level dedicated to the casting.,resist = Willpower, noBlock = 1, effect =All targets in a 3m spherical radius of the caster take 1d4 points of psychic damage\comma{} and awaken if they are sleeping. The damage is halved on a successful Resist.
}
\spell{
	name = Shrivelled Ears, school = Illusion, discipline = Psionics, type = Instant, level =Beginner, range =Close, incant = raxus, duration = 1 minute,noHigh = 1, resist = Logic, noBlock = 1, effect =On a failed Resist\comma{} causes the target to believe that their ears have shrivelled up and fallen off\comma{} and temporarily removes the link between ears and the brain. 

Target is effectively deaf and all checks which rely on hearing fail. They also take check\minus{}disadvantage on all Perception checks.
}
}
 \spellBook{l}{Trivial \& Beginner-level Conjuration}{
\spell{
	name = Palpatation, school = Maledictions, discipline = Conjuration, type = Instant, level =Trivial, range =Close, incant = vena, noDur = 1, noHigh = 1, resist = Vitality, noBlock = 1, effect =On a failed Resist\comma{} you cause the target\apos{}s heart to miss a beat. Next cycle\comma{} the target\apos{}s speed is halved.
}
}
 \spellBook{g}{Trivial \& Beginner-level Curse}{
\spell{
	name = Backlash, school = Maledictions, discipline = Curse, type = Instant, level =Trivial, range =Close, incant = vindictus, noDur = 1, noHigh = 1, noResist =1, negation = Blockable,effect =You imbue the air around the target with a positive energy field which discharges whenever they perform an action which causes harm. 

Whenever the target causes any other being to lose HP\comma{} they take 1d4 points of force damage.
}
\spell{
	name = Bubbling Warts, school = Maledictions, discipline = Curse, type = Instant, level =Beginner, range =Close, incant = furnunculus, duration = 1 hour,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =After being hit with this spell\comma{} the target breaks out in a horrendous case of warts and boils all over their body. This boils are incredibly itchy and distracting\comma{} giving the afflicted disadvantage on all Spirit checks.
}
\spell{
	name = Curse of the Bogies, school = Maledictions, discipline = Curse, type = Instant, level =Beginner, range =Close, incant = Mucous ad nauseam, duration = 1 day,noHigh = 1, resist = Vitality, noBlock = 1, effect =A fine green mist floats from the end of your wand\comma{} into the face of the target. On a failed Resist\comma{} they contract an awful cold. The target becomes visibly ill\comma{} their nose drips snot constantly\comma{} and their throat is sore. 

Every time they open their mouth to speak\comma{} they must succeed a DV 10 Vitality Resist to avoid sneezing. Sneezing during a spell incantation causes the spell to fail.
}
\spell{
	name = Jelly Legs, school = Maledictions, discipline = Curse, type = Focus, level =Beginner, range =Close, incant = locomotor wibbly, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =If this spell makes contact with a living being\comma{} it causes their legs to turn to jelly and collapse underneath them. The target takes the {\it Prone Position} status and cannot remove it whilst concentration is maintained.
}
\spell{
	name = Minor Curse, school = Maledictions, discipline = Curse, type = Instant, level =Trivial, range =Sight, incant = lombus, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =A beam of light causes the target\apos{}s muscles to atrophy and their mind to cloud for an instant\comma{} before the effect wears off. The target must deduct 1d4 from the value of their next check.
}
\spell{
	name = Stickfast, school = Maledictions, discipline = Curse, type = Instant, level =Beginner, range =Close, incant = colloshoo, duration = 15 seconds,noHigh = 1, resist = Strength, negation = Blockable  and Dodgeable,effect =If this spell strikes a target\comma{} it glues their feet to the ground\comma{} setting their movement speed to 0 (though it does not effect magical transport such as apparation). The target may use a major action to perform a Resist check to break free.
}
\spell{
	name = Sudden Sound, school = Maledictions, discipline = Curse, type = Instant, level =Trivial, range =Close, incant = ferio, noDur = 1, noHigh = 1, resist = Attention, noBlock = 1, effect =You create a loud sound of your choice to crash into a target\apos{}s ears. On a failed Resist\comma{} the target is mildly distracted and loses any check\minus{}advantage it may have on accuracy checks this turn. 

If the target is currently concealed from allies of the caster\comma{} they may take an additional Observation check with advantage\comma{} to detect the target.
}
\spell{
	name = Taste of Blood, school = Maledictions, discipline = Curse, type = Ward, level =Beginner, range =Close, incant = sanguinifors, duration = 1 minute,higher = The additional damage increases by 1d4 (or 1d6 if damaged) \forEvery{}.,resist = Intimidation, noBlock = 1, effect =You place a cursed ward onto a target of your choice\comma{} if they fail to Resist. 

This ward allows you to deal an additional 1d4 damage whenever you perform a damage roll against this target. This increases to 1d6 if you had damaged the target before casting this spell.
}
\spell{
	name = Tripwire, school = Maledictions, discipline = Curse, type = Instant, level =Beginner, range =Close, incant = lubricor, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =If the target is moving this turn cycle and fails to Resist\comma{} they go sprawling onto the ground taking 1 bludgeoning damage\comma{} and take the {\it Prone Position} status.
}
}
 \spellBook{h}{Trivial \& Beginner-level Hex}{
\spell{
	name = Knockback, school = Maledictions, discipline = Hex, type = Instant, level =Trivial, range =Close, incant = flipendo, noDur = 1, higher = Each additional casting level dedicated to this spell increases the power of the energy\minus{}wave: do an additional 1d8 force damage and push the target back an extra 2 metres.,resist = Strength, negation = Blockable  and Dodgeable,effect =A wave of energy strikes into the target\comma{} causing 1d6 force damage\comma{} and if the target fails to Resist\comma{} pushing the target backwards up to 1 metre.
}
\spell{
	name = Magnetising Strike, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Close, incant = adtraho, duration = 30 seconds,higher = \additional{1d8}{force},resist = Acrobatics or Speed, noBlock = 1, effect =A pulse of energy streaks out towards the target faster than a normal `dodge\apos{} could avoid. 

On a failed Resist\comma{} the target takes 1d8 force damage\comma{} and becomes mildly magnetic. All attacks made on them with melee weapons made of metal are at advantage for the duration of the spell..
}
\spell{
	name = Mortar Pulse, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Close, incant = sivango, noDur = 1, higher = \additional{2d4}{concussive},resist = Acrobatics, noBlock = 1, effect =Raising your wand into the air\comma{} you send a small blue blob arcing upwards until it smashes down onto a targeted area within range\comma{} releasing a pulse out into a circle 3 metres in radius. 

All beings take 1d4 concussive damage\comma{} halved on a successful Resist.
}
\spell{
	name = Rainbow Sparks, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Close, incant = verdimillious, noDur = 1, higher = Create an additional packet of sparks for each level above Beginner used to cast this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =Shoots a packet of small sparks from your wand\comma{} which rocket from the end of your wand towards a single enemy. 

You may choose the colour of the sparks from red\comma{} blue\comma{} green or yellow. The colour of the sparks reflects the damage done: fire\comma{} cold\comma{} acid and electric respectively. 

Each packet does 1d8 damage of the chosen type.
}
\spell{
	name = Sting, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Sight, incant = ictus, noDur = 1, higher = \additional{1d6}{poison},noResist =1, negation = Blockable,effect =A blast of purplish energy rockets from your wand\comma{} seeking to strike the enemy in the face. Stings the target for 1d6+1 poison damage.
}
\spell{
	name = Ticklish Blast, school = Maledictions, discipline = Hex, type = Instant, level =Beginner, range =Close, incant = rictumsempra, duration = 1 minute,higher = \additional{1d6}{Concussive},noResist =1, negation = Blockable  and Dodgeable,effect =When this spell touches the target\comma{} they take 1d6 concussive damage\comma{} and in addition they begin chuckling uncontrollably for the duration of the spell\comma{} reducing their awareness of their surroundings. 

The target takes disadvantage on all perception checks for the duration.
}
}
 \spellBook{I}{Trivial \& Beginner-level Healing}{
\spell{
	name = Boost Health, school = Recuperation, discipline = Healing, type = Instant, level =Beginner, range =Close, incant = levo, duration = 12 hours,higher = Gain an additional 1d6 temporary health points for every additional spell\minus{}level used to cast this spell.,noResist =1, noBlock = 1, effect =Emit a calming\comma{} healing warmth from the end of your wand to bolster the strength of your allies. Target up to 2d4 beings in range\comma{} and provide them with 5 temporary health points.
}
\spell{
	name = Minor Healing, school = Recuperation, discipline = Healing, type = Instant, level =Beginner, range =Wandtip, incant = enervate, noDur = 1, higher = This spell heals for an additional 1d8 damage for every additional spell level dedicated to it.,noResist =1, noBlock = 1, effect =Your wand emits healing rays which close small wounds as you pass your wand over them. Heal for 1d8 points of health.
 
If the target has a serious wound\comma{} i.e. a broken bone\comma{} cannot heal beyond 50\% health. Only works on living creatures.
}
\spell{
	name = Relinquish Grip, school = Recuperation, discipline = Healing, type = Instant, level =Beginner, range =Close, incant = relashio, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =Force physical objects\comma{} spells and beings to release their grip\comma{} and remove all impediments to moving for the targeted individual. Beings may perform a Resist check to nullify this effect.
}
\spell{
	name = Spare the Wounded, school = Recuperation, discipline = Healing, type = Instant, level =Beginner, range =Sight, incant = clementia, duration = 1 day,noHigh = 1, resist = Evil, noBlock = 1, effect =If the subject falls below 5HP\comma{} they are considered a non\minus{}combatant and can only be targeted by beings which successfully Resist. This spell is negated if subject engages in hostile activity\comma{} and subjects may be damaged by area of effect attacks centred on other valid targets.
}
\spell{
	name = Stabilise Patient, school = Recuperation, discipline = Healing, type = Instant, level =Trivial, range =Wandtip, incant = firmum, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Stabilises the patient and replaces the \textit{Critical Condition} status with {\it Critical But Stable}.
}
}
 \spellBook{j}{Trivial \& Beginner-level Warding}{
\spell{
	name = Caterwauling Alarm, school = Recuperation, discipline = Warding, type = Ward, level =Beginner, range =Wandtip, incant = caterwaul, duration = 2 weeks,noHigh = 1, noResist =1, noBlock = 1, effect =Casts a ward on an area which detects when a living being larger than a rat touches or enters a designated region up to 10m in radius. You may choose the form of the alarm on casting \minus{} either mental or audible. 

A mental alarm forms a psychic connection which alerts you when activated\comma{} and can awaken you if you are sleeping. This connection has a maximum range of 1km. 

The audible alarm produces an ear\minus{}splitting screech when the perimiter is breached. The sound is loud enough to be heard over large distances.
}
\spell{
	name = Flame Freezing Shield, school = Recuperation, discipline = Warding, type = Ward, level =Beginner, range =Wandtip, incant = glaciagnis, duration = 1 hour,noHigh = 1, resist = Power, noBlock = 1, effect =Causes non\minus{}magical fire to feel lightly cool and tickle the warded subject\comma{} rather than burning them. 

Whenever a caster attempts to inflict magical fire damage on the protect being\comma{} they must succeed on a Resist check\comma{} or the damage is halved.
}
\spell{
	name = Force Shield, school = Recuperation, discipline = Warding, type = Focus, level =Beginner, range =Self, incant = protego, noDur = 1, higher = Increase the strength of the shield by 1 point \forEvery{}.,noResist =1, noBlock = 1, effect =An ethereal shield blossoms from the end of your wand\comma{} protecting you from both magical and physical harm. 

Whenever an attack is performed against you whilst the shield is active\comma{} roll 2d4 and add this value to your Resist check or your Block value\comma{} as appropriate. If a successful Resist would limit the amount of damage taken\comma{} negate it entirely instead. 

If you fail to Resist\comma{} or the Accuracy exceeds your augmented Block value\comma{} the shield crumples and the spell is ended. The spell which broke the shield is then applied to you at half damage\comma{} with any other effects unmodified. Any other spells which hit you this round act as normal. 

The caster is not considered {\it Distracted} when casting this spell\comma{} unless attacked by an enemy that they cannot see.
}
\spell{
	name = Privacy Ward, school = Recuperation, discipline = Warding, type = Ward, level =Beginner, range =Wandtip, incant = muffliato, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Ward a region up to 5m in radius. This ward prevents sound from inside the region being heard from the outside. When inside the region\comma{} sound from both inside and outside may be heard.
}
\spell{
	name = Silent Step, school = Recuperation, discipline = Warding, type = Ward, level =Beginner, range =Close, incant = quiesco, duration = 5 minutes,higher = You may choose 3 additional targets \forEvery{},noResist =1, noBlock = 1, effect =Target a being and place a benevolent ward on them\comma{} which muffles all sounds made by the being\comma{} including footsteps and spoken language\comma{} making them incredibly hard to hear. 

Affected beings get check\minus{}advantage on Stealth checks.
}
\spell{
	name = Vengeance Field, school = Recuperation, discipline = Warding, type = Instant, level =Beginner, range =Self, incant = joder voste, duration = 20 seconds,higher = When cast as a higher level spell\comma{} the field absorbs more energy and does an additional 1d8 damage for each additional spell\minus{}level dedicated to the casting.,noResist =1, noBlock = 1, effect =Erect a field of energy around you. The next time you take damage of any type\comma{} this field becomes charged with energy corresponding to that damage type. 

The next attack you make with a physical weapon deals an additional 1d8 damage of the absorbed type.
}
}
 \spellBook{k}{Trivial \& Beginner-level Alteration}{
\spell{
	name = Aerodynamic Rectification, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Wandtip, incant = volant, duration = 1 minute,noHigh = 1, noResist =1, noBlock = 1, effect =You imbue a 1d4 small stones or other small\comma{} nearby object with a magical aura which causes them to move more easily through the air.

When you or another being uses these as improvised throwing weapons\comma{} or as ammunition for a sling\comma{} you may add your proficiency modifier to the accuracy check\comma{} even if you are not proficient in the relevant field. On a successful hit\comma{} the object deals an additional 1d6 bludgeoning damage.
}
\spell{
	name = Degrade, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Close, incant = prolabor, duration = 1 minute,higher = This spell effects an additional object or being \forEvery{}.

When cast as an Adept level spell or higher\comma{} you may select two degredations from the list.,resist = Power, noBlock = 1, effect =Choose up to three target objects or beings that you can see within range\comma{} and make subtle minor alterations which generally lessen the quality of the targets.

An object might gain layer of grime\comma{} whilst imperfections develop across the surface. A previously well\minus{}oiled joint might begin to produce a horrendous squeaking noise. This spell cannot break an object and remove functionality\comma{} but instead generally makes an object less pleasant and high\minus{}quality than it was before. When used in this fashion\comma{} the spell has no duration\comma{} and the degredations are considered permanent. 

When this spell is targeted at a living being\comma{} the `degredation' instead allows you to fatigue the muscles of the target to reduce their aim\comma{} or give them a mild headache to disrupt their concentration.

For each targeted being which fails to Resist\comma{} the caster chooses one of the following:
\begin{spellitemize}
\item Attribute checks
\item Resist checks
\item Accuracy checks
\item Damage checks
\end{spellitemize}

For the duration of the degradation\comma{} whenever an effected being performs one of their selected checks\comma{} they must roll an additional 1d4 and subtract that result from the result of the roll.
}
\spell{
	name = Horrific Armaments, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Self, incant = armatum, duration = 1 minute,higher = The damage dealt by these effects increases by 1d8\comma{} 1d6 and 1d6 respectively \forEvery{}.,noResist =1, noBlock = 1, effect =You alter your own body\comma{} molding it into a lethal weapon\comma{} choosing from one of these effects:

\begin{spellitemize}
\item You grow long claws and fangs: your melee attacks now deal 1d6 + Alteration modifier slashing damage.
\item You grow a large articulated tail ending in a vicious point which you can use to perform a melee attack at targets up to 2m away\comma{} dealing 1d6 + Alteration modifier piercing damage. 
\item Your body sprouts large spines all over\comma{} which deal 1d6 + Alteration modifier piercing damage to any being which performs a melee attack on you. 
\end{spellitemize}
}
\spell{
	name = Magical Makeover, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Self, incant = crinus muto, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Alters the colour and style of the caster\apos{}s hair\comma{} apply a layer of makeup\comma{} and scrapes the dirt from under your fingernails. You may alter your appearance as if you had been attended to by a competent hair stylist and make\minus{}up artist.   

Useful for disguises\comma{} or to make yourself look suave in an instant.
}
\spell{
	name = Refine, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Close, incant = excolo, duration = 1 minute,higher = This spell effects an additional object or being \forEvery{}.

When cast as an Adept level spell or higher\comma{} you may select two improvements from the list.,noResist =1, noBlock = 1, effect =Choose up to three target objects or beings that you can see within range\comma{} and make subtle minor alterations which generally improve the quality of the object at your direction.

An object might lose a layer of grime\comma{} and imperfections would lessen in severity\comma{} or several dents might fix themselves. A poorly fitting hinge might become smooth and well\minus{}oiled. This spell cannot fix a broken object to restore functionality\comma{} but generally makes an object more pleasant and high\minus{}quality than it was before. When used in this fashion\comma{} the spell has no duration\comma{} and the improvements are considered permanent. 

When this spell is targeted at a living being\comma{} the `improvement' instead allows you to tweak the muscles of the target to give them a burst of speed and improve their reflexes\comma{} or clear their mind to allow to improve memory and increase their motor skills. 

For each targeted being\comma{} the caster chooses one of the following:
\begin{spellitemize}
\item Attribute checks
\item Resist checks
\item Accuracy checks
\item Damage checks
\end{spellitemize}

For the duration of the refinement\comma{} whenever an effected being performs one of their selected checks\comma{} they may roll an additional 1d4 and add that result to the result of the roll.
}
\spell{
	name = Slip, school = Transfiguration, discipline = Alteration, type = Focus, level =Beginner, range =Sight, incant = glisser, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =Whilst Focus is maintained\comma{} up to 1 square metre of the targeted surface becomes slippery\comma{} as if it was covered in grease. When a target touches the effected surface and fails the resist check\comma{} they fall over and take the {\it Prone Position} status.
}
\spell{
	name = Small Change Charm, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Wandtip, incant = psilus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =The only spell which can alter magical currency. By casting this charm on a set of Galleons\comma{} Sickles and Knuts you may transfigure them into any other combination of coins with an equal monetary value.
}
\spell{
	name = Solidify \& Strengthen, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Close, incant = duro, duration = 1 hour,higher = Hardened objects can absorb an additional 5 points of damage \forEvery{}.,noResist =1, noBlock = 1, effect =Freezes a non\minus{}living object into its current form\comma{} such that it can no longer bend or flex and reinforce the structure of the object with magical energy. Hardened objects can absorb an additional 10 points of damage before they crumble and break and can be used to provide cover.
}
\spell{
	name = Touch of Colour, school = Transfiguration, discipline = Alteration, type = Instant, level =Trivial, range =Close, incant = pigmentus, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Causes the colour of an object to change to that specified by the caster. The resulting colour is not purely monochromatic\comma{} but appears as if you were viewing the object through a thick pane of coloured glass of the chosen colour.
}
\spell{
	name = Transmutation, school = Transfiguration, discipline = Alteration, type = Instant, level =Beginner, range =Close, incant = mutatio, duration = 1 hour,higher = The maximum mass this spell is capable of transfiguring multiplies by 5 for every additional spell level used to cast it.,resist = Power, noBlock = 1, effect =Transform a 1kg non\minus{}sapient animal (or part of an animal) or object into a different animal or solid object\comma{} negated on a successful Resist. If you are targeting a being which is in combat with you\comma{} they take advantage on the Resist check. 

The transformation must (approximately) conserve mass – you cannot turn a rat into a T\minus{}Rex\comma{} for example. The final product of the transfiguration must be a non\minus{}magical in nature (i.e. you cannot enchant items through Transmutation)
}
}
 \spellBook{l}{Trivial \& Beginner-level Conjuration}{
\spell{
	name = Conjure Bubble, school = Transfiguration, discipline = Conjuration, type = Instant, level =Beginner, range =Close, incant = ebublio, duration = 1 hour,higher = Gain  +10 HP to the bubble for every additional casting level dedicated to this spell.,noResist =1, noBlock = 1, effect =Conjures a large\comma{} hard\minus{}to\minus{}pop\comma{} airtight\comma{} spherical bubble radius specified by the caster (max: 2m). The bubble can use to encase enemies\comma{} or to protect the caster. The bubble provides a bonus to Block of +2\comma{} and has a HP of 20\comma{} but is instantly destroyed upon taking 1 point of piercing damage.
}
\spell{
	name = Conjure Flowers, school = Transfiguration, discipline = Conjuration, type = Instant, level =Trivial, range =Wandtip, incant = orchideous, duration = 3 days,noHigh = 1, noResist =1, noBlock = 1, effect =Conjures a bouquet of flowers from thin air. You may choose the species of flower from any of the common species. The flowers remain perfectly preserved for the duration of the spell\comma{} but wilt and die in an instant at the end of the spell\apos{}s effect.
}
\spell{
	name = Erupting Spike, school = Transfiguration, discipline = Conjuration, type = Instant, level =Beginner, range =Close, incant = voco dens, noDur = 1, higher = An extra spike is generated for every additional spell level used to cast this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =Conjure an enormous spike to transfigure itself from the surrounding walls or floor\comma{} impaling the target. A spike which lands true does 2d6 piercing damage. 

Spikes can only reach up to 2m in length\comma{} and so cannot effect enemies which are more than 2m from a solid surface.
}
\spell{
	name = Grasping Tendrils, school = Transfiguration, discipline = Conjuration, type = Instant, level =Beginner, range =Close, incant = manibarius, duration = 30 seconds,higher = \additional{1d4}{piercing},resist = Reflex, noBlock = 1, effect =You summon a set of grasping\comma{} oily tentacles from the other side of the astral realm\comma{} allow them to reach through a portal which you set into a wall or floor. The tendrils can reach up to 3m from the portal\comma{} and will attack anyone who enters into this region\comma{} dealing 1d4+1 piercing damage as the tentacles strike out at them\comma{} halved on a successful Resist.
}
\spell{
	name = Prank, school = Transfiguration, discipline = Conjuration, type = Instant, level =Trivial, range =Close, incant = riddikulus, duration = 2 minutes,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =You conjure something onto or near your target with the express intention of making them look as stupid as possible: Summon a funny hat onto an individual\comma{} or conjure up a note with a funny message and stick it to their back\comma{} this spell allows you to perform minor\comma{} harmless pranks in an instant.
}
\spell{
	name = Shimmering Confetti, school = Transfiguration, discipline = Conjuration, type = Instant, level =Beginner, range =Close, incant = chamak, noDur = 1, noHigh = 1, resist = Logic, noBlock = 1, effect =Conjures a shower of golden\comma{} shimmering particles to cover every person and surface in a 4m radius. If a being fails to resist\comma{} the first attack to land this turn cycle is considered a {\it Critical Strike}.
}
\spell{
	name = Silver Shield, school = Transfiguration, discipline = Conjuration, type = Instant, level =Beginner, range =Wandtip, incant = argentipus, duration = 1 hour,higher = The HP of the shield increased by 1d8 for every additional spell level dedicated to the spell.,noResist =1, noBlock = 1, effect =Conjures a floating silver shield from thin air\comma{} to defend you. 

The shield actively intercepts incoming attacks\comma{} providing you with a your Block statistic equal to your Expertise Bonus. 

When the shield blocks an attack\comma{} it takes the damage. The shield has 3d8HP and shatters into dust when it reaches 0HP. Any excess damage from the attack which reduced the shield to 0HP is transferred to the caser.
}
\spell{
	name = Swordstrike, school = Transfiguration, discipline = Conjuration, type = Instant, level =Trivial, range =Wandtip, incant = galdio, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =After casting this spell\comma{} a non\minus{}magical shortsword erupts into existence and makes an attack against an enemy within melee range. You may perform the accuracy check using either a Conjuration Spellcasting check\comma{} or a normal shortsword check. 

If the strike hits the target\comma{} it deals 1d6 slashing damage. If the caster is proficient in the use of a shortsword\comma{} their \attPhys{} modifier is added to the damage.
}
}
 \spellBook{m}{Trivial \& Beginner-level Necromancy}{
\spell{
	name = Envelop in Shadows, school = Dark Arts, discipline = Necromancy, type = Instant, level =Trivial, range =Sight, incant = malusangui, noDur = 1, higher = Gain 1d10 additional necrotic damage for each additional spell level.,noResist =1, negation = Blockable  and Dodgeable,effect =You concentrate\comma{} and the nearby shadows flock to your wand\comma{} curling around like an evil candy floss\comma{} before launching themselves at your target dealing 1d6 necrotic damage.
}
\spell{
	name = Instil Terror, school = Dark Arts, discipline = Necromancy, type = Instant, level =Beginner, range =Close, incant = timeant, duration = 4 minutes,noHigh = 1, resist = Willpower, noBlock = 1, effect =On a failed Resist\comma{} the target becomes {\it Terrified} of the caster.
}
\spell{
	name = Vicious Slash, school = Dark Arts, discipline = Necromancy, type = Instant, level =Beginner, range =Close, incant = sectumsempra, noDur = 1, higher = Gain an additional 1d8 slashing damage for each additional spell level dedicated to casting this spell.,noResist =1, negation = Blockable,effect =Bolts of energy strike out at the target\comma{} goughing at them and leaving deep\comma{} cursed wounds\comma{} for 1d8 points of slashing damage. This damage is halved on a successful Block.
}
}
 \spellBook{n}{Trivial \& Beginner-level Occultism}{
\spell{
	name = Blood Pact, school = Dark Arts, discipline = Occultism, type = Ritual (1 hour), level =Trivial, range =Self, noIncant = 1, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Perform a ritual in which all members of a group mix their blood in the centre of  a pentagram\comma{} binding them together. For the duration of the spell\comma{} whenever all members of this group work together to complete a task\comma{} gain a bonus to the group check equal to the number of people in the pact.
}
\spell{
	name = Demoncall, school = Dark Arts, discipline = Occultism, type = Instant, level =Beginner, range =Sight, incant = profundum, duration = 30 minutes,higher = For every additional spell\minus{}level dedicated to casting this spell\comma{} the maximum MoM rating of a demon that you can summon increases by 1. Demons with ratings IV and above can take more complex commands – up to a single phrase.,noResist =1, noBlock = 1, effect =Convince a demon (MoM rating II or less) to break through the walls between reality and come to your aid\comma{} opening a rift at a spot you choose within 10m of your position. You may choose the type of demon from those that you have previously studied or encountered.

The demon will take a single\minus{}word command when it leaps into existence\comma{} and the caster may use a minor action to give it an additional one\minus{}word command\comma{} replacing the first. The demon will follow these commands to the best of its abilities. The demon remains in existence until its HP reaches zero\comma{} the spell duration ends\comma{} or the caster uses a minor action to dismiss it\comma{} at which point the demon returns to its home dimensions.

The summoned will remain friendly to you and your allies until any of them cause it to lose HP\comma{} or force it to perform a Resist check for any reason\comma{} at which point it will consider you foes\comma{} and will engage you if appropriate. In doing so you lose the ability to command or dismiss the demon.
}
\spell{
	name = Draw Power, school = Dark Arts, discipline = Occultism, type = Ritual (1 hour), level =Trivial, range =Self, noIncant = 1, duration = 1 day,higher = Increase the spellcasting bonus by +1 for every two additional spell levels used to cast this spell.,noResist =1, noBlock = 1, effect =When at a site of ancient magic \minus{}\minus{} be it at a place where some great feat of magic was achieved\comma{} the residence of some powerful being\comma{} or simply somewhere where magic has seeped into the very walls \minus{}\minus{} you may perform this ritual to tap into those ancient powers to gain a +2 bonus to spellcasting checks whilst in this area. This ritual cannot be used at the same site for the next 7 days.
}
\spell{
	name = Shroud of Darkness, school = Dark Arts, discipline = Occultism, type = Instant, level =Beginner, range =Close, incant = tenebrosa, duration = 2 minutes,noHigh = 1, resist = Power, noBlock = 1, effect =A layer of darkness settles on the immediate vicinity\comma{} extinguishing all sources of light within a 10 metre radius. 

For the duration of the spell all attempts to create new light fail\comma{} unless the caster manages to Resist.
}
\spell{
	name = Unfathomable Visage, school = Dark Arts, discipline = Occultism, type = Instant, level =Beginner, range =Self, incant = facadus horribilis, duration = 1 minute,higher = Gain an additional bonus of 1d4 \forEvery{}.,noResist =1, noBlock = 1, effect =Imbue yourself with the essence of one of the Eldritch beings\comma{} giving a bonus to any one of your Attributes equal to 1d4\comma{} in doing so\comma{} however\comma{} your face transforms into a horrifying edifice which drives all who gaze upon it to go insane: they will either fly into a murderous rage\comma{} become catatonic\comma{} or flee from you.
}
}
 \spellBook{Lighting the Spark: An Introduction to Elemental Magic}{Novice-level Elemental}{
\spell{
	name = Burst of Frost, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Close, incant = isti, noDur = 1, higher = Gain an additional 1d10 Cold damage for every additional spell level dedicated to casting this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =The air around the tip of your wand freezes\comma{} condensing the surrounding water vapour into a tiny globe of ice\comma{} which launches towards your target. If it hits\comma{} the globe explodes doing 2d10 Cold damage.
}
\spell{
	name = Dancing Bolt, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Close, incant = arka gola, noDur = 1, higher = Gain an additional 2 bursts \forEvery{}.,noResist =1, negation = Blockable  and Dodgeable,effect =2 bursts of fire spiral and dance in towards your target\comma{} each dealing 1d10 fire damage on contact (rolling accuracy for each).
}
\spell{
	name = Douse Flame, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Sight, incant = sitim, noDur = 1, higher = When cast as an Expert level spell\comma{} this spell can effect {\it Fiendfyre},noResist =1, noBlock = 1, effect =Extinguish all active fires in a region up to 3m in radius\comma{} removing the danger and stopping any continuing damage effects. 

However\comma{} this spell does not prevent an ongoing spell from producing more fire after it is removed\comma{} and nor does it effect the `Burned' status of a being.
}
\spell{
	name = Earthen Excavation, school = Charms, discipline = Elemental, type = Focus, level =Novice, range =Close, incant = wykopat, noDur = 1, higher = When cast as a higher level spell\comma{} you may triple the total volume targeted for every additional spell level.,noResist =1, noBlock = 1, effect =Focus on a region of Earth with a volume of 1 cubic metre. You may excavate and move this loose earth around at will\comma{} at a speed of 5m per turn cycle. You may use this earth to raise walls and columns\comma{} or to dig large pits\comma{} but the total amount of matter must be conserved in all actions.
}
\spell{
	name = Elemental Weapon, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Wandtip, incant = gladio subtantia, noDur = 1, higher = The blade gains an additional 1d8 of the chosen damage type \forEvery,noResist =1, noBlock = 1, effect =The elements are bent to your will\comma{} and a blade of nature\minus{}incarnate solidifies around your wand. You now wield a 1d6 shortsword made out of pure fire\comma{} ice\comma{} lightning or earth\comma{} or light\comma{} held together by your strength of will. In addition to the physical cutting effect\comma{} this blade also imparts an elemental effect of 1d8 fire\comma{} cold\comma{} electric\comma{} bludgeoning or celestial damage respectively. 
 
No additional spells can be cast until this effect is dismissed as a minor action.
}
\spell{
	name = Far\minus{}Flung Flames, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Sight, incant = ignis, noDur = 1, higher = \additional{2d6}{Fire},resist = Logic, noBlock = 1, effect =You wave your wand in a complicated pattern\comma{} and an area of the target up to 1m squared bursts into flames\comma{} and begins to expand over the rest of the target. 

Ignited beings take 3d6 fire damage per turn\comma{} and the effect lasts until they come into contact with sufficient water or wind to extinguish the flames\comma{} or they pass a DV 12 Resist check\comma{} and voluntarily take the {\it Prone} status. The resist check can be performed once per turn.
}
\spell{
	name = Hovering Globe, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Self, incant = globus, duration = 1 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =Summons a glowing orb\comma{}around 5cm in diameter that hovers above the caster\apos{}s head\comma{} casting bright light for 4m\comma{} and dim light for a further 15m. As a minor action\comma{} the caster may move this light up to 10m in any direction.
}
\spell{
	name = Speedswim, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Self, incant = delfini, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =For the duration of the spell\comma{} you retain the ability to conjure a small bubble of air\comma{} and manipulate the water around you\comma{} enabling you to move extremely rapidly whilst in water. Your swimspeed becomes equal to twice your normal movement speed\comma{} and you do not need to breath whilst underwater. 

You also do not take disadvantage for using items\comma{} attacks or spellcasting whilst underwater.
}
\spell{
	name = Voltaic Surprise, school = Charms, discipline = Elemental, type = Ward, level =Novice, range =Wandtip, incant = rarnus, noDur = 1, higher = \additional{1d10}{Electric},resist = Observation, noBlock = 1, effect =Imbue a non\minus{}metallic object up to 3m in size with an enourmous electric charge. The next being to touch the object takes 2d10 electric damage\comma{} halved on a successful Resisist. Although this spell is classed as a `ward'\comma{} the threat is non\minus{}magical in nature after the spell has been cast. The charge\minus{}buildup therefore does not register to Detect Magic\minus{}style investigation.
}
\spell{
	name = Vortex Field, school = Charms, discipline = Elemental, type = Instant, level =Novice, range =Self, incant = dini, duration = 2 minutes,noHigh = 1, resist = Strength, noBlock = 1, effect =A swirling wall of wind evelopes a radius 1m around you\comma{} and follows you around for the duration of the spell. All physical objects entering the field are hurled in a random direction\comma{} and beings take 2d8 bludgeoning damage to pass through (halved on a resist).
}
}
 \spellBook{The Standard Book of Spells}{Novice-level Kinesis}{
\spell{
	name = Counterspell, school = Charms, discipline = Kinesis, type = Instant, level =Novice, range =Wandtip, incant = finite incantatem, noDur = 1, higher = For every additional spell\minus{}level dedicated to casting this spell\comma{} the maximum spell level which can be ended increases by one. 

In addition\comma{} when contesting against an active spellcaster\comma{} gain a one\minus{}point bonus to your spellcasting check per additional level.,noResist =1, noBlock = 1, effect =End the ongoing effects of any active Beginner\minus{}level spell on the targeted object or being\comma{} or disrupt the spellcasting efforts of an opponent.

This spell does not work on shields and wards\comma{} or spells from the curses discipline.

If you target a being which is actively casting a spell this turn cycle\comma{} perform a Kinesis spellcasting check against the Arcane Subjugation value of the spellcaster\comma{} plus a 1\minus{}point bonus per spell level of the spell they are casting. If your check succeeds\comma{} the caster loses focus and ends their spellcasting is disrupted before it is completed. A counterspell can itself be counterspelled\comma{} in which case the original spell functions as intended.
}
\spell{
	name = Deadlock Seal, school = Charms, discipline = Kinesis, type = Instant, level =Novice, range =Wandtip, incant = colloportus, noDur = 1, higher = The lockpicking DV increases by 2 \forEvery{}.,noResist =1, noBlock = 1, effect =Magically lock a door\comma{} chest or similar object. All mundane attempts to open the lock automatically fail\comma{} though a set of wizarding Lockpicking Tools can bypass the lock with a DV 15 check. Magical attempts to unlock the door must be cast using an unlocking spell at least one level greater than the spell\minus{}level used to cast this spell.
}
\spell{
	name = Destroy Lock, school = Charms, discipline = Kinesis, type = Instant, level =Novice, range =Close, incant = alohomora, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Magical and mundane locks on a the targeted door\comma{} chest\comma{} window\comma{} manacle and other such objects splinter and disintegrate with a loud clatter\comma{} or in the case of a magical lock\comma{} a loud arcane crash. For this spell to open magically locked objects\comma{} you must cast this spell at one level higher than that at which the locking spell was cast.
}
\spell{
	name = Golden Lasso, school = Charms, discipline = Kinesis, type = Focus, level =Novice, range =Close, incant = carpe rectractum, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =A lasso of golden light whips out from your wand\comma{} allowing you to initiate a {\it grapple} with the target using a Kinesis Spellcasting check\comma{} instead of your Strength. Target may resist following the usual grappling rules.
}
\spell{
	name = Reconstruction, school = Charms, discipline = Kinesis, type = Focus, level =Novice, range =Close, incant = reparo, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Fix a broken targeted object. 

Can only fix an object if it is reasonable that you could have repaired it with your bare hands (i.e. you cannot repair complex machinery without expert knowledge). Simple tasks (i.e. repairing glasses) work in a single turn\comma{} but repairing larger structures (i.e. a full stained glass window) require continued Focus.

You can use this to repair a magical object which is physically broken but has its magical nexus intact\comma{} but it cannot restore magic to an object that has lost its nexus.
}
\spell{
	name = Vertical Burst, school = Charms, discipline = Kinesis, type = Instant, level =Novice, range =Wandtip, incant = ascendio, noDur = 1, higher = This spell can launch targets an additional 5 metres \forEvery{}.,resist = Power, noBlock = 1, effect =Launches the target vertically upwards into the air or through water\comma{} up to a height of 10 metres in a matter of moments. A target may choose to Resist the effects of this spell\comma{} with advantage if they are heavier than the caster.

If a target hits a ceiling\comma{} they take 1d10 bludgeoning damage\comma{} and then if they fail to grab onto anything and fall back to the ground\comma{} they take 1d4 bludgeoning damage for every 2 metres fallen. 

This spell can be cast on the self.
}
\spell{
	name = Walk on Water, school = Charms, discipline = Kinesis, type = Ritual (2 minutes), level =Novice, range =Close, incant = iasus, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Up to 10 willing beings that you see gain the ability to walk on water and other liquid surfaces such as mud\comma{} snow\comma{} quicksand or lava without sinking or slowing down. Other environmental effects (such as heat) still apply.
}
}
 \spellBook{Reading People\comma{} Reading Minds}{Novice-level Telepathy}{
\spell{
	name = Bestial Ally, school = Divination, discipline = Telepathy, type = Instant, level =Novice, range =Sight, incant = nonparum, duration = 10 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =Establish a psychic connection with a friendly or {\it Charmed} beast. You may use an instantaneous action to communicate with the beast\comma{} and it will follow them if it would obey a spoken being. The beast can communicate simple emotions and images back through the link.
}
\spell{
	name = Detect Minds, school = Divination, discipline = Telepathy, type = Focus, level =Novice, range =Close, incant = psychopractum, noDur = 1, noHigh = 1, resist = Empathy (Passive), noBlock = 1, effect =You may search for any beings in possession of a Sapient mind in a radius of 4m\comma{} learning the distance and direction to every such being within range. 

You may then observe the mind of a target individual from a distance. Thought\minus{}detection is not an exact science\comma{} and you will only get a vague shape of their current thoughts and emotions \minus perhaps a quick flash of colour\comma{} a name\comma{} or a feeling of fear. On a successful (passive) Resist\comma{} target becomes aware of the process. 

You may attempt to reshape their surface level thoughts by asking questions\comma{} or showing them objects or images likely to trigger memories or strong feelings.
}
\spell{
	name = Divine Truth, school = Divination, discipline = Telepathy, type = Focus, level =Novice, range =Close, incant = veritas liberit, noDur = 1, noHigh = 1, resist = Deception, noBlock = 1, effect =Target a sapient being\comma{} on a failed Resist\comma{} the caster is notified by a glowing aura and a soft chime whenever the target makes a statement which they know to be false. The target is unaware of the casting of this spell unless they pass a DV 15 Observation check.
}
\spell{
	name = Telepathic Bond, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Novice, range =Wandtip, incant = conanimus, duration = 2 days,higher = The duration of this spell increases by 2 days for every additional level used to cast this spell.,noResist =1, noBlock = 1, effect =Form a mental connection between your mind and the mind of a willing target. You may then use this connection to communicate silently. Target must be within touching distance when the spell is cast\comma{} but the bond has no distance limit after that.
}
\spell{
	name = Trapsense, school = Divination, discipline = Telepathy, type = Focus, level =Novice, range =Close, incant = antidolus, noDur = 1, higher = The detection radius of this spell increases by 2m \forEvery{}.,noResist =1, noBlock = 1, effect =Discover any traps in a 4m radius. If successful\comma{} you may learn the location of all relevant traps\comma{} and their triggers (but not the effects which would result). 

As a telepathy spell which works on detection and interpretation of psychic energies\comma{} this spell can only detect devices\comma{} spells or altered environments which were {\bf deliberately} laid out with the intention of harming\comma{} hindering or altering upon being triggered. Hence\comma{} whilst a pitfall trap would show up to the effects of this spell\comma{} a floor that has been rendered unstable by decay does not\comma{} as there is no malicious psychic residue for the spell to detect\comma{} despite their similar physical result.
}
}
 \spellBook{The Dream Oracle}{Novice-level Temporal}{
\spell{
	name = All\minus{}seeing Eye, school = Divination, discipline = Temporal, type = Instant, level =Novice, range =Self, incant = orbis, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You may create an invisible\comma{} floating eye in front of you. You are telepathically linked to the eye\comma{} and see everything that the eye sees\comma{} and may use a minor action to instruct the eye to move up to 20m in any direction (including vertical). The Eye cannot pass through solid walls\comma{} but may squeeze through gaps as small as 4cm in diameter. 

The Eye can see into the Astral Realm and the Mortal Plain simultaneously.
}
\spell{
	name = Astral Caltrops, school = Divination, discipline = Temporal, type = Instant, level =Novice, range =Sight, incant = mobilum lespum, duration = 15 seconds,higher = For every additional spell\minus{}level dedicated to casting this spell\comma{} you may effect another individual within range.,resist = Conviction, noBlock = 1, effect =Weaken the barriers between the astral and mortal realms around a given individual\comma{} creating an environment which causes friction to the very soul.  The target acts as if any terrain they touch has caltrops\comma{} for the duration of the spell. Caltrops do 1d4 psychic damage for every metre moved by the target. Resist for half damage.
}
\spell{
	name = Crystal Gazing, school = Divination, discipline = Temporal, type = Ritual (1 minute), level =Novice, range =Self, incant = Gazing, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Gaze into your crystal ball\comma{} and ask a question of the cosmos. You will receive a yes or a no answer to any question you ask.
}
\spell{
	name = Detect Casting History, school = Divination, discipline = Temporal, type = Ritual (1 minute), level =Novice, range =Wandtip, incant = priori incantatem, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =Target a sapient being\comma{} or the wand belonging to a sapient being. On a failed resist\comma{} You instantly learn the last 5 spells that were cast\comma{} and the time at which they were cast.
}
\spell{
	name = Hunter\apos{}s Mark, school = Divination, discipline = Temporal, type = Instant, level =Novice, range =Sight, incant = venari, duration = 3 days,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =Attach a marker to the target which glows brightly in the astral realm. The Caster remains aware of the location of the target for the duration of the spell\comma{} or until the mark is removed by magical means.
}
}
 \spellBook{Easy Spells to Fool Muggles}{Novice-level Bewitchment}{
\spell{
	name = Calm Being, school = Illusion, discipline = Bewitchment, type = Instant, level =Novice, range =Close, incant = paxus, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =Calms the target down. Remove {\it Terrified} status\comma{} {\it Rage} effects and  other related phenomena from target such as a Berserker\apos{}s Battle Fury. An unwilling target can mitigate this effect by attempting to Resist.
}
\spell{
	name = Charm Creature, school = Illusion, discipline = Bewitchment, type = Instant, level =Novice, range =Close, incant = quorum, duration = 1 hour,higher = Target one additional being \forEvery{}.,resist = Logic, noBlock = 1, effect =Upon casting the spell\comma{} a pleasant aroma seems to suffuse around you\comma{} and you emit a calming aura. 

Target a non\minus{}sapient Beast in range. This being must succeed on a Resist check (with advantage if you are currently in combat with it)\comma{} or take the {\it Charmed} status effect and regard you as a valued ally. This effect is negated the next time the target takes damage from you or your allies.
}
\spell{
	name = Conceal Inscription, school = Illusion, discipline = Bewitchment, type = Instant, level =Novice, range =Close, incant = occulto, duration = 1 year,noHigh = 1, noResist =1, noBlock = 1, effect =Makes a message\comma{} drawing or marking on a surface invisible to the naked eye for the duration of the spell.
}
\spell{
	name = Doppelg\umlaut{a}ngers, school = Illusion, discipline = Bewitchment, type = Instant, level =Novice, range =Close, incant = effingo, duration = 1 minute,noHigh = 1, resist = Observation, noBlock = 1, effect =Upon casting this spell\comma{} your form appears to blur and shift until there are suddenly 4 identical copies of you standing in the space (you plus 3 duplicates). These duplicates perfectly mimic everything you do\comma{} shifting and moving so that it is incredibly difficult to keep track of who is who. 

When a being makes an accuracy check to target you\comma{} they must succeed on a Resist check to correctly identify which target is you\comma{} with the DV set by your Arcane Subjugation (AS) and how many doppelg\umlaut{a}ngers you have remaining:

\begin{rndtable}{ c c}
\bf Doppelg\umlaut{a}ngers & DV \\
3 &  AS + 3 \\
2 &  AS + 1 \\
1 &  AS
\end{rndtable}

On a failed Resist\comma{} they instead attack the duplicate. Duplicates have a Dodge value equal to your own and block value of 0\comma{} if any attack or spell hits them\comma{} they disintegrate. This effect only applies to being which rely on sight – if they have tremorsense\comma{} alien senses or can detect illusions with truesight they ignore all duplicates.
}
\spell{
	name = Implant Message, school = Illusion, discipline = Bewitchment, type = Ward, level =Novice, range =Wandtip, incant = occultus nuntius, duration = 100 years,higher = The ward can contain an additional 20 words \forEvery{}.,noResist =1, noBlock = 1, effect =Imbue a warded region with a message up to 20 words long. You can decide how this message is revealed: either spoken by a ghostly voice\comma{} or revealed through magical lettering\comma{} and the triggering condition for the message to be activated. 

The triggering condition can be chosen by the caster in any form they wish\comma{} though it is limited to an audible or visual trigger occuring within 5 metres of the ward.
}
}
 \spellBook{Cool Cantrips to Make You Crazy}{Novice-level Psionics}{
\spell{
	name = Illiteracy, school = Illusion, discipline = Psionics, type = Instant, level =Novice, range =Close, incant = illegibilus, duration = 1 minute,noHigh = 1, resist = Logic, noBlock = 1, effect =On a failed resist\comma{} the target\apos{}s brain becomes scrambled\comma{} and they temporarily lose the ability to read. 

This means they cannot book\minus{}cast\comma{} and if they attempt to focus on a bit of writing for more than 10 seconds\comma{} they take the {\it confused} status.
}
\spell{
	name = Psychic Crush, school = Illusion, discipline = Psionics, type = Instant, level =Novice, range =Close, incant = myalo synthis, noDur = 1, higher = \additional{1d8}{psychic},resist = Logic, noBlock = 1, effect =A great psychic force smashing to your opponent\comma{} overloading their psyche and brinigng them to the edge of insanity. 

The target takes 2d8 psychic damage\comma{} halved on a successful resist.
}
\spell{
	name = Violent Phantasms, school = Illusion, discipline = Psionics, type = Instant, level =Novice, range =Close, incant = umbra impetia, duration = 20 seconds,higher = \additional{1d6}{Psychic},resist = Conviction, negation = Blockable,effect =Purple ethereal energy seeks out the target and infiltrates their mind. The spell causes the target to believe that multiple phantasms are attacking them target\comma{} doing 1d6 psychic damage at the beginning of every  turn that the phantasms are active. 

Afflicted individuals may take a minor action at the end of each turn to re\minus{}perform the Resist check and end the effect.
}
}
 \spellBook{The Illusion of {\it Thin Air}}{Novice-level Conjuration}{
}
 \spellBook{A Compendium of Common Curses}{Novice-level Curse}{
\spell{
	name = Conjunctivitis, school = Maledictions, discipline = Curse, type = Instant, level =Novice, range =Close, incant = ranki, duration = 15 seconds,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =Causes the eyes of the victim to swell shut\comma{} effectively {\it blinding} them for the duration of the spell.
}
\spell{
	name = Dilute Blood, school = Maledictions, discipline = Curse, type = Instant, level =Novice, range =Close, incant = aenemius, duration = 1 miunte,noHigh = 1, resist = Vitality, noBlock = 1, effect =On a failed Resist\comma{} the target\apos{}s blood becomes thin and diluted\comma{} making them bleed profusely from even a minor cut. 

The target is considered Susceptible to slashing and piercing damage for the duration of the spell. 

This does not effect beings which do not have blood.
}
\spell{
	name = Disarm, school = Maledictions, discipline = Curse, type = Instant, level =Novice, range =Close, incant = expelliarmus, noDur = 1, noHigh = 1, resist = Strength, negation = Dodgeable,effect =A streak of white light launches from your wand. If it strikes the target\comma{}their muscles spasm and they must succeed on a Resist check\comma{} or else an object in the target\apos{}s hand is hurled 1d4 metres in a random direction.
}
\spell{
	name = Disorient, school = Maledictions, discipline = Curse, type = Instant, level =Novice, range =Sight, incant = confundo, duration = 15 seconds,noHigh = 1, resist = Willpower, noBlock = 1, effect =If target fails to resist\comma{} they take the {\it Confused} status for the duration of the spell.
}
\spell{
	name = Prevent Movement, school = Maledictions, discipline = Curse, type = Focus, level =Novice, range =Close, incant = impedimentia, duration = 1 minute,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =As this spell hits the target\comma{} a magical rune forms on the floor beneath their feet\comma{} forcing their feet to remain rooted to the ground. The target acquires the Trapped status effect. Their remaining appendages are still free to move\comma{} and the target can still speak – but they cannot move until the spell ends.
}
}
 \spellBook{Basic Hexes for the Busy \& Vexed}{Novice-level Hex}{
\spell{
	name = Acidic Burst, school = Maledictions, discipline = Hex, type = Instant, level =Novice, range =Wandtip, incant = ambustum, duration = 20 seconds,higher = The acid damage increase by 1d4 per turn for every additional spell\minus{}level dedicated to the casting.,resist = Observation, noBlock = 1, effect =Fills a cube of size 4m with an acidic cloud that does 1d4 acid damage once per turn to all beings which spent any time within the cloud this turn\comma{} until the end of the spell duration. Any being which is within the cloud at the moment it is summoned may attempt to Resist to negate the damage taken on their first turn within the cloud. 

In a confined space\comma{} such as a cramped tunnel or a sealed room\comma{} the duration of the spell is tripled.
}
\spell{
	name = Bat Bogey Hex, school = Maledictions, discipline = Hex, type = Instant, level =Novice, range =Sight, incant = vespernasum, duration = 10 seconds,higher = The spell produces an additional bat\comma{} and lasts fro an additional 10 seconds  \forEvery,noResist =1, negation = Blockable  and Dodgeable,effect =Causes the mucus in the target{\apos}s nose to gain sentience\comma{} take the form of a tiny bat\comma{} and then attack the target. 
Each bat\minus{}bogey does 1d6 points of acid damage per turn for the duration of the spell.
}
\spell{
	name = Bolt from the Blue, school = Maledictions, discipline = Hex, type = Instant, level =Novice, range =Close, incant = mirum, noDur = 1, higher = \additional{1d10}{Force},resist = Observation, noBlock = 1, effect =A bolt of magical energy strikes out at the target from a random direction\comma{} punishing the unaware. If the target fails to resist\comma{} they take 2d10 force damage.
}
\spell{
	name = Crackling Fist, school = Maledictions, discipline = Hex, type = Instant, level =Novice, range =Wandtip, incant = grothia, noDur = 1, higher = \additional{2d6}{Bludgeoning},noResist =1, negation = Blockable  and Dodgeable,effect =As you ram your wandtip into an opponent\comma{} an enormous fist\minus{}shaped field of energy explodes into the target\comma{} dealing 3d6 bludgeoning damage.
}
\spell{
	name = Shockwave, school = Maledictions, discipline = Hex, type = Instant, level =Novice, range =Self, incant = inpusla, noDur = 1, higher = \additional{1d6}{Concussive},resist = Acrobatics, noBlock = 1, effect =A shockwave emanates from the caster in every direction\comma{} for a radius of 3m\comma{} doing 2d6 concussive damage (halved on a successful Resist) to all beings caught in the radius. Beings which fail to resist must roll a 1d4. On a 1\comma{} they are knocked prone.
}
}
 \spellBook{Cures\comma{} Cantrips and Coughs}{Novice-level Healing}{
\spell{
	name = Celestial Burst, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Sight, incant = sol maxima, noDur = 1, higher = \additional{2d4}{Celestial},resist = Power, noBlock = 1, effect =A bolt of magic is released from the end of your wand\comma{} rocketing towards a targeted region. The bolt explodes on contact with any solid or astral objects in its path\comma{} releasing a searing white light that does 4d4 Celestial Damage in a 5m radius\comma{} halved on a successful Resist. Beings which are immune to Celestial damage are healed by 2 points instead.
}
\spell{
	name = Checkup, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Wandtip, incant = dispungo, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Enquire as to the health status of the target\comma{} find out their remaining HP\comma{} as well as any status effects\comma{} illnesses\comma{} curses or diseases they currently posses.
}
\spell{
	name = Clear Airways, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Wandtip, incant = Anapneo, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =The target has their airways cleared\comma{} allowing them to breath freely and negating any choking effects.
}
\spell{
	name = Endure Environment, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Wandtip, incant = omnium, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Target is protected from the ravages of the environment\comma{} and hence can exist in temperatures in the range \minus{}40  to 50 celsius\comma{} and is unaffected by heavy rain and other weather phenomena. The target is not protected against fire and cold damage\comma{} however.
}
\spell{
	name = Heal Wounds, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Wandtip, incant = episkey, noDur = 1, higher = Heal an additional 1d8 HP \forEvery.,noResist =1, noBlock = 1, effect =Heal the target for 2d8 HP and remove any minor status effects such as burns\comma{} hypoxia and confusion.

If target has a serious wound (i.e. a broken bone or a serious burn)\comma{} this spell cannot heal beyond 75\% their maximum health.
}
\spell{
	name = Stasis Field, school = Recuperation, discipline = Healing, type = Instant, level =Novice, range =Want, incant = tempocessus, duration = 10 days,noHigh = 1, noResist =1, noBlock = 1, effect =A non\minus{}living target is unaffected by the flow of time for the duration of the spell\comma{} and does not rot or otherwise decay. If the target is the body of a being\comma{} this being cannot become one of the Unliving.
}
}
 \spellBook{Self\minus{}Defensive Spellwork}{Novice-level Warding}{
\spell{
	name = Beartrap, school = Recuperation, discipline = Warding, type = Ward, level =Novice, range =Close, incant = ursa dentes, duration = 5 days,higher = The ward gains an additional 1d8 piercing damage for every additional spell\minus{}level dedicated to casting it.,resist = Acrobatics, noBlock = 1, effect =Ward a region of a flat surface (Such as the walls or the floor) which creates an invisible trap of 2m in radius. When a being crosses over the threshold\comma{} the ward slams shut\comma{} doing 3d8 worth of piercing damage and applying the Trapped status effect. A successful resist takes half damage and nullifies the Trapping effect.
}
\spell{
	name = Create Trap, school = Recuperation, discipline = Warding, type = Ward, level =Novice, range =Wandtip, incant = dolus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Combine a magical ward with one of your existing spells. After casting the trap spell\comma{} cast the effect\minus{}spell to imbue the trap with that effect. 
If successful\comma{} creates a hidden magical trap of radius 50cm on any solid surface.

When an entity touches the warded region\comma{} the trap explodes\comma{} releasing the magical effect of the second spell you cast.
}
\spell{
	name = Halting Field, school = Recuperation, discipline = Warding, type = Ward, level =Novice, range =Wandtip, incant = stabit vallio, duration = 1 day,noHigh = 1, resist = Speed, noBlock = 1, effect =Erects a circular field 1m in radius anywhere within 2m of the caster. 

This field halts any physical object that touches or passes through it. Objects in flight drop to the ground\comma{} as if the {\it Halt} spell had been cast on them. Beings attempting which touch the field must Resist or have their speed halved this turn cycle.
}
\spell{
	name = Reinforce Shield, school = Recuperation, discipline = Warding, type = Focus, level =Novice, range =Wandtip, incant = praesidium, noDur = 1, higher = This spell restores an additional 1d8 strength to shields and wards for every additional level dedicated to the spell.,noResist =1, noBlock = 1, effect =Restore the strength of a target shield or magical ward by 1d8 points per turn that this spell is maintained. Cannot restore the strength to more than the original level.
}
\spell{
	name = Runic Shield, school = Recuperation, discipline = Warding, type = Ward, level =Novice, range =Wandtip, incant = scutum, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Choose a Damage Type. Target is Resistant to that damage type for the duration of the spell. Each individual may only have one Runic Shield active at a time.
}
}
 \spellBook{A Beginner\apos{}s Guide to Transfiguration}{Novice-level Alteration}{
\spell{
	name = Alter Size, school = Transfiguration, discipline = Alteration, type = Instant, level =Novice, range =Close, incant = engorgio/reducio, duration = 5 minutes,noHigh = 1, resist = Power, noBlock = 1, effect =Multiply or divide the size of a target by 2 on a failed resist. If the target is in combat with you\comma{} it takes advantage on the Resist. 

Any clothing or items carried by the target is also transformed along with them. Physical weaponry gains or loses 1d10 damage to accommodate their new size (cannot go below one). 

If you attempt to enlarge an object or being such that it no longer fits in the region\comma{} the object takes 6d10 bludgeoning damage.
}
\spell{
	name = Fabricate Object, school = Transfiguration, discipline = Alteration, type = Instant, level =Novice, range =Close, incant = facere, noDur = 1, higher = The mass of raw material which you can manipulate is multiplied by 10 \forEvery{},noResist =1, noBlock = 1, effect =You manipulate up to 1kg of raw material and manipulate and arrange it to a new\comma{} manufactured form. 

You can only produce an object that you could reasonably produce yourself given enough time\comma{} so this spell can assemble a pile of wood into a bridge\comma{} but without incredibly intensive training you could not assemble a smartphone.

The effects of this spell are permanent\comma{} and do not wear off – to undo the effects you would need to physically destroy the object.
}
\spell{
	name = Featherweight, school = Transfiguration, discipline = Alteration, type = Instant, level =Novice, range =Wandtip, incant = pluma gravitas, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Make a targeted object lighter and easier to pick up. 

In general\comma{} this would make a Medium object become Light\comma{} a Heavy object to become Medium\comma{} and so on.
}
\spell{
	name = Stoneskin, school = Transfiguration, discipline = Alteration, type = Instant, level =Novice, range =Wandtip, incant = lapis pellium, duration = 5 minutes,higher = When cast as a higher level spell\comma{} the Block statistic increases by 2 (and \attFin{} decreases by one) for every additional spell levels dedicated to this spell.,noResist =1, noBlock = 1, effect =Increase the target{\apos} Block statistic by +5 by transfiguring their skin into solid stone. Target suffers a penalty to their \attFin{} (and hence Dodge) statistic equal to half the block bonus as their skin stiffens and hardens.
}
\spell{
	name = Thick Air, school = Transfiguration, discipline = Alteration, type = Focus, level =Novice, range =Close, incant = temporio, duration = 1 minute,higher = You may target an additional individual \forEvery{}.,resist = Speed, noBlock = 1, effect =Transforms the air around the 1d6 targets into a thick soup. Each targeted being must succeed on a Resist check or reduce their movement speed to 50\% of its normal value for the duration of the spell.
}
}
 \spellBook{The Illusion of {\it Thin Air}}{Novice-level Conjuration}{
\spell{
	name = Bestial Summons, school = Transfiguration, discipline = Conjuration, type = Instant, level =Novice, range =Wandtip, incant = dicobessia, duration = 10 minutes,higher = Double the number of snakes summoned \forEvery,noResist =1, noBlock = 1, effect =Summon a Non\minus{}Sapient Beast (or a number of beasts) into existence in a space that you can see within range. 

You have a number of `points’ equal to the spell level used to cast this spell – the maximum MoM rating of any beast you can summon is equal to this value. Alternatively you may distribute these `points’ by summoning several lower\minus{}rated creatures\comma{} as long as the total MoM rating does not exceed the spell level used (for this purpose a rating of 0 is assigned a value of 0.5). At second level you could summon 1 rating\minus{}II creature\comma{} 2 rating\minus{}I creatures or 4 rating\minus{}0 creatures. At third level you could summon a rating III creature or 1 rating\minus{}II creature and a rating\minus{}I creature\comma{} and so on. 

Within this restriction\comma{} you may choose the kind of beast from any that you have previously encountered or studied in detail. The summoned creatures will obey your commands as if they were well\minus{}trained pets and are considered friendly towards you and your allies. If no command is given\comma{} they will act as a normal wild animal and retaliate if attacked\comma{} or run away if outmatched.
}
\spell{
	name = Binding Ropes, school = Transfiguration, discipline = Conjuration, type = Instant, level =Novice, range =Close, incant = incarcerous, duration = 5 minutes,noHigh = 1, resist = Strength, noBlock = 1, effect =Conjures thick ropes from thin air\comma{} to wrap around the target\comma{} immobilising them if they fail to Resist\comma{} giving them the {\it Trapped} status effect. 

Target may Resist once per turn to break free.
}
\spell{
	name = Conjure Object, school = Transfiguration, discipline = Conjuration, type = Ritual (30 seconds), level =Novice, range =Close, incant = siestum, duration = 1 hour,higher = You may double the maximum mass and monetary value of a conjured object \forEvery{}.,noResist =1, noBlock = 1, effect =Produce an inanimate\comma{} non\minus{}living object out of thin air\comma{} in the palm of your outstretched hand. This object cannot exceed 1kg in weight\comma{} or \sickle{10} in value. 

You must be very familiar with an object in order to conjure it \minus{} enough to describe what the object looks like in great detail. 

You cannot conjure a magical item\comma{} and if you attempt to summon a part of a living being (i.e. the leaf from a tree )\comma{} you can only summon a crude facsimile. Conjured objects are of a noticeably lower quality than a real version. Conjured objects that are required to match a specific pattern\comma{} such as a key to fit a specific lock\comma{} are almost always insufficient unless you are intimitely familiar with the base design.
}
\spell{
	name = Eternal Flame, school = Transfiguration, discipline = Conjuration, type = Instant, level =Novice, range =Wandtip, incant = bangala, duration = Infinite,noHigh = 1, resist = Reflex, noBlock = 1, effect =Summon a minor fire spirit. If you have a glass container\comma{} you may use it to trap the spirit\comma{} whereupon it acts as a dim torch (bright light 1m\comma{} dim light 4m) and as a heat source sufficient to keep one person comfortable in arctic conditions. If the spirit is not trapped\comma{} a random being within 5m radius of caster takes 4d6 fire damage\comma{} halved on a successful Resist.
}
\spell{
	name = Smokescreen, school = Transfiguration, discipline = Conjuration, type = Instant, level =Novice, range =Close, incant = fumus insterio, duration = 20 seconds,noHigh = 1, noResist =1, noBlock = 1, effect =Thick white smoke issues from the end of your wand\comma{} filling a sphere 10m in radius\comma{} giving a Severe obscuration for all sightlines which pass through this region. 

In a confined area\comma{} duration is doubled.
}
}
 \spellBook{Necromancy: A Misunderstood Skill}{Novice-level Necromancy}{
\spell{
	name = Blight, school = Dark Arts, discipline = Necromancy, type = Instant, level =Novice, range =Close, incant = thanatos, noDur = 1, higher = The radius of this spell is doubled for every additional spell level used to cast it.,resist = Vitality, noBlock = 1, effect =A cylinder of necrotic energy extends outwards from you in a radius of 10m and height 100 metres. All simple plants within range die instantly\comma{} and all other living beings take 2d8 necrotic damage (halved on a successful resist)
}
\spell{
	name = Drain Life, school = Dark Arts, discipline = Necromancy, type = Instant, level =Novice, range =Wandtip, incant = tenebrosa sudarium, noDur = 1, higher = Increase the draining effect by 1d8 \forEvery.,resist = Willpower, noBlock = 1, effect =Channel vampric energy through your wand\comma{} to drain the life from a helpless individual. Drain 2d8 HP from an {\it Incapacitated} target (halved on a successful Resist)\comma{} and restore half of this value to your own HP.
}
\spell{
	name = Fatiguing Force, school = Dark Arts, discipline = Necromancy, type = Instant, level =Novice, range =Sight, incant = dulcis mortem, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =A wave of exhaustion washes over your target. They must succeed on a Resist check\comma{} or increase their exhaustion level by 1.

This spell cannot be used to increase the exhaustion level above 4th.
}
\spell{
	name = Hellish Light, school = Dark Arts, discipline = Necromancy, type = Instant, level =Novice, range =Close, incant = lumos infernalis, duration = 1 hour,noHigh = 1, resist = Logic, noBlock = 1, effect =By drawing on unearthly powers\comma{} you summon an eerie greenish\minus{}yellow light to illuminate an area 10m in radius around the point of casting. This light is bright\comma{} but appears to emanate from both everywhere\comma{} and nowhere – and casts no shadows. 

All beings besides the caster must succeed on a Logic Resist check the first time they enter the illuminated region\comma{} or become {\it Distracted} next turn cycle.
}
\spell{
	name = Necrosis, school = Dark Arts, discipline = Necromancy, type = Instant, level =Novice, range =Sight, incant = carnes mortis, noDur = 1, higher = \additional{1d10}{necrotic},noResist =1, negation = Blockable,effect =A bolt of sickly green energy crackles into your opponent\comma{} seeking to destroy their life force and spreading evil and decay. Do 2d10 necrotic damage.
}
}
 \spellBook{An A\minus{}Z of Spooky Spells}{Novice-level Occultism}{
\spell{
	name = Abyssal Fluid, school = Dark Arts, discipline = Occultism, type = Focus, level =Novice, range =Close, incant = sucus infernum, noDur = 1, higher = Gain an additional 1d8 necrotic damage for every additional spell\minus{}level used to cast this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =A pencil\minus{}thin jet of inky black fluid emerges from the end of your wand for as long as Focus is maintained\comma{} reaching in an arc up to 2m away. All targets touched by the fluid take 2d8 necrotic damage this turn\comma{} and half as much again on their next turn.
}
\spell{
	name = Demonic Command, school = Dark Arts, discipline = Occultism, type = Instant, level =Novice, range =Close, incant = ausculto profanus, duration = 30 seconds,noHigh = 1, resist = Conviction, noBlock = 1, effect =You issue a single command to a demonic being\comma{} and force it to obey you. On a failed resist\comma{} the targeted demon must obey your command for the duration of the spell\comma{} or until the command is completed. 

If the demon is currently under the thrall of another spellcaster\comma{} either through the {\it Demoncall} spell\comma{} or another {\it Demonic Command} (or similar)\comma{} both the demon and the spellcaster perform the resist – if either succeeds\comma{} the command does not take hold.
}
\spell{
	name = Eldritch Knowledge, school = Dark Arts, discipline = Occultism, type = Ritual (30 minutes), level =Novice, range =Self, incant = vetitum scenticus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Attune your mind to the Eldritch Domains. The Demons of the Deep will answer one of your questions\comma{} but the answers might drive you mad.
The question must be said out loud for all to hear\comma{} but the answer may be written down and passed to your privately.
}
\spell{
	name = Shadowsight, school = Dark Arts, discipline = Occultism, type = Focus, level =Novice, range =Self, incant = ivertus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Invert your vision \minus{}\minus{} pure darkness is considered bright light\comma{} and bright light is considered pure darkness for as long as the spell is maintained.
}
\spell{
	name = Will\minus{}O\apos{}\minus{}the\minus{}Wisp, school = Dark Arts, discipline = Occultism, type = Instant, level =Novice, range =Close, incant = desuno, noDur = 1, higher = \additional{1d8}{fire and necrotic},resist = Willpower, negation = Blockable,effect =A small burst of rainbow light dances from the end of your wand\comma{} and streaks towards your opponent\comma{} dealing 1d8 fire damage and an additional 1d8 necrotic damage when it makes contact.

The target must then Resist\comma{} or take the {\it Distracted} status next turn.
}
}
 \spellBook{Further Elemental Studies}{Adept-level Elemental}{
\spell{
	name = Broiling Beam, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Sight, incant = flagrante, duration = 3 turns,noHigh = 1, resist = Speed, noBlock = 1, effect =Causes a target object to heat up to unimaginable temperatures\comma{} melting and deforming plastics or rubber\comma{} and igniting objects such as papers. More resilient materials such as stone or metal retain the heat unchanged\comma{} though they may glow red hot. 

If the object is not imediately destroyed\comma{} every time the target object is touched it deals 2d8 +4 fire damage\comma{} halved on a successful Resist. The target must drop the object (if held)\comma{} or otherwise attempt to remove themselves from the source of heat before committing any other actions. A being may attempt a second Willpower Resist to nullify this effect\comma{} and remain in contact with the object\comma{} though this grants the {\it Burned: Severe} status effect.
}
\spell{
	name = Cloudmove, school = Charms, discipline = Elemental, type = Ritual (30 minutes), level =Adept, range =Sight, incant = syneffo, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Perform a ritual to attune yourself to the weather and climate around you. By gently altering the wind\comma{} the pressure and the humidity you can subtly alter the weather in a 1km radius. You may push a raincloud out of the way to clear the skies\comma{} summon a light drizzle\comma{} or alleviate the worst of a storm. 

This spell cannot be used for large\minus{}scale weather manipulation \minus{} you can only slightly alter what is already present.
}
\spell{
	name = Fireball, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Sight, incant = confringo, noDur = 1, higher = \additional{2d6}{Fire},noResist =1, negation = Blockable  and Dodgeable,effect =Launches a fireball at the target\comma{} which explodes on contact for 4d6 Fire Damage on all targets within 2m of the target. This effect is negated on a successful dodge\comma{} and halved on a successful block.
}
\spell{
	name = Floodlight, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Wandtip, incant = caecus, duration = White beam,noHigh = 1, resist = Speed, noBlock = 1, effect =Direct a brilliant beam of light from the tip of your wand\comma{} illuminating a cone 10m  in front of you with Bright light\comma{} and dim light a further 10m. If a target is illuminated by the beam and fails to resist\comma{} they are blinded for 2 turns.
}
\spell{
	name = Freeze Fluids, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Close, incant = glacius, noDur = 1, higher = When cast as a higher level spell\comma{} you may double the volume of water you can freeze\comma{} and add an additional 1d10 Cold damage to the blast.,resist = Vitality, noBlock = 1, effect =Your wand emits a blast of air so cold it makes even the caster\apos{}s fingers feel numb.

This blast may freeze a body of water up equal in size to a cube with sides of length 2m\comma{} or when used on an individual\comma{} the freezing blast does 3d10 cold damage\comma{} halved on a successful Resist.
}
\spell{
	name = Icicle Barrage, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Close, incant = krystallium, noDur = 1, higher = Gain an additional 2 shards \forEvery{},noResist =1, negation = Blockable  and Dodgeable,effect =At your command 3 razor sharp shards of ice fling themselves at your target\comma{} performing an accuracy check for each. 

Each shard does 1d8 piercing damage and 1d8 cold damage.
}
\spell{
	name = Lightning Bolt, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Sight, incant = baubilious, noDur = 1, higher = \additional{1d12}{Electrical},resist = Vitality, negation = Blockable  and Dodgeable,effect =Releases a bolt of lightning from the end of your wand. 
Lightning can initiate fires\comma{} provide electrical current or can be used directly in combat\comma{} where it deals 3d12 electric damage. Targets struck by lightning must succeed in a Resist check\comma{} or be blinded and deafened next turn.
}
\spell{
	name = Stonemeld, school = Charms, discipline = Elemental, type = Ward, level =Adept, range =Self, incant = intermescio, duration = 8 hours,noHigh = 1, noResist =1, noBlock = 1, effect =You step into a stone object or surface large enough to fully contain your body\comma{} melding yourself and all the equipment you carry with the stone for the Duration. Using a movement action\comma{} you step into the stone at a point you can touch. Nothing of your presence remains visible or otherwise detectable by nonmagical means.

While merged with the stone\comma{} you can't see what occurs outside it\comma{} and any Perception checks you make to hear sounds outside it are made with disadvantage. You remain aware of the passage of time and can cast Spells on yourself while merged in the stone. You can use a movement  actionto leave the stone where you entered it\comma{} which ends the spell. You otherwise can't move.

Minor physical damage to the stone doesn't harm you\comma{} but its partial destruction or a change in its shape (to the extent that you no longer fit within it) expels you and deals 6d6 bludgeoning damage to you. The stone's complete destruction (or Transmutation into a different substance) expels you and deals 50 bludgeoning damage to you. If expelled\comma{} you fall prone in an unoccupied space closest to where you first entered.
}
\spell{
	name = Subsoil Construct, school = Charms, discipline = Elemental, type = Instant, level =Adept, range =Close, incant = elus, duration = 1 hour,higher = The animating magic increases in power with each additional spell level: the HP increased by 20 and the damage inflicted increases by 2d6.,noResist =1, negation = Blockable  and Dodgeable,effect =Breath a limited amount of intelligence into a region of earth 1m in radius. This region of earth may rearrange itself into a crude object such as a giant hand\comma{} or a waving club\comma{} which follows a single simple order given to it on its creation. The caster may use a minor action to give another order\comma{} if they are within hearing range of the animated construct.

The animated earth can attack\comma{} move and attempt to grapple targets in order to complete its order. The earth has a movement speed of 5m per round\comma{} but can only move through areas of exposed earth (or grass\minus{}covered earth\comma{} for example). When performing attacks or attempting grapples\comma{}  the animated Earth has a Strength modifier equal to your Elemental Spellcasting modifier\comma{} and it can attack a creature it has grappled without letting it go. Attacks by the animated Earth deals damage equal to 2d6 + Strength modifier. 

The earthen construct can absorb 40 points of damage\comma{} before the magic holding it together dissipated and the spell effect ends.
}
\spell{
	name = Wind Tunnel, school = Charms, discipline = Elemental, type = Focus, level =Adept, range =Close, incant = vente polus, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =Summon a powerful blast of wind from your wand\comma{} in a line 20m long and 2m wide. Every being which is in this region at the beginning of each cycle\comma{} or enters it during the course of the cycle\comma{} must Resist\comma{} or be blown to the end of the line. Those that succeed have their movement speed halved when moving towards you. 

Any unsecured objects or are also flung to the end of the line\comma{} and any open flames are extinguished.
}
}
 \spellBook{Achievements in Charming}{Adept-level Kinesis}{
\spell{
	name = Dampen Deadly Drop, school = Charms, discipline = Kinesis, type = Instant, level =Adept, range =Sight, incant = sofus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Painlessly break the fall of the target from any height up to 50 metres.
}
\spell{
	name = Merlin\apos{}s Stutter, school = Charms, discipline = Kinesis, type = Ritual (30 minutes), level =Adept, range =Self, incant = anavos, duration = 1 week,higher = Gain an additional token \forEvery{}.,noResist =1, noBlock = 1, effect =You imbue three small disks of glass with magical power. At any point in the next week you may use a Reaction to crush one of these tokens\comma{} which teleports you randomly to another location within sight.
}
\spell{
	name = Sonic Splinter, school = Charms, discipline = Kinesis, type = Focus, level =Adept, range =Wandtip, incant = tootanus focum, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Focus an ultrasonic vibration into a single target object or being made of crystal\comma{} class\comma{} ceramic or porcelain\comma{} and cause it to break. The tip of your wand must touch the target for the duration of the spell\comma{} and the spell gets stronger the longer it is maintained. 

In the first turn objects 5kg or lighter shatter\comma{} in the second turn\comma{} 10kg objects shatter\comma{} and so on.
}
\spell{
	name = Spatial Swap, school = Charms, discipline = Kinesis, type = Instant, level =Adept, range =Close, incant = allaxo, noDur = 1, noHigh = 1, resist = Power, noBlock = 1, effect =Target two objects within range\comma{} and magically switch the two objects in space. 

If either of the objects is a sentient being\comma{} they may each attempt to Resist. If even one resist attempt is successful\comma{} the spell fails. The spell also fails if the swapping would cause one of the objects to phase through other matter\comma{} or enter into a region they do not physically fit.
}
\spell{
	name = Spidercrawl, school = Charms, discipline = Kinesis, type = Instant, level =Adept, range =Sight, incant = aranerum fiducia, duration = 5 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =Imbue the target with the ability to traverse up vertical walls using their hands and feet. Climbing movement checks are half the speed of a regular movement check.
}
\spell{
	name = Summon From Afar, school = Charms, discipline = Kinesis, type = Focus, level =Adept, range =Self, incant = accio, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Summon non\minus{}shielded objects within a 500m radius. They will fly to your current position at a speed of 100m per cycle as long as Focus is maintained. Objects must be light enough that the caster could reasonably pick it up.
}
}
 \spellBook{Detection is the Best Defense}{Adept-level Telepathy}{
\spell{
	name = Commune with Nature, school = Divination, discipline = Telepathy, type = Ritual (5 turns), level =Adept, range =Self, incant = naturus amicus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You tap into the consciousness that binds all living things together\comma{} and receive information about the natural order of things in the vicinity. Outdoors\comma{} the range is 3km\comma{} whilst underground it is only 100m. Spell fails in artificial environments such as towns. You instantly learn any 3 three bits of information about \begin{spellitemize}\item terrain and bodies of water \item nearby buildings \item abundant plants\comma{} animals or minerals \item frequent visitors\comma{} both sapient and bestial \end{spellitemize}
}
\spell{
	name = Ethereal Tag, school = Divination, discipline = Telepathy, type = Instant, level =Adept, range =Sight, incant = signum, duration = 2 minutes,higher = The bonus to accuracy increases by 1 \forEvery{}.,resist = Stealth, noBlock = 1, effect =If the target fails to Resist\comma{} place a mystical marker on the target which enables your allies to strike more accurately at them. Target takes disadvantage on Stealth checks and attacks against them are performed with a +1 bonus to accuracy.
}
\spell{
	name = Psychic Immersion, school = Divination, discipline = Telepathy, type = Focus, level =Adept, range =Self, incant = tevidius, noDur = 1, noHigh = 1, resist = Deception, noBlock = 1, effect =Your eyes are imbued with a mystical energy which allows you to see the web of psychic energy stretching between all living beings. 

Whilst this effect is active\comma{} you can see a golden thread connecting any beings which possess a `psychic link’\comma{} such as that between a summoned being or a familiar and their master\comma{} as well as any enthralling or {\it Charm} effects which are being supported by magical energy. You can also see if any beings are connected by a {\it Telepathic Bond} or similar effects\comma{} and any spells which deal psychic damage show up in your vision as a bright white lance coming from the attacker towards the victim. 

Individuals may attempt to hide or obfuscate their links by performing a successful Resist check\comma{} though the caster knows that something is being hidden from them.
}
\spell{
	name = Speak in Tongues, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Adept, range =Self, incant = lingua maxima, duration = 4 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =By meditating for 5 minutes\comma{} you may understand and speak the language of a willing target individual. Target must be a sapient being\comma{} or otherwise able to speak at least one language.
}
}
 \spellBook{The Future is an Open Book (And so is This)}{Adept-level Temporal}{
\spell{
	name = Astral Onslaught, school = Divination, discipline = Temporal, type = Instant, level =Adept, range =Sight, incant = devonus, noDur = 1, higher = This spell gains an additional 1d6 points of Celestial damage for every additional spell\minus{}level used to cast it.,noResist =1, negation = Blockable  and Dodgeable,effect =By focussing your inner energies\comma{} you are able to summon an ethereal weapon to strike at enemies with a presence on other planes of existence. Do 5d6 Celestial damage to targets in both the material world\comma{} and the astral realm.
}
\spell{
	name = Foresight, school = Divination, discipline = Temporal, type = Instant, level =Adept, range =Wandtip, incant = providentia, duration = 1 turn,noHigh = 1, noResist =1, noBlock = 1, effect =By predicting the flow of time\comma{} you can give the target the ability to make moves without thinking: give the target an extra major action next turn. Each target can only get this boost once per day.
}
\spell{
	name = Glimpse Future, school = Divination, discipline = Temporal, type = Instant, level =Adept, range =Self, incant = posterus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Get a fleeting glimpse into the future. Choose one of the following:
\begin{spellitemize}
\item + 4 bonus to block {\bf or} dodge next turn
\item +4  bonus to accuracy checks made next turn
\end{spellitemize}
}
\spell{
	name = Locate Being, school = Divination, discipline = Temporal, type = Instant, level =Adept, range =Self, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =After casting this spell\comma{} you must shout a description or the name of a living being you are searching for. If you are within 1km of the being\comma{} you gain a snapshot of the object you are searching for\comma{} and the direction in which it is moving. 

If you are looking for a specific being\comma{} you must be familiar with them (i.e. have seen the\comma{} up close at least once). Alternatively\comma{} you may describe a class of being (i.e. a horklump)\comma{} and the spell will find the nearest such object. 

This spell fails if there is no such being within range\comma{} if the object is protected by any kind of magical ward\comma{} or if the being no longer lives.
}
\spell{
	name = Move Through Time, school = Divination, discipline = Temporal, type = Focus, level =Adept, range =Close, incant = qortina, noDur = 1, higher = The speed at which objects tumble through time doubles \forEvery{}.,noResist =1, noBlock = 1, effect =Target a non\minus{}sapient being or object within range\comma{} and send it spinning forward or backward in time by 1 days per second. Plants will grow and age\comma{} food will rot and wilt (or\comma{} rotten food may become fresh again)\comma{} and weapons will rust and grow dull.
}
\spell{
	name = Obfuscation, school = Divination, discipline = Temporal, type = Ritual (1 hour), level =Adept, range =Wandtip, incant = obscuras, duration = 1 week,noHigh = 1, noResist =1, noBlock = 1, effect =All attempts to identify\comma{} locate\comma{} scry on\comma{} or otherwise detect the target using magical means fail.
}
}
 \spellBook{Jiggery Pockery \& Hocus Pocus}{Adept-level Bewitchment}{
\spell{
	name = Bedazzle, school = Illusion, discipline = Bewitchment, type = Ward, level =Adept, range =Wandtip, incant = chameleo, duration = 1 day,higher = When cast as a higher level spell\comma{} choose one additional target \forEvery{}.,resist = Observation, noBlock = 1, effect =This spell creates a ward on the target\comma{} which produces a beddazzling and befuddling field\comma{} which causes eyes to simply slide off from the warded region without the brain properly processing it\comma{} rendering the warded target almost perfectly invisible. 

This spell only works on Sapient and Non\minus{}Sapient beings and beasts with a (relatively advanced) neural system. Alien and Ineffable beings such as dementors and poltergeists do not have a brain which this field can confuse. 

If the target fails to Resist\comma{} they cannot observe or otherwise detect the warded region\comma{} as if it had become perfectly invisible. If the hidden target interacts with a being in any way\comma{} the spell is broken and they can detect them once again.
}
\spell{
	name = Captivate, school = Illusion, discipline = Bewitchment, type = Instant, level =Adept, range =Wandtip, incant = meamicus, duration = 1 minute,higher = Target one additional being \forEvery{}.,resist = Conviction, noBlock = 1, effect =You attempt to convince a targeted sapient being that you are an ally of theirs. Target a humanoid\comma{} gigantoid or imp in range. This being must succeed on a Resist check (with advantage if you are currently in combat with it)\comma{} or take the {\it Charmed} status effect and regard you as a valued ally. This effect is negated the next time the target takes damage from you or your allies.
}
\spell{
	name = Illusory Construct, school = Illusion, discipline = Bewitchment, type = Focus, level =Adept, range =Close, incant = lux maxima, noDur = 1, higher = The size of the illusory region (i.e. the side\minus{}length of the bounding cube) doubles \forEvery{}.,resist = Attention, noBlock = 1, effect =Create an illusion\comma{} a construction of light\comma{} sound and smells\comma{} in a region of space within range. The image occupies a space no larger than a cube with sides 3m in length\comma{} and the form can be anything that the caster can clearly envisage. 

Outside of its non\minus{}corporeal nature\comma{} the illusion seems perfectly real\comma{} and can produce appropriate sounds\comma{} smells and temperature (though not enough to cause harm). Whilst the caster maintains focus\comma{} the illusion (and the space it ocucpies) may be manipulated and altered to mimic the illusion walking\comma{} talking and taking other actions. 

If the caster chooses to end the spell as an instantaneous action\comma{} they may leave the illusion with a simple command which it will continue to execute for the remainder of the duration. If the spellcaster\apos{}s focus is broken unwillingly\comma{} however\comma{} the illusion dissolves. The commands left to the illusion must be simple\comma{} and\comma{} for example\comma{} the illusion loses the ability to hold a conversation or otherwise actively react to its surroundings\comma{} though you could direct the illusion to repeat a single phrase over and over\comma{} or to walk in a particular direction. 

An observer may determine that the illusion is not real by performing a Resist check as a major action\comma{} or by attempting to physically interact with it.
}
\spell{
	name = Sleep, school = Illusion, discipline = Bewitchment, type = Instant, level =Adept, range =Close, incant = somnus, duration = 1 hour,noHigh = 1, resist = Vitality, negation = Blockable,effect =If a living target fails to resist the drowsiness that washes over them\comma{} they enter into a deep slumber\comma{} taking the {\it Asleep} status effect and falling {\it Prone}. 

The being remains asleep until they take damage\comma{} or an ally takes a major action to shake them awake.
}
\spell{
	name = Suggestion, school = Illusion, discipline = Bewitchment, type = Instant, level =Adept, range =Close, incant = facite, duration = 2 hours,noHigh = 1, resist = Willpower, noBlock = 1, effect =You speak a sentence or two to a creature which can hear and understand you which suggest a simple course of action\comma{} and imbue those words with compelling magic\comma{} which makes the creature want to follow the command. 

The suggestion must be worded in a manner that the creature would find reasonable and compelling – courses of action which inevitably and obviously lead to harm would cause the spell to fail\comma{} as would actions that are obviously incongruent to the situation they are in\comma{} unless carefully worded. 

On a failed Resist\comma{} the target will willingly attempt to carry out this action to the best of its abilities. If the action is completed\comma{} or becomes impossible (i.e. a building you told them to enter is destroyed)\comma{} before the spell duration is completed\comma{} the spell ends prematurely\comma{} but otherwise they will continue attempting to carry out the suggested course of action. When the spell effect ends\comma{} the target may be confused as to why they listened to you\comma{} but will not automatically know that they have been enchanted. 

The spell effect ends if the caster or their allies damage the target.
}
}
 \spellBook{Your Mind\comma{} the Weapon}{Adept-level Psionics}{
\spell{
	name = Babbling, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Close, incant = longardo, duration = 2 minutes,noHigh = 1, resist = Willpower, noBlock = 1, effect =On a failed Resist\comma{} the target begins babbling incoherently and without control. 

For the duration of the spell\comma{} whenever the target wishes to speak or cast a spell with a verbal component they must successfully Resist to do so without babbling over their intended phrase.
}
\spell{
	name = Drain Fortitude, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Close, incant = delcrus, noDur = 1, higher = \additional{2d6}{Fatigue},resist = Willpower, noBlock = 1, effect =If the target fails to Resist\comma{} you impose your will over them\comma{} doing  2d6 Fatigue damage to the target.
}
\spell{
	name = Fury, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Sight, incant = irafors, duration = 30 seconds,noHigh = 1, resist = Empathy, noBlock = 1, effect =Target performs a Resist check\comma{} if they fail\comma{} target flies into a mindless rage and begins attacking all those around them.
}
\spell{
	name = Shatter Illusions, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Close, incant = conlidus, noDur = 1, higher = When casting as a higher level spell\comma{} you may remove more powerful illusions \minus{} matching the level this spell is cast at.,noResist =1, noBlock = 1, effect =Target an individual and remove all Illusion spells of Adept level and below from them.
}
\spell{
	name = Silence, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Sight, incant = silencio, duration = 15 seconds,noHigh = 1, resist = Willpower, noBlock = 1, effect =If the target fails to Resist\comma{} they may not speak or otherwise vocalise for the duration of the spell.
}
\spell{
	name = Suppress Intelligence, school = Illusion, discipline = Psionics, type = Instant, level =Adept, range =Wandtip, incant = romanes, duration = 2 minutes,higher = The Intelligence drain increases by 2 points \forEvery{}.,resist = Intelligence, noBlock = 1, effect =By touching your wand\minus{}tip to the head of the target\comma{} reduce their Intelligence attribute by 3 points (min 0) for the duration of the spell. This effect is negated on a successful Resist.
}
}
 \spellBook{Making and Unmaking: The Art of Conjuration}{Adept-level Conjuration}{
}
 \spellBook{Curses \& Counter Curses}{Adept-level Curse}{
\spell{
	name = Break Focus, school = Maledictions, discipline = Curse, type = Instant, level =Adept, range =Close, incant = adtono, duration = 20 seconds,noHigh = 1, resist = Willpower, noBlock = 1, effect =Disorienting noises and lights distract prevent the target from continued Focus. Afflicted beings cannot cast Focus spells for the duration of this spell \minus{}\minus{} all attempts to do so count as `failed'\comma{} and any current Focus effects are terminated. 

A successful Resist negates this effect\comma{} but target must perform a spellcasting check for Focus spells for the duration\comma{} even if they have them memorised.
}
\spell{
	name = Comatosing Blast, school = Maledictions, discipline = Curse, type = Instant, level =Adept, range =Close, incant = stupefy, duration = 1 minute,noHigh = 1, resist = Willpower, negation = Blockable  and Dodgeable,effect =If the spell hits the target\comma{} they are rendered {\it unconscious} for the duration of the spell. 

At the end of each turn cycle\comma{} they perform a Resist check to remove this effect.
}
\spell{
	name = Delayed Effect, school = Maledictions, discipline = Curse, type = Instant, level =Adept, range =Close, incant = mora maledictus, duration = 1 hour,noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =This spell may be cast as if it were a spell of any level greater than Beginner. After a target is hit by this spell\comma{} you must write down another curse that you are able to cast\comma{} of a lower level than the one chosen to cast this spell. At any point in the next hour\comma{} you may reveal the chosen curse\comma{} and the effects of that spell are then immediately applied to the target (if they fail the associated Resist check).
}
\spell{
	name = Petrify, school = Maledictions, discipline = Curse, type = Instant, level =Adept, range =Close, incant = petrificus totalus, duration = 1 minute,noHigh = 1, resist = Power, negation = Blockable  and Dodgeable,effect =The target is {\it Paralyzed} as they are encased in a protective\comma{} petrifying layer of magic. 

The target is Immune to all forms of damage except psychic whilst it is petrified. At the end of each turn in which they are petrified\comma{} a being may perform a Resist check to remove this effect.
}
\spell{
	name = Strangle, school = Maledictions, discipline = Curse, type = Instant, level =Adept, range =Close, incant = offoco, noDur = 1, noHigh = 1, resist = Vitality, negation = Blockable  and Dodgeable,effect =If this spell hits a living being\comma{} the target must Resist at the end of every turn until they succeed. Until then\comma{} they are deprived of oxygen and cannot speak. After 6 turns\comma{} the victim can no longer take any other actions then attempting to Resist\comma{} and after this they eventually succumb to hypoxia under the usual rules.
}
}
 \spellBook{Hexes to Make Your Head Spin (Literally)}{Adept-level Hex}{
\spell{
	name = Exploding Missile, school = Maledictions, discipline = Hex, type = Instant, level =Adept, range =Close, incant = bombarda, noDur = 1, higher = \additional{2d12}{fire},noResist =1, negation = Blockable  and Dodgeable,effect =A small missile launches from the end of your wand and explodes on contact with the target\comma{} dealing 2d12 concussive damage and 1d12 fire damage.
}
\spell{
	name = Object Swarm, school = Maledictions, discipline = Hex, type = Focus, level =Adept, range =Close, incant = oppugno, noDur = 1, higher = An additional 3 objects are enchanted for every additional spell level dedicated to this spell.,noResist =1, negation = Blockable  and Dodgeable,effect =Causes 5 nearby objects to hurl themselves at the target. 

Each object does 1d4 bludgeoning damage\comma{} with the caster performing an accuracy check for each of them.
}
\spell{
	name = Recurring Light, school = Maledictions, discipline = Hex, type = Focus, level =Adept, range =Close, incant = catena, noDur = 1, higher = \additional{1d8}{force},noResist =1, negation = Blockable,effect =A beam of blinding energy shoots from your wand in a line up to 8m long\comma{} striking one target before seeking the next. Each target takes 3d8 force damage as the beam refracts through them and onto the next target. 

The beam stops only if there are no new\comma{} detectable targets within 8m\comma{} or if one of the targeted beings successfully blocks it. If multiple beings are valid next target\comma{} the next one is chosen at random.
}
\spell{
	name = Spiral Inversion, school = Maledictions, discipline = Hex, type = Instant, level =Adept, range =Close, incant = anstroff maxima, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =A twisting\comma{} crushing force lashes out at your target\comma{} seeking to wrap them into a horrifying\comma{} spiralling knot of flesh. 

The target takes 3d10 bludgeoning damage\comma{} halved on a successful Resist.
}
\spell{
	name = Stream of Acid, school = Maledictions, discipline = Hex, type = Focus, level =Adept, range =Close, incant = saeclifors, noDur = 1, higher = Gain an additional 2d6 acid damage for every additional spell\minus{}level used to cast this spell.,noResist =1, negation = Dodgeable,effect =You conjure a pencil\minus{}thin stream of corrosive green acid in a line from the tip of your wand up to a distance of 3m. A being which falls into this region must succeed in dodging\comma{} or the acid dissolves armour\comma{} clothes and skin alike\comma{} doing 4d6 acid damage.
}
}
 \spellBook{Magic to Make Others Better}{Adept-level Healing}{
\spell{
	name = Countercurse, school = Recuperation, discipline = Healing, type = Instant, level =Adept, range =Wandtip, incant = finite maledictum, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Remove the effects of an active spell from the Curse discipline. 

This spell can only remove spells caused by a curse of an equal level as this spell is cast at \minus{} to remove an Expertly cast curse\comma{} this spell must be cast at an Expert level.
}
\spell{
	name = Healing Lance, school = Recuperation, discipline = Healing, type = Instant, level =Adept, range =Close, incant = lavi thera, noDur = 1, higher = Heals an additional 1d10 \forEvery{}.,noResist =1, noBlock = 1, effect =A bolt of healing energy bursts from your wand a shoots towards your target\comma{} healing them for 3d10 health points.
}
\spell{
	name = Mend Bones, school = Recuperation, discipline = Healing, type = Instant, level =Adept, range =Wandtip, incant = ossium emendo, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Repair bones and heal the body. Removes the \textit{Broken Bone} status effect and the associated \textit{Serious Injury} (unless another status effect blocks this).
}
\spell{
	name = Revive, school = Recuperation, discipline = Healing, type = Instant, level =Adept, range =Wandtip, incant = renervate, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Removes the {\it Unconscious} status effect (unless another status effect prevents that) and awakens targets from even the deepest of slumbers.
}
}
 \spellBook{How Not to be Killed: A Guide for the Discerning Wizard}{Adept-level Warding}{
\spell{
	name = Anti\minus{}Muggle Ward, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Wandtip, incant = repello mugletum, duration = 1 month,higher = The radius of the ward trebles with every additional spell level dedicated to its casting.,noResist =1, noBlock = 1, effect =Forms a warded area up to 10m in radius that muggles cannot enter or even perceive. 

A muggle will not willingly enter the region\comma{} and if forced to\comma{} will permanently take the {\it Confused} status until they leave.
}
\spell{
	name = Blade Wall, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Wandtip, incant = heus nocivious, duration = 30 minutes,higher = For every additional spell\minus{}level dedicated to casting this spell\comma{} increase the maximum length by 5m and the height by 1m.,noResist =1, noBlock = 1, effect =Create an impenetrable\comma{} opaque warded region up to 10m long and 2m tall. This wall is composed of swirling magical blades that do 3d10 slashing damage to any creature that touches it (targets may attempt to block the damage\comma{} with an assumed accuracy of 15). The wall can withstand 40 points of damage before disintegrating.
}
\spell{
	name = Minefield Ward, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Wandtip, incant = denarlium, duration = 1 week,higher = \additional{1d10}{},resist = Observation, noBlock = 1, effect =Lay magical {\it mines} in a 15m radius\comma{} with a 5m radius gap at the centre. You may designate a single safe route through the minefield (a path of width 0.5m). 

If a being touches any part of the minefield other than the path\comma{} the mines explode doinig 3d10 damage of a type of the caster\apos{}s choosing. Each subsequent metre travelled triggers another explosion. Explosions may be Resisted for half damage.
}
\spell{
	name = Protective Field, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Close, incant = tueor, duration = 2 minutes,higher = Gain an additional +1 bonus to Block \forEvery{},noResist =1, noBlock = 1, effect =Erects a ward in a cylinder around an individual or an object. If cast around an object\comma{} the ward has a radius of 2m and a height of 4m. When cast around a person\comma{} the field is 20cm larger in radius than the individual is wide\comma{} and 20cm taller. The ward moves as the target is moved. 

This field gives a +4 bonus to Block statistic for the duration of the spell.
}
\spell{
	name = Threshold Ward, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Sight, incant = desino, duration = 1 year,higher = Double the maximum size of the ward \forEvery{}.,noResist =1, noBlock = 1, effect =Prevents any objects or beings from passing over the edge of the ward. Usually cast on doorways and entrances\comma{} the maximum size of the ward is a circle 2m in radius. The ward is immune to all physical damage\comma{} but can only survive 10 points of spell damage.
}
\spell{
	name = Zone of Silence, school = Recuperation, discipline = Warding, type = Ward, level =Adept, range =Wandtip, incant = umbra silentium, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Ward an area up to 3 metres in radius with a powerful enchantment which prevents sound from travelling. No sound can penetrate or travel within this zone whilst the ward remians active. 

All non\minus{}silent spellcasting attempts fail\comma{} as do all hearing\minus{}related checks.
}
}
 \spellBook{Transmutation and Transformative Tricks}{Adept-level Alteration}{
\spell{
	name = Alter Astral Aspect, school = Transfiguration, discipline = Alteration, type = Instant, level =Adept, range =Close, incant = madas, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Change how the object is registers when viewed by magical means (I.e the {\it Identify} spell)\comma{} make a mundane object appear magical\comma{} or make a wizard appear as a sofa\comma{} or a dragon. 

Because this spell truly alters the object\apos{} astral nature\comma{} spells such as {\it True Sight} can be fooled by this effect. However\comma{} this spell does nothing to change the nature of the being (so a chair which has the aura of a dragon is still just a chair)\comma{} and non\minus{}magical investigation is unaltered.
}
\spell{
	name = Irongrip, school = Transfiguration, discipline = Alteration, type = Instant, level =Adept, range =Wandtip, incant = fero, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Gives a willing target an incredibly strong grip. Gain check advantage on all grappling checks and attempts to resist disarmament.
}
\spell{
	name = Ironmass, school = Transfiguration, discipline = Alteration, type = Instant, level =Adept, range =Close, incant = ferrus gravitas, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Target a non\minus{}sapient object up to 50kg in weight\comma{} and increase its density such that it becomes so heavy that it cannot be lifted by a single individual. The total mass of the object increases by a hundredfold.
}
\spell{
	name = Reshape Body, school = Transfiguration, discipline = Alteration, type = Instant, level =Adept, range =Close, incant = subsintus, duration = 1 hour,higher = For every additional spell\minus{}level dedicated to this spell you may alter the MoM rating (or equivalent) by an additional 1 point.,resist = Conviction, noBlock = 1, effect =You transform and reshape the body of a target being\comma{} molding it into a new\comma{} animalistic form. An unwilling target can nullify this effect by succeeding on a Resist check\comma{} which is performed with advantage if the target is currently in combat with the caster. 

The final form of the target is chosen by the caster\comma{} and should be a creature that they know of whose Ministry Rating differs from that of their current form by only 1 point\comma{} in either direction. If the target does not have a Ministry Rating (i.e. a sapient being)\comma{} use the following conversion table:

\begin{rndtable}{c c}
\bf Level & \bf MoM Equivalent \\
1\minus{}5   & III \\
6\minus{}9  &  IV \\
10\minus{}14 & V \\
15\minus{}18  & VI \\
18 + & VII
\end{rndtable}

The target replaces all of their statistics\comma{} including those associated with their consciousness\comma{} with those of the selected being. The target retains basic memories of their previous life\comma{} allies and enemies\comma{} though these are filtered through the intellectual limitations of their new form. Any equipment that the target had on their person is merged into their new form\comma{} and cannot be used until the effect ends. The target is limited in their actions to only those that their chosen form can carry out\comma{} and so (generally) cannot speak\comma{} cast spells or use items. 

The effect ends either when the magic is dispelled\comma{} the spell effect ends\comma{} or the creature drops to 0HP. The target reassumes their natural form with the original number of HP. If the reversion was because of dropping to 0HP\comma{} any excess damage is then dealt to the original form\comma{} but they do not suffer any additional side effects from having been reduced to 0HP in their animal form.
}
\spell{
	name = Sculpt Matter, school = Transfiguration, discipline = Alteration, type = Focus, level =Adept, range =Close, incant = perseids, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Sculpt a target solid object with your mind\comma{} as if it were made of soft clay. The total mass of the object must remain constant\comma{} but you can shift and sculpt the matter at will.
}
}
 \spellBook{Making and Unmaking: The Art of Conjuration}{Adept-level Conjuration}{
\spell{
	name = Banish, school = Transfiguration, discipline = Conjuration, type = Instant, level =Adept, range =Sight, incant = valeo fendus, noDur = 1, noHigh = 1, resist = Power, noBlock = 1, effect =Target a creature from another plane of existence\comma{} either a summoned creature\comma{} or one which has travelled here through other means. If it fails to Resist\comma{} it is banished from this reality and returns home. If the target is a summoned creature and the caster is aware of the Banishment being cast\comma{} they can use a Reaction to give their creature advantage in the check. 

This spell has no effect on beings native to this plane of existence.
}
\spell{
	name = Duplicate Object, school = Transfiguration, discipline = Conjuration, type = Instant, level =Adept, range =Wandtip, incant = gemino, duration = 12 hours,noHigh = 1, resist = Investigation, noBlock = 1, effect =Creates a copy of an object in your possession\comma{} which is identical to the first\comma{} until it disintegrates 12 hours later. These duplicates can be determined to be fake through a successful Resist.
}
\spell{
	name = Entombment, school = Transfiguration, discipline = Conjuration, type = Instant, level =Adept, range =Close, incant = magnus petris, noDur = 1, higher = \additional{3d6}{bludgeoning},noResist =1, negation = Dodgeable,effect =With a flick of the wrist\comma{} you summon a larger boulder floating in space above the head of your enemy and allow it to fall onto their head. If it hits\comma{} the target takes 6d6 bludgeoning damage/.
}
\spell{
	name = Smoke Daggers, school = Transfiguration, discipline = Conjuration, type = Instant, level =Adept, range =Close, incant = fumus defendus, noDur = 1, higher = Gain an additional 4 daggers \forEvery{},noResist =1, negation = Blockable  and Dodgeable,effect =Causes 8 daggers to coalesce out of nearby smoke or dust\comma{} and fly towards a single target. Each dagger that hits the target does 1d4 piercing damage.
}
\spell{
	name = Vanish Object, school = Transfiguration, discipline = Conjuration, type = Instant, level =Adept, range =Close, incant = evanesco, noDur = 1, higher = The mass of objects you can vanish doubles \forEvery{}.,resist = Power, noBlock = 1, effect =Cause a 1kg animal or object to vanish\comma{} without a trace. Sentient beings must pass a DV8 resist check to avoid being vanished.
}
}
 \spellBook{The Forbidden Arts}{Adept-level Necromancy}{
\spell{
	name = Blood Barrier, school = Dark Arts, discipline = Necromancy, type = Ward, level =Adept, range =Wandtip, incant = confusangui, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Use blood to draw warding runes onto an object or person. Erects a swirling\comma{} red barrier which is impenetrable\comma{} though not opaque or soundproof. Barrier absorbs up to 20d6 damage\comma{} but takes triple damage from Celestial damage. 
Each individual{\apos}s blood can only be used once for blood magic.
}
\spell{
	name = Fiendfyre, school = Dark Arts, discipline = Necromancy, type = Instant, level =Adept, range =Sight, incant = pyrkagius, duration = 1 hour,higher = \additional{1d12}{Fire},noResist =1, negation = Blockable  and Dodgeable,effect =Summons a cursed fire that consumes everything that it touches\comma{} and actively seeks to destroy living beings as if it were a living being telepathically linked to the caster. The caster may direct the fire may send out up to 1d4 tendrils per turn to strike at a target (performing an accuracy check for every atack)\comma{} doing 3d12 fire damage to all it touches.

Fiendfyre cannot be extinguished by mundane means. Attempting to do so infuriates the fiendfyre and triggers an automatic attack on you.
}
\spell{
	name = Insect Plague, school = Dark Arts, discipline = Necromancy, type = Instant, level =Adept, range =Sight, incant = prorepere, duration = 2 minutes,higher = \additional{1d4}{each of poison and piercing},noResist =1, noBlock = 1, effect =Summon a swarm of insects from the ground in an radius 10 metres around a targeted point. All beings besides the caster within the region take 1d4 poison damage and 1d4 piercing damage every turn that they spend time inside the region.
}
\spell{
	name = Pain Beyond Measure, school = Dark Arts, discipline = Necromancy, type = Focus, level =Adept, range =Close, incant = Crucio, noDur = 1, higher = For every additional spell\minus{}level dedicated to casting this spell\comma{} it inflicts an extra 2d6 psychic damage. .,resist = Willpower, noBlock = 1, effect =Causes immense pain to the target\comma{} rendering them {\it Incapacitated} whilst the spell is cast and dealing 4d6 psychic damage to the target. A successful Resist negates the status effect\comma{} but not the damage taken. 

However\comma{} this spell cannot be used to reduce a target below 1HP
}
}
 \spellBook{Rehabilitating Blood and Darkness in Everyday Magic}{Adept-level Occultism}{
\spell{
	name = Solidify Ghost, school = Dark Arts, discipline = Occultism, type = Ritual (10 minutes), level =Adept, range =Close, noIncant = 1, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =By spending time performing a ritual in which you enchant a pinch of salt or ash with occult words and runes\comma{} you gain the ability to solidify ghosts and other etheral apparitions. 

You must blow the ash into the face of the ghostly creature\comma{} at which point it loses the ability to pass through solid objects for the duration of the spell. 

Whilst they are solid\comma{} they may interact with the physical world\comma{} but can also feel pain. If their HP is reduced to zero\comma{} they fall unconscious until they revert back to their ghostly form.
}
\spell{
	name = Voidsphere, school = Dark Arts, discipline = Occultism, type = Focus, level =Adept, range =Sight, incant = inanis, duration = 1 minute,higher = \additional{1d8}{cold},resist = Acrobatics, noBlock = 1, effect =Summon a true Void anywhere within 15m of your current position\comma{} a gap in the fabric of reality in the form of an inky black orb\comma{} 1m in radius. 

As a minor action\comma{} you may move the sphere up to 10m in any direction (including vertically)\comma{} and shrink or grow the void by a factor of two each turn (cannot exceed its original size). 

Any being which passes through the space occupied by the sphere must succed in a Resist check\comma{} or take 3d8 cold damage and be randomly teleported anywhere in a 30metre radius.
}
}
 \spellBook{Secrets of Elemental Sorcery}{Expert-level Elemental}{
\spell{
	name = Adjust Climate, school = Charms, discipline = Elemental, type = Ritual (1 hour), level =Expert, range =Self, incant = kilmas, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Summon a magical wind which drastically alters the climate in a region. Bring a hot\comma{} arid wind to the arctic \minus{} or an arctic wind into the Sahara.

You may control the windspeed\comma{} the temperature and the level of preciptation. 

Mild alterations (i.e. cooling the temperature by a few degrees\comma{} summoning a brisk wind) happen as soon as the ritual is complete. Larger changes (i.e. dismissing an enormous storm\comma{} warming an ice\minus{}cold night) take place gradually over the course of several hours. 

After the changes occur\comma{} the normal climate gradually reasserts itself.
}
\spell{
	name = Drowning Sphere, school = Charms, discipline = Elemental, type = Focus, level =Expert, range =Close, incant = panigus, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =A stream of water from every nearby source streams and collects in a sphere up to 3 metres in radius\comma{} hovering above the ground\comma{} a violently twisting vortex of water and matter. 

Any being caught in the initial area\comma{} or which subsequently passes through the sphere must succeed on a Resist\comma{} or be sucked into the sphere. Up to 5 humanoids\comma{} or 1 larger creature (if within the size of the sphere) can be restrained at any one time. Beings inside the sphere are deprived of oxygen and are considered {\it Incapcitated}\comma{} able only to perform a Resist check at the beginning of each turn. 

Succeeding in a resist check deposits you prone at a random point outside the sphere. 

The sphere remains whilst concentration is maintained\comma{} and can be moved at a speed of 3 metres per cycle. When focus is broken\comma{} the sphere disintegrates and the water crashes down. Any being restrained or below the sphere at this point takes 5d8 bludgeoning damage.
}
\spell{
	name = Electrical Arc, school = Charms, discipline = Elemental, type = Focus, level =Expert, range =Close, incant = electrum maxima, noDur = 1, higher = \additional{1d10}{Electrical},noResist =1, negation = Blockable  and Dodgeable,effect =Whilst you maintain Focus\comma{} a bolt of energy arcs from the end of your wand\comma{} doing 5d10 electrical damage per turn.
}
\spell{
	name = Erupting Earth, school = Charms, discipline = Elemental, type = Instant, level =Expert, range =Close, incant = purskama, noDur = 1, higher = \additional{2d12}{bludgeoning},noResist =1, negation = Dodgeable,effect =Target a being standing on a patch of earth or mud. The ground underneath them explodes upwards in a violent eruption of loose stones and tumultuous ground\comma{} dealing 5d12 bludegoning damage.
}
\spell{
	name = Incinerating Expanse, school = Charms, discipline = Elemental, type = Focus, level =Expert, range =Close, incant = ustulo, noDur = 1, higher = \additional{4d10}{Fire},noResist =1, negation = Blockable,effect =An enormous burst of flame rips from the end of your wand\comma{} incinerating everything in a cone up to 5 metres in front of the caster. 

All beings in the cone which fail to block take 8d10 fire damage.
}
}
 \spellBook{The Standard Book of Spells (Grade 2)}{Expert-level Kinesis}{
\spell{
	name = Apparate/Disapparate, school = Charms, discipline = Kinesis, type = Instant, level =Expert, range =Self, noIncant = 1, noDur = 1, higher = You may bring an additional passenger \forEvery{}.,noResist =1, noBlock = 1, effect =You may teleport yourself and up to 2 additional passengers to a place you are intimately familiar with. Passengers must be in physical contact with you the moment this spell is cast. 

This spell may be cast without the use of a wand. 

If anything happens to the caster in the turn that this spell is cast which would disrupt a Focus spell\comma{} all passengers become splinched and take 2d12 force damage.
}
\spell{
	name = Leapfrog, school = Charms, discipline = Kinesis, type = Instant, level =Expert, range =Sight, incant = raneus, duration = 1 minute,higher = Add an additional 3m to the maximum jump length \forEvery{}.,noResist =1, noBlock = 1, effect =Target may leap up to 3m in any direction as a major action\comma{} and land safely whilst the spell is active.
}
}
 \spellBook{Communing with Others\comma{} and with Yourself}{Expert-level Telepathy}{
\spell{
	name = Disrupt Connection, school = Divination, discipline = Telepathy, type = Instant, level =Expert, range =Sight, incant = ruinosus, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =Sever a telepathic connection possessed by the target. This may be used to sever a link such as that caused by the {\it Telepathic Bond} spell\comma{} or the link between caster and a summoned being. An untethered summoned being no  longer accepts orders from their creator\comma{} and will potentially attack them. A successful resist negates this effect\comma{} but the target takes 2d4 psychic damage instead.
}
\spell{
	name = Occlumency, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Expert, range =Self, incant = occlumens, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Set up barriers around your mind to defend yourself from psychic attacks and dedection.

You are gain advantage on all Resist checks against spells from the Psionics and Bewitchment disciplines and are considered Resistant to psychic damage for the duration of the spell.
}
\spell{
	name = Scry, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Expert, range =Self, incant = videro, noDur = 1, noHigh = 1, resist = Observation, noBlock = 1, effect =Name a being\comma{} location or object which you are familiar with or are able to describe and visualise in great detail. An astral `camera' appears above the target\comma{} and transmits the image that it sees to a nearby pool of water\comma{} or a mirror. The sound that a person would hear at that location is also transmitted. 

The camera moves with the target\comma{} staying at least 4m away from them. The caster may move the sensor to a different angle as a major action. 

If the target successfully resists\comma{} they become aware of the scrying attempt\comma{} and may use a minor action to disable it either immediately\comma{} or at any subsequent point. You may not re\minus{}establish a scrying connection for 24 hours after a scrying effort is terminated in this fashion.
}
}
 \spellBook{Unfogging the Future}{Expert-level Temporal}{
\spell{
	name = Legends of the Past, school = Divination, discipline = Temporal, type = Instant, level =Expert, range =Self, incant = gabulus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Name or describe a person\comma{} place\comma{} or object. The spell brings to your mind a brief summary of the significant lore about the thing you named. The lore might consist of current tales\comma{} forgotten stories\comma{} or even secret lore that has never been widely known. If the thing you named isn't of legendary importance\comma{} you gain no information. The more information you already have about the thing\comma{} the more precise and detailed the information you receive is.
}
\spell{
	name = Mists of Time, school = Divination, discipline = Temporal, type = Ritual (1 hour), level =Expert, range =Self, incant = momento aeternitatis, noDur = 1, higher = When cast as a Master spell\comma{} you may observe up to 10 years into the past. As an Ascendant spell\comma{} you may observe up to 1000 years into the past.,noResist =1, noBlock = 1, effect =Enter into a trance\comma{} whereby you can observe the past\comma{} to uncover what happened at your current location\comma{} or to a specific person or object you can touch. 

You may observe your chosen timestream up to 1 year into the past.
}
\spell{
	name = Timeslip, school = Divination, discipline = Temporal, type = Instant, level =Expert, range =Sight, noIncant = 1, duration = 2 minutes,noHigh = 1, resist = Power, noBlock = 1, effect =Create a perturbation in the temporal vortex which\comma{} on a failed Resist\comma{} catapaults the target forward in time\comma{} effectively removing them from reality for the duration of the spell. When the spell ends\comma{} the target reappears at their original location\comma{} unaware that time has passed.
}
}
 \spellBook{A Gentle Guide to Persuading the Mind}{Expert-level Bewitchment}{
\spell{
	name = Beguiling Totem, school = Illusion, discipline = Bewitchment, type = Instant, level =Expert, range =Wandtip, incant = fascinare, duration = 1 day,higher = Increase the effective radius by 50m \forEvery{}.,resist = Willpower, noBlock = 1, effect =Target an object between 1m and 20m in size and enchant it with an aura that sings an enticing song into the minds of your targets\comma{} or fills them with fear and dread. 

The caster decides upon a single type of being (humanoid\comma{} gigantoid\comma{} monster\comma{} etc.)\comma{} and imbues the targeted object with an aura that either attracts or repels that species in a radius of 50 metres. Members of the chosen type within the radius that fail to resist feel an irresistible urge to either approach or flee the object\comma{} and must use all of their action to act on this urge\comma{} until they have completed the action\comma{} at which point the spell is broken.
}
\spell{
	name = Hidden Hologram, school = Illusion, discipline = Bewitchment, type = Ward, level =Expert, range =Wandtip, incant = occultus indis, duration = 100 years,noHigh = 1, resist = Investigation, noBlock = 1, effect =As with the {\it Implant Message} spell\comma{} you implant a message or other illusion into a warded region\comma{} and choose an audible or visual trigger which activates the illusion. 

When activated\comma{} an illusion of your choice springs into life over a region up to 2 metres cubed\comma{} and executes a series of verbal messages and/or physical movements at your discretion. This could be a person delivering a message when a passphrase is uttered\comma{} or a hidden box of treasure opening tantalisingly over a pitfall. 

The illusion can be seen to be fake on a successful Resist check\comma{} or after the construction is interacted with\comma{} as physical beings pass through them.
}
\spell{
	name = Perfect Disguise, school = Illusion, discipline = Bewitchment, type = Instant, level =Expert, range =Wandtip, incant = dissimulato, duration = 8 hours,noHigh = 1, resist = Conviction, noBlock = 1, effect =Choose any number of targets within range and change their appearance by layering a complex illusion on top of their physical form. An unwilling target may attempt to Resist these changes. 

The spell disguises physical appearance as well as clothing\comma{} armor\comma{} weapons\comma{} and equipment. You can make each target seem 30cm shorter or taller and appear thin\comma{} fat\comma{} or in between. You can't change a target's body type\comma{} so you must choose a form that has the same basic arrangement of limbs. Otherwise\comma{} the extent of the illusion is up to you. The spell lasts for the duration\comma{} unless you use a minor action to dismiss it sooner.

The disguises mimic any sounds\comma{} smells and any other stimuli that would be associated with your new forms\comma{} though cannot duplicate magical auras or effects beyond their simple appearance. 

It is important to note that these effects are illusory in nature\comma{} not true alterations to your form. If a being tries to interact with you and\comma{} for example\comma{} finds you are much fatter than your disguise makes out to be\comma{} they will become aware of you being disguised. Equally\comma{} the disguises are non\minus{}corporeal and so objects will pass through them.
}
}
 \spellBook{Mindmakers\comma{} Mindbreakers}{Expert-level Psionics}{
\spell{
	name = Delusion, school = Illusion, discipline = Psionics, type = Instant, level =Expert, range =Close, incant = falasarium, duration = 5 hours,noHigh = 1, resist = Conviction, noBlock = 1, effect =If target fails a Resist check\comma{} the caster may make them believe one piece of information\comma{} which they will believe to be irrefutably true. The delusion must be vaguely rational\comma{} and may not incur excessive self\minus{}harm\comma{} as judged by the GM.
}
\spell{
	name = Psychosis, school = Illusion, discipline = Psionics, type = Instant, level =Expert, range =Sight, incant = demensus, noDur = 1, higher = \additional{3d12}{psychic},noResist =1, negation = Dodgeable,effect =The target is wracked with uncontrollable pain as their very perception of reality is messed with. 

Target takes 5d12 psychic damage.
}
\spell{
	name = Psychosomatism, school = Illusion, discipline = Psionics, type = Focus, level =Expert, range =Sight, incant = animo materia, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =You exploit the link between the mind and the body to cause harm to the body by making them truly believe they are suffering harm. 

You conjure an image in their mind of an assailant \minus{} a fearsome dragon or a cloaked duelist. In their mind\comma{} this assailant inflicts damage on them of a damage type chosen by you. 

On a failed Resist\comma{} their body responds as if this attack had been real \minus{} deep wounds open up on their flesh\comma{} and burns or boils appear on their skin. The target takes 6d10 of the chosen damage type.
}
\spell{
	name = Relive Memory, school = Illusion, discipline = Psionics, type = Instant, level =Expert, range =Close, incant = legilimens, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =Target performs a resist magic check\comma{} if it fails\comma{} the caster plunges both themselves and the target into a memory of the caster\apos{}s choice\comma{} which both parties then experience in detail. 

The actual reliving of the memory occurs in an instant\comma{} and is over almost instantaneously.
}
\spell{
	name = Waking Dreams, school = Illusion, discipline = Psionics, type = Focus, level =Expert, range =Close, incant = oneiro, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =Create an illusion\comma{} not out of light\comma{} but in the mind of a given individual. 

This spell allows you to force your way into the target\apos{}s mind and rearrange their reality as you see fit. You can make them see monsters and mortal enemies\comma{} or their long lost love. This internal illusion can interact with them and speak at your command. 

The target will react as if what they see is real (for them\comma{} it appears to be)\comma{} and will take actions accordingly. This illusion can remove no HP or FP\comma{} but the dreamer will believe that they can . 

This effect is negated on a successful Resist\comma{} which occurs whenever you introduce a new element to the illusion (i.e. a new character\comma{} or a new scenario).
}
}
 \spellBook{Summoning Your Desires}{Expert-level Conjuration}{
}
 \spellBook{Voodoo and Vomiting: A Study in Curses}{Expert-level Curse}{
\spell{
	name = Curse Being, school = Maledictions, discipline = Curse, type = Ritual (10 minutes), level =Expert, range =Sight, incant = maledicto, noDur = 1, noHigh = 1, resist = Power, noBlock = 1, effect =Casts a permanent curse on a target being\comma{} object or location that you can see within range. You may choose the effects of this curse\comma{} though they must be commensurate with the casting level of this spell\comma{} and the GM has a veto. Be inventive!
}
\spell{
	name = Perpetual Hunger, school = Maledictions, discipline = Curse, type = Instant, level =Expert, range =Close, incant = inedia, duration = 10 minutes,noHigh = 1, resist = Vitality, noBlock = 1, effect =Choose a living being that you can see within range. The afflicted feels perpetual\comma{} soul\minus{}sapping hunger. Every minute (20 turns) where at least two mouthfuls of food is not consumed\comma{} suffer necrotic damage equal to the number of minutes since food was last consumed\comma{} until the spell effect ends. Target may perform a Resist check every 3 minutes to end the effect.
}
\spell{
	name = Shield Breaker, school = Maledictions, discipline = Curse, type = Instant, level =Expert, range =Close, incant = misericorde, noDur = 1, noHigh = 1, noResist =1, negation = Dodgeable,effect =Damage a target\apos{}s armour\comma{} reducing its effectiveness by 1d4 points. If the total damage to the armour exceeds its Block bonus\comma{} the armour is destroyed and all positive modifiers are removed. 

For larger creatures who\apos{}s `armour' is their natural scales or tough hide\comma{} this spell effects an area one square metre in area at a time.
}
}
 \spellBook{Hexing Your Problems \minus{} the Healthy Coping Mechanism}{Expert-level Hex}{
\spell{
	name = Arctic Blast, school = Maledictions, discipline = Hex, type = Instant, level =Expert, range =Close, incant = gelidus, duration = 3 turns,higher = \additional{2d6}{Cold},resist = Vitality, noBlock = 1, effect =A cylinder of radius 5m and height 2m around the target is decreased in temperature by 50 degrees celsius. 

Those caught in the region take 6d6 of cold damage\comma{} and apply the mild Frostbite status effect. Resist for half damage and to negate the status effect.
}
\spell{
	name = Black Dragon\apos{}s Fury, school = Maledictions, discipline = Hex, type = Focus, level =Expert, range =Close, incant = draco flammor, noDur = 1, higher = \additional{1d12}{Force},noResist =1, negation = Blockable,effect =A torrent of black\comma{} crackling energy erupts from the tip of your wand in a cone 3 metres in front of the caster\comma{} devastating everything in its path. 

This spell deals 3d12 Force damage to all targets caught in the region\comma{} halved on a successful Block.
}
\spell{
	name = Detonation, school = Maledictions, discipline = Hex, type = Instant, level =Expert, range =Sight, incant = expulso, noDur = 1, higher = \additional{2d6}{Force},resist = Power, negation = Dodgeable,effect =Launches a magical bolt at the target which\comma{} if it makes contact\comma{} causes the object to violently tear itself apart\comma{} doing 5d12 force damage. Resist for half damage.
}
\spell{
	name = Witch Hunter\apos{}s Bane, school = Maledictions, discipline = Hex, type = Instant, level =Expert, range =Close, incant = iboq plustra, noDur = 1, noHigh = 1, noResist =1, negation = Blockable,effect =A searing white light solidifies into a maelstrom of vicious barbs\comma{} striking towards the target and dealing 4d10 slashing damage. 

If the attack hits\comma{} the caster may use the distraction to direct a tendril of the energy to remove any {\it Trapped} status effects\comma{} and perform a DV 15 Speed check. On a success\comma{} the caster uses the confusion to teleport to a place they can see within 10 metres of their current location.
}
}
 \spellBook{Life\comma{} and How to Preserve it}{Expert-level Healing}{
\spell{
	name = Final Cure, school = Recuperation, discipline = Healing, type = Instant, level =Expert, range =Close, incant = requiescat in pace, noDur = 1, higher = \additional{2d8}{celestial},resist = Evil, noBlock = 1, effect =A heavenly glow descends upon an area 3m in radius around the caster. Any Ghost\comma{} Inferi\comma{} or other Unliving that once used to be a living creature caught in this radius takes 5d8 celestial damage\comma{} as the sound of an angelic choir sings out. Damage is halved on a successful Resist.
}
\spell{
	name = Major Healing, school = Recuperation, discipline = Healing, type = Instant, level =Expert, range =Wandtip, incant = sana, noDur = 1, higher = Heal an additional 2d12 HP \forEvery{},noResist =1, noBlock = 1, effect =Heals the target of all burns\comma{} frostbite\comma{} poisons and diseases\comma{} and other status effects\comma{} regardless of severity.

In addition\comma{} restores 8d12 HP
}
\spell{
	name = Shield of Mortality, school = Recuperation, discipline = Healing, type = Ward, level =Expert, range =Wandtip, incant = morte discerde, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =You bless a targeted individual with a warm\comma{} healing energy. 

The next time that a spell effect would reduce the target to 0HP\comma{} they are instead reduced to 1HP\comma{} and the spell ends.
}
}
 \spellBook{An Anthology of Safeguarding Measures}{Expert-level Warding}{
\spell{
	name = Holy Ward, school = Recuperation, discipline = Warding, type = Ward, level =Expert, range =Wandtip, incant = pervetutem luminis, noDur = 1, higher = The spell is capable of inflicting an additional 20 damage \forEvery{}.,noResist =1, noBlock = 1, effect =Create a region up to 10m in radius where the Unlife cannot pass. Unlife attempting to cross the barrier are ignited for 4d12 worth of Celestial  damage per turn that they remain inside the area.

The shield fails when 50 damage has been inflicted.
}
\spell{
	name = Ironwall, school = Recuperation, discipline = Warding, type = Ward, level =Expert, range =Wandtip, incant = ferromurrum, duration = 1 day,higher = Gain an additional 30 HP for the Ironwall \forEvery{}.,noResist =1, noBlock = 1, effect =Forms a shield around an area up to 5m in radius\comma{} that absorbs 60 points of damage. The Ironwall is impenetrable\comma{} opaque and soundproof\comma{} and is two\minus{}way. Nothing can enter or leave across the threshold of the ward until it is deactivated by the caster\comma{} or destroyed.
}
\spell{
	name = Patronus, school = Recuperation, discipline = Warding, type = Instant, level =Expert, range =Close, incant = expecto patronus, noDur = 1, higher = When cast as a higher\minus{}level spell\comma{} add 4d8 additional celestial damage for every additional spell\minus{}level.,resist = Evil, noBlock = 1, effect =Summon your greatest\comma{} happiest memories into physical form: your patronus. 

Your patronus may also take a turn as if were a real being (albeit an Astral being) at your command. The patronus is astral in nature and cannot interact with the physical realm\comma{} however\comma{} it may move at a speed of 30metres per round and any Unlife it passes within 1m of must succeed on a Resist check or take the {\it Terrified} status and 4d8 of Celestial damage.
}
}
 \spellBook{Theories of Transubstantial Transfiguration}{Expert-level Alteration}{
\spell{
	name = Draconic Guardians, school = Transfiguration, discipline = Alteration, type = Instant, level =Expert, range =Close, incant = draconifors, duration = 1 hour,higher = The number of dragons summoned increases by 3 \forEvery{}.,noResist =1, noBlock = 1, effect =Choose up to three small objects\comma{} such as nearby rocks and imbue them with draconic fury. The objects transfigure themselves into small dragonlike entities\comma{} which take flight and\comma{} on your command\comma{} attack your foes. The dragons remain in their form for the duration of the spell\comma{} or until their HP is reduced to zero\comma{} at which point they revert to their original form. 

The statistics for the Draconic Guardians can be found in the `Commonly Summoned Creatures’ section below.
}
\spell{
	name = Elemental Imbuement, school = Transfiguration, discipline = Alteration, type = Ritual (1 minute), level =Expert, range =Wandtip, noIncant = 1, duration = 8 hours,noHigh = 1, noResist =1, noBlock = 1, effect =Perform a ritual in which you imbue a target with energy and merge their form with a token of some elemental force: an icicle or a burning ember\comma{} for example. For the duration of the spell\comma{} the target\apos{}s physical form alters to accommodate this new elemental force within their body – electrical sparks dance across their fingers\comma{} or rocks and patches of grass cover their skin\comma{} depending on what elemental token was used in the ritual. 

For the duration of the spell\comma{} you gain the following benefits:

\imbuement{Fire}{
\item You are immune to Fire Damage\comma{} and Resistance to Cold Damage.
\item Any creature which spends any part of a turn cycle within melee range of you takes 1d10 fire damage
\item You can cast {\it Compel Flames} and {\it Produce Fire} up to Adept level as silent\comma{} wandless actions 
}

\imbuement{Water/Ice}
{
\item You are immune to Cold damage and Resistant to Fire damage. 
\item The ground around you in a radius of 3m is frozen solid\comma{} any being other than you which passes through this space must move at one\minus{}quarter speed. 
\item You can cast {\it Direct Fluids} and {\it Freeze} up to Adept level as silent\comma{} wandless actions. 
}

\imbuement{Earth}
{
\item You are immune to bludgeoning damage and Resistant to piercing and slashing damage.
\item The ground around you is continually suffering minor Earthquakes\comma{} beings which pass within 5m must pass a DV 12 Acrobatics check or fall Prone. 
\item You can cast {\it Subsoil Construct} and {\it Earthen Excavation} up to Adept level as silent\comma{} wandless actions. 
}

\imbuement{Air}
{
\item You are immune to falling damage and all ranged weapon attacks against you take disadvantage. 
\item Your movement speed increases by 4m 
\item You may take an additional minor action once per turn\comma{} or choose to use this minor action as a Reaction even if you have not recovered your reaction yet. 
}

\imbuement{Electric/Thunder}
{
\item You are immune to electric damage and resistant to fire damage
\item Whenever a being comes within 6m of you\comma{} a thunderclap rings out\comma{} alerting you to its presence. All beings within this radius must make a DV 15 Vitality Resist\comma{} or become deafened. 
\item You may cast {\it Lightning Bolt} and {\it Voltaic Surprise} up to Adept level as silent\comma{} wandless actions. 
}

\imbuement{Radiance/Light}
{
\item You are immune to the {\it Blinded} status\comma{} gain perfect Darkvision and are resistant to electric damage. 
\item You can choose to emit a bright light\comma{} illuminating a radius of 20m and dealing 1d8 celestial damage to beings in this radius. 
\item You can cast {\it Floodlight} and {Silent Illusion} up to Adept level as silent\comma{} wandless actions. 
}
}
\spell{
	name = Treacherous Terrain, school = Transfiguration, discipline = Alteration, type = Instant, level =Expert, range =Close, incant = transgresso, duration = 2 hours,noHigh = 1, noResist =1, noBlock = 1, effect =Target an area up to 5m in radius and transform it into a deep bog\comma{} a bed of sharpened blades\comma{} or into a sticky mess\comma{} with the associated terrain costs and other effects.
}
}
 \spellBook{Summoning Your Desires}{Expert-level Conjuration}{
\spell{
	name = Conjure Elemental, school = Transfiguration, discipline = Conjuration, type = Instant, level =Expert, range =Wandtip, incant = diconativus, duration = 10 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =Summon an Elemental creature or a Sprite (or a number of such beings) into existence in a space that you can see within range. 

You have a number of `points’ equal to the spell level used to cast this spell – the maximum MoM rating of any being you can summon is equal to this value. Alternatively you may distribute these `points’ by summoning several lower\minus{}rated creatures\comma{} as long as the total MoM rating does not exceed the spell level used (for this purpose a rating of 0 is assigned a value of 0.5). At second level you could summon 1 rating\minus{}II creature\comma{} 2 rating\minus{}I creatures or 4 rating\minus{}0 creatures. At third level you could summon a rating III creature or 1 rating\minus{}II creature and a rating\minus{}I creature\comma{} and so on. 

Within this restriction\comma{} you may choose the kind of being from any that you have previously encountered or studied in detail. If Non\minus{}sapient\comma{} the summoned creatures will obey your commands as if they were well\minus{}trained pets\comma{} if Sapient\comma{} the creature acts as a loyal servant and is considered friendly towards you and your allies. If no command is given\comma{} they will act as a normal being\comma{} and retaliate if attacked\comma{} or run away if outmatched.
}
\spell{
	name = Create Golem, school = Transfiguration, discipline = Conjuration, type = Ritual (1 week), level =Expert, range =Wandtip, incant = lapis libiri, duration = 1 week,noHigh = 1, noResist =1, noBlock = 1, effect =Conjure a powerful spirit from the outer realms\comma{} and imprison it inside a hulking frame\comma{} to follow your every command. You may create a golem out of clay\comma{} rock\comma{} iron or crystal.  

The golem\minus{}creation ritual requires you to enchant a large amount of the raw material ($\sim$ 2000kg)\comma{} which must be natural in origin. Over the course of the ritual\comma{} you enchant and form this material into the shape you desire\comma{} with wards and runes which allow it to walk and move around \minus{} and to contain the powerful spirit inside. 

After completing the ritual\comma{} you place a small slip of parchment inside the mouth of the golem\comma{} on which is inscribed your name. This summons the golem\comma{} and binds it to you with a psychic link. 

You may use a minor action to give a psychic order to the golem\comma{} which it will follow to the letter with a single minded purpose.

Beware: the slip of paper is burned to ash after 1 week. If it is not replaced within 12 hours\comma{} the golem is free of your service and will go on a rampage to seek revenge on the one who imprisoned it.
}
\spell{
	name = Summon Monster, school = Transfiguration, discipline = Conjuration, type = Instant, level =Expert, range =Wandtip, incant = dicobelua, duration = 10 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =Summon a Monster or Draconid  (or a number of such beings) into existence in a space that you can see within range. 

You have a number of `points’ equal to the spell level used to cast this spell – the maximum MoM rating of any being you can summon is equal to this value. Alternatively you may distribute these `points’ by summoning several lower\minus{}rated creatures\comma{} as long as the total MoM rating does not exceed the spell level used (for this purpose a rating of 0 is assigned a value of 0.5). At second level you could summon 1 rating\minus{}II creature\comma{} 2 rating\minus{}I creatures or 4 rating\minus{}0 creatures. At third level you could summon a rating III creature or 1 rating\minus{}II creature and a rating\minus{}I creature\comma{} and so on. 

Within this restriction\comma{} you may choose the kind of being from any that you have previously encountered or studied in detail. If Non\minus{}sapient\comma{} the summoned creatures will obey your commands as if they were well\minus{}trained pets\comma{} if Sapient\comma{} the creature acts as a loyal servant and is considered friendly towards you and your allies. If no command is given\comma{} they will act as a normal being\comma{} and retaliate if attacked\comma{} or run away if outmatched.
}
}
 \spellBook{Defying Nature}{Expert-level Necromancy}{
\spell{
	name = Blood Moon, school = Dark Arts, discipline = Necromancy, type = Ritual (1 day), level =Expert, range =Wandtip, noIncant = 1, duration = 1 day,higher = The duration of this spell increases sevenfold for every additional spell\minus{}level used to cast it.,noResist =1, noBlock = 1, effect =By sacrificing an animal larger than a cat\comma{} you may use the inherent power of its blood to manipulate the power of the Sun and the Moon: the sky becomes overcast and takes on an unhealthy red glow. This blocks out the effects of the sun and the moon on Vampires\comma{} Werewolves\comma{} and other such creatures. Werewolves may still choose to undergo their transformation\comma{} but retain humanoid intelligence when doing so.
}
\spell{
	name = Contagion, school = Dark Arts, discipline = Necromancy, type = Instant, level =Expert, range =Wandtip, incant = vastantes, duration = 2 days,higher = When cast as an Expert level spell or higher\comma{} you may choose which effect is inflicted\comma{} rather than rolling.,resist = Vitality, noBlock = 1, effect =Inflict a virulent\comma{} cursed disease upon the target\comma{} and will it to spread to infect others. At the end of every turn cycle\comma{} the target must perform a Resist check in order to fight off the contagion. This spell is broken and the contagion is healed upon the afflicted succeeding these Resists on two consecutive turns. Failing two consecutive Resists causes the contagion to set in for the duration. Whenever an afflicted individual comes into physical contact with another living being\comma{} they become infected by the same disease and must perform Resists as if the spell had been cast on them too.

The effect of the disease is determined by rolling a d6 on the following table:

\begin{spellitemize}
\item \boldItem{1: Dormant Virus}{Patient Zero feels no ill symptoms\comma{} but still spreads the disease like normal. When a secondary victim is infected\comma{} roll again on this table until the true nature of the disease is found.}
\item \boldItem{2: Fleshrot}{A deep necrosis sets into the infected\comma{} causing them to be considered Susceptible to all forms of damage they are not already immune to.}
\item \boldItem{3: Wheezing Lungs}{The victims\apos{}s lungs become filled with fluid and phlegm. The afflicted takes disadvantage on all \attPhys{} checks (except those used to resist {\it Contagion})\comma{} and has their movement speed halved.}
\item \boldItem{4: Itching Pox}{The afflicted is covered is itching welts\comma{} boils and rashes. Every minute the victim must succeed on a Willpower Resist against the caster\apos{}s Arcane Subjugation or scratch themselves until they bleed\comma{} becoming {\it Distracted} for 5 seconds and dealing 1d4 slashing damage to themselves.}
\item \boldItem{5: Blinding Migraines}{The afflicted suffers from terrible headaches which render them blind and force them to take disadvantage on all \attInt{} checks.}
\item \boldItem{6: Quivering Rheumatism}{The victim\apos{}s joints and muscles are aflame\comma{} causing them to take disadvantage on all accuracy checks.}
  \end{spellitemize}

This spell does not affect the Unliving (i.e. undead\comma{} phantasms\comma{} constructs or celestials).
}
\spell{
	name = Enthrall, school = Dark Arts, discipline = Necromancy, type = Instant, level =Expert, range =Close, incant = Imperius, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =A target sapient being is placed under the complete control of the caster until their concentration is broken. 

As an instantaneous action\comma{} the caster may issue simple commands through the psychic link such as `go over there' or `fight him'\comma{} this does not take up any part of their turn. The enthralled individual will complete the task to the best of their ability\comma{} but if directed to perform an action that would inevitably lead to their death or serious harm\comma{} they may perform an additional Resist check (with advantage) to break free of the enchantment.

A thrall which has not been given an order (or which has completed its orders) acts in a very basic fashion \minus{} they can defend themselves and answer simple questions\comma{} but will otherwise appear vacant and confused. 

Alternatively\comma{} the caster may devote a major action to take total control of the target \minus{} the action will be completed under their direct specification and the Thrall must do every minute thing their master commands. 

This spell is classed as an {\it Instant} spell\comma{} so the Master may cast other spells whilst this spell remains active. However\comma{} outside of this\comma{} this spell is considered a concentration spell\comma{} and hence whenever the Master takes damage they must succeed on a Resist check to maintain concentration. If the Master loses concentration\comma{} the target is freed.
}
\spell{
	name = Flesh Puppet, school = Dark Arts, discipline = Necromancy, type = Ritual (5 minutes), level =Expert, range =Wandtip, incant = inferi exorior, noDur = 1, higher = Double the number of inferi you can create \forEvery{}.,noResist =1, noBlock = 1, effect =Conduct a profane rite which breathes unlife into dead bodies\comma{} and turns them into ghastly puppets\comma{} performing your every whim: the inferi. Inferi act as golems\comma{} obeying every word of their creator. 

The caster may give verbal orders to the inferi\comma{} which they will follow without question until the task is complete\comma{} or they are given a new order. 

You may create up to 2d4 inferi at a time.
}
}
 \spellBook{Living in Shadow: The Memoirs of an Occultist}{Expert-level Occultism}{
\spell{
	name = Commune with the Dead, school = Dark Arts, discipline = Occultism, type = Ritual (2 hours), level =Expert, range =Self, incant = amisit amicum, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You may summon a spirit of a deceased humanoid\comma{} and ask 3 questions of them\comma{} or temporarily borrow one of their skills and/or spells for 1 minute. 

You must know the target\apos{}s name to summon them\comma{} though they may refuse to help you if you summon a hostile or uncooperative spirit.
}
\spell{
	name = Dreamscape, school = Dark Arts, discipline = Occultism, type = Ritual (10 minutes), level =Expert, range =Self, noIncant = 1, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =By entering into a trance\comma{} you can enter into the dream of a being that you are familiar with. If the target is asleep when you complete the ritual\comma{} you may enter into their dreams and converse with them for as long as they remain asleep. During this time\comma{} you remain in a trance and are considered {\it Asleep}\comma{} until you choose to end the effect or the target wakes. 

You may shape the dreamscape at your will\comma{} appearing in any form you choose and altering the environment as you see fit. If you choose to communicate\comma{} the target remembers everything that was said. 

You may also choose to make the dreamscape horrifying and nightmarish. The target must succeed on a Resist\comma{} or suffer from a phantasmal attack that deals 5d12 damage. 

If the target is not awake when this ritual is attempted\comma{} the spell fails and there is no FP cost\comma{} though you only discover this at the end of the 10 minute ritual.
}
\spell{
	name = Summoning Circle, school = Dark Arts, discipline = Occultism, type = Ward, level =Expert, range =Wandtip, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =By gathering together a group (only one of whom needs to be able to cast this spell)\comma{} you create a special altar from which conjuration spells are especially powerful. The radius of this region is 2m\comma{} and whilst inside it\comma{} you gain a bonus to Conjuration casting checks equal to the number of people who created the summoning circle.
}
}
 \spellBook{The Fundamental Power}{Master-level Elemental}{
\spell{
	name = Almighty Deluge, school = Charms, discipline = Elemental, type = Instant, level =Master, range =Close, incant = chimeros, noDur = 1, noHigh = 1, noResist =1, negation = Dodgeable,effect =You summon a truly gargantuan jet of water\comma{} which you make into either needle\minus{}thin jet\comma{} or a hammer\minus{}blow blast. If it makes contact with a target\comma{} deals 8d10 bludgeoning or piercing damage (your choice).
}
\spell{
	name = Fiery Whip, school = Charms, discipline = Elemental, type = Instant, level =Master, range =Close, incant = ignellum, noDur = 1, noHigh = 1, resist = Strength, negation = Blockable  and Dodgeable,effect =You summon a thin trail of fire from the end of you wand\comma{} which you can then use as a whip\comma{} performing a melee attack using your Elemental modifier (if you are proficient in Exotic weapons\comma{} you may add your Expertise modifier even if you have already added it). 

Any target hit by your flaming whip takes 9d12 fire damage\comma{} and you may direct the whip such that it wraps around them\comma{} rendering them {\it Incapacitated} until they successfully resist at the end of their turn. A trapped individual takes a further 3d12 Fire damage per turn. 

This spell lasts until you drop your wand\comma{} or you dismiss it as an instant action. No further spells can be cast whilst the whip is active.
}
\spell{
	name = Sorcerous Tornado, school = Charms, discipline = Elemental, type = Focus, level =Master, range =Close, incant = stilipare, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =A swirling\comma{} twisting column of cloud forms in the atmosphere above a targeted region within range. After 1 turn cycle of concentration the tornado slams into the ground as a cylinder 5m in radius and 50m tall. You may spend a minor action moving the tornado up to 10m per turn cycle. 

Any being which spends any part of a turn cycle in this region takes 8d8 bludgeoning damage and must succeed on a Resist check\comma{} or be caught in the vortex\comma{} taking the {\it Trapped} status effect.

Beings caught in the vortex take 2d8 bludgeoning damage per cycle and are sucked 5 metres higher into the vortex. Trapped beings may take a major action to perform the Resist check again to escape\comma{} at which point they drop out of the column onto the floor\comma{} with any associated falling damage. 

When the spell ends\comma{} the tornado disspates and all trapped beings are dropped to the floor.
}
\spell{
	name = Yawning Fissue, school = Charms, discipline = Elemental, type = Instant, level =Master, range =Close, incant = lohe, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =Target a line of natural ground (earth\comma{} mud\comma{} natural stone) up to 5m long. The earth rips asunder along this line\comma{} forming a fissure 1m wide and 10m deep. Any being caught in this region must pass a Resist check\comma{} or fall inside.

The fissure slams shut at the end of the turn cycle\comma{} trapping those inside underground and dealing 8d12 bludgeoning damage\comma{} and leaving them starved of air until they succeed in a DV 15 Strength check to dig their way out.
}
}
 \spellBook{Charms: An Expert Guide}{Master-level Kinesis}{
\spell{
	name = Gravimetric Destabilisation, school = Charms, discipline = Kinesis, type = Instant, level =Master, range =Close, incant = reimannius, duration = 1 minute,noHigh = 1, resist = Strength, noBlock = 1, effect =By focussing your intellect on a cylinder 10m in radius and 40m in height\comma{} you reverse the fall of gravity. Any unsecured objects or beings fall upwards\comma{} and those near an anchored object must Resist to hold on. 

If an upwards\minus{}falling being encounters an obstacle during their flight\comma{} they are considered `falling' and take appropriate damage. If no ceiling or obstacle is encountered before an object reaches the top of the affected cylinder\comma{} they remain are suspended at the top of the cylinder until the effect ends\comma{} or they move horizontally out of the cylinder by other means.

Whilst in freefall\comma{} or suspended in space\comma{} beings take disadvantage on all \attPhys{} and \attFin{} checks.
}
\spell{
	name = Sonic Sphere, school = Charms, discipline = Kinesis, type = Instant, level =Master, range =Close, incant = tootanus, noDur = 1, higher = \additional{2d6}{Concussive},resist = Strength, noBlock = 1, effect =Release a shockwave of sonic energy in a sphere of radius of 10m\comma{} which causes all brittle objects to shatter. All objects made of crystal\comma{} glass\comma{} ceramic or porcelain are shattered into many hundreds of pieces.

Living entities caught in the radius take 10d6 concussive damage\comma{} halved on a successful Resist
}
\spell{
	name = Teleportation Field, school = Charms, discipline = Kinesis, type = Instant, level =Master, range =Close, incant = cruratele, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You may send a non\minus{}living object up to 1 cubic metre in size to anywhere that you have previously visited\comma{} are familiar with\comma{} or know the exact spatial location of. Spell failure still teleports the object\comma{} but to an unknown location.
}
}
 \spellBook{Peeking Behind the Mystic Veil}{Master-level Telepathy}{
\spell{
	name = Link Inversion, school = Divination, discipline = Telepathy, type = Instant, level =Master, range =Sight, incant = ruinosus invertus, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =As with the {\it Disrupt Connection} spell\comma{} if the target fails to Resist\comma{} this spell severs the link between two beings such as that caused by {\it Telepathic Bond}\comma{} or by summoning a being. 

This link is then given to you \minus{}\minus{} giving you access to the telepathic network\comma{} or giving your control over the summoned creature etc\comma{} for the remainder of the original effect.
}
\spell{
	name = Network of the Minds, school = Divination, discipline = Telepathy, type = Ritual (10 minutes), level =Master, range =Close, incant = reticulum, duration = 1 day,higher = When cast for 7 days in a row\comma{} the spell has a duration of 6 months.,noResist =1, noBlock = 1, effect =Establish a telepathic link between you and up to 6 other individuals. All beings in the link are able to communicate with any other members of the link\comma{} regardless of distance\comma{} the lack of a shared language and status effects such as {\it Paralyzed}.
}
}
 \spellBook{Death Omens: What to Do When You Know the Worst is Coming}{Master-level Temporal}{
\spell{
	name = Astral Cloak, school = Divination, discipline = Temporal, type = Instant, level =Master, range =Self, incant = moxus, duration = 5 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =After uttering the incantation\comma{} you step partially into the astral realm. Most of your being resides within the Mortal Realm\comma{} but enough of your physical form seems to twist into infinite dimensions beyond the scope of human eyesight that most beings find it difficult to focus on where you actually are. 

Beings which cannot see into the Astral Realm take check double disadvantage on all accuracy checks against you.
}
\spell{
	name = Contingency, school = Divination, discipline = Temporal, type = Instant, level =Master, range =Self, incant = fortasse, noDur = 1, higher = Add an additional 2 contingencies \forEvery{}.,noResist =1, noBlock = 1, effect =You forsee a need for a certain spell in the future\comma{} but you can{\apos}t quite see when. The contingency charm allows you to store a spell in an alternative dimension\comma{} to be called forth instantly when you need it. After casting the contingency charm\comma{} you may then cast the spell that you wish to store. 

You may sacrifice your {\it Instinct} action to summon your contingency as an instantaneous action. You may have a maximum of three contingencies at any one time.
}
}
 \spellBook{On the Mysteries of the Human Mind}{Master-level Bewitchment}{
\spell{
	name = Invisibility, school = Illusion, discipline = Bewitchment, type = Ward, level =Master, range =Wandtip, incant = levis obliqua, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =Choose up to 3 target beings or objects and render them perfectly invisible until the spell ends\comma{} or the invisibility field is broken. Any equipment and clothing held by the targets is also invisible as long as it remains on their person.

The invisibility field can be disrupted by additional magic passing over the boundary of the field:  such as when spells are cast by or on an invisible being\comma{} they move into the region of an existing magical effect\comma{} or magical weapons are used by or on them. When such an effect occurs\comma{} the caster must perform an additional spellcasting check (even if the spell is memorised) to maintain the invisibility field. This does not cost additional FP\comma{} but cannot be performed if the caster is incapacitated\comma{} unconscious\comma{} asleep\comma{} or otherwise unable to attend to the magic.
}
\spell{
	name = Mass Suggestion, school = Illusion, discipline = Bewitchment, type = Instant, level =Master, range =Close, incant = faciite maxima, duration = 12 hours,noHigh = 1, resist = Willpower, noBlock = 1, effect =You speak a sentence or two to 4d6 creatures which can hear and understand you which suggest a simple course of action\comma{} and imbue those words with compelling magic\comma{} which makes the creatures want to follow the command. 

The suggestion must be worded in a manner that the targets would find reasonable and compelling – courses of action which inevitably and obviously lead to harm would cause the spell to fail\comma{} as would actions that are obviously incongruent to the situation they are in\comma{} unless carefully worded. 

On a failed Resist\comma{} the targets will willingly attempt to carry out this action to the best of its abilities. If the action is completed\comma{} or becomes impossible (i.e. a building you told them to enter is destroyed)\comma{} before the spell duration is completed\comma{} the spell ends prematurely\comma{} but otherwise they will continue attempting to carry out the suggested course of action. When the spell effect ends\comma{} the target may be confused as to why they listened to you\comma{} but will not automatically know that they have been enchanted. 

The spell effect ends if the caster or their allies damage the target.
}
\spell{
	name = Soul Ripple, school = Illusion, discipline = Bewitchment, type = Instant, level =Master, range =Wandtip, incant = cessabit, duration = 2 minutes,noHigh = 1, resist = Evil, noBlock = 1, effect =With the gentlest of touches\comma{} you prod the mind of the targeted being\comma{} causing a ripple throughout their soul. A corrupted soul may attempt to resist this effect\comma{} negating it. 

You may choose to make the target either Immune or Susceptible to a chosen damage type for the duration of the spell. If this spell is cast a second time\comma{} the previous effect is instantly ended.
}
}
 \spellBook{The Immoral Art of Psionics}{Master-level Psionics}{
\spell{
	name = Linguistic Aphasia, school = Illusion, discipline = Psionics, type = Instant, level =Master, range =Close, incant = squiddle\minus{}de\minus{}bop, duration = 1 hour,noHigh = 1, resist = Logic, noBlock = 1, effect =On a failed resist\comma{} the target\apos{}s mind becomes so completely ruined that they lose the ability to process language. The target can no longer communicate either verbally or with written language properly. 

As far as they are concerned\comma{} everyone is speaking or writing pure nonsense to them\comma{} whilst to everyone else they appear to be spouting gibberish. 

The victim may attempt to resist every turn to end the effect\comma{} though a successful resist (including the first) deals 3d10 psychic damage.
}
\spell{
	name = Modify Memory, school = Illusion, discipline = Psionics, type = Instant, level =Master, range =Close, incant = obliviate, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =If target fails a Resist check\comma{} you may modify the memories of the target\comma{} erasing memories\comma{} or fabricating new ones. 

You may even cause them to forget skills and spells that they currently know: remove one memorised spell or Skill from their character sheet.
}
\spell{
	name = Psionic Overload, school = Illusion, discipline = Psionics, type = Instant, level =Master, range =Close, incant = onero mentis, noDur = 1, noHigh = 1, resist = Willpower, noBlock = 1, effect =Unleash a blast of psionic energy from the end of your wand\comma{} filling the heads of all those caught in a the blast radius with chaotic and destructive energy. 

This spell extends out in a cone up to 3 metres from your wand. All creatures caught in this region take 7d12 psychic damage\comma{} halved on a successful resist.
}
}
 \spellBook{Conjuring and Summoning for the Experienced Witch}{Master-level Conjuration}{
}
 \spellBook{Cursing your Way to Revenge}{Master-level Curse}{
\spell{
	name = Corrupt Object, school = Maledictions, discipline = Curse, type = Ritual (1 hour), level =Master, range =Wandtip, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =This spell allows you to corrupt and redirect the magical nexus of an enchanted object\comma{} causing it to malfunction\comma{} gain additional negative effects\comma{} or destroying it completely. 

You may alter the meaning of the runechains on an enchanted object slightly (i.e. causing a bludger to attack a single person\comma{} rather than follow the rules of quidditch)\comma{} remove a runechain entirely\comma{} or add an additional negative effect of your choosing.
}
\spell{
	name = Cursed Step, school = Maledictions, discipline = Curse, type = Instant, level =Master, range =Close, incant = gradus maledictus, duration = 1 day,noHigh = 1, resist = Acrobatics, negation = Blockable  and Dodgeable,effect =When this spell hits the target\comma{} their very presence in an area is enough to leave a cursed aura. 

Every step taken by the afflicted leaves a footprint in the astral realm\comma{} which lasts for 5 minutes after the being last stood there. Any being which touches one of these footprints takes check disadvantage on all checks for the next minute (this timer resets every time they touch a different footprint). 

If the afflicted stays in one place for more than 5 seconds\comma{} they too become afflicted by their own footprint.
}
\spell{
	name = Wither, school = Maledictions, discipline = Curse, type = Instant, level =Master, range =Close, incant = unis, duration = 1 minute,higher = The \attPhys{} penalty is increased by 2 \forEvery{}.,resist = Vitality, noBlock = 1, effect =Necrotic energy seeps up from the ground\comma{} into the target\comma{} causing them to undergo a severe physical degradation\comma{} reducing their \attPhys{} score by 4 for the duration of the spell. 

This effect is halved on a successful Resist.
}
}
 \spellBook{Dark Forces: A Guide to Self\minus{}Defense}{Master-level Hex}{
\spell{
	name = Crush Bones, school = Maledictions, discipline = Hex, type = Instant, level =Master, range =Sight, incant = obcillo ossium, noDur = 1, higher = \additional{4d10}{bludgeoning},resist = Strength, noBlock = 1, effect =A great force smashes into the opponent\comma{} breaking their bones. Does 8d10 bludgeoning damage\comma{} and applying the {\it Broken Bone} status effect and the associated {\it Serious Injury} status. 

If the target succeeds in a resist\comma{} the damage is halved and the status effects are negated.
}
\spell{
	name = Meteor Strike, school = Maledictions, discipline = Hex, type = Instant, level =Master, range =Sight, incant = bothynus, noDur = 1, higher = The meteor deals an additional 2d6 fire damage and 2d6 concussive damage \forEvery{}.,resist = Acrobatics, noBlock = 1, effect =A giant orb of fire and rock slams down into the ground at a targeted point\comma{} releasing a shockwave over a region 5m in radius. All beings in the region take 5d6 fire damage and 5d6 concussive damage.
}
}
 \spellBook{Ponderances on Advanced Healing}{Master-level Healing}{
\spell{
	name = Regenerate, school = Recuperation, discipline = Healing, type = Instant, level =Master, range =Wandtip, incant = regus, duration = 5 minutes,noHigh = 1, noResist =1, noBlock = 1, effect =This spells vastly increases the natural healing rate of a being \minus{} they heal at a rate of 40HP per minute (2HP per combat cycle)\comma{} broken bones mend themselves and even severed limbs regrow over the course of the spell.
}
\spell{
	name = Suspended Animation, school = Recuperation, discipline = Healing, type = Ritual (30 minutes), level =Master, range =Wandtip, incant = fautis, duration = 3 hours,noHigh = 1, noResist =1, noBlock = 1, effect =When cast upon a willing living being\comma{} they are placed into a state of suspended animation which perfectly replicates the outward appearance of death. All magical effects\comma{} poisons\comma{} curses and other time\minus{}dependent effects currently in place on the target are paused until the spell wears off. 

The target is {\it Unconscious} for the duration\comma{} awakening only when the spell duration finishes\comma{} or the original caster expends a major action to reawaken them.
}
}
 \spellBook{Shields and Wards}{Master-level Warding}{
\spell{
	name = Anti\minus{}Apparition Ward, school = Recuperation, discipline = Warding, type = Ward, level =Master, range =Wandtip, incant = nonvidetus, duration = 1 week,noHigh = 1, noResist =1, noBlock = 1, effect =Prevents apparition inside the designated area: no human can apparate in our out for the duration of the ward. Attempts to apparate into the region trigger a {\it splice} and reflect the individual back to their origin.
}
\spell{
	name = Anti\minus{}Magic Ward, school = Recuperation, discipline = Warding, type = Ward, level =Master, range =Wandtip, incant = prohibere incatatum, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Establish a spherical region up to 10 metres in radius inside which all magic is utterly useless. No magic can be cast inside the warded area\comma{} enchanted items have no power\comma{} and all magic effects passing over the boundary vanish. 

Enchanted items regain their abilities after they are removed from the region\comma{} but enchantments on individuals are not re\minus{}established.
}
}
 \spellBook{The Subtle Nuances of Transmogrification\comma{} Transformation and Transfiguration}{Master-level Alteration}{
\spell{
	name = Mass Reshape Body, school = Transfiguration, discipline = Alteration, type = Instant, level =Master, range =Close, incant = subsintus, duration = 1 hour,noHigh = 1, resist = Conviction, noBlock = 1, effect =You transform and reshape the body of up to 3d4 target beings within range\comma{} molding them into a new\comma{} animalistic forms. Unwilling targets can nullify this effect by succeeding on a Resist check\comma{} which is performed with advantage if the target is currently in combat with the caster. 

The final form of each target is chosen by the caster\comma{} and should be a creature that they know of whose Ministry Rating differs from that of the target\apos{}s current form by only 2 points\comma{} in either direction. If the target does not have a Ministry Rating (i.e. a sapient being)\comma{} use the following conversion table:

\begin{rndtable}{c c}
\bf Level & \bf MoM Equivalent \\
1\minus{}5   & III \\
6\minus{}9  &  IV \\
10\minus{}14 & V \\
15\minus{}18  & VI \\
18 + & VII
\end{rndtable}

The target replaces all of their statistics\comma{} including those associated with their consciousness\comma{} with those of the selected being. The target retains basic memories of their previous life\comma{} allies and enemies\comma{} though these are filtered through the intellectual limitations of their new form. Any equipment that the target had on their person is merged into their new form\comma{} and cannot be used until the effect ends. The target is limited in their actions to only those that their chosen form can carry out\comma{} and so (generally) cannot speak\comma{} cast spells or use items. 

The effect ends either when the magic is dispelled\comma{} the spell effect ends\comma{} or the creature drops to 0HP. The target reassumes their natural form with the original number of HP. If the reversion was because of dropping to 0HP\comma{} any excess damage is then dealt to the original form\comma{} but they do not suffer any additional side effects from having been reduced to 0HP in their animal form.
}
\spell{
	name = Permanence, school = Transfiguration, discipline = Alteration, type = Ritual (30 seconds), level =Master, range =Close, incant = perpetuus, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =When cast on any transfigured or conjured object\comma{} makes the transformation permanent and removes any associated time constraints. 

This does not protect against {\it Banishments}\comma{} and this spell can be removed by a successful counterspell\comma{} at which point any `duration' timer associated with the transformation continues as if it had been paused.
}
\spell{
	name = Selfshift, school = Transfiguration, discipline = Alteration, type = Instant, level =Master, range =Self, incant = muto, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You assume the form of any object you wish\comma{} or a being with a MoM rating less than or equal to V. 

You take on the physical attributes and abilities of your new form\comma{} though you keep your intellect and consciousness intact: replace your \attPhys{}\comma{} \attFin{}\comma{} \attChr{} and \attPow{} attributes and attributes with those of your new form. Though your \attInt{} and \attSpr{} values remain unchanged\comma{} if the target form possess additional proficiencies in those areas that you do not have\comma{} take those in addition to your original ones.

Under all but powerful magical investigation\comma{} you are indistinguishable from this chosen form until the spell is broken. Any equipment that the you had on their person is merged into your new form\comma{} and cannot be used until the effect ends. You are limited in your actions to only those that your chosen form can carry out (if any)\comma{} and so you (generally) cannot speak\comma{} cast spells or use items\comma{} with the exception of ending this spell effect.

The effect ends either when the magic is dispelled\comma{} the spell effect ends\comma{} or your chosen form is destroyed or drops to 0HP. You reassume your natural form with the original amount of HP. If the reversion was because of dropping to 0HP\comma{} any excess damage is then dealt to your original form\comma{} you do not suffer any additional side effects from having been reduced to 0HP in their animal form.
}
}
 \spellBook{Conjuring and Summoning for the Experienced Witch}{Master-level Conjuration}{
\spell{
	name = Dimensional Binding, school = Transfiguration, discipline = Conjuration, type = Ritual (5 turns), level =Master, range =Self, incant = subjungus, duration = 1 day,noHigh = 1, resist = Power, noBlock = 1, effect =By inscribing a magic circle on the floor\comma{} you create a region where celestial beings from other planes can be trapped and bent to your will. For the next hour\comma{} if an Unlife\comma{} or other being originating from any plane other than the Mortal Realm\comma{} enters into the region\comma{} you may cast a pinch of salt into the circle to complete the ritual and attempt to impose your will over it. 

On a failed resist\comma{} the being is bound to serve you for the duration of the spell. If the being was summoned or created by another spell\comma{} that spell is extended to match the duration of this spell. The being will obey your commands to the letter for the duration of the spell\comma{}and if they are hostile to you\comma{} they may do so in a deliberately obtuse fashion.
}
\spell{
	name = Extraplanar Champion, school = Transfiguration, discipline = Conjuration, type = Ritual (1 hour), level =Master, range =Self, incant = lacerabis, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Summon a Celestial or Abomination from across the dimensions\comma{} and bind it to your will.

You have a number of `points’ equal to the spell level used to cast this spell – the maximum MoM rating of any beast you can summon is equal to this value. Alternatively you may distribute these `points’ by summoning several lower\minus{}rated creatures\comma{} as long as the total MoM rating does not exceed the spell level used (for this purpose a rating of 0 is assigned a value of 0.5). At second level you could summon 1 rating\minus{}II creature\comma{} 2 rating\minus{}I creatures or 4 rating\minus{}0 creatures. At third level you could summon a rating III creature or 1 rating\minus{}II creature and a rating\minus{}I creature\comma{} and so on. 

Within these restrictions\comma{} you may summon a Champion(s) of your choice that you have previously encountered or studied\comma{} or alternatively you may allow random chance to decide which beings answer your call. 

The chosen beings enter into this dimension bound to your will\comma{} they will obey any command you give them through the psychic link which connects you (costing a minor action). If a summoned being reaching 0HP the link is broken and the being returns to its native plane.
}
}
 \spellBook{Magick Moste Evile}{Master-level Necromancy}{
\spell{
	name = Burning Blood, school = Dark Arts, discipline = Necromancy, type = Focus, level =Master, range =Close, incant = zesto sidero, noDur = 1, noHigh = 1, noResist =1, negation = Dodgeable,effect =You corrupt their very blood\comma{} turning it into a burning acid\comma{} or molten lead. Whilst you maintain focus\comma{} the target takes 6d12 acid or fire damage (your choice).
}
\spell{
	name = Inevitable Death, school = Dark Arts, discipline = Necromancy, type = Instant, level =Master, range =Sight, incant = avada kedavra, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =If the spell makes contact with the target\comma{} kills them instantly. 

When encountering shields and other protective barriers\comma{} deals 10d10 damage to them.
}
\spell{
	name = Transcend Mortality, school = Dark Arts, discipline = Necromancy, type = Ritual (1 day), level =Master, range =Self, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =After performing a profane ritual (the secrets of which are too disgusting to write down here\comma{} though it is safe to say it involves the gruesome death of at least one innocent soul)\comma{} the caster places a portion of their soul into another object. Write down the horcrux on a piece of paper and keep it hidden. 

Whilst a horcrux exists\comma{} the character cannot be killed\comma{} though they undergo a horrifying spiritual transformation\comma{} becoming one of the {\it Et Iniquum}\comma{} a corrupted non\minus{}human spirit residing within the humanlike shell of their former self. Whenever an Et Iniquum is killed\comma{} this corrupted spirit remains bound to the Earth in the form of an {\it \inotator}\comma{} a ghostly spirit which seeks out living beings to attach itself to\comma{} before regaining its physical form as an {\it Aileni}. Whilst the Et Iniquum retained their humanlike appearance\comma{} the Aileni are every bit as horrifying on the outside as their soul is\comma{} gaining immense magical power in the process. 

A horcrux can only be destroyed through extremely potent spells or poisons\comma{} and a being may create multiple such horcruxes\comma{} though you are warned that a soul can only be splintered so many times before it shatters completely – creating more than 2 + SPR modifier horcruxes can lead to horrifying consequences.
}
}
 \spellBook{Covens: The Power in the Circle}{Master-level Occultism}{
\spell{
	name = Coven\apos{}s Protection, school = Dark Arts, discipline = Occultism, type = Ritual (4 hours), level =Master, range =Wandtip, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =This ritual can only be performed in an isolated area\comma{} in the middle of the night. By gathering together and invoking the name of an unspeakable\comma{} unknowable power\comma{} you bind the life forces of all participants together\comma{} to form a unified whole. While the Coven exists\comma{} any member may use a minor action to transfer their own HP or FP to any other member of the coven\comma{} and multiple members may send HP/FP to the same target at any given moment. This cannot be used to raise a target\apos{}s HP/FP above their maximum values. If too many points are sent to a target\comma{} the excess points are lost. It is possible for a coven member to die by transferring all of their HP to the network. 

If psychic damage is inflicted on any member of the Coven in the same turn\minus{}cycle that HP or FP are being transferred\comma{} that damage is done to all members of the Coven. If this damage is also a Critical Strike\comma{} then the ritual is distrupted and the spell is ended.
}
\spell{
	name = Unbreakable Vow, school = Dark Arts, discipline = Occultism, type = Ritual (30 minutes), level =Master, range =Wandtip, noIncant = 1, duration = $\infty$,noHigh = 1, resist = Deception, noBlock = 1, effect =Two willing participants enter into an agreement\comma{} and this spell is cast upon them. If neither of the parties succeed on a Resist check\comma{} this vow becomes utterly unbreakable. 

Any attempt to deviate from the exact wording of the vow causes the participant to instantly perish.
}
}
 \spellBook{Storms\comma{} Seas and Seismic Shocks}{Ascendant-level Elemental}{
\spell{
	name = Channel Cataclysm, school = Charms, discipline = Elemental, type = Instant, level =Ascendant, range =Close, incant = moqai, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =Raise your wand into the air\comma{} and summon the raw energy of the universe. A bolt of energy descends from the heavens\comma{} into your wand and is directed from your other\comma{} outstretched hand as an energetic blast\comma{} focussed on a single individual.

If the bolt strikes the target\comma{} they take 15d10 force\comma{} electric or celestial damage.
}
\spell{
	name = Earthquake, school = Charms, discipline = Elemental, type = Instant, level =Ascendant, range =Close, incant = krakato, noDur = 1, noHigh = 1, resist = Acrobatics, noBlock = 1, effect =Summon a powerful seismic disturbance in a radius of 50m around a region that you can see. 

The powerful rocking of the earth knocks all beings into the {\it Prone Position} unless they Resist\comma{} and all beings performing a Focus action must perform the usual Resist check to maintain concentration.

The earthquake also spawns 2d4 {\it Fissures} at locations chosen by the caster (see the relevant spell). 

For every building or structure in the region\comma{} roll a d4. If the result is a one\comma{} the building collapses and is destroyed. Beings in a destroyed building take 10d10 bludgeoning damage.
}
\spell{
	name = Immolation, school = Charms, discipline = Elemental, type = Instant, level =Ascendant, range =Close, incant = uro, noDur = 1, noHigh = 1, noResist =1, negation = Dodgeable,effect =A small ember drifts lazily from the end of your wand\comma{} and latches onto your target\comma{} igniting a small part of the target. Once it has taken root\comma{} nothing can extinguish this fire until it either runs out of fuel\comma{} or out of air. No magical intervention known to wizardkind can end its life before one of these conditions is met. 

The ember deals 1d6 damage per turn. Every time a magical or mundane attempt is made to extinguish the fire\comma{} it doubles in intensity spreading rapidly\comma{} and doubles the damage it deals per turn. 

The fire may be moved using the {\it Control Fire} spell\comma{} but only when cast as a Master Level spell\comma{} and even then requires a DV 20 Power check to successfully remove the fire.
}
\spell{
	name = Primal Tempest, school = Charms, discipline = Elemental, type = Ritual (2 hours), level =Ascendant, range =Self, incant = thyella, noDur = 1, noHigh = 1, resist = Vitality, noBlock = 1, effect =Spend 2 hours adorning yourself with special paints and oils\comma{} attuning yourself to the wrathful spirits of the Air Domain. At any point in the next day\comma{} raise your wand to the heavens and shout the incantation\comma{} summoning the most powerful storms in existence. 

Thick black clouds appear\comma{} blotting out the sun and torrential rain and powerful winds are summoned\comma{} providing severe obscuration to vision. All ranged accuracy and spellcasting checks take disadvantage. 

The caster may also take a minor action to summon bolts of lightning to strike 2d4 targets in sight\comma{} dealing 8d10 electric damage (halved on a resist)\comma{} or to spawn a {\it Tornado} (see relevant spell) which stays fixed at a specified location for 5 turns.
}
\spell{
	name = Tsunami, school = Charms, discipline = Elemental, type = Focus, level =Ascendant, range =Sight, incant = unda maxima, noDur = 1, noHigh = 1, resist = Strength, noBlock = 1, effect =You conjure a gigantic wall of water\comma{} 15 metres long and 5 metres tall. You may choose how to orient the wave\comma{} which proceeds to move forward at a speed of 20 metres per round.

For every 20 metres the wave moves forward\comma{} it loses 1 metre of height. The wave lasts until its height reaches zero\comma{} or concentration is broken. 

Any being which spends any part of its turn in the wave takes 8d12 damage (halved on a successful resist) and have their speed set to zero until the end of the next round.
}
}
 \spellBook{Extreme Incantations}{Ascendant-level Kinesis}{
\spell{
	name = Mass Kinesis, school = Charms, discipline = Kinesis, type = Focus, level =Ascendant, range =Close, incant = ballatutti, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Control huge numbers of objects as they levitate and move around: write a thousand books with a thousand quills\comma{} conduct a swordfight with multiple blades at once. 

This spell can only replicate the effects of an item if you would normally be able to use them without magic\comma{} but otherwise you can move the objects around in 3D space at your own discretion. 

You may only perform up to 5 unique actions with the objects\comma{} but you may duplicate those exact actions an arbitrary number of times in a 30m radius. For example\comma{} you could only copy out 5 books at a time\comma{} as each book requires a unique action\comma{} but you can copy the same book out as many times as you like\comma{} as the action is identical.
}
\spell{
	name = Sphere of Immobility, school = Charms, discipline = Kinesis, type = Instant, level =Ascendant, range =Self, incant = stabit maxima, duration = 1 minute,noHigh = 1, noResist =1, noBlock = 1, effect =Enforce a {\it Halt} charm so strong that nothing in a sphere 10m in radius\comma{} centred on the caster (at the moment of casting) can move. Time moves normally\comma{} and sentient beings are aware of what is happening\comma{} but no being or object other than the caster can move in this region until the spell ends\comma{} at which point the previous movement resumes.   

Beings outside the region can observe the interior\comma{} but attempting to enter the region causes 15d6 force damage\comma{} as the being also becomes partially trapped.
}
}
 \spellBook{Mind Beyond Body}{Ascendant-level Telepathy}{
\spell{
	name = Join Minds, school = Divination, discipline = Telepathy, type = Ritual (3 hours), level =Ascendant, range =Self, noIncant = 1, duration = 1 week,noHigh = 1, noResist =1, noBlock = 1, effect =You perform a ritual which involves two people (only one of whom needs to know how to cast this spell). This spell joins your souls together in an intricate fashion. You become but one soul\comma{} in two bodies. 

At any point during the spell\apos{}s duration\comma{} you may decide to use your minor movement action to switch bodies\comma{} transplanting your soul from one body to the other. 

Change your \attSpr{}\comma{} \attInt{}\comma{} \attChr{} and \attEvl{} with your joined partner (and any associated proficiencies) and you now reside in their body. You may then take actions as if you were them until you decide to switch back\comma{} or the spell is ended. 

When the spell ends\comma{} your soul always returns to your original body.
}
\spell{
	name = True Sight, school = Divination, discipline = Telepathy, type = Ritual (5 minutes), level =Ascendant, range =Self, incant = vidergo sumus, duration = 1 hour,noHigh = 1, noResist =1, noBlock = 1, effect =You prepare for this spell by daubing a third eye onto your forhead. On completion of the sell\comma{} this eye glows for a second\comma{} before vanishing. 

For the duration of the spell\comma{} you see things as they truly are. You see hidden traps\comma{} secret doors\comma{} and even into the Astral plane. You can see through illusion spells\comma{} and attempts to deceive or trick you are in vain. All Perception checks automatically succeed\comma{} and you are immune to being surprised. 

You can also see into the minds of your enemies\comma{} giving you an extra few moments to anticipate their actions. You gain check advantage on all accuracy checks\comma{} and they take disadvantage on all accuracy checks against you.
}
}
 \spellBook{Time \& its Mysteries}{Ascendant-level Temporal}{
\spell{
	name = Astral Projection, school = Divination, discipline = Temporal, type = Ritual (2 minutes), level =Ascendant, range =Self, incant = ambilofors, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Leave your physical form behind\comma{} and project your spirit into the Astral Realm. You mortal body falls unconscious as your spirit leaves it. 

Your astral self is undetectable to most living beings\comma{} but appears almost identical to your physical form\comma{} including astral copies of all your equipment. Your astral form has 8d6 HP\comma{} but can only interact with other entities on the Astral Realm and effects which explicitly state they effect the astral realm. 

If your astral self is killed\comma{} your physical body{\apos}s HP is reduced to zero\comma{} and your enter into the {\it Critical But Stable} status. Equally\comma{} if your mortal body is reduced to 0HP\comma{} the effects of this spell are ended and your spirit immediately returns to your body. 

Whilst in the astral realm you may perceive all events occuring in the Mortal plane\comma{} and you may move through regions that are inaccessible in the mortal plane. 

If you attempt to leave the astral plane\comma{} either willingly by ending this spell effect\comma{} or by an effect that states that it removes you from the realm (such as a portal)\comma{} your body is teleported to the location corresponding to your spirit\apos{} new location.
}
\spell{
	name = Control Time, school = Divination, discipline = Temporal, type = Ritual (various lengths), level =Ascendant, range =Self, incant = tempus fugit, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =At the moment you begin the ritual\comma{} you start a stopwatch\comma{} and begin pouring magical energy into the timepiece\comma{} as you focus your understanding of the mysteries of time into this object. 

For every second that you spend performing this ritual\comma{} the stopwatch ticks forward an additional minute. 

When you finish the ritual\comma{} the stopwatch rises into the air\comma{} and forms a shimmering portal to either the past or the future (decided by the caster)\comma{} capable of transporting up to 5 beings. Upon stepping into the portal\comma{} you are transported through time by an amount equal to the reading on the stopwatch. The portal deposits you at your present physical location (taking into account any changes in the local height that may have happened in the intervening time)\comma{} and then closes.
}
}
 \spellBook{Merlin\apos{}s Tricks and Incantations}{Ascendant-level Bewitchment}{
\spell{
	name = True Illusion, school = Illusion, discipline = Bewitchment, type = Ritual (10 minutes), level =Ascendant, range =Sight, incant = stultuvisus, duration = 1 day,noHigh = 1, resist = Investigation, noBlock = 1, effect =Create a perfect illusion which can be interacted with and touched by the target. This illusion replicates sounds\comma{} smells\comma{} heat and all other imaginable stimuli. The illusion can occupy a space up to 20m in radius and can include any environments\comma{} people\comma{} beasts and monsters that the caster can imagine. 

The caster may also imbue any `characters’ within the illusion with a semblance of life – illusory people\comma{} for example\comma{} will walk\comma{} talk and interact with others (real or illusory) in the environment. The Illusiory beings can only have the knowledge that the caster has\comma{} but they operate as individuals and mimic the people they represent. The caster may use a minor action to give a psychic command to some aspect of the illusion to change its appearance\comma{} or cause it to undertake some action. 

An observer may determine that the illusion is not real by performing a Resist as a major action.
}
}
 \spellBook{Melting Minds: The Master Guide to Psionics}{Ascendant-level Psionics}{
\spell{
	name = Destroy Mind, school = Illusion, discipline = Psionics, type = Instant, level =Ascendant, range =Close, incant = mentis perdero, noDur = 1, noHigh = 1, resist = Conviction, noBlock = 1, effect =Shatter the mind of a sapient target being on a failed resist\comma{} rendering them a shadow of their former self. Choose from one of the following effects:

\begin{spellitemize}
\item Render them incapable of using magic (target gets advantage on resist if you choose this effect)
\item Remove up to 1d4 spell\comma{} attribute\comma{} tool or weapon proficiencies from the target 
\item Render them unable to learn new information
\item Place them into a coma for 1d20 years
\end{spellitemize}
}
\spell{
	name = Mass Delusion, school = Illusion, discipline = Psionics, type = Instant, level =Ascendant, range =Sight, incant = falasarium maxima, duration = 12 hours,noHigh = 1, resist = Conviction, negation = Blockable,effect =Apply the {\it Delusion} spell to 4d6 targets of your choice. The delusion is the same to all targets.
}
}
 \spellBook{The Demons Beyond the Veil}{Ascendant-level Conjuration}{
}
 \spellBook{The Bumper Book of Crooked Curses}{Ascendant-level Curse}{
\spell{
	name = Revoke Power, school = Maledictions, discipline = Curse, type = Instant, level =Ascendant, range =Close, incant = anakalo, duration = 1 hour,noHigh = 1, resist = Power, noBlock = 1, effect =On a failed Resist\comma{} the caster may revoke one ability of the target for the duration of the spell. 

This includes degrading an Immunity to a Resistance\comma{} or removing a Resistance entirely. You may also remove any ability listed in a being\apos{}s ability or actions block\comma{} or remove a sapient being\apos{}s ability to cast spells from one magical discipline. If this spell is cast on a being every day for a week\comma{} the being eventually has the ability permanently removed.
}
\spell{
	name = Taboo, school = Maledictions, discipline = Curse, type = Ritual (1 week), level =Ascendant, range =Self, noIncant = 1, duration = 1 year,noHigh = 1, noResist =1, noBlock = 1, effect =A particularly powerful an unusual curse \minus{} the Taboo curse is placed on an individual word\comma{} rather than on a person. 

When casting the Taboo curse\comma{} the caster designates up to 7 {\it enforcers}\comma{} and a single word. If that word is spoken aloud\comma{} anywhere in the world\comma{} the enforcers are alerted and may take a major action to teleport directly to that location\comma{} ignoring any wards or shields protecting it. The arrival of the enforcers is treated as a surprise\comma{} and the first attack made by each of the enforcers is a critical strike. 

Care must be taken\comma{} however\comma{} that the chosen word is not too common \minus{} as the enforcers have no way of sifting through which uses of the chosen word are relevant or not.
}
}
 \spellBook{An Auror\apos{}s Toolkit}{Ascendant-level Hex}{
\spell{
	name = Disintegrate, school = Maledictions, discipline = Hex, type = Instant, level =Ascendant, range =Sight, incant = reducto, noDur = 1, noHigh = 1, noResist =1, negation = Blockable  and Dodgeable,effect =If the spell makes contact with matter\comma{} causes it to instantly disintegrate. Living beings take 15d10 worth of force damage.
}
\spell{
	name = Heavenly Arsenal, school = Maledictions, discipline = Hex, type = Instant, level =Ascendant, range =Sight, incant = ouranios, duration = 1 minute,noHigh = 1, resist = Power, noBlock = 1, effect =As you cast this spell\comma{} 7 motes of heavenly light and sit above your head like a celestial halo. Over the next minute\comma{} you may choose to up to 3 any number of these motes at a target of your choice as an instant action once per turn. 

Each mote does 4d6 of damage\comma{} negated on a successful Resist. The type of damage is determined by rolling a d10:
\begin{spellitemize}
\item 1: Fire
\item 2: Cold
\item 3: Force
\item 4: Acid
\item 5: Bludgeoning
\item 6: Piercing
\item 7: Slashing
\item 8: Psychic
\item 9: electric
\item 10: celestial
\end{spellitemize} 

If the target is Immune to the chosen damage type\comma{} you may roll again. Whilst you have at least one mote in your halo\comma{} you cast bright light around you for 10m\comma{} and dim light for a further 20\comma{}
}
}
 \spellBook{Journals of St. Mungo\comma{} the Master Healer}{Ascendant-level Healing}{
\spell{
	name = Mass Healing, school = Recuperation, discipline = Healing, type = Instant, level =Ascendant, range =Close, incant = enervate maxima, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Roll 10d10\comma{} and multiply this result by 10 (alternatively\comma{} use the average result of 500). 

You may restore this amount of HP to all living beings within range\comma{} distributed as you wish. If a creature receives at least 1HP and is above 0HP\comma{} all negative status effects are removed.
}
\spell{
	name = Spark of Life, school = Recuperation, discipline = Healing, type = Ritual (12 hours), level =Ascendant, range =Wandtip, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You spend hours pouring over the corpse of a being which has been dead no more than 24 hours at the beginning of the ritual. The body of the corpse must be (mostly) intact\comma{} such that they won't immediately perish again. 

By summoning great power and energies\comma{} you nuture the tiniest\comma{} vanishing flicker of life which remains within this being\comma{} and restore them back to life. The being comes back with 0HP and the {\it Critical but Stable} condition.
}
}
 \spellBook{The Shield in the Dark}{Ascendant-level Warding}{
\spell{
	name = Fidelius Ward, school = Recuperation, discipline = Warding, type = Ritual (2 weeks), level =Ascendant, range =Wandtip, incant = onsigno scientia, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Select a target object\comma{} being or region of radius 10m in radius\comma{} and a second being\comma{} the {\it Keeper}\comma{} which cannot be the caster. 

The target can then only be detected or interacted with by the Keeper. The Fidelius ward ensures that even if another being were touching the subject of the spell\comma{} their brain is simply unable to comprehend what it is they are looking at\comma{} and will not recognise it. The same is true of instructions and maps which lead to the hidden object which were written before the object was hidden: they appear as meaningless squiggles\comma{} and memories regarding the subject become ethereal and dreamlike \minus{} with important details becoming just out of reach. 

However\comma{} if the Keeper willingly divulges information (either written\comma{} or verbal) to another being\comma{} then that person also becomes a Keeper. If a Keeper dies\comma{} and no other Keeper remains alive\comma{} they return as a Ghost and cannot pass on until they create a new Keeper. 

This charm is broken if any Keeper touches the subject of the Ward (or for a region\comma{} enters it).
}
\spell{
	name = Incineration Field, school = Recuperation, discipline = Warding, type = Ward, level =Ascendant, range =Wandtip, incant = kafsis, duration = 5 minutes,noHigh = 1, resist = Observation, noBlock = 1, effect =You place an incredibly powerful ward at a point in space\comma{} erecting a force field with a maximum radius equal to your twice your power attribute (in metres). 

Any being which attempts to pass over the threshold must succeed on a Resist\comma{} or take a step inside the field. Taking a step inside the field deals 8d12 force damage\comma{} and if the target then fails a subsequent DV 10 Acrobatics Resist\comma{} they continue entirely over the threshold and are incinerated entirely. 

A successful Resist at either point allows one to pull back before too much damage is done. 

The ward can absorb 10d20 points of damage (any type) before it disintegrates.
}
}
 \spellBook{Altering the World}{Ascendant-level Alteration}{
\spell{
	name = Guardian Army, school = Transfiguration, discipline = Alteration, type = Instant, level =Ascendant, range =Close, incant = piertotom locomotum, duration = 1 day,noHigh = 1, noResist =1, noBlock = 1, effect =Transform up to 5d6 nearby statues\comma{} trees and other large inanimate objects into powerful guardians to fight by your side\comma{} and imbue them with purpose. These guardians are considered as Stone Golems unless otherwise indicated/. 

The caster possess a psychic link to one which may be designated as a `general’. The caster may use an instantaneous command to issue orders to the general\comma{} which will then coordinate the remaining guardians in completing this action. The guardians are fiercly loyal and will willingly destroy themselves in the line of duty. If the general is destroyed\comma{} the caster may use a minor action to touch another of the guardians\comma{} promoting them to the new general. 

When the action is completed\comma{} their orders become irrelevant\comma{} or the general is destroyed\comma{} the Guardian\apos{}s default to their standard behaviour\comma{} which is preventing any harm coming to the caster\comma{} in any way they can.

When the HP of a Guardian is reduced to zero\comma{} their physical forms crumbles into dust and shards.
}
\spell{
	name = True Transfiguration, school = Transfiguration, discipline = Alteration, type = Instant, level =Ascendant, range =Close, incant = omnio mutare, noDur = 1, noHigh = 1, resist = Power, noBlock = 1, effect =On a failed resist\comma{} the target undergoes a complete and true transformation of their nature\comma{} on both a spiritual and a physical level. The end result of the transformation can be chosen by the caster. 

To all intents and purposes\comma{} the target acts as if they have always been of your chosen form – replacing all of their statistics and abilities with those associated with their new body. It is up to the caster if the equipment and clothing merge into the new form\comma{} or simply fall away as the change takes hold. 

This spell is permanent\comma{} and cannot be dispelled. The only way to undo the effects of this spell is through a second {\it True Transfiguration} back into the original form\comma{} in which case the target may retain only fleeting memories of their time in their new body. 

This spell cannot {\it create} a soul\comma{} however. Attempting to convert a non\minus{}living\comma{} dead\comma{} or un\minus{}life object or being into a sapient creature results in spell failure\comma{} or creates an organic body which is in a coma.
}
}
 \spellBook{The Demons Beyond the Veil}{Ascendant-level Conjuration}{
\spell{
	name = Archon\apos{}s Spirit, school = Transfiguration, discipline = Conjuration, type = Ritual (1 week), level =Ascendant, range =Self, noIncant = 1, duration = 1 minute,noHigh = 1, noResist =1, noBlock = 1, effect =Spend an entire week imbuing yourself with the energies of far\minus{}flung realities\comma{} melding your very soul with the mighty powers beyond this reality\comma{} the Archons\comma{} and convincing the almighty beings that exist there to aid you in your quest. Upon completing this ritual\comma{} you are granted a single Celestial Token. 

If any being besides the original caster attempts to wield the Celestial Token\comma{} or if the caster attempts to cast this spell again whilst still in posession of another Token\comma{} they take 15d10 psychic damage. Whilst in the hands of the caster\comma{} they may use an instantaneous action to activate the token\comma{} summoning the spirit of an Archon into their own body. Whilst the Archon inhabits the caster\apos{}s body they have the following abilities:
\begin{spellitemize}
\item They float in midair\comma{} and have a flying speed equal to their movement speed
\item They glow with a mighty radiance\comma{} emitting a bright light for 30m 
\item The caster\apos{}s Power attribute is doubled\comma{} and take advantage on all spell\minus{}related checks.
\item Considered resistant to all damage\comma{} and take advantage on all Resist checks
\item Spells cost no FP to cast\comma{} and can take three spellcasting actions per turn.
\end{spellitemize}

When the spell effect ends\comma{} the spirit leaves the caster\apos{}s body. The exertion of hosting such a powerful spirit causes the caster to immediately fall unconscious.
}
\spell{
	name = Riftstorm, school = Transfiguration, discipline = Conjuration, type = Focus, level =Ascendant, range =Close, incant = vis nihil, duration = 1 minute,noHigh = 1, noResist =1, negation = Blockable,effect =When summoning an object into existence\comma{} a conjurer ever\minus{}so\minus{}briefly forms a crack in the manifold surfaces of reality\comma{} before sealing it shut before serious damage can be done. This spell does not do that. 

You open a yawning chasm in reality\comma{} in a region of space that you can see within range. This rift emanantes a tremendous amount of energy as it attempts to widen the crack you have created\comma{} and pulses and flashes of extradimensional energy flash from the rift. 

Every turn you may designate up to 5 targets within 15m of the rift\comma{} and a bolt of blinding energy strikes out towards the target. If the target fails to block the attack\comma{} they take 10d8 psychic\comma{} fire\comma{} cold or force damage (caster\apos{}s choice). 

If this attack reduces them to 0HP\comma{} they are instantly absorbed into the void and you may replace them with a single summoned beast or elemental not exceeding a MoM rating of V\comma{} as if you had cast the relevant {\it Summon} spell. 

When the spell ends\comma{} either because the duration is completed or the caster loses focus\comma{} the rift slams shut\comma{} releasing a shockwave which deals a further 4d12 concussive damage to beings within 3m of the rift.
}
}
 \spellBook{Spelles Moste Vyle}{Ascendant-level Necromancy}{
\spell{
	name = Army of the Dead, school = Dark Arts, discipline = Necromancy, type = Ritual (1 day), level =Ascendant, range =Self, noIncant = 1, duration = A year and a day,noHigh = 1, noResist =1, noBlock = 1, effect =You may raise the bodies of up to 10d20 deceased individuals found within a radius of 1 km. 

You may decide what composition are raised as Inferi\comma{} Zombies and Wights. 

These Undead are then perfectly loyal to you and will obey every command you give them through the telepathic network that connects you. 

When the spell duration ends\comma{} the bodies crumble into ashes.
}
\spell{
	name = Snare Souls, school = Dark Arts, discipline = Necromancy, type = Instant, level =Ascendant, range =Self, incant = nerco decipula, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Capture the soul of an enemy killed in the past 30 seconds. 

This soul may be used to instantly cast any other spell (even one you do now know) at a Master level without a casting check or fortitude cost.

Alternatively you may choose to absorb the soul to heal the character to full health and fortitude. 

Only one soul may be trapped at any given time.
}
}
 \spellBook{Theories on the World Beyond}{Ascendant-level Occultism}{
\spell{
	name = Sacrifice\apos{}s Shield, school = Dark Arts, discipline = Occultism, type = Ward, level =Ascendant, range =Self, noIncant = 1, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =You allow the next strike made against you to kill you\comma{} and banish your soul to the Eldritch domains. In return\comma{} your sacrifice and love fuels a charm so powerful it cannot be resisted or overcome by force alone. 

You may nominate an individual sapient being. That individual cannot be harmed by the being which killed you. Any attempt by your killer to harm your nominated individual simply reflects the charm back upon you. 

This spell does not need a casting check to cast.
}
\spell{
	name = Universal Tear, school = Dark Arts, discipline = Occultism, type = Ritual (1 week), level =Ascendant, range =Close, incant = ostium, noDur = 1, noHigh = 1, noResist =1, noBlock = 1, effect =Punch a hole in the fabric of reality\comma{} and establish a portal to one of the Higher Planes. 

This portal takes the form of a shimmering door\comma{} approximately 2 metres in height\comma{} and 1 metre in width. Stepping through the door instantaneously takes you to the chosen Plane.

Portals are permanent rips in the fabric of the multiverse\comma{} and there is no known method to repair them.
}
}
%%SpellbookEnd
\cleartorightpage
~
\cleartorightpage
~\cleartorightpage
~\cleartorightpage
~
\end{document}
