\twocolumn
\chapter{Changelog}

\section{Changes in V4.0}

The 4.0 system is a complete overhaul from the old 1.0-3.0 system - as such, the changes are too numerous to truly encoude here, so only a brief overview will be given.

\subsection{Core System Change}

Whilst previous systems were based (more or less) on a standard d20-plus-bonuses mechanic, the new system uses instead a \key{Dice Pool}. Here there are no static bonuses, but instead rolling different numbers of dice (d12s) against the DV. 

This allows a measurement of different degrees of success, rather than a simple pass/failure. 

Because of this, almost every other aspect of the game has been altered in some way. 

\subsection{Spells}

Rather than a defined spelllist where near every outcome was articulated in the spell description, the system now uses a much more vague system - spells are described by a single word (i.e. \imp{Burn}, \imp{Control}), with the players and the GM determining the power level that would be required for the desired outcome. 

A number of examples of possible effects are provided (in fact, these almost outnumber the previous spell list), but are a) only suggestions b) deliberately vague. 

\subsection{Money}

Rather than keeping track of every penny spent, the game has moved onto a more abstract idea of currency - essentially only tracking large purchases, though with some leeway on how exactly to implement that.
\section{To Do List}

\begin{itemize}
	\keyItem{Add additional backgrounds}{Think of some more non-exotic, non-human backgrounds that could reasonably be fitted into the game.}
	\keyItem{Harm/Health/Healing calculations}{Need to explicitly lay out how harm is dealt in C2.}
	\keyItem{Potion making}{No progress as yet on potioneering}
	\keyItem{More item stuff}{Armour, enchanting examples, books - all need to be fleshed out.}
	\keyItem{Spells}{Some more refinement needed on the spell text + some more examples can never hurt}
	\keyItem{Beasts}{Lots of beasts left to finish + many of them are probably horrifyingly unbalanced.}
\end{itemize}
