\documentclass[CoreRulebook.tex]{subfile}
\newpage
\begin{strip}
\setlength{\parskip}{4pt}

\section{Brute}

Towering above the rest of the population, their muscles rippling, the brute wades through the crowd, with people parting in front of them, gaping in awe. A hulk of a being, with incredible strength, a brute is capable of 
physical feats beyond most of wizardkind, and as such often rely on their strength instead of magical talent. 

Whilst all brutes are strong beyond measure, they may choose to channel this strength in different ways. Some use it to become ferocious warriers, using their frenzied strength to beat their enemies to a pulp: the {\bf beserkers}. Others recognise that having strength does not require one to use it to dominate, and instead dedicate their strenght to protecting their friends and allies, the {\bf gentle giants}.


%%archBegin\archetype{Brute}{Beserker}{Gentle Giant}{0}{featureI=Incredible Strength, featureII=Natural Armour, alphaFeatureIII=Berserker Rage, betaFeatureIII=Protect Others, featureIV=Unarmed Strike, betaFeatureIV=Gentle Aura, featureV=Intimidating Presence, alphaFeatureV=Stunning Strike, featureVI=Giant Hands, betaFeatureVI=Nature Affinity, alphaFeatureVII=Brutal Critical, alphaFeatureVIII=Berserker Rage II, betaFeatureVIII=Protective Rampage, featureIX=Bludegoning Strength, featureX=Natural Armour II, alphaFeatureX=Primal Senses, betaFeatureX=Carry Packs, betaFeatureXI=Brush Aside, featureXII=Incredible Resilience, alphaFeatureXII=Impulsive Rush, betaFeatureXIII=Gentle Aura II, featureXIV=Indomitable, featureXV=Raw Strength, alphaFeatureXV=Mindless Attacks, betaFeatureXVI=Nature Affinity II, featureXVIII=Smite, betaFeatureXVIII=Pure Heart, alphaFeatureXX=Berserker Rage III, betaFeatureXX=Pure Heart II}%%archEnd

\end{strip}


\subsection{Starting Equipment}
\begin{itemize}[itemsep=0em]
	\item Basic pack
	\item Wand (roll on Wand table to determine composition)
	\item 2d6 $\times 5$ gold
	\item One of:
	\begin{itemize}
		\item club
		\item warhammer
		\item musical instrument
	\end{itemize}
\end{itemize}
\subsection{Starting Spells}

Brutes may choose 3 spells from the basic spells table.


\subsection{Archetype Features}
\feat{Incredible Strength}

From 1st level, Brutes are assumed to be proficient in any melee weapon that requires an ATH(strength) check, and get a bonus to their Strength proficiency equal to 1 + one third of their brute level. 

\jump
\feat{Natural Armour}

At second level, Brutes gain a natural resistance to attacks, giving an effective AC equal to twice their ATH(strength) modifier. This AC is damaged in the same way as normal AC, but also protects against heat changes. It is restored by healing spells or upon 8 hours sleep. 
\jump
\newpage
\feat{Unarmed Strike}

From 4th level onwards, an unarmed strike does bludgeoning damage equal to the Brute level.

\jump
\feat{Intimidating Presence}

From 5th level, gain a bonus to your Intimidation proficiency equal to one 1 + one quarter of your Brute level.

\feat{Giant Hands}

From 6th level, you may wield two-handed weapons as one-handed. 
\jump
\feat{Bludgeoning Strength}

At 9th level, when an attack roll requires a Strength proficiency, you may, if possible, use one dice larger than the prescribed one. 
\jump
\feat{Incredible Resilience}


From 12th level, if you pass a SPR(willpower) check (DV 25, minus 1 for each Brute level), you may ignore the resitriction on immobility from the {\it Critical Condition} and {\it Critical But Stable} conditions. 

\jump
\feat{Raw Strength}

From 15th level, if you perform an ATH(strength) check and the total is less than your total (ATH + Strength) values, you may use that value instead. 
\jump
\feat{Smite}

At 18th, by dedicating two major actions to an attack, you may do triple the amount of damage of a normal attack roll. 

\newpage
\subsection{Beserker Features}
\feat{Beserker Rage}

At 3rd level, you may choose to enter a state known as {\it frenzy} up to twice a day. When in a frenzied state:

\begin{itemize}[itemsep=0em]
	\item Gain check-advantage on all checks that use an ATH checks
	\item Melee attack rolls get a bonus equal to one third of your beserker level
	\item Your {\it Natural Armour} AC increases by 50\%
	\item You are 50\% weaker to psychic damage
\end{itemize}

At 8th level, you may enter a frenzy up to 4 times per day and you get the following additional bonuses:
\begin{itemize}
	\item You may take two melee attacks, instead of one, as a single major actions
	\item You may use a Resist dice one larger than your current one, when resisting spell effects. If you use a d20, get a +4 bonus instead.
\end{itemize}

At 20th level:
\begin{itemize}
	\item You may take up to 4 melee attacks as a single action
	\item You automatically succeed on any resist checks against magical effects.
\end{itemize}

Frenzy lasts for 2 minutes (10 combat rounds), or may be stopped as a minor action. 

\jump
\feat{Stunning Strike}

From 5th level, when you successfully perform a bludgeoning attack, target performs an ATH(endurance) Resist check (DV = beserker level). If they fail, become stunned for one turn.

\jump
\feat{Brutal Critical}

From 7th level, when you land a Critical Hit, you may roll the attack dice one additional time, and add that to the damage check. 

At 17th level, you may roll the attack dice 3 additional times. 

\jump
\feat{Primal Senses}

From 10th level, your senses are honed to a razor. Your passive perception check is doubled. 
\jump
\feat{Impulsive Rush}

From 12th level, if you are initiating conflict, you may choose to rush in, catching your opponent off-guard. You gain check-advantage on attack rolls for 3 turns, but afterwards your opponents have check-advantage on attack rolls against you for 2 turns.
\jump
\feat{Mindless Attacks}

At 15th level, once per day you may choose to take a 6-point reduction in all INT and EMP checks for one hour, in return for doubling all damage you do for 5 minutes. 
\newpage
\subsection{Gentle Giant Features}
\feat{Protect Others}

From 3rd level, if you are within 3m of an ally, you may take your major action to leap in front of them and intercept any attacks on that ally. 

\jump
\feat{Gentle Aura}

From 4th level, you may `switch off' the {\it Indimidating Presence} skill at will, and instead take a +1 bonus to Persusion and Understand Other proficiencies. You may not have both bonuses active at the same time, and performing the change takes a minor action. 

At 13th level, this increases to a +2 bonus to both proficiencies.
\jump
\feat{Nature Affinity}

From 6th level, get a bonus to your Flora \& Fauna proficiency equal to one quarter of your Gentle Giant level.

At 16th level, you may get a beast as a Familiar. 
\jump
\feat{Protective Rampage}

From 8th level, if one of your allies (or a particularly cute bunny) takes damage, you may fly into a protective frenzy. 

Your {\it Natural Armour} AC increases gets a +15 bonus, and you get check-advantage on strength checks, however, you may not kill whilst in the rampage. Any character that would be killed by your attack is instead reduced to 1HP. 
\jump
\feat{Carry Packs}
From 10th level, you may elect to help carry your group's luggage on a long journey, increasing the `Duration' of each movement class by 50\%.
\jump
\feat{Brush Aside}
From 11th level, if you are in melee range with a character smaller than you, you may simply pick a target up, and move them out of your way. Target resists with an ATH(Strength) Resist check (DV = 1d20 ATH(Strength)). 
\jump
\feat{Pure Heart}

At 18th level, your heart is so pure that necrotic damage does not affect you -- gain 100\% immunity from necrotic damage. 

At 20th level, your purity imbues your fists with righteousness, and your unarmed strikes do an equal amount of holy damage.
