\documentclass[CoreRulebook.tex]{subfile}
\newpage
\begin{strip}
\setlength{\parskip}{4pt}

\section{Empath}

You feel their eyes burrowing into you. They're seeing not just the physical form, but are seeing straight into your soul. An empath knows you better than you know yourself -- inside and out. They achieve this, not through magical spells, but through their deep and abiding compassion -- coupled to a heightened perceptive sense. Often nomadic in nature, Empaths travel not to see the world or experience adventures -- but to help as many people as possible. 

Some Empaths dedicate their lives to using this increased perception to peer beyond the mystic veil, and learn the true secrets of the cosmos; the {\bf Seers}. Some dedicate their lives to helping others, and use their ability to heal the sick and wounded; {\bf Healers}. The root of their power, is their empathy and compassion for all living beings. 

%%archBegin\archetype{Empath}{Seer}{Healer}{0}{featureI=Compassionate Heart, featureII=Perceptive Eyes, featureIII=Spellcasting Improvement, alphaFeatureIII=Channel Ability, betaFeatureIII=Healing hands\comma{} Tool Proficiency, featureIV=Lie Detector, alphaFeatureV=Arcane Focus, alphaFeatureVI=Psychic Trauma, betaFeatureVI=Effortless Healing, featureVII=Compassionate Heart II, betaFeatureVII=Bane of Unlife, featureVIII=Spellcasting Improvement, alphaFeatureVIII=Magical Nexus I, betaFeatureVIII=Red Cross, alphaFeatureIX=Other Eyes, featureX=Empathic Shield, betaFeatureX=Mass heal, alphaFeatureXI=Retrocognition, betaFeatureXII=Holistic Care, featureXIII=Spellcasting Improvement, alphaFeatureXIII=Psychic Trauma II, alphaFeatureXIV=Font of Knowledge, betaFeatureXIV=Red Cross II, featureXV=Calming Aura, betaFeatureXVII=Stabilizing Influence, featureXVIII=Spellcasting Improvement, alphaFeatureXVIII=Magical Nexus II, alphaFeatureXX=True Sight, betaFeatureXX=Reverse Death}%%archEnd

\end{strip}

\subsection{Starting Equipment}

Empaths  start with:
\begin{itemize}[itemsep=0em]
	\item  a Wand (roll on the wand table to determine composition)
	\item a Basic Pack
	\item 1d6 $\times 4$ gold
\end{itemize}
%\newpage
\subsection{Starting Spells}

Empaths may choose three of the following spells to start:
{\it
\begin{itemize}[itemsep=0em]
	\item Minor Healing Spell
	\item Identification Charm
	\item Astral Caltrops
	\item Shielding Charm
	\item Blur Spell
	\item Night Vision charm
\end{itemize}
}

\subsection{Archetype Features}
\feat{Compassionate Heart}

At first level, get a +1 bonus to Perception and Understand Other proficiency. 

At 7th level, this bonus increases to +2. 
\jump
\feat{Perceptive Eyes}

From 2nd level, by performing a 1d20 EMP (Understand Other) check (DV = 17 - Empath level, minimum 5), you may know the HP and any status effects of a target individual. 
\jump
\feat{Spellcasting Improvement}

At 3rd level, and then again at 8th, 13th and 18th level, you may increase the size of the dice you use to cast divination {\bf or} recuperative spells. This feat does {\it not} count when calculating the Arcane Wisdom bonuses detailed on page \pageref{S:Auto}. 
\jump
\feat{Lie Detector}

From 4th level, you may use your combined Perception and Understand Other profiencies on lie-detection checks. 
\jump
\feat{Empathic Shield}

From 10th level, you may project your empathic abilities outwards, giving all allies in 1d6 metre radius an effective `psychic AC' equal to your Empath level when taking damage from sapient beings. Unlike normal armour, this protects against all damage dealt to you by sapients, and is only destroyed by psychic damage. 

Has no effect on against environmental damage or damage from Beasts. Lasts for 2 minutes (5 combat rounds). 
\jump
\feat{Calming Aura}
At 15th level, you may use your major action once per day to remove
all confusion, enraging and terrified status effects from all targets
in a 1d4 metre radius. If the target is not afflicted by any of these
effects and is in combat, they immediately exit combat for 2 turns, or
until next harmed. Target may resist by performing a SPR(willpower)
Resist check (DV = Empath Level-5). 
\subsection{Seer Features}
\feat{Channel Ability}

From 3rd level onwards, by performing a 1d20 EMP (Understand Other) check (DV 12), tap into a cosmic web of knowledge and choose either one set of tools to become proficient in, or one skill to get check-advantage in for 5 minutes (25 combat rounds). 

This takes two major actions to complete. 
\jump
\feat{Arcane Focus}

At 5th level, choose a small, non-magical object such as a crystal ball (or roll on the Trinket table). This object becomes your Arcane Focus. When focussing upon this object, gain +3 perception. Upon losing your focus, you may meditate for 1 day to choose a new one. 

\jump
\feat{Psychic Trauma}

From 6th level onwards, peer into the timestream of a target and force them to relive a horrific event from their past or their future. If target fails a SPR(willpower) Resist check (DV = 5 + Seer level), they take 1d6 psychic damage. 

At 13th level, you may expand this effect to 1d6 targets.  
\jump
\feat{Magical Nexus}

At 8th level, you tap into the magical web underpinning reality, and can identify focus points in that web. Detect all magic in your vicinity, as if you had a permanent {\it Detect Magic} spell. 

At 18th level, you are so attuned to the mystical web that you can sense humans even when they{\apos} not using magic, as if you had a permanent {\it Sense Humans} charm. 
\jump
\feat{Other Eyes}

From 9th level, you may use 3 major actions to see through the eyes of any non-magical creature. You may not control the creature, but you see and hear what the creature sees. Effect ends when you lose focus due to, i.e. taking damage. 
\jump
\feat{Retrocognition}
Starting at 11th level, you can call up visions of the past that relate to an object you hold or your immediate surroundings. You must spend at least 1 minute (5 combat rounds) in uninterrupted meditation, then receive a vision. This costs 10FP. 

\begin{itemize}[itemsep=0em]
\item {\bf Object Reading}: Holding an object as you meditate,
you can see visions of the object's previous owner.
After meditating for 1 minute, you learn how the owner
acquired and lost the object, as well as the most recent
significant event involving the object and that owner.
If the object was owned by another creature in the
recent past (within a number of days equal to your
EMP score), you can spend 1 additional minute
for each owner to learn the same information about
that creature.

\item {\bf Area Reading}: As you meditate, you see visions
of recent events in your immediate vicinity (a room,
street, tunnel, clearing, or the like, up to a 10m cube),
going back a number of days equal to your EMP
score. For each minute you meditate, you learn about
one significant event, beginning with the most recenl.
Significant events typically involve powerful emotions,
such as battles and betrayals, marriages and murders,
births and funerais. However, they might also include
more mundane events that are nevertheless important
in your current situation.
\end{itemize}
\jump
\feat{Font of Knowledge}

Starting at 14th level, you may meditate upon a question. If you succeed a 1d20 EMP (perception) check (DV 15), the universe will answer your question with a single word. 

Asking a question costs 5FP, and you may only ask 1 question per day. 
\jump
\feat{True Sight}

From 20th level, you are so in-tune with the universe, that you may automatically use the {\it True Sight} spell at will (no action cost). Having {\it True Sight} active costs 5FP per minute (or 1 FP per combat round). 
\subsection{Healer Features}
\feat{Healing Hands}

From 3rd level onwards, gain a bonus to your Healing proficiency equal to 1 + a quarter of your Healer level. 
\jump
\feat{Tool Proficiency}

At 3rd level you are proficient with the {\it surgeons tools}. 
\jump
\feat{Effortless Healing}

From 6th level, you may deduct half of your Healer level from the FP costs of healing spells. 
\jump
\feat{Bane of Unlife}
At 7th level, all healing spells cast are assumed to do an equal amount of Holy damage. Holy damage does not harm living beings, but banishes foul abominations. 

\jump
\feat{Red Cross}

From 8th level, if there are other targets in combat, sapient enemies will not harm you until you harm them first, or are otherwise deemed to be a combatant. If you are the only combatant, they will attempt to incapacitate you without harming you. 

At 14th level you may designate a 15m$^2$ area as a field hospital. No sapient being will enter this boundary, and will not harm anyone inside it, until the area is deemed a combat-zone (i.e. when an inhabitant uses it for non-medical purposes.) 

At all levels, if a character has an EVL score greater than or equal to your EMP score, they may violate the accords protecting you. 
\jump
\feat{Mass Heal}

At 10th level, you may cast healing spells that are at least one level below your current Skill level on all targets in a 3m area. 
\jump
\feat{Holistic Care}

From 12th level, your healing spells restore an equal amount of FP. 
\jump
\feat{Stabilizing Influence}

At 17th level, whenever any PC in a 5m radius falls below zero HP, they are automatically stabilised and take the Critical but Stable status, instead of Critical Condition.
\jump
\feat{Reverse Death}

At 20th level, if a character has been dead less than 24 hours, you may expend 30FP to rekindle the tinest flicker of life in their body, and restore them to -9 HP, with the Critical but Stable status. 

Only works if the body is whole. 

This effect takes 2 hours to complete, and may only be used once per week. 
