\documentclass[CoreRulebook.tex]{subfile}
\newpage
\begin{strip}
\setlength{\parskip}{4pt}
\newpage
\section{Hufflepuff Student}
Hufflepuff House is home to those students who are kind and hard working, as the Sorting-Song elaborates:
\begin{displayquote}
\it You might belong in Hufflepuff,
\\
Where they are just and loyal,
\\
Those patient Hufflepuffs are true,
\\
And unafraid of toil.
\end{displayquote}
Traditionally seen as ``the other house'', and often mercilessly mocked as such, Hufflepuff has come into its own recently. Certainly,the combination of hard-work, loyalty and kindness is not something to be sneered at. Even if they are not always the highest achievers, a Hufflepuff Student is someone you want to be around. Though sometimes timid, they make friends quickly and are often perceptive above what is usual for a student.

This house is home to two distinct groups -- the {\bf Hard Workers} and the {\bf Student Counsellors}. What the Hard Workers lack in natural talent, they more than make up for in their dedication to completing tasks. The Student Counsellors, on the other hand, are kind and empathetic souls who want to help others feel happy and comfortable. 

%%archBegin\archetype{Hufflepuff Student}{Hard{\dash}Worker}{Student Counsellor}{1}{featureI=Heart of Loyalty, featureII=Ally Assist, alphaFeatureIII=Night-Owl, betaFeatureIII=Kind Heart, featureIV=Heart of Loyalty II, alphaFeatureIV=Industrious Attitude, betaFeatureIV=Calming Aura, alphaFeatureV=Dedicated Training}%%archEnd

\end{strip}


\subsection*{Archetype Features}

\textbf{\textit{Heart of Loyalty:}} 

Starting at level 1, the Heart of Loyalty gives your character a +1 boost to the Understand Other and Perception proficiencies. This increases to +2 at level 4. 
\par
~
\par
\textbf{\textit{Ally Assist:}} 

Starting at level 2, you gain check-advantage when performing spells on your allies. 




\subsection*{Hard Worker Features}

\textbf{\textit{Night Owl:}}

From 3rd level onwards, you may dedicate 1 night to auto-succeed on any research or learning check, at the cost of acquiring a lvl 2 exhaustion status. 

\par
~
\par
\textbf{\textit{Industrious Attitude:}}

At 4th level, your dedication to work means that you get more done than most students. You may learn 2 more spells per level, and research/learning checks take only half the time. 

At 5th level, news of your work ethic has reached teachers, and you get +2 persuasion checks against teachers. 

\par
~
\par
\textbf{\textit{Dedicated Training:}}

At 5th level, you are able to turn your determined mind to a project outside of academia. Get one of the following abilities:
\begin{itemize}
	\item \textbf{\textit{Physical Training:}} get check-advantage in movement and acrobatics checks.
	\item \textbf{\textit{Weapons Training:}}  get check-advantage in melee and ranged combat checks
	\item \textbf{\textit{Musical Training:}} learn to play a new musical instrument
	\item \textbf{\textit{Language Training:}} learn to speak a new language
\end{itemize}

\subsection*{Student Counsellor Features}

\textbf{\textit{Kind Heart:}}

From 3rd level, when you help someone you may forgo all rewards for helping someone, and instead get a permanent check-double-advantage when interacting with that person. 

At 5th level, your reputation for kindness gives you a check-advantage when negotiating with all non-evil sapients.
\par
~
\par
\textbf{\textit{Calming Aura:}}

Once per day, as your major action you may remove all confusion, enraging and terrified status effects from all targets in a 1d4 metre radius. If the target is not afflicted by any of these effects and is in combat, they immediately calm down and exit combat for 2 turns, or until next harmed. 

At 5th level, this effects all targets in 1d8 metre radius. 
