

\chapter*{Slytherin Student}
\addcontentsline{toc}{section}{Slytherin Student}
As a house, Slytherin has a bad repuation \minus{}\minus{} even the words of the Sorting Hat have a menacing air:
\begin{displayquote}
\it Or perhaps in Slytherin,
\\
You{\apos}ll make your real friends,
\\
Those cunning folk use any means,
\\
To achieve their ends.
\end{displayquote}
This repuation is, for the most part, undeserved. Slytherin is not a house of evil students; rather it is the house of people with ambition, charm and with lofty goals. Driven by their desire to make something of their lives, the Slytherins can indeed be deceptive, but they can also be charming and persuasive. Never underestimate a Slytherin student, for they will surely never underestimate you. 
%%archBegin\archetype{name=Slytherin Student, hp=8, fp=8, armour=None, tool=Choose one from: Repair Kit\comma{} Forgery Tools\comma{} Navigator\apos{}s tools, disc=Choose any two disciplines from the Illusion or Charms schools., weapon=Wands\comma{} Simple Weapons, prof=Choose any two from Chicanery\comma{} Deception\comma{} Persuasion\comma{} Intimidation., equip=Wand\comma{} a Student\apos{}s pack and the tools selected above., memorised=Any two from the basic spells table., expertI = 2, maxspellI = Beginner, bonusI = Token of Leadership, expertII = 2, maxspellII = Beginner, bonusII = Charm Offensive, expertIII = 2, maxspellIII = Beginner, bonusIII = Sly Action, expertIV = NaN, maxspellIV = , expertV = NaN, maxspellV = , expertVI = NaN, maxspellVI = , expertVII = NaN, maxspellVII = , expertVIII = NaN, maxspellVIII = , expertIX = NaN, maxspellIX = , expertX = NaN, maxspellX = , expertXI = NaN, maxspellXI = , expertXII = NaN, maxspellXII = , shortmode = 1}
%%archEnd

\newpage
\section*{Acquired Feats}


\feat{Token of Leadership}{Acquired at 1st level, the Token of Leadership symbolises everything that Slytherin House stands for: cunning and persuasive words, eloquent speeches and the ability to inspire and deceive with a simple phrase. \\~\\
You may use this Token once per day to give yourself check\minus{}advantage on all Charisma checks for the next hour.}

\feat{Charm Offensive}{Learned at 2nd level, the Charm Offensive is, perhaps, the oldest trick in the book. \\~\\Target a being within hearing range, and use your prodigious charm to lower their guard. The next strike made on the target by you or an ally takes check\minus{}advantage on the accuracy check, {\bf or} they take disadvantage on the next Resist check they have to perform. \\~\\ This ability can only be used once per short rest. }

\feat{Sly Action}{On a turn in which no beings attacked, or otherwise interacted with you, you may take an additional minor action to consume an item, move, or attempt to hide. }
