
\section{Spell Shapes}

Some spells produce bolts of energy which fly towards a target, whilst others project their energy into a given region, which are often classified via geometrical shapes: a {\it line}, a {\it cube}, a {\it sphere}, a {\it circle} a {\it cone} or a {\it cylinder}. These shapes may either originate around the caster, or from a point designated by the spell. 

\subsection{Circle}

A circular spell extends outwards from the point of origin in a 2D circular shockwave that lies parallel to the ground. The height of the shockwave above the ground is set by the point of origin, which is not included in the shockwave region (unless the caster chooses it to be). Because of its 2D nature, a circular spell can be avoided by ducking beneath it, or jumping over it -- it is only if the shockwave impacts you that the spell effect is applied. 

\subsection{Cone}

The point of origin of a cone is typically the caster's wand, and a cone extends outwards from the wand, in the direction that the wand is pointing. A cone extends forwards to the specified distance, and has a circular cross section, the radius of which is equal to the distance away from the point of origin (so it is a 45$^\circ$ cone).

 The point of origin of the cone is not considered part of the spell area. 

\subsection{Cube}

The point of origin for a cubic spell may be selected to be either the centre of the cube, or the centre of one of its 6 sides. The cube's side-length is specified by the spell effect. The cube point of origin is only affected by the spell if you choose the centre-origin.

\subsection{Cylinder}

A cylinder point of origin is specified to be a point on the ground, around which a circular cross section is drawn, and then a cylinder of energy rises up vertically to a specified height. Generally, a cylinder spell adjusts its size to an individual, and if not otherwise specified, the cylinder is 5cm wider than the target individual is wide, and 5cm taller than the target. The point of origin is affected by the spell. 

\subsection{Line}

A line extends in a straight path from the origin (a caster's wand) towards the target for a specified distance. Unless otherwise specified, the beam is considered to have the cross section equivalent to a pencil. The point of origin is not affected by the spell. 

\subsection{Sphere}

A sphere's point of origin lies at the centre, and the spell effect expands equally out in all directions from that point. Generally, the spell effect cannot penetrate into the ground or through solid objects (unless, for example, it is an explosion). The point of origin is affected by the spell. 
