\chapter{Potions}\label{S:Alchemy}

\key{Potioneering}, also known as the arcane art of \key{Alchemy}, is one of the most ancient of the \imp{artificing} practices.

Whilst the sister arts of \key{enchanting} and \key{crafting} focus on the creation and imbuement of physical items, \imp{potioneering} focuses on the mixing, brewing and steeping of magical fluids, balms and tinctures: \imp{potions} which imbue the user with magical effects when they are drunk, spilled, applied to the skin, or any other myriad forms of application. 

Unlike the other \imp{artificing arts}, the ingredients used for \imp{alchemy} are almost entirely natural, herbal or bestial in nature - rather than the refined and manufactured products required for smithing, for example. A \imp{potion master's} toolkit contains leaves, claws, eyeballs and all manner of other organic ingredients - the ingredients for the most powerful potions have to be harvested from rare and dangerous magical beasts - though some mundane plants also have some surprisingly powerful magical effects. 

\section{Mixing a Potion}

Mixing a \imp{potion} is far more than simply throwing ingredients into a bowl and hoping for the best - it is a delicate, magical art that involves imbuing the mages own power into the creation as it infuses - shaped by their understanding of the ingredients and the processes involved. 

Even if a muggle (or, indeed, simply an untrained wizard) were to follow a tried-and-tested recipe to the letter, they would not end up with a batch of \imp{felix felices} potion, but rather some upsetting bogwater creation. In order for the potion to work, the mage must have a level of understanding, an intuitive connection, to the potion. 

Potion mixing inherently requires the use of a set of \imp{tools} - specifically an \imp{Alchemy Set}, which contains the all-important cauldron, as well as tools for preparing and filtering samples, purifying chemicals 
and other such important aspects of potionmaking.

\subsection{Ingredients}

After deciding on the potion you wish to make, you must then select at least three ingredients you wish to include to induce the desired effect. 

Each ingredient found in the list below is described by a number of simple phrases, which indicate the magical properties possessed by the ingredient - you should simply choose a selection of ingredients, and construct a narrative for why the chosen ingredients would produce the desired effect. 

For example, if \imp{Sean} were trying to mix a powerful \imp{Healing potion}, he would note that the combination of \imp{Wiggentree bark}, \imp{Horklump Juice} and \imp{Moly} would be a powerful healing combination. When narrating the potion making, \imp{Sean}'s player would describe something along the lines of:

{\it I use my Wiggentree Bark and the Horklump Juice to produce a basic healing mixture, to which I then add a dash of my extremely rare Moly, thereby magnifying the effects of the potion.}

Equally, you can mix and match additional properties to create a `story' about the potion - the \imp{Weasley twins} were infamous for their stink bombs: an attempt to make a stink bomb might invoke the \imp{aerosol} properties of \imp{peppermint}, the \imp{smelly} and \imp{Disgusting} properties of a \imp{pungent onion}, tied together with the \imp{catalyst} property of \imp{octopus powder} - together these properties clearly bind together to create a foul-smelling gas. 

You may also choose to add in ingredients to counteract any unwanted effects - the polyjuice potion famously uses a lot of ingredients which have the \imp{disgusting} property, resulting in a truly vile-tasting beverage. The discerning potioneer might decide that a dash of \imp{ginger} (with the \imp{tasty} property) might help the potion go down a bit more smoothly. 



\subsubsection{Improvised Ingredients}

The players are perfectly free (in fact, encouraged!) to work with the \imp{GM} to expand the list of ingredients - if they defeat a \imp{hippogriff} in battle, and come away with a handful of feathers, they are welcome to try and work together to come up with some additional words to describe the alchemical effects of their bounty. Equally, new `words' to describe alchemical properties can be invoked at any time by the \imp{GM}, in conjunction with the players. 

A final note is that you may also elect to use ingredients as symbolic entities - a potion designed to transform something into gold would be made out of \imp{metamorphic} ingredients, and then some gold itself - even though this does not match with the `words' used to describe it. Equally, a polyjuice potion uses a part of the target individual - even though this has no intrinsic magical property. 

This system is designed to be largely freeform, allowing players to experiment and innovate with their own mixtures and recipes. - as long as a coherent narrative can be constructed as to why the chosen ingredients come together to give the specified effect, the \imp{GM} should be lenient.


\subsection{Preparing the Project}

The \imp{GM} should now attempt to determine the exact details of the potion you are making (and also perhaps dream up some complications or mitigating factors). They should ask the potion mixer to describe exactly the effects of the potion they are trying to make, the magnitude of the effects, and the number of doses intended. 

The \imp{difficulty} of the mixing is determined using the basic \imp{artificing rules} found on page \pageref{T:ArtificingDV}. In short, the \imp{GM} uses the rarity of the ingredients and the properties of the potion mixing that is being attempted to divine a \imp{Rarity} for the potion.

As suggested on page \pageref{T:ArtificingDV}, the \imp{Rarity} also corresponds to the number of required successes for the potion to be completed. However, attempting to brew a larger dose may increase the number of required successes. Most \imp{alchemy} attempts would produce only a small number of samples of the desired potion - usually between 1 and 3 (at the \imp{GM}s discretion). This number can be increased by voluntarily increasing the \imp{complexity} of the project by one level - if a \imp{Fiddly} project would produce 2 samples, then you may brew 4 potions by making the mixing \imp{arduous}, or 6 potions by making it \imp{tough}



\input{Chapters/Part5_Artificing/IngredientList}
\newcommand\effect[3]
{
	{\footnotesize \key{#1}}	&	\parbox[t]{8cm}{\scriptsize #2} &	\parbox[t]{6cm}{\scriptsize #3} \\
}
\begin{strip}
\section{Ingredient Properties}
Below is a list of the ingredient properties which are used for the `default' alchemical ingredients included in this guide. Each effect is described (deliberately vaguely) by a single word, which is elaborated upon in this list. 
{\scriptsize 
\begin{center}
\begin{rndtable}{l c c}
	{\normalsize \key{Effect Name}}	&	{\normalsize\key{Effect Description}}	&	{\normalsize \key{Sample Ingredients}}
	\\
	\effectList{}
\end{rndtable}
\end{center}
}
\end{strip}

\section{Ingredients}

Below is presented a list of ingredients, along with a brief description of their origin, as well as the all-important descriptions of its \imp{alchemical properties}. 

\subsection{Harvesting \& Acquiring Ingredients}

Character are encouraged, wherever possible, to gather their own ingredients for potion mixing - after all, it is always more satisfying to mix things that you harvested yourself, rather than using store-bought ingredients. The potency of the magic is just a {\it bit} stronger when there is a personal connection. 

However, sometimes it is just not practical to go dragon hunting when you want to whip up a quick batch of \key{fire-breathing philter} - in which case merchants in all magical centres can surely be found who will service your needs. 

 
\subsection{Retroactive Purchases}

In keeping with the general theme of abstraction and simplifaction present in the \imp{financial} system of the game, so to is a certain level of abstraction levied at the purchasing and tracking of ingredients.

Some players may simply not find it fun to keep a coherent list of all the alchemical supplies they have gathered, and any serious potion-oriented character would quickly find themselves overwhelmed with the maintenance of such a list. It is therefore encouraged that a level of \key{retroactive purchasing} be allowed. 

When ingredients are purchased at a shop, rather than purchasing (for example), {\it five samples of dragons blood, two samples of newts eyes and a scoop of scarab beetles}, instead the character sheet encodes the ability to purchase {\it $x$ samples of rare ingredients, or $y$ samples of a common ingredient}. 

The exact ingredients that were purchased can be decided retroactively - when a potion mixing requires some {\it fairy wings}, as long as you have purchased a \imp{common} ingredient, you can decide that the `mystert' ingredient was in fact the fairy wings you require, before marking it off. 

When purchasing `retroactive ingredients', the following price guides may suffice:

\begin{center}
\begin{rndtable}{c c}
\key{Rarity}	&	\key{Cost}
\\
\imp{Abundant}	&	100+ samples for \galleon{1}
\\
\imp{Common}	&	20 samples for \galleon{1}
\\
\imp{Singular}	&	10 samples for \galleon{1}
\\
\imp{Unusual}	&	3 samples for \galleon{1}
\\
\imp{Rare}	&	1 sample for \galleon{1}
\\
\imp{Extraordinary}	&	\galleon{3} per sample
\\
\imp{Mythical}	&	\galleon{10}+ per sample
\end{rndtable} 
\end{center}

The secondary character sheet contains slots to mark how many `retroactive' ingredients you have purchased in the form of a number of diamonds for each rarity. Each time you select which ingredient was purchased from your set, remove the mark. Note that \imp{Abundant} ingredients are so cheap and easily available that any respectable potion-maker may assume that they have a near-infinite supply. The \imp{GM} should only charge for these ingredients if truly monumental quantities are being used. 

The \imp{GM} may, of course, rule that the desired ingredient was not available at the time of purchase (or perhaps has not survived the months or years that have passed since it was purchased...), in which case you may have to track down an ingredient specifically, though this should generally only apply to specific volatile, rare or hard to obtain ingredients. 

This also does not apply to ingredients which you have harvested yourself - you use those as you would normally expect, recording them individually and marking them off as they are used or sold. 

\subsection{Ingredient Rarity}
As with all items, \imp{Ingredients} are classified by their \imp{rarity}, which encompasses the difficulty of acquiring, harvesting, processing and preserving the ingredient. 

It may be assumed that a rarer ingredient is necessarily more powerful - to the extent that the limiting factor on most potion mixing efforts is the rarest item used in the mixture. Unless a particularly good `ingredient narrative' can be concocted, a \imp{potion} can never be assigned a \imp{rarity} higher than that of its most rare ingredient. 

In this fashion, potions are limited in their effectiveness by the availability of ingredients - you cannot mix a \imp{mythical} poison capable of bringing down dragons with a single droplet without some seriously \imp{mythical} ingredients. 



\newcommand\ingredient[3]
{
	\parbox[t]{2 cm}{\raggedright\small \key{#1}} &	\parbox[t]{4cm}{#2}	&	\parbox[t]{2.5 cm}{\raggedright #3} \\
}

\newcommand\ingredientList[2]
{
	\subsection{		#1}
{
	\scriptsize
\begin{rndtable}{l l l}
{\small \key{Ingredient}}	&	{\small \key{Description} } &	{\small \key{Effects}} \\
#2
\end{rndtable}
}
}

\ingredientList{Abundant Ingredients}{\AbundantList}
\ingredientList{Common Ingredients}{\CommonList}
\ingredientList{Singular Ingredients}{\SingularList}
\ingredientList{Unusual Ingredients}{\UnusualList}
\ingredientList{Rare Ingredients}{\RareList}
\ingredientList{Extraordinary Ingredients}{\ExtraordinaryList}
\ingredientList{Mythical Ingredients}{\MythicalList}

\section{Selected Recipes}

Though alchemy is inherently a very personal affair, with individual witches and wizards harbouring their own secret recipes which they pass on down through the generations, the following suggests some very common base recipes for a number of potions. 



\newcommand\potion[5]
{
	\subsubsection{#1}
	
	{\it #2}
	
	\begin{tabular}{l p{5cm}}
		\key{Rarity:}	& #3
		\\
		\key{Ingredients:}	& \imp{#4}
		\\
		\key{Effect:}	& #5
	\end{tabular}
}

\potion{Antidote to Common Poisons}{A standard concoction learned in every potions class - this foul-tasting, black fluid purges the body of toxins and poisons}{Singular}{Moondew, Eye of Newt, Bezoar}{Removes the \imp{Poisoned} status effect (and other toxin-induced effects) with a \imp{Power} of 10.}

\potion{Amortentia}{A vibrant pink fluid which exudes an aroma unique to individual: it mimics the scent of the things the individual finds most attractive. Whilst \imp{True Love} cannot be mimicked, this potion produces a powerful infatuation and lust.}{Extraordinary}{Ashwinder Eggs, Unicorn Hair, Pearl Dust, Fire Seed, plus a token of the focus of desire}{The drinker becomes immediately \imp{Charmed} (Power = 25) towards the focus of the potion, feeling great sexual and romantic urges towards them until the potion wears off.} 

\potion{Baruffio's Brain Elixir}{Though the actual effects of this potion are debated, it is a popular item on the \imp{Hogwarts} black market come exam time.}{Rare}{Runespoor Eggs, Dragon Claw, Griffin Claw}{For one hour after consuming, the drinker's \imp{Intelligence} statistic cannot be below 5.}

\potion{Draught of the Living Death}{A pitch-black liquid, said to cause the drinker to fall into a sleep so deep it mimics death.}{Unusual}{Asphodel, Sloth Brain, Venemous Tentacula}{Target falls asleep with \imp{Power} 5. This does not wear of without external intervention.}

\potion{Felix Felices}{Lustrous, liquid gold fills a tiny phial - this potion is incredibly difficult to brew, but the results are truly astounding. Use with extreme caution.}{Mythical}{Runespoor Egg, Angel's Feather, Squill Bulb, Gold, Fairy Wings}{For 1 hour after consuming, all rolls performed by the consumer score the maximum possible result. If consumed more than once in a 1 year period, the drinker becomes addicted and permanently reduces their maximum \imp{Health} by one for every day in which a sample is not consumed. }

\potion{Pepperup Potion}{A vibrant blue fluid with white steam billowing out from it - upon drinking, similar puffs of steam shoot out of your ears!}{Singular}{Coffee Beans, Ginger, Chizpurfle Fange, Fire Seed}{The drinker is reinvigorated. Roll a DV 10 \imp{Willpower} check - on failure, restore a single \imp{Fortitude} point, on a success, restore two.}

\potion{Nirvan's Noxious Clouds}{An unassuming glass vial seems almost completely empty, containing only a whisp of green gas. When smashed, the gas expands outwards into a suffocating, toxic gas cloud.}{Rare}{Ash, Dragon Fire Gland, Lobalug Venom, Mercury}{When released, expands to cover a radius of 3m. Any being entering the cloud suffers \imp{Level 3 Poison} damage per cycle, and cannot breathe whilst remaining inside the cloud.}

\potion{Wiggenweld Potion}{This bright red fluid is instantly recognisable as a basic healing potion: inducing the natural healing abilities of the drinker}{Common}{Wiggentree Bark, Horklump Juice, Dittany}{Drinker rolls a DV 7 \imp{Vitality} check, healing for 1 level + 1 for each success.}\label{P:Wiggenweld} 
