\def\AbundantList{
	\ingredient{Ash}{Burned and blackened organic matter.} {\imp{Absorbant}, \imp{Dry}, \imp{Insulating} and \imp{Suffocating}}
	\ingredient{Asphodel}{A mundane member of the lily family\comma{} used in sleeping potions} {\imp{Soothing} and \imp{Soporific}}
	\ingredient{Caterpillar}{Pupae form of a butterfly. A variety of species and colours.} {\imp{Colourful} and \imp{Metamorphic}}
	\ingredient{Coffee Beans}{Small brown berries with a high caffeine content. Used by muggles as a restorative.} {\imp{Stimulant}}
	\ingredient{Copper}{A chemical element with many intruiging properties.} {\imp{Conductive}, \imp{Hard} and \imp{Voltaic}}
	\ingredient{Daisy}{A small white and yellow flower familiar to muggles.} {\imp{Aphrodesiac} and \imp{Fragrant}}
	\ingredient{Dittany}{A mundane green leaf with powerful healing properties.} {\imp{Healing}}
	\ingredient{Flobberworm Mucous}{The green\minus{}grey goo extruded by the most useless of creatures.} {\imp{Irritant}, \imp{Smelly} and \imp{Sticky}}
	\ingredient{Ginger}{A pleasant smelling plant and foostuff. Gives life a bit of zing.} {\imp{Stimulant} and \imp{Tasty}}
	\ingredient{Honeywater}{A dilute form of honey. Useful as a potion base.} {\imp{Nutritious}, \imp{Stabilising} and \imp{Sticky}}
	\ingredient{Lavender}{A pleasant smelling purple plant with powerful calming effects.} {\imp{Fragrant}, \imp{Soothing} and \imp{Soporific}}
	\ingredient{Lemon Juice}{Cloudy\comma{} acidic juice – a good addition to many potions.} {\imp{Acidic}, \imp{Nutritious} and \imp{Tasty}}
	\ingredient{Moondew}{Dew gathered at midnight on a new moon. Absorbs all light that hits it.} {\imp{Absorbant} and \imp{Purifying}}
	\ingredient{Morning Dew}{Dew harvested by naked virgins from only the purest oak leaves\comma{} just as the first rays of morning infuse them.} {\imp{Slippery}}
	\ingredient{Nettles}{Stinging plant\comma{} but has restorative properties when brewed.} {\imp{Healing} and \imp{Irritant}}
	\ingredient{Peppermint}{A pleasant smelling and tasting herb\comma{} which produces a cloud of gas when heated with acids.} {\imp{Aerosol}, \imp{Fragrant} and \imp{Tasty}}
	\ingredient{Rose Petals}{Red petals that exude lust.} {\imp{Aphrodesiac} and \imp{Fragrant}}
	\ingredient{Tea Leaf}{A muggle plant that awakens the brain\comma{} and broadens the senses. Good with milk.} {\imp{Prescient} and \imp{Stimulant}}
	\ingredient{Vodka}{A strong mixture of ethanol and water\comma{} usually distilled from grain or potatoes.} {\imp{Confusing} and \imp{Resilient}}
}
\def\CommonList{
	\ingredient{Aconite}{The brilliant blue flower of a common\comma{} non\minus{}magical (but poisonous) plant.} {\imp{Floating} and \imp{Poisonous}}
	\ingredient{Asp Tail}{The tail of a poisonois European snake\comma{} used in potion making for thousands of years.} {\imp{Paralytic} and \imp{Poisonous}}
	\ingredient{Billywig Sting}{The venom inside this vicious barb causes giddiness and levitation.} {\imp{Floating} and \imp{Hallucinogenic}}
	\ingredient{Boomberry}{A small brown nut that explodes when disturbed.} {\imp{Explosive} and \imp{Fragrant}}
	\ingredient{Bubotuber Juice}{White  sap from the magic tree causes boils on contact.} {\imp{Acidic}, \imp{Irritant} and \imp{Paralytic}}
	\ingredient{Bulbadox Powder}{Volatile orange powder capable of causing boils and itching} {\imp{Disgusting} and \imp{Irritant}}
	\ingredient{Bundium Fluid}{A powerfully acidic\comma{} foul smelling grey secretion.} {\imp{Acidic}, \imp{Smelly} and \imp{Sticky}}
	\ingredient{Chizpurfle Fang}{The fang of the magic\minus{}absorbing insects is a powerful mental restorative.} {\imp{Stimulant} and \imp{Tasty}}
	\ingredient{Doxy Eggs}{The bright blue eggs of the trickster\minus{}fairies are mildly poisonous.} {\imp{Confusing} and \imp{Poisonous}}
	\ingredient{Eye of Newt}{A classic potion ingredient\comma{} these black orbs are often used to stabilise volatile potions.} {\imp{Disgusting}, \imp{Purifying} and \imp{Stabilising}}
	\ingredient{Fairy Wings}{Fairies regrow their iridescent wings regularly\comma{} though fresh\minus{}plucked wings are the most potent.} {\imp{Floating}, \imp{Hallucinogenic} and \imp{Lucky}}
	\ingredient{Fluxweed}{A magical plant known for its healing and transformative properties.} {\imp{Flexible}, \imp{Healing} and \imp{Metamorphic}}
	\ingredient{Hemlock Essence}{A well known poison\comma{} known for its purple hue.} {\imp{Poisonous}}
	\ingredient{Horklump Juice}{The deep red juice of the horklump is a healing agent.} {\imp{Healing} and \imp{Tasty}}
	\ingredient{Iron}{A plentiful\comma{} hard metal. Used as a base in alchemy.} {\imp{Conductive} and \imp{Hard}}
	\ingredient{Lacewing Flies}{A species of small green insects\comma{} known for their transparent wings.} {\imp{Invisible} and \imp{Metamorphic}}
	\ingredient{Leeches}{Animals that feed off blood. Powerful healing properties\comma{} but gross.} {\imp{Disgusting}, \imp{Healing} and \imp{Sapping}}
	\ingredient{Lobalug Venom}{This white fluid is a mild poison\comma{} often used to amplify other ingredients.} {\imp{Amplifying} and \imp{Poisonous}}
	\ingredient{Lovage}{A mundane plant with nausea inducing qualities.} {\imp{Disgusting}}
	\ingredient{Magnesium}{This lustrous metal is so reactive it must be stored in oil to prevent it reacting with air.} {\imp{Amplifying}, \imp{Conductive} and \imp{Explosive}}
	\ingredient{Mallowsweet}{The yellow berries of this plant have many beneficial properties.} {\imp{Flexible} and \imp{Tasty}}
	\ingredient{Murtlap Tentacles}{The pink tentacles have a soothing effect on the skin.} {\imp{Flexible}, \imp{Healing}, \imp{Slippery} and \imp{Soothing}}
	\ingredient{Nightshade}{A poisonous purple flower\comma{} used as a cosmetic by muggles throughout history.} {\imp{Aphrodesiac} and \imp{Poisonous}}
	\ingredient{Owl Feather}{Proximity to wizards mean that an owls feathers pick up many properties.} {\imp{Floating}}
	\ingredient{Pungent Onion}{A bright green onion with a powerfully repulsive odour.} {\imp{Aerosol}, \imp{Disgusting} and \imp{Smelly}}
	\ingredient{Slug Slime}{Horned slugs produce an acidic green\minus{}grey fluid that slow their targets down.} {\imp{Acidic} and \imp{Sticky}}
	\ingredient{Stinksap}{A foul smelling green sap that permeates all surfaces it touches.} {\imp{Penetrating}, \imp{Smelly} and \imp{Sticky}}
	\ingredient{Tormentil Tincture}{A bright yellow fluid extracted from a plant known for its soothing properties.} {\imp{Colourful} and \imp{Soothing}}
	\ingredient{Wartcap Powder}{A sickly yellow powder that causes boils and rashes to break out.} {\imp{Irritant} and \imp{Resilient}}
	\ingredient{Wiggentree Bark}{A thick lump of bark from a magical tree. Powerful restorative properties.} {\imp{Hard}, \imp{Healing} and \imp{Insulating}}
}
\def\ExtraordinaryList{
	\ingredient{Acheron Water}{Water from one of the rare magic rivers\comma{} the Acheron is the river of pain. Drinking this water is not advised.} {\imp{Painful} and \imp{Paralytic}}
	\ingredient{Acromantula Venom}{Thick\comma{} black venom of the giant spiders. Very rare and potent.} {\imp{Paralytic}, \imp{Poisonous} and \imp{Preserving}}
	\ingredient{Bicorn Horn}{The golden horn of a legendary beast\comma{} with many properties.} {\imp{Fortifying}, \imp{Metamorphic}, \imp{Penetrating} and \imp{Stimulant}}
	\ingredient{Cocytus Water}{Water from one of the rare magic rivers\comma{} the Cocytus is the river of wailing.} {\imp{Freezing}, \imp{Hallucinogenic} and \imp{Melancholic}}
	\ingredient{Dementor Cloak}{A cutting from the cloak of a dementor. Oozes cold\comma{} and saps your will.} {\imp{Cursed}, \imp{Freezing} and \imp{Melancholic}}
	\ingredient{Erumpet Horn}{A grey\comma{} twisted horn that has a nasty habit of exploding.} {\imp{Amplifying}, \imp{Explosive} and \imp{Penetrating}}
	\ingredient{Lethe Water}{Water from one of the rare magic rivers\comma{} the Lethe is the river of forgetfulness\comma{} and so the water is a powerful amnesiac.} {\imp{Amnesic}, \imp{Confusing} and \imp{Stabilising}}
	\ingredient{Occamy Egg}{Seemingly made of solid silver\comma{} yet constantly growing in size.} {\imp{Aphrodesiac}, \imp{Colourful}, \imp{Lucky} and \imp{Metamorphic}}
	\ingredient{Phlegiston Water}{Water from one of the rare magic rivers\comma{} the Phlegiston is the river of fire\comma{} and the water drawn from this river is unusually reactive and explosive.} {\imp{Amplifying}, \imp{Burning} and \imp{Explosive}}
	\ingredient{Quintaped Leg}{A brown\comma{} hairy leg from a magic abomination. Filled with hatred and power.} {\imp{Amplifying}, \imp{Enraging} and \imp{Ugly}}
	\ingredient{Re\apos{}em Blood}{A vibrant yellow fluid that imbues the drinker with immense strength.} {\imp{Amplifying} and \imp{Fortifying}}
	\ingredient{Sphinx Saliva}{Used to keep the sphynx cool in the hot deserts\comma{} this fluid is also incredibly acidic.} {\imp{Acidic} and \imp{Freezing}}
	\ingredient{Styx Water}{Water from one of the rare magic rivers\comma{} the Styx is the river of hatred\comma{} but is also rumoured to provide near\minus{}invulnerability.} {\imp{Aquatic}, \imp{Enraging} and \imp{Resilient}}
	\ingredient{Unicorn Hair}{A pure\minus{}white hair with many beneficial properties\comma{} if taken politely.} {\imp{Amplifying}, \imp{Aphrodesiac} and \imp{Aphrodesiac}}
}
\def\MythicalList{
	\ingredient{Angel’s Feather}{A feather of the purest white\comma{} glowing with incandescent magical power. Some say that they come from actual\comma{} real angels – whilst others are more doubtful about their origins.} {\imp{Lucky}, \imp{Magical}, \imp{Purifying} and \imp{Radiant}}
	\ingredient{Basilisk Venom}{Potent purple venom from the fangs of a monstrous snake.} {\imp{Acidic}, \imp{Paralytic} and \imp{Poisonous}}
	\ingredient{Manticore Skin}{The manticore{\apos}s magic resistance resides within its tanned skin.} {\imp{Absorbant}, \imp{Insulating} and \imp{Resilient}}
	\ingredient{Moly}{A golden\comma{} glowing plant that helps to heal the wounded and break curses. It can only be picked by an immortal at the exact moment of dawn\comma{} else it shrivels and dies.} {\imp{Aphrodesiac}, \imp{Fragrant}, \imp{Healing} and \imp{Purifying}}
	\ingredient{Nundu Venom Sac}{A black lump of flesh responsible for producing the poisonous aura of the nundu.} {\imp{Aerosol}, \imp{Amplifying}, \imp{Poisonous} and \imp{Suffocating}}
	\ingredient{Pheonix Feather}{A scarlet feather with many wonderful magical properties.} {\imp{Burning}, \imp{Healing}, \imp{Inspiring}, \imp{Purifying} and \imp{Radiant}}
	\ingredient{Thunderbird Feather}{A pale\comma{} golden feather which seems to crackle with energy. Merely touching it causes your hair to stand on end.} {\imp{Accelerant}, \imp{Conductive}, \imp{Floating} and \imp{Voltaic}}
	\ingredient{Unicorn Blood}{Visibly similar to mercury\comma{} the blood of a unicorn carries a powerful curse.} {\imp{Cursed}, \imp{Healing}, \imp{Sapping} and \imp{Unlucky}}
}
\def\RareList{
	\ingredient{Ashwinder Eggs}{A clutch of the eggs of a fire\minus{}snake. They are red\minus{}hot\comma{} and are renowned in love potions.} {\imp{Aphrodesiac} and \imp{Burning}}
	\ingredient{Cyclops Eye}{The single eye torn from the thunder giant tribe\comma{} very rare and very dangerous} {\imp{Enraging}, \imp{Prescient} and \imp{Voltaic}}
	\ingredient{Demiguise Hair}{An invisible strand of hair\comma{} with many beneficial properties.} {\imp{Incorporeal} and \imp{Invisible}}
	\ingredient{Dragon Blood}{Dumbledore is said to have discovered 12 uses for this scarlet substance.} {\imp{Acidic}, \imp{Amplifying}, \imp{Burning}, \imp{Magical} and \imp{Radiant}}
	\ingredient{Dragon Claw}{The powdered claw of a dragon is said to provide a potent brain\minus{}boost.} {\imp{Hard}, \imp{Sapping} and \imp{Stimulant}}
	\ingredient{Dragon Fire Gland}{The red\minus{}hot glands that sit inside the mouth of a dragon\comma{} responsible for their fire\minus{}breathing.} {\imp{Aerosol} and \imp{Burning}}
	\ingredient{Dragon Liver}{The liver of a dragon takes on the qualities of the food that the dragon eats.} {\imp{Disgusting} and \imp{Healing}}
	\ingredient{Dragon Scale}{A hardened scale from the hide of a dragon \minus{} the colour varies depending on the species it was harvested from.} {\imp{Colourful}, \imp{Hard}, \imp{Insulating} and \imp{Resilient}}
	\ingredient{Fire Crab Shell}{A jewel\minus{}encrusted ruby shell that occaisionally emits a gout of flame.} {\imp{Burning}, \imp{Colourful}, \imp{Insulating}, \imp{Radiant} and \imp{Resilient}}
	\ingredient{Gold}{A rare and lustrous metal. The goal of alchemists throughout history.} {\imp{Aphrodesiac}, \imp{Conductive} and \imp{Magical}}
	\ingredient{Griffin Claw}{A magic raptor\minus{}like claw. Said to confer its great intelligence to the owner.} {\imp{Fortifying}, \imp{Prescient} and \imp{Stimulant}}
	\ingredient{Kelpie Hair}{The grey hair of the shapeshifter retains some of this magic.} {\imp{Aquatic} and \imp{Metamorphic}}
	\ingredient{Mackled Malaclaw Tail}{A powerful iridescent blue ingredient\comma{} useful but unstable.} {\imp{Amplifying}, \imp{Explosive} and \imp{Unlucky}}
	\ingredient{Runespoor Egg}{Deep blue eggs with an orange aura\comma{} they are said to focus the mind} {\imp{Magical} and \imp{Stimulant}}
	\ingredient{Sea\minus{}Serpent Spine}{Shed from the fins of aquatic beasts\comma{} these spines are used by poisoners worldwide\comma{} and are renowned for their ability to pierce even the toughest materials.} {\imp{Aquatic}, \imp{Penetrating} and \imp{Poisonous}}
}
\def\SingularList{
	\ingredient{Abyssinian Shrivelfig}{A purple fruit found in the African desert. Dries up and shrinks when picked.} {\imp{Dry} and \imp{Metamorphic}}
	\ingredient{Boomslang Skin}{The brown\comma{} sloughed of skin of a nonmagical snake.} {\imp{Disgusting} and \imp{Metamorphic}}
	\ingredient{Doxy Venom}{This clear fluid deeply affects the brain of the victim.} {\imp{Confusing} and \imp{Poisonous}}
	\ingredient{Dugbog Bark}{Very dense wood\minus{}like material from the back of a dugbog.} {\imp{Hard} and \imp{Resilient}}
	\ingredient{Fire Seed}{A seed that burns with a hot flame whilst growing. Takes hours to cool once picked.} {\imp{Aphrodesiac}, \imp{Burning} and \imp{Purifying}}
	\ingredient{Gillyweed}{A magical plant with the ability to confer the consumer with gills.} {\imp{Aquatic}, \imp{Disgusting} and \imp{Nutritious}}
	\ingredient{Glumbumble Treacle}{A melancholy inducing substance that looks like pink honey.} {\imp{Melancholic}, \imp{Sapping} and \imp{Sticky}}
	\ingredient{Grindylow Claw}{A grey talon used by the creature to suffocate its victims.} {\imp{Paralytic}, \imp{Sapping} and \imp{Suffocating}}
	\ingredient{Jarvey Fang}{A curved fang containing a venom that causes involuntary babbling.} {\imp{Aphrodesiac} and \imp{Babbling}}
	\ingredient{Knotgrass}{The result of magical experimentation on a muggle plant \minus{} the result is an unusually resilient weed which can grow almost anywhere.} {\imp{Metamorphic} and \imp{Resilient}}
	\ingredient{Mandrake Root}{Trimmings from a sentient plant that act as a powerful antidote.} {\imp{Babbling}, \imp{Nutritious} and \imp{Purifying}}
	\ingredient{Mercury}{A liquid silver metal that is constantly changing shape and form.} {\imp{Metamorphic}, \imp{Poisonous} and \imp{Slippery}}
	\ingredient{Moke Skin}{A green scaled pouch that shrinks at the sign of approaching danger.} {\imp{Flexible}, \imp{Resilient} and \imp{Resilient}}
	\ingredient{Moonstone}{A gemstone of unknown provenance. Glows with an inner light.} {\imp{Conductive} and \imp{Radiant}}
	\ingredient{Octopus Powder}{A disgusting orange powder\comma{} but a powerful catalyst.} {\imp{Amplifying} and \imp{Disgusting}}
	\ingredient{Salamander Blood}{Bright red fluid that emits huge amounts of heat. A powerful catalyst.} {\imp{Amplifying}, \imp{Burning} and \imp{Radiant}}
	\ingredient{Scarab Beetles}{Once considered sacred by the ancient egyptians\comma{} these contain a surprising amount of magical power for a mundane beetle.} {\imp{Healing} and \imp{Resilient}}
	\ingredient{Sloth Brain}{The diced brain of a sloth is said to contain the essence of the being.} {\imp{Confusing}, \imp{Sapping} and \imp{Soporific}}
	\ingredient{Squill Bulb}{The root of a non\minus{}magical plant found at high altitudes\comma{} often used to make potions palatable.} {\imp{Lucky}, \imp{Soothing} and \imp{Tasty}}
}
\def\UnusualList{
	\ingredient{Alihotsy Leaves}{Consuming the speckled leaves of the `hyena tree\apos{} results in uncontrollable laughter} {\imp{Hallucinogenic}}
	\ingredient{Bezoar}{A hard\comma{} brown lump formed in the stomach of a goat. Horrifying to look at\comma{} but said to be a powerful antidote.} {\imp{Purifying} and \imp{Ugly}}
	\ingredient{Centaur Hoof}{Shavings from the hoof is said to contain the wisdom of the mystical people.} {\imp{Prescient} and \imp{Stimulant}}
	\ingredient{Frost Salamander Blood}{The ice\minus{}cold blood of the frost salamander\comma{} a pleasant sky\minus{}blue colour.} {\imp{Freezing} and \imp{Stabilising}}
	\ingredient{Hippocampus Hair}{This multicoloured hair is said to help the memory.} {\imp{Babbling}, \imp{Colourful} and \imp{Stimulant}}
	\ingredient{Kneazle Claw}{When powdered\comma{} increases the consumer{\apos}s perception enormously.} {\imp{Hallucinogenic}, \imp{Prescient} and \imp{Stimulant}}
	\ingredient{Mooncalf Tears}{Glowing fluid that seems to calm you down just by looking at it.} {\imp{Fragrant}, \imp{Inspiring}, \imp{Soothing} and \imp{Soporific}}
	\ingredient{Nogtail Trotter}{The foot of the nogtail makes one as fleet as the beast itself.} {\imp{Accelerant} and \imp{Hallucinogenic}}
	\ingredient{Pearl Dust}{A lustrous powder that gleams with positive energy.} {\imp{Aphrodesiac} and \imp{Radiant}}
	\ingredient{Pogrebin Shell}{A lump of hardened flesh that resembles stone. Exudes an ominous aura.} {\imp{Hard} and \imp{Melancholic}}
	\ingredient{Raiju Shaving}{A clump of fur torn from the lightning\minus{}fast thunder dog\comma{} crackles with energy.} {\imp{Accelerant} and \imp{Voltaic}}
	\ingredient{Silver}{A rare and lustrous metal\comma{} second only to gold in its value. Feared by the undead.} {\imp{Conductive} and \imp{Purifying}}
	\ingredient{Troll Snot}{A thick grey goo that dulls the senses\comma{} but bolsters the muscles.} {\imp{Disgusting}, \imp{Fortifying} and \imp{Sticky}}
	\ingredient{Venemous Tentacula}{A green goo formed from the mashed plant. Highly toxic.} {\imp{Poisonous}}
}


\def\effectList{
	\effect{Absorbant}{Causes things to be swallowed up\comma{} or incorporated into the target} {\imp{Ash}, \imp{Manticore Skin} and \imp{Moondew}}
	\effect{Accelerant}{Speeds up the metabolic rate\comma{} and even the passage of time} {\imp{Nogtail Trotter}, \imp{Raiju Shaving} and \imp{Thunderbird Feather}}
	\effect{Acidic}{Corrosive\comma{} inflicts acid damage and degrades physical objects.} {\imp{Bundium Fluid}, \imp{Dragon Blood} and \imp{Lemon Juice}}
	\effect{Aerosol}{Produces a cloud of gas or air\comma{} ideal for producing long\minus{}lasting clouds.} {\imp{Pungent Onion}, \imp{Peppermint} and \imp{Nundu Venom Sac}}
	\effect{Amnesic}{Induces amnesia\comma{} causes a target to forget things} {\imp{Lethe Water}}
	\effect{Amplifying}{Increase the strength of the things it is applied to\comma{} either physically\comma{} magically or alchemically} {\imp{Re\apos{}em Blood}, \imp{Phlegiston Water} and \imp{Erumpet Horn}}
	\effect{Aphrodesiac}{Makes things appear beautiful\comma{} induces lust and desire} {\imp{Daisy}, \imp{Gold} and \imp{Jarvey Fang}}
	\effect{Aquatic}{Imbued with the essence of water\comma{} gives the consumer aspects of underwater creatures.} {\imp{Styx Water}, \imp{Kelpie Hair} and \imp{Sea\minus{}Serpent Spine}}
	\effect{Babbling}{Induces excessive talkativeness\comma{} usually with a sense of mania} {\imp{Hippocampus Hair}, \imp{Jarvey Fang} and \imp{Mandrake Root}}
	\effect{Burning}{Creates heat and fire\comma{} can ward off cold\comma{} protect from fire or outright burn things} {\imp{Dragon Blood}, \imp{Dragon Fire Gland} and \imp{Salamander Blood}}
	\effect{Colourful}{Brightly coloured\comma{} induces specific colour changes in the potion or its consumer} {\imp{Caterpillar}, \imp{Tormentil Tincture} and \imp{Fire Crab Shell}}
	\effect{Conductive}{Allows electricty and heat to pass through easily} {\imp{Thunderbird Feather}, \imp{Silver} and \imp{Magnesium}}
	\effect{Confusing}{Induces confusion in the minds of living beings} {\imp{Vodka}, \imp{Doxy Eggs} and \imp{Sloth Brain}}
	\effect{Cursed}{Contains powerful dark magic that bring about foul curses} {\imp{Dementor Cloak} and \imp{Unicorn Blood}}
	\effect{Disgusting}{Vile\comma{} likely to induce nausea and vomiting} {\imp{Eye of Newt}, \imp{Bulbadox Powder} and \imp{Dragon Liver}}
	\effect{Dry}{Rapidly absorbs liquids\comma{} helps mop up spillages} {\imp{Abyssinian Shrivelfig} and \imp{Ash}}
	\effect{Enraging}{Induces anger and rage\comma{} turning the afflicted into a mindless beast.} {\imp{Cyclops Eye}, \imp{Quintaped Leg} and \imp{Styx Water}}
	\effect{Explosive}{Powerfully unstable\comma{} liable to explode or detonate} {\imp{Phlegiston Water}, \imp{Boomberry} and \imp{Magnesium}}
	\effect{Flexible}{Unbrittle and able to deform and contort\comma{} but always able to return to original shape} {\imp{Mallowsweet}, \imp{Fluxweed} and \imp{Murtlap Tentacles}}
	\effect{Floating}{Flies or moves about in space of its own accord} {\imp{Fairy Wings}, \imp{Billywig Sting} and \imp{Aconite}}
	\effect{Fortifying}{Increases the positive attributes of things – increases strength or intelligence (when applied correctly).} {\imp{Troll Snot}, \imp{Bicorn Horn} and \imp{Griffin Claw}}
	\effect{Fragrant}{Has a pleasant aroma} {\imp{Peppermint}, \imp{Rose Petals} and \imp{Moly}}
	\effect{Freezing}{Cold to the touch: can ward off excess heat\comma{} protect from cold or freeze things solid} {\imp{Cocytus Water}, \imp{Sphinx Saliva} and \imp{Dementor Cloak}}
	\effect{Hallucinogenic}{Induces euphoria and brings about visions and false memories.} {\imp{Billywig Sting}, \imp{Nogtail Trotter} and \imp{Cocytus Water}}
	\effect{Hard}{Hard\comma{} unbending and immune to change – ideal for protective ointments} {\imp{Copper}, \imp{Dugbog Bark} and \imp{Dragon Scale}}
	\effect{Healing}{Induces healing to living beings} {\imp{Fluxweed}, \imp{Dragon Liver} and \imp{Scarab Beetles}}
	\effect{Incorporeal}{Not quite there\comma{} allows one to step briefly into the astral plane} {\imp{Demiguise Hair}}
	\effect{Inspiring}{Induces hope and bravery into things\comma{} pushing them to achieve their best and defy the odds.} {\imp{Mooncalf Tears} and \imp{Pheonix Feather}}
	\effect{Insulating}{Prevents heat and electricity from passing through easily} {\imp{Fire Crab Shell}, \imp{Wiggentree Bark} and \imp{Manticore Skin}}
	\effect{Invisible}{Causes things to become invisible or hard to see} {\imp{Demiguise Hair} and \imp{Lacewing Flies}}
	\effect{Irritant}{Causes itching\comma{} swelling and boils to erupt on the skin} {\imp{Bulbadox Powder}, \imp{Wartcap Powder} and \imp{Nettles}}
	\effect{Lucky}{Said to bring good luck to those who bear it} {\imp{Occamy Egg}, \imp{Angel’s Feather} and \imp{Squill Bulb}}
	\effect{Magical}{Acts as a conduit or a source of raw magical power} {\imp{Angel’s Feather}, \imp{Gold} and \imp{Runespoor Egg}}
	\effect{Melancholic}{Induces melancholy\comma{} despair and in extreme doses\comma{} terror} {\imp{Cocytus Water}, \imp{Pogrebin Shell} and \imp{Glumbumble Treacle}}
	\effect{Metamorphic}{Causes objects to alter their shape and change form} {\imp{Lacewing Flies}, \imp{Kelpie Hair} and \imp{Knotgrass}}
	\effect{Nutritious}{Supplies vitamins\comma{} minerals and energy for living beings and plants to thrive upon} {\imp{Honeywater}, \imp{Mandrake Root} and \imp{Lemon Juice}}
	\effect{Painful}{Creates incredible mind\minus{}numbing pain if consumed} {\imp{Acheron Water}}
	\effect{Paralytic}{Causes muscles to lock up and induce paralysis} {\imp{Grindylow Claw}, \imp{Bubotuber Juice} and \imp{Asp Tail}}
	\effect{Penetrating}{Seeps through defensive\comma{} or bursts through armour} {\imp{Stinksap}, \imp{Erumpet Horn} and \imp{Sea\minus{}Serpent Spine}}
	\effect{Poisonous}{Toxic to living beings\comma{} inflicts poison damage} {\imp{Sea\minus{}Serpent Spine}, \imp{Basilisk Venom} and \imp{Acromantula Venom}}
	\effect{Prescient}{Stimulates psychic abilities\comma{} allowing glimpses into the future\comma{} or into the minds of others} {\imp{Kneazle Claw}, \imp{Cyclops Eye} and \imp{Centaur Hoof}}
	\effect{Preserving}{Prevents rot and decay\comma{} holds things as they are} {\imp{Acromantula Venom}}
	\effect{Purifying}{Drives away disease\comma{} poisons and corruption} {\imp{Fire Seed}, \imp{Eye of Newt} and \imp{Moly}}
	\effect{Radiant}{Emits a glow} {\imp{Fire Crab Shell}, \imp{Salamander Blood} and \imp{Pearl Dust}}
	\effect{Resilient}{Unusually immune or resistive to external influence} {\imp{Manticore Skin}, \imp{Dugbog Bark} and \imp{Knotgrass}}
	\effect{Sapping}{Drains the positive attributes from things} {\imp{Dragon Claw}, \imp{Unicorn Blood} and \imp{Leeches}}
	\effect{Slippery}{Causes things to slide\comma{} induces movement} {\imp{Mercury}, \imp{Morning Dew} and \imp{Murtlap Tentacles}}
	\effect{Smelly}{Has an unpleasant aroma} {\imp{Stinksap}, \imp{Pungent Onion} and \imp{Flobberworm Mucous}}
	\effect{Soothing}{Calms the target of mental stress\comma{} prevents itchiness} {\imp{Tormentil Tincture}, \imp{Mooncalf Tears} and \imp{Asphodel}}
	\effect{Soporific}{Sends things off to sleep} {\imp{Lavender}, \imp{Asphodel} and \imp{Mooncalf Tears}}
	\effect{Stabilising}{Prevents instability\comma{} makes things more predictable and reliable} {\imp{Honeywater}, \imp{Eye of Newt} and \imp{Lethe Water}}
	\effect{Sticky}{Causes things to stick in place\comma{} prevents movement} {\imp{Stinksap}, \imp{Troll Snot} and \imp{Flobberworm Mucous}}
	\effect{Stimulant}{Brings about mental acuity\comma{} prevents sleepiness} {\imp{Centaur Hoof}, \imp{Chizpurfle Fang} and \imp{Bicorn Horn}}
	\effect{Suffocating}{Prevents target from breathing} {\imp{Ash}, \imp{Grindylow Claw} and \imp{Nundu Venom Sac}}
	\effect{Tasty}{Yummy to eat} {\imp{Lemon Juice}, \imp{Mallowsweet} and \imp{Ginger}}
	\effect{Ugly}{Horrible to look at\comma{} induces revulsion and hatred} {\imp{Bezoar} and \imp{Quintaped Leg}}
	\effect{Unlucky}{Said to bring about chronic bad luck} {\imp{Mackled Malaclaw Tail} and \imp{Unicorn Blood}}
	\effect{Voltaic}{Possessing or generating an electrical charge} {\imp{Copper}, \imp{Thunderbird Feather} and \imp{Cyclops Eye}}
}